### 2014-05-02 writeDown/pub.jcp/chem-pot-jcp.tex
add the version submitted to JCP

% LaTex
%\documentclass[aps,twocolumn]{revtex4-1}
\documentclass[a4paper,preprint,unsortedaddress]{revtex4-1}
%\documentclass[a4paper]{article}
\usepackage{amsmath,amssymb,amsfonts,latexsym,graphicx}
\usepackage[dvips]{color}
\usepackage{indentfirst}

% \parindent=0mm
% \textheight=23cm \textwidth=14cm
% \parskip=0mm
% \renewcommand\baselinestretch{1.2}
% \oddsidemargin30pt \evensidemargin30pt

\def\pd#1#2{\frac{\partial #1}{\partial #2}}
\renewcommand{\vec}[1]{\mbox{\boldmath \small $#1$}}
\newcommand{\concen}{C}
\setlength\parindent{2em} 
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}

\begin{document}
%--------------------------------------------------------------------
%-----------------------------------------------------------------
\title{Chemical potential of liquids and mixtures via Adaptive Resolution Simulation}
\author{Animesh Agarwal}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"{u}tte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, and Zuse Institute Berlin (ZIB), Berlin, Germany}
\author{Luigi Delle Site}
\email{dellesite@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

\begin{abstract}
We employ the adaptive resolution approach AdResS, in its recently developed Grand Canonical-like version (GC-AdResS) [Wang {\it et al.} Phys.Rev.X 3, 011018 (2013)], to calculate the excess chemical potential, $\mu^{ex}$, of various liquids and mixtures.
We compare our results with those obtained from full atomistic simulations using the technique of thermodynamic integration and show a satisfactory agreement. In GC-AdResS the procedure to calculate $\mu^{ex}$ corresponds to the process of standard initial equilibration of the system; this implies that, independently of the specific aim of the study, $\mu^{ex}$, for each molecular species, is automatically calculated every time a GC-AdResS simulation is performed. 
\end{abstract}

\maketitle

\section{Introduction}
The chemical potential represents an important thermodynamic information for any system, in particular for liquids, where the possibility of combining different substances for forming optimal mixtures is strictly related to knowledge of the chemical potential of each component in the mixture environment. In this perspective, molecular simulation represents a powerful tool for predicting the chemical potential of complex molecular systems. Popular, well established methodologies in Molecular Dynamics (MD) are Widom particle insertion (IPM) \cite{widom} and thermodynamic integration (TI) \cite{ti}. IPM is computationally very demanding often beyond a reasonable limit even in presence of large computational resources, but upon convergence, is rather accurate. TI is computationally convenient but specifically designed to calculate the chemical potential and thus  it may not be optimal for employing MD for studying other properties. In fact TI requires artificial modification of the atomistic interactions (see Appendix).
Recently we have suggested that the chemical potential could be calculated by employing the Adaptive Resolution Simulation method in its Grand Canonical-like formulation (GC-AdResS) \cite{prl12,jctchan,prx}.
AdResS was originally designed  to interface regions of space at different levels of molecular resolution within one simulation set up. This allows for large and efficient multiscale simulations where the high resolution region is restricted to a small portion of space and the rest of the system is at coarser level. The recent version of the method, GC-AdResS, given its theoretical framework, should automatically calculate the chemical potential during the process of initial equilibration: in this work we prove that this is indeed the case and report results for the chemical potential for various liquids and mixtures of particular relevance in (bio)-chemistry and material science. We compare our results with those from full atomistic TI and find a satisfactory agreement. This agreement allows us to conclude that every time a multiscale GC-AdResS is performed, $\mu^{ex}$ is automatically calculated for each liquid component and implicitly confirm that the basic thermodynamics of the system is well described by the method.
Below we provide the basic technical ingredients of GC-AdResS which are relevant for the calculation of the chemical potential, more specific details can be found in \cite{jctchan, prx}.
\section{From AdResS to GC-AdResS}
The original idea of AdResS is based on a simple intuitive physical principle:
\begin{itemize}
\item divide the space in three regions, one with atomistic resolution and one with coarse-grained (spherical) resolution interfaced by a smaller region with an hybrid treatment.
\item couple the molecules in the different regions through a spatial interpolation formula on the forces:
\begin{equation}
{\bf F}_{\alpha \beta}=w(X_\alpha)w(X_\beta){\bf
  F}_{\alpha\beta}^{atom}+[1-w(X_\alpha)w(X_\beta)]{\bf F}^{cg}_{\alpha\beta} 
\label{eqforce}
\end{equation}
where $\alpha$ and $\beta$ indicates two molecules, ${\bf F}^{atom}$ is the
force derived from the atomistic force field and  ${\bf F}^{cg}$
from the corresponding coarse-grained potential, $X$ is the $x$ coordinate of the center of mass of
the molecule and $w$ is an interpolating function which smoothly goes from $0$
to $1$ (or vice versa) in the interface region ($\Delta$) where the lower resolution is then
slowly transformed (according to $w$) in the high resolution (or vice versa),
as illustrated in Fig.\ref{fig1}. .  
\item In the interface region a thermodynamic force acting on the center of mass (CM) of each molecule and a locally acting thermostat are added to assure the overall thermodynamic equilibrium at a given temperature. The thermodynamic force is defined in such a way that ${\bf F}_{th}=p_{AT}+\rho_{0}\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}=p_{CG}$, where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)\cite{prl12}. An additional locally acting thermostat is added to take care of the loss/gain of energy in the transition region.
\end{itemize}
\begin{figure}
\center
\includegraphics[width=0.475\textwidth]{adapt-schem.eps}
\caption{Pictorial representation of the adaptive box and
molecular representation. Here it is shown the case of the tetrahedral molecule used as a test case in the original development of AdResS. The region on the right,
is the low resolution region (coarse-grained), the central part is
the transition (hybrid) region $\Delta$, where the switching function
$w(x)$ (in green) is defined, and the region on the left, is the high resolution region (atomistic). It must be noticed that differently from the original AdResS, in GC-AdResS the range of definition of $w(x)$ is extended of an amount of ${\bf R}_{c}$. The extension of this additional region is equal to the cutoff radius of the atomistic interactions and $w(x)$ takes the constant value of $1$. The consequence is that molecules in the atomistic region interact with the rest of the system always and only via well defined atomistic interactions. This characteristic, in turn, allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a Grand-Canonical fashion.\label{fig1}}
\end{figure} 
In \cite{prx} we have defined necessary conditions in $\Delta$ such that the spatial probability distribution of the full-atomistic reference system was reproduced up to a certain (desired) order in the atomistic region of the adaptive system. Moreover we have shown that, because of such conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
 In the simulation set up, ${\bf F}_{th}$ is calculated via an iterative procedure as a function of the molecular density in $\Delta$. The iterative scheme consists of calculating ${\bf F}^{i+1}_{th}({\bf r})=\frac{1}{\rho_{0}\kappa_{T}}\nabla \rho^{i}({\bf r})$, ($\kappa_{T}$ the isothermal compressibility) and the force is considered converged when in $\Delta$ the target density $\rho_{0}$ is reached. As a result, ${\bf F}_{th}({\bf r})$, acting in $\Delta$, assures that there are no artificial density variations across the system, thus it allows to accurately reproduce the first order of the probability distribution in the atomistic region. Higher orders can be systematically achieved by imposing in $\Delta$ a corrective force proportional to the gradient of the corresponding higher order of the probability distribution; for example, the gradient of the CM-CM radial distribution function for the second order. Next it was proved that indeed the target Grand Canonical distribution, that is the probability distribution of a subsystem (of the size of the atomistic region in GC-AdResS) in a large full atomistic simulation is accurately reproduced. A large number of tests were performed and the reproduction by GC-AdResS of the probability distribution was numerically proved up to (at least) the third order, more than sufficient in MD simulations. Within this framework it was finally shown that the sum of work of ${\bf F}_{th}({\bf r})$ and that of the thermostat corresponds to the difference in chemical potential between the atomistic and coarse-grained resolution; this subject is treated in the next section.
\section{Calculation of $\mu$}
In Ref.\cite{prx} it has been shown that the chemical potential of the atomistic and coarse-grained resolution are related by the following formula: 
\begin{equation}
\mu_{CG}=\mu_{AT}+\omega_{th}+\omega_{Q}
\label{mu}
\end{equation}
 with $\mu_{CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{AT}$  the chemical potential of the atomistic system, $\omega_{th}=\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}$ the work of the thermodynamic force in the transition region, $\omega_{Q}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region. $\omega_{Q}$ is composed by two parts, one, called $\omega_{extra}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{DOF}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational). According to the equipartition theorem $\omega_{DOF}$ is equal to $\frac{1}{2}k_{B}T$ per degree of freedom. $\omega_{th}$ can be calculated in a straightforward way. The calculation of $\omega_{Q}$ is instead not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS. Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in AdResS. Since in the Hamiltonian approach we have the same equilibrium of the original adaptive (and full atomistic) system  and in addition we do not need to use a thermostat, the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{Q}$. Moreover we have proven numerically, for the case of liquid water, that $\omega_{Q}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$, where $V_{AT}$ and $V_{CG}$ are the atomistic and coarse-grained potential. The result above implies that $\omega_{Q}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. It must be noticed that the relation we obtained for the chemical potential is the similar to that  obtained in a complementary work by Potestio {\it et al.} \cite{h-adress}. In \cite{h-adress} an Hamiltonian approach  (H-AdResS) was explored and the expression of the chemical potential was derived via an elegant thermodynamic procedure. However, H-AdResS and GC-AdResS are essentially the same up to the first order in reproducing the probability distribution in the atomistic region. It is not a surprise that the calculation of the chemical potential can be done in a very similar way; in fact the chemical potential of a system in equilibrium requires (essentially) that the density of molecules is the same across the simulation box. The differences between the two methods emerge when higher orders of the probability distribution in the atomistic region are required. However the intention of this paper is not to discuss the difference between the two methods but rather to show their capability in accurately calculating the chemical potential; a discussion about the difference between the two approaches of AdResS can be found in \cite{luigientropy}. At this point according to \eqref{mu}, if one knows $\mu_{CG}$, then  GC-AdResS can automatically provide $\mu_{AT}$. However we need to do one step more, in fact the quantity of interest is not the total chemical potential, but the excess chemical potential $\mu^{ex}_{AT}$ which corresponds to the expression of \eqref{mu} where the kinetic (ideal gas) part is subtracted. Regarding the kinetic part, one can notice that the contribution coming from the center of mass is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
The kinetic part of $\mu_{AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{DOF}$ and can be calculated by hand removing $\frac{1}{2}k_{B}T$ per degree of freedom. Actually this calculation is not required, in fact the technical set up of AdResS considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}. Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference. Finally, the calculation of $\mu^{ex}_{CG}$ can be done with standard methods, TI or IPM, which for simple spherical molecules, like those of the coarse-grained system, requires a negligible computational cost.
In conclusion, we have the final expression:
\begin{equation}
\mu^{ex}_{AT}=\mu^{ex}_{CG}-\int_{\Delta}{F}_{th}({\bf r})d{\bf r}-\int_{\Delta}\langle w\nabla_{x} w(x) (V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}
\label{finalmu}
\end{equation}
In the next section we apply this procedure to several liquids and mixtures.
\section*{Results and Discussion}
We have calculated $\mu^{ex}$ for different liquids and mixtures, choosing cases which are representative of a large class of systems. Hydrophobic solvation in methane/water and in ethane/water mixtures, hydrophilic solvation in urea/water, a balance of both in water/tert-Butyl alcohol (TBA) mixture, other liquids, e.g. pure methanol and DMSO (and their mixtures with water), non aqueous mixtures in TBA/DMSO and alkane liquids such as methane, ethane and propane. Moreover, systems as water/urea are commonly used as cosolvent of biological molecules \cite{nico-debashish} while systems as tert-Butyl alcohol/water play a key role in modern technology \cite{irata}, thus they are of high interest {\it per se}. All technical details of each simulation are presented in the Appendix.
Results are reported in Table \ref{table} where the comparison with values obtained using full atomistic TI and available experiments, at the same concentrations, of our calculation is made; in our previous work we have already shown that value of the chemical potential of liquid water obtained with IPM is well reproduced by GC-AdResS, however the computational cost of IMP was very large, thus we do not consider calculations done with IPM in this paper. 
The agreement with full atomistic TI simulations is satisfactory in all cases, and thus it proves the solidity of GC-AdResS in describing the essential thermodynamics of a large class of systems.
We also compare the obtained values with those available in literature \cite{vang,nico}. Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; we have verified  such a supposed consistency. 
The chemical potential of $i$-th liquid's component in a mixture is calculated as:
\begin{equation}
\mu^{ex,i}_{AT}=\mu^{ex,i}_{CG}-\int_{\Delta}{F}^{i}_{th}({\bf r})d{\bf r}-\int_{\Delta}\langle w\nabla_{x_{i}} w(x)(V_{AT}-V_{CG})\rangle_{\bf r}d{\bf r}
\label{icomp}
\end{equation}
where ${F}^{i}_{th}(x)$ is the thermodynamic force applied to the molecules of the $i$-th component; this assures that, at the given concentration, the density of molecules of species $i$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation. $\nabla_{x_{i}} w(x)$ is the gradient along $x$ (in a rectangular box) applied to the switching function $w(x)$ in the center of mass of molecules of component $i$. 
\begin{table}[htpb]
\begin{center}
%\begin{tabular}{ccccc}
\begin{tabular}{ccccc}
\hline \hline
 Liquid component & Mole fraction of solute & GC-AdResS & TI & Experiment \\
\hline
water    & -- & -22.8 $\pm$ 0.2  & -22.1 $\pm$ 0.3 & -23.5 \cite{florian} \\
methane  & -- & -4.6 $\pm$ 0.1  & -5.2 $\pm$ 0.1 & -- \\
ethane   & -- & -8.2 $\pm$ 0.3  &  -8.8 $\pm$ 0.1 & -- \\
propane  & -- & -8.5 $\pm$ 0.1 & -9.5 $\pm$ 0.2 & -- \\
methanol  & -- & -20.1 $\pm$ 0.1 & -20.6 $\pm$ 0.4 & -20.5 \cite{vang}  \\
DMSO & -- & -32.2 $\pm$ 0.3 & -34.7 $\pm$ 0.7 & -32.2 \cite{dmso}  \\
methanol in methanol/water mixture & 0.01 & -18.1 $\pm$ 0.2 & -19.7 $\pm$ 0.2 & -- \\
methane in methane/water mixture & 0.006 & 9.1 $\pm$ 0.1  & 8.5 $\pm$ 0.2 & -- \\
urea in urea/water mixture & 0.02 & -56.1 $\pm$ 0.6 & -58.2 $\pm$ 0.5 & -57.8 $\pm$ 2.5 \cite{urea} \\
ethane in ethane/water mixture & 0.006 & 7.2 $\pm$ 0.2 & 7.4 $\pm$ 0.3 & -- \\ 
TBA in water/TBA mixture & 0.02 & -20.5 $\pm$ 0.6 & -21.4 $\pm$ 0.5 & -- \\
DMSO in DMSO/water mixture & 0.01 & -31.4 $\pm$ 0.5 & -33.2 $\pm$ 0.3 & -- \\
TBA in TBA/DMSO mixture & 0.02 & -24.8 $\pm$ 0.4 & -24.0 $\pm$ 0.5 & -- \\
\hline \hline
\end{tabular}
\caption{The excess chemical potential of different liquids and mixtures in $kJ/mol$ calculated from GC-AdResS and TI of full atomistic simulations. Experimental values for systems at the same concentrations used in simulation are also reported for comparison. For pure systems (water and methanol) we compare our values with those obtained in literature using the same force field and computational code. For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); however since we are always in a very dilute regime the chemical potential does not change significantly; we have verified that such consistency holds. Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
}
\label{table}
\end{center}
\end{table}

\begin{figure}
\center
\includegraphics[width=0.475\textwidth]{alcohol_rho.eps}\\
\includegraphics[width=0.475\textwidth]{water_rho.eps}
\caption{Top: Molecular density profile in $\Delta$ for TBA/water mixture; bottom, the same plot for water. Among all the systems considered, in this case the action of the thermodynamic force and that of the thermostat leads to the largest deviation from the reference all atomistic average density; however even in this case the discrepancy is negligible.\label{urea-TBA}}
\end{figure}
\begin{figure}
\center
\includegraphics[width=0.475\textwidth]{alcohol-alcohol.eps}\\
\includegraphics[width=0.475\textwidth]{alcohol-water.eps}\\
\includegraphics[width=0.475\textwidth]{water-water.eps}
\caption{Top: TBA-TBA radial distribution function; middle: the same plot for TBA-water; bottom: for water-water. The $g(r)$ is calculated only in the atomistic region.  Molecules located beyond a distance equal to the interactions' cut off, $0.9 nm$, are not considered since would include hybrid and coarse-grained molecules. \label{gr}}
\end{figure} 
In essence, according to the results obtained, GC-AdResS allows an on-the-fly determination of $\mu^{ex}$ of each component of a liquid, whenever a simulation is performed, without extra computational costs.
Moreover, Fig.\ref{urea-TBA} shows the action of the thermodynamic force and of the thermostat in the transition region $\Delta$ for TBA-water; the molecular density is sufficiently close to that of reference (the largest difference is below $20\%$ and the average difference is below $10\%$), and thus it assures that in the atomistic region there are no (significant) artificial effects on the molecular density due to the perturbation represented by the interpolation of forces in $\Delta$. In Fig.\ref{gr} we report various radial distribution functions for TBA-water in the atomistic region of the adaptive set up. The agreement with data from a full atomistic simulation is highly satisfactory. Moreover, it must be underlined that, on purpose, we have chosen extreme technical conditions, that is, a very small atomistic and coarse-grained region ($0.5 nm$) and a relatively large transition region ($2.7 nm$). Even in these conditions we prove that local properties as those of Fig.\ref{urea-TBA} and Fig.\ref{gr}, together with a relevant thermodynamics quantity as $\mu^{ex}$ are well reproduced.
This example shows the key features of GC-AdResS, that is, a multiscale simulation where the chemical potential of each component is obtained without extra computational costs and with high accuracy in a simulation where other properties are also calculated with high accuracy. It must be also noticed that the system corresponding to the figures is, among all the system considered, the case where the action of the thermodynamic force and of the thermostat produces the less accurate agreement with the reference data.
\section{Current computational convenience: a critical appraisal}
The natural question arising from the discussion above is whether or not GC-AdResS is a more convenient technical tool for calculating $\mu^{ex}$ compared to TI.
Currently the answer is negative although the current work is the first step towards a potentially positive answer for the future. In fact, the fastest version of AdResS is implemented in the GROMACS code \cite{gromacs}; using the Gromacs version 4.5.1 a speedup of a factor four with respected to full atomistic simulations has been reported for aqueous mixtures~\cite{debashish1,nico-debashish}. In this case GC-AdResS was more convenient than TI because in one simulation one could obtain the chemical potential of each liquid component and at the same time calculate structural properties (e.g. radial distribution functions). However in the successive version of GROMACS 4.6.1 the performance of atomistic simulations (above all of SPC/E water) has been highly improved while the corresponding implementation of AdResS is not optimized yet. At the current state, AdResS can only assure a speed up factor between 1.5 and 1.9 for large systems (30000 molecules) compared to full atomistic simulations without SPC/E water. As a consequence for the calculation of $\mu^{ex}$, TI is computationally less demanding than AdResS. Another point that must be considered (in perspective) for a fair comparison between TI and GC-AdResS, is the following: even if AdResS is optimized, in any code, TI has the advantage that one can use one single molecule in the simulation box to mimic the minor component of a mixture. In our case, instead, we must treat, technically speaking, a true mixture with a certain number of molecules of the minor component immersed in the liquid of the major component. Thus, at low concentrations, GC-AdResS simulations require larger systems than those required by TI, moreover, because of the low density of the minor component, the convergence of the corresponding thermodynamic force requires long simulations. 
Thus, for very dilute systems, if one is interested only in the chemical potential, TI shall be preferred to GC-AdResS, however if the interest goes beyond the calculation of the chemical potential, (e.g. radial distribution functions) then (optimized) GC-AdResS would still be more convenient.
When the concentration becomes higher, GC-AdResS may become preferable for both tasks: general properties of the mixture and chemical potential, not only because in this case one requires larger systems, but also because the convergence of the thermodynamic force of the minor component is much faster. Moreover, we would have the flexibility of calculating the chemical potential
of both components in one simulation run, whereas in TI, one needs to run two separate simulations in order to get the chemical potential of both components.
However, at the current state, the technical aspects of code optimization must be reported and we must make clear that the aim of this work is to show that  the automatic calculation of $\mu^{ex}$, independently from the simulation code in which is implemented and its computational cost, is a ``conceptual'' feature of GC-AdResS.

\section*{Conclusion} 
We have shown the accuracy of GC-AdResS in calculating the excess chemical potential for a representative class of complex liquids and mixtures. 
For any system, the initial equilibration process, that is the determination of the thermodynamic force, automatically delivers the chemical potential. The only additional calculation required is that of $\mu^{ex}_{CG}$ which implies the use of IPM or TI, but for a liquid of simple spheres, thus computationally negligible.  
The essential message is that GC-AdResS would be, {\it per se}, a reliable multiscale technique to calculate the chemical potential and, in perspective, upon computational/technical optimization it may become an efficient tool for calculating $\mu^{ex}$ compared to current techniques in MD such as TI.

\section*{Acknowledgments}
This work was supported by the Deutsche Forschungsgemeinschaft (DFG) with the Heisenberg grant provided to L.D.S (grant code DE 1140/5-1) and with its associate DFG grants for A.G.(grant code DE 1140/7-1) and for H.W. (grant code DE 1140/4-2).H.W.~and C.S.~thank the financial support by DFG research center MATHEON.

\section*{Appendix}
The potential energy function and the force field parameters for all the molecules
were taken from GROMOS53A6 parameter set. Liquid water was described by the SPC
model~\cite{spc}, methanol was described by the model developed by Walser et al~\cite{walser},
urea by the model described in~\cite{urea}, tert-butyl alcohol by the parameter set of~\cite{tba}
and DMSO was described by the model given by Geerke et.al.~\cite{dmso1}. For liquid methanol simulations, 
GROMOS43A1 parameter set was used, as it was shown to be more accurate for calculating excess free energy of 
solvation of methanol in methanol~\cite{vang}.

In all the AdResS simulations, 30 iterations were performed to obtain a 
converged thermodynamic force and a flat density profile. Each iteration consisted 
of 200 ps of equilibration which was followed by 200 ps of data collection. 
The simulations were performed at NVT conditions where the temperature was kept constant 
at 298 K. Simulations of liquid methane and ethane were performed at
111.66 K and 184.52 K respectively. To obtain the chemical potential of coarse-grained component, 
insertion particle method was used, where a trajectory of 8 ns was obtained and the coordinates were written
after every 0.4 ps. \recheck{The insertions of the molecule were performed 4,000,000 times in each 
frame at random locations}. The chemical potential value and
the error were calculated by taking the average and standard deviation of the last ten iterations.

The excess chemical potential of the solute or the excess free energy of solvation was calculated using the 
thermodynamic integration (TI) approach. In the thermodynamic integration, the 
interaction of solute with the rest of the molecules in the systems is a function 
of a coupling parameter $\lambda$, which indicates a level of change taken place between states
A and B. The interactions are switched off as $\lambda$ is 
continuously decreased in the stepwise manner. Simulations conducted at different values of 
$\lambda$ allow to plot a $\frac{\partial H}{\partial \lambda}$ curve, from which 
$\mu^{excess}$ is derived \cite{mu}. 
\begin{equation}
 \mu_{iB} - \mu_{iA} = \int_{0}^{1} \left \langle \frac{\partial H}{\partial \lambda} \right \rangle_{\lambda} d\lambda 
\end{equation}
where $U_{i}$ is the interaction energy of particle $i$ with the remaining particles and $\langle . \rangle$
denotes the canonical (NVT) or isobaric-isothermal (NPT) ensemble average. We computed the excess 
free energy using a two-stage approach as described in~\cite{mobley}, first coupling van der Waals interactions to transform the 
non-interacting molecule into a partially-interacting uncharged molecule, then coupling Coulomb
interactions from an uncharged interacting molecule to fully-interacting molecule. The resulting 
free energy $\Delta G_{final}$ is the sum of $\Delta G$ values obtained from the two procedures,
\begin{equation}
 \Delta G_{final} = \Delta G_{ele} + \Delta G_{vdw}
\end{equation}
where $\Delta G_{ele}$ is the free energy change associated with introducing the van der Waals interactions and 
$\Delta G_{vdw}$ is the free energy change associated with introducing Coulomb interactions. 
We evaluated the above integral for 21 values of $\lambda$ (evenly spaced between 0 and 1) in both the procedures.
At each value of $\lambda$, first a steepest descent energy minimization was performed followed 
by 200 ps of NPT equilibration and 400 ps of data collection under constant volume and temperature
conditions, in accordance with AdResS simulations. 
During the van der Waals coupling, soft-core interactions were used with soft-core parameters $\alpha_{LJ} = 0.5$, 
$\sigma = 0.3$ and the power of $\lambda$ in soft-core equation was taken as $1$. Free energy estimates and the errors
were calculated through Bennet's acceptance ratio method (BAR)~\cite{bar}. 
For both the AdResS and full-atom simulations, the system size was kept same. Below is a table 
with number of solute molecules, solvent molecules, system dimensions, size of hybrid and atomistic region (in AdResS simulations)
for each system studied. 
\begin{table}[!ht]
\begin{center}
\begin{tabular}{ccccc}
\hline \hline
 System & $N_{solute}$ & $N_{solvent}$ & System size ($nm^{3}$) &  AT + HY region ($nm^{3}$)  \\
\hline
water    & --- & 13824 & $29.9 \times 3.7 \times 3.7$ & $6.7 \times 3.7 \times 3.7$ \\
methane & --- & 2000 & $9.0 \times  3.7 \times 3.6$ & $6.0 \times 3.7 \times 3.6$ \\
ethane & --- & 2000 & $12.0 \times 3.9 \times 3.7$ & $7.0 \times 3.9 \times 3.7$ \\
propane & --- & 1433 & $10.0 \times 4.5 \times 4.5$ & $7.0 \times 4.5 \times 4.5$ \\
methanol & --- & 3200 & $9.6 \times 4.8 \times 4.8$ & $6.8 \times 4.8 \times 4.8$ \\
DMSO & --- & 1500 & $15.0 \times 3.6 \times 3.3$ &  $7.0 \times 3.6 \times 3.3$ \\
methanol/water mixture & 40 & 3960 & $9.2 \times 3.7 \times 3.7$ & $6.5 \times 3.7 \times 3.7$ \\
methane/water mixture & 40  & 6960 & $10.0 \times 4.8 \times 4.7$ & $6.5 \times 4.8 \times 4.7$ \\
urea/water mixture & 50 & 2500 & $9.7 \times 2.9 \times 2.8$ & $6.8 \times 2.9 \times 2.8$ \\
ethane/water mixture & 40 & 6960 & $10.0 \times 4.7 \times 4.6$ & $6.5 \times 4.7 \times 4.6$ \\ 
TBA/water mixture & 80 & 4400 & $10 \times 3.9 \times 3.8$ & $6.5 \times 3.9 \times 3.8$  \\
DMSO/water mixture & 50 & 4950 & $12.0 \times 4.0 \times 3.3$ & $7.0 \times 4.0 \times 3.3$ \\
TBA/DMSO mixture & 80 & 4400 & $10.0 \times 7.3 \times 7.2$ &  $7.0 \times 7.3 \times 7.2$ \\
\hline \hline
\end{tabular}
\caption{Summary of AdResS and full-atom simulations.}
\label{table2}
\end{center}
\end{table}

In all the simulations, a leap-frog stochastic dynamics integrator with a time step
of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS~\cite{lincs}
algorithm. In AdResS simulations, it was 
seen that the excess chemical potential values converge after a specific cut-off radius value. Hence, a different 
cut-off radius was used for different simulations in order to obtain a converged value. The full-atom simulations 
were performed using the same cut-off value to have a fair comparison. For liquid water, methanol/water, methane/water, ethane/water
and TBA/water systems, a cut-off radius of 0.9 nm was used for van der Waals and Coulomb interactions, while for rest 
of the systems, a cut-off radius of 1.4 nm was used. Electrostatic 
interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{tba}, 61 for other solutes in SPC
water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.

\begin{thebibliography}{24}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi

\bibitem{widom}
B.Widom, J.Chem.Phys.{\bf 39}, 2808 (1963)
\bibitem{ti}
I. G. Tironi and W. F. van Gunsteren, Mol.Phys. {\bf 83}, 381 (1994)
\bibitem{prl12}
S.Fritsch, S.Poblete, C.Junghans, G.Ciccotti, L.Delle Site and K.Kremer, Phys.Rev.Lett. {\bf 108}, 170602 (2012)
\bibitem{jctchan}
H.Wang, C.Sch\"{u}tte and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 2878 (2012)
\bibitem{prx}
H.Wang, C.Hartmann, C.Sch\"{u}tte and L.Delle Site, Phys.Rev.X, {\bf 3}, 011018 (2013)
\bibitem{h-adress}
R.Potestio, S.Fritsch, P.Espanol, R.Delgado-Buscalioni, K.Kremer, R.Everaers, and D.Donadio, Phys.Rev.Lett. {\bf 110}, 108301 (2013)
\bibitem{luigientropy}
L.Delle Site, Entropy {\bf 15} (2013); doi:10.3390
\bibitem{simon-ch}
C.Junghans and S.Poblete, Comp.Phys.Comm. {\bf 181}, 1449 (2010)
\bibitem{nico-debashish}
D. Mukherji, N. F. A. van der Vegt, and K. Kremer, J.Chem.Th.Comp. {\bf 8}, 3536 (2012)
\bibitem{irata}
K.Yoshida, T.Yamaguchi, A.Kovalenko and F.Hirata, J.Phys.Chem.B {\bf 106} 5042 (2002)
\bibitem{florian}
H. Eslami and F. M\"{u}ller-Plathe, J. Comput. Chem. {\bf 28}, 1763 (2007)
\bibitem{vang}
D.P.Geerke, W.F. van Gunsteren, ChemPhysChem, {\bf 7}, 671 (2006)
\bibitem{dmso}
Josefredo R. Pliego Jr and Jose  M. Riveros, Phys. Chem. Chem. Phys., {\bf 4}, 1622 (2002)
\bibitem{urea}
Lorna J. Smith,Herman J. C. Berendsen, and Wilfred F. van Gunsteren, J. Phys. Chem. B, {\bf 108}, 1065 (2004)
\bibitem{nico}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{debashish1}
D.Mukherji, N.F.A.van der Vegt, K.Kremer and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 375 (2012)
\bibitem{gromacs}
http://www.gromacs.org/
\bibitem{spc}
H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans, Reidel, Dordrecht, 331 (1981)
\bibitem{walser}
R. Walser, A. E. Mark, W. F. van Gunsteren, M. Lauterbach, G. Wipff, J. Chem. Phys. {\bf 112}, 10450 (2000)
\bibitem{tba}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{dmso1}
Daan P. Geerke , Chris Oostenbrink , Nico F. A. van der Vegt ,and Wilfred F. van Gunsteren, J. Phys. Chem. B. {\bf 108}, 1436 (2004)
\bibitem{mu}
T. Kristof and G. Rutkai, Chemical Physics Letters. {\bf 445}, 74 (2007). 
\bibitem{mobley}
David L. Mobley, John D. Chodera and Ken A. Dill  J.Chem.Phys. {\bf 125}, 084902 (2006).
\bibitem{bar}
Charles H. Bennett, Journal of Computational Physics {\bf 22}, 245 (1976).
\bibitem{lincs}
Hess, B. and Bekker, H. and Berendsen, H.J.C. and Fraaije, J.G.E.M., Journal of Computational Chemistry {\bf 18}, 1463 (1997).
\bibitem{rf}
I. G. Tironi, R. Sperb, P. E. Smith, W. F. van Gunsteren, J. Chem. Phys. {\bf 102}, 5451 (1995).
\end{thebibliography}

\end{document}

### 2014-05-07 writeDown/pub.jcp/chem-pot-jcp.tex
add appendix

@@
 \newcommand{\redc}[1]{{\color{red} #1}}            
+\newcommand{\vect}[1]{\textbf{\textit{#1}}}
+\newcommand{\dof}{{\textrm{DOF}}}
+\newcommand{\AT}{{\textrm{{AT}}}}
+\newcommand{\EX}{{\textrm{EX}}}
+\newcommand{\CG}{{\textrm{CG}}}
+\newcommand{\HY}{{\Delta}}
+\newcommand{\rdf}{{\textrm{rdf}}}
+\newcommand{\thf}{{\textrm{th}}}
+\newcommand{\res}{{\textrm{rep}}}
+\newcommand{\ext}{{\textrm{extra}}}
+\newcommand{\exc}{{\textrm{exc}}}
+\newcommand{\thermo}{{\textrm{Q}}}
+\newcommand{\hadress}{{\textrm{H}}}
+\newcommand{\dadress}{{\textrm{D}}}
 
@@
 
-\section*{Appendix}
+\section*{Appendix I}
 The potential energy function and the force field parameters for all the molecules
@@
 insertion particle method was used, where a trajectory of 8 ns was obtained and the coordinates were written
-after every 0.4 ps. \recheck{The insertions of the molecule were performed 4,000,000 times in each 
-frame at random locations}. The chemical potential value and
+after every 0.4 ps. The insertions of the molecule were performed 4,000,000 times in each 
+frame at random locations and with random orientations of the molecule. The chemical potential value and
 the error were calculated by taking the average and standard deviation of the last ten iterations.
@@
 In all the simulations, a leap-frog stochastic dynamics integrator with a time step
-of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS~\cite{lincs}
+of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS 
 algorithm. In AdResS simulations, it was 
@@
 water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.
+
+\section*{Appendix II: The deriviation of the $w_{extra}$}
+
+We consider the potential interpolation of the system:
+\begin{align}
+  V =
+  \sum_{i<j} w(\vect r_i) w(\vect r_j)
+  V^\AT_{i,j}
+  +
+  \sum_{i<j}[1- w(\vect r_i) w(\vect r_j)]
+  V^\CG_{i,j},
+\end{align}
+where  $\vect r_i$ denotes
+the center-of-mass (COM) position of the molecule with index $i$.
+$V^\AT_{i,j}$ and $V^\CG_{i,j}$ are the atomistic and coarse-grained potential energy between molecule $i$ and $j$, respectively.
+Being more precisely, they are
+\begin{align}
+  V^\AT_{i,j} =
+  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta),\quad
+  V^\CG_{i,j} =
+  V^\CG(\vect r_i - \vect r_j).
+\end{align}
+where index $\alpha$ and $\beta$ denotes the atom position of the corresponding molecule.
+The center of mass of the molecule can be calculated by
+\begin{align}
+  \vect r_i = \sum_{\alpha\in i} \frac{m_\alpha}{\sum_{\alpha\in i} m_\alpha} \vect r_\alpha,
+\end{align}
+where $m_\alpha$ is the mass of atom $\alpha$.
+The
+corresponding intermolecular force is given by
+\begin{align}\label{eqn:interpol-f}
+  \vect F_{i,j} =
+  w(\vect r_i) w(\vect r_j)
+  \vect F^\AT_{i,j}
+  +
+  [1- w(\vect r_i) w(\vect r_j)]
+  \vect F_{i,j}^\CG
+  -
+  \nabla w(\vect r_i) w(\vect r_j)
+  (V^\AT_{i,j} - V^\CG_{i,j})
+\end{align}
+We define the force of changing representation:
+\begin{align}\label{eqn:frep}
+  \vect F_{\res,i} = 
+  \sum_j \nabla w(\vect r_i) w(\vect r_j)
+  (V^\AT_{i,j} - V^\CG_{i,j})
+\end{align}
+An important fact is that the force of changing representation is not
+symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
+action-reaction law (momentum conservation) does not hold anymore for
+the potential interpolation approach. On the other hand, the force
+interpolation scheme does not preserve
+energy, while the potential interpolation
+approach has the advantage of energy conservation. In sum, both the
+force and potential interpolation approaches do not hold all physical
+conservation laws, because the hybrid region is artificially
+designed. Therefore, we will take the advantage of both the method and
+develop the thermodynamic relation (between the atomistic and
+coarse-grained resolutions)  for them at the same time.\\
+
+We use the same notation as in our previous work~\cite{prx}.
+The thermodynamic variables for the atomistic and coarse-grained regions
+are denoted by $(N_1, V_1, T)$ and $(N_3, V_3, T)$, respectively.
+We assume that the hybrid region is an infinitely thin filter that allows
+changing of resolution when a molecule passes through it. Therefore, we
+reasonably assumes that
+\begin{align}
+  V &= V_1 + V_3\\
+  N &= N_1 + N_3
+\end{align}
+where $V$ and $N$ are the whole system volume and total number of
+molecules in the system, respectively. In this work, we adopt the same
+assumptions as those listed in Sec.III.C of Ref.~\cite{prx},
+i.e. the system is under the thermodynamic limit, and is short-range
+correlated. When the thermodynamic force for both approaches are calculated
+(denoted by $\vect F_\thf$ and $\vect F^\hadress_\thf$, respectively.
+We use the superscript H to indicate that the thermodynamic force is of the
+potential interpolation AdResS),
+the flat density profile is enforce to the system:
+\begin{align}
+  \rho_\HY &= \rho_\AT = \rho_\CG = \rho_0\\
+  \rho_\HY^\hadress &= \rho_\AT = \rho_\CG = \rho_0
+\end{align}
+Where $\rho_0$ is the equilibrium number density of the system defined by $\rho_0 = N/V$.
+The thermodynamic force in force interpolation scheme provides the
+balance of the grand potential~\cite{prl12}, or equivalently
+\begin{align}\label{eqn:peq}
+  p_\AT = p_\CG - \rho_0 \,\omega_\thf 
+\end{align}
+where $p$ denotes the pressure, and $ \omega_\thf$ denotes the
+integral of the thermodynamic force. \\
+
+Since the existence of the force of changing representation breaks the
+Newton's action-reaction law, the pressure relation between the AT and CG
+resolution~\eqref{eqn:peq} does not hold anymore for the potential interpolation,
+and should be derived again.
+Now assume, for simplicity, the system only changes resolution in $x$ direction.
+We impose an infinitesimal increment of the volume $\Delta V$ to the
+AT region, and the same decrement of the volume $-\Delta V$ of the CG
+region.  The volume of the hybrid region is kept the invariant,
+so it is a ``piston''
+moves toward the CG region by $\Delta L$,
+where we assume $\Delta V = \Delta L\cdot S$, where $S$ is the
+cutting surface area.
+Here we talk about the infinitely small displacement  $\Delta L$
+in the sense that it is even much smaller than the size of the
+hybrid region. This is achievable by taking the limit of $\Delta L\rightarrow 0$,
+while keeping the system size fixed.
+Please also notice the displacement of the molecules are infinitely small,
+so one can reasonably assume
+the resolution of molecules remains the same under displacement $\Delta L$.
+Therefore, the change of the free energy of the system is
+\begin{align}\nonumber
+  \Delta A \approx&\,
+  A_\AT(N_1, V_1+\Delta V, T) -
+  A_\AT(N_1, V_1, T)
+  +
+  A_\CG(N_3, V_3-\Delta V, T) -
+  A_\CG(N_3, V_3, T)\\\label{eqn:apptmp3}
+  &+
+  \int d r\, \rho_0 S\cdot \Delta L\cdot
+  \vect F^\hadress_\thf(r)
+  -
+  \int d r\, \rho_0 S\cdot \Delta L\cdot
+  \big\langle \vect F_\res(r)\big\rangle
+\end{align}
+where $A_\AT$ and $A_\CG$ are the free energy of the AT and CG region, respectively.
+$N_1$ and $N_3$ are the number of molecules in the AT and CG region, and
+$V_1$ and $V_3$ are the volumn in the AT and CG region, respectively. $T$ is the temperature
+of the system.
+The last term comes from the work done on the piston. It is composed by
+two parts, the fist is the work done by the thermodynamic force, and the
+second is due to 
+the force of changing representation, which does not vanish due to the break of the Newton's
+action-reaction law. The fist and second part of Eq.~\eqref{eqn:interpol-f}
+do not contribute, because they obey the Newton's action-reaction law, so
+their works cancel as long as the transition region move infinitesimally toward one direction.
+The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
+It is straightforward to show that 
+\begin{align}\label{eqn:peq-d}
+  \Delta A \approx
+  -p_\AT\Delta V + p_\CG\Delta V -
+  \rho_0 \Delta V (\omega_\thf^\hadress - \omega_\res), 
+\end{align}
+where $w_\thf^\hadress$ is the integral of the potential interpolation
+thermodynamic force $\vect F_\thf^\hadress$, and
+$ \omega_\res$ is the work of changing representation,
+which can be explicitly written down as:
+\begin{align}\label{eqn:w-rep}
+  \omega_\res
+  = \int_\HY d r\,\langle \vect F_\res (r)\rangle
+  = \int_\HY d r\,\nabla\omega(r)\,
+  \big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+\end{align}
+The ensemble is taken over all possle positions of the second molecule
+in the pairwise interaction. In the case of molecules that contain
+more than one atom, the averge is also taken over all possible
+conformations of the molecules. 
+By using the same argument as the Section III.C of Ref.~\cite{prx}, we can
+show that in the thermodynamic limit, the equilibrium volumn of the AT region maxiimize the
+free energy, i.e.~$\Delta A / \Delta V
+= 0$ that yields
+\begin{align}\label{eqn:peq-h}
+  p_\CG - p_\AT =  \rho_0 (\omega_\thf^\hadress - \omega_\res).
+\end{align}
+Comparing with the result of the standard AdResS~Eq.~\eqref{eqn:peq},
+we have 
+\begin{align}\label{eqn:hd-rel}
+  \omega_\res = \omega_\thf^\hadress -   \omega_\thf,
+\end{align}
+which relates the thermodynamic force of the potential interpolation
+and force interpolation AdResS.\\
+
+In Ref.~\cite{prx} we proved that under proper assumptions,
+when the flat density profile is enforced by the thermodynamic force,
+the chemical potential difference between the different resolutions
+is given by
+\begin{align}\label{eqn:mueq-d}
+ \mu_\CG - \mu_\AT =   \omega_\thf + \omega_\dof + \omega_\ext
+\end{align}
+where the last term $\omega_\ext$ contributes because the
+force interpolation violates the energy conservation of the system.
+The same argument can be applied to the potential interpolation approach,
+and yields  the chemical potential difference between the AT and CG resolutions
+\begin{align}\label{eqn:mueq-h}
+ \mu_\CG - \mu_\AT =   \omega^\hadress_\thf + \omega_\dof 
+\end{align}
+Since we have an auxiliary Hamiltonian by using the the potential
+interpolation, we do not have the term $w_\ext$ in the above
+fomula.
+By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-d}, we have the
+relation
+\begin{align}\label{eqn:hd-rel-2}
+  \omega_\thermo^\ext = \omega^\hadress_\thf - \omega_\thf,
+\end{align}
+which also relates the thermodynamic force of the potential interpolation
+and force interpolation AdResS.\\
+\\
+
+From Eq.~\eqref{eqn:hd-rel} and \eqref{eqn:hd-rel-2}, we
+find the extra work of the thermostat being identical to the work of changing
+representation:
+\begin{align}\label{eqn:wextra}
+  \omega_\ext = \omega_\res,
+\end{align}
+which basically proves the main conclusion of the paper.  The ensemble
+average on the R.H.S.~of Eq.~\eqref{eqn:w-rep} is measured in the
+ensemble of the potential interpolation simulation, and the problem is
+that whether it is possible to calculate it efficiently in the force
+interpolation.  It is obvious that the phase space probability density
+of the potential interpolation is consistent with the force
+interpolation up to the 1st order (i.e.~density profile, which is
+forced to be constant by the thermodynamic force).  It is also
+possbile to derive the higher orders of correction, for example, for
+the 2nd order property: The radial distribution function~\cite{jctchan}.
+However, here we do not consider higher order corrections, because it
+has been numerically shown that actually the ensemble average of
+$\vect F_\res$ dose not depend on in which ensemble it is
+calculated~\cite{prx}. Therefore, we use Eq.~\eqref{eqn:wextra} to
+calculate $\omega_\ext$, and measure the ensemble average by the
+standard AdResS.  Since in the computer implementation, the CG
+molecules also keep the atomistic degrees of freedom eventhough they
+are in the CG region, therefore, the kinetic part of $\mu_\AT$ and
+$\mu_\CG$ are identical, and $\omega_\dof$ vanishes. Therefore,
+by inserting Eq.~\eqref{eqn:wextra} into \eqref{eqn:mueq-d}, we have
+\begin{align}
+  \mu_\AT^\ext = \mu_\CG^\ext - \int_\HY dr \vect F_\thf(r)
+  -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+\end{align}
 
@@
 Charles H. Bennett, Journal of Computational Physics {\bf 22}, 245 (1976).
-\bibitem{lincs}
-Hess, B. and Bekker, H. and Berendsen, H.J.C. and Fraaije, J.G.E.M., Journal of Computational Chemistry {\bf 18}, 1463 (1997).
 \bibitem{rf}

### 2014-05-07 writeDown/pub.jcp/chem-pot-jcp.tex
Luigi's revise, start unifying the notations, and so on

--- 2014-05-02 writeDown/pub.jcp/chem-pot-jcp.tex
@@
 \newcommand{\redc}[1]{{\color{red} #1}}            
+\newcommand{\bluec}[1]{{\color{blue} #1}}            
+\newcommand{\vect}[1]{\textbf{\textit{#1}}}
+\newcommand{\dof}{{\textrm{DOF}}}
+\newcommand{\AT}{{\textrm{{AT}}}}
+\newcommand{\EX}{{\textrm{EX}}}
+\newcommand{\CG}{{\textrm{CG}}}
+\newcommand{\HY}{{\Delta}}
+\newcommand{\rdf}{{\textrm{rdf}}}
+\newcommand{\thf}{{\textrm{th}}}
+\newcommand{\res}{{\textrm{rep}}}
+\newcommand{\ext}{{\textrm{extra}}}
+\newcommand{\exc}{{\textrm{exc}}}
+\newcommand{\thermo}{{\textrm{Q}}}
+\newcommand{\hadress}{{\textrm{H}}}
+\newcommand{\dadress}{{\textrm{D}}}
 
@@
 
+\bluec{
+  Unified of terminology:
+  \begin{itemize}
+  \item interface region $\rightarrow$ transition region
+  \item hybrid region $\rightarrow$ transition region
+  \end{itemize}
+}
+
 \section{Introduction}
@@
 This agreement allows us to conclude that every time a multiscale GC-AdResS is performed, $\mu^{ex}$ is automatically calculated for each liquid component and implicitly confirm that the basic thermodynamics of the system is well described by the method.
+\recheck{Moreover, in recent work AdResS has been merged with the MARTINI force field \cite{matej-sw1,matej-sw2}.
+In this context, the possibility of having a quantity like the chemical potential under \bluec{what is ``explicit control''} can be used as a further argument for the validity of the method in applications to large systems of biological interest.}
 Below we provide the basic technical ingredients of GC-AdResS which are relevant for the calculation of the chemical potential, more specific details can be found in \cite{jctchan, prx}.
+
 \section{From AdResS to GC-AdResS}
@@
 \begin{itemize}
-\item divide the space in three regions, one with atomistic resolution and one with coarse-grained (spherical) resolution interfaced by a smaller region with an hybrid treatment.
+\item divide the space in three regions, one with atomistic resolution (AT) and one with coarse-grained (spherical) resolution (CG) interfaced by a smaller region with an hybrid treatment, which is usually called transition region or hybrid region.
 \item couple the molecules in the different regions through a spatial interpolation formula on the forces:
 \begin{equation}
-{\bf F}_{\alpha \beta}=w(X_\alpha)w(X_\beta){\bf
-  F}_{\alpha\beta}^{atom}+[1-w(X_\alpha)w(X_\beta)]{\bf F}^{cg}_{\alpha\beta} 
+{\vect F}_{i,j}=w(\vect r_i)w(\vect r_j){\vect
+  F}_{i,j}^{\AT}+[1-w(\vect r_i)w(\vect r_j)]{\vect F}^{\CG}_{i,j} 
 \label{eqforce}
 \end{equation}
-where $\alpha$ and $\beta$ indicates two molecules, ${\bf F}^{atom}$ is the
-force derived from the atomistic force field and  ${\bf F}^{cg}$
-from the corresponding coarse-grained potential, $X$ is the $x$ coordinate of the center of mass of
+where $i$ and $j$ indicates two molecules, ${\vect F}^{\AT}$ is the
+force derived from the atomistic force field and  ${\vect F}^{\CG}$
+from the corresponding coarse-grained potential, $\vect r$ is the center of mass (COM) position of
 the molecule and $w$ is an interpolating function which smoothly goes from $0$
@@
 \item In the interface region a thermodynamic force acting on the center of mass (CM) of each molecule and a locally acting thermostat are added to assure the overall thermodynamic equilibrium at a given temperature.
-The thermodynamic force is defined in such a way that ${\bf F}_{th}=p_{AT}+\rho_{0}\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}=p_{CG}$, where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)\cite{prl12}.
+The thermodynamic force is defined in such a way that $p_{AT}+\rho_{0}\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}=p_{CG}$, where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)\cite{prl12}.
 An additional locally acting thermostat is added to take care of the loss/gain of energy in the transition region.
@@
 In \cite{prx} we have defined necessary conditions in $\Delta$ such that the spatial probability distribution of the full-atomistic reference system was reproduced up to a certain (desired) order in the atomistic region of the adaptive system.
-Moreover we have shown that, because of such conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
+\recheck{We have defined the $i$th order of a spatial (configurational) probability distribution of $N$ molecules, $p({\bf r}_{1}, \cdots, {\bf r}_{N})$, as:
+\begin{equation}
+p^{(i)}({\bf r}_{1}, \cdots, {\bf r}_{i})=\int p({\bf r}_{1}, \cdots, {\bf r}_{i},{\bf r}_{i+1}, \cdots, {\bf r}_{N}) \: d{\bf r}_{i+1}\cdots d{\bf r}_{N}
+\label{order}
+\end{equation}
+The first order, often mentioned in this work corresponds to the molecular number density $\rho({\bf r})$.}
+Moreover we have shown that, because of the necessary conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
  In the simulation set up, ${\bf F}_{th}$ is calculated via an iterative procedure as a function of the molecular density in $\Delta$.
@@
 $\omega_{Q}$ is composed by two parts, one, called $\omega_{extra}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{DOF}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-According to the equipartition theorem $\omega_{DOF}$ is equal to $\frac{1}{2}k_{B}T$ per degree of freedom.
-$\omega_{th}$ can be calculated in a straightforward way.
-The calculation of $\omega_{Q}$ is instead not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS.
+\recheck{ While the determination of $\omega_{DOF}$ is not required for the our final aim (that is the calcualtion of the excess chemical potential, as explain later on), the calculation of $\omega_{Q}$ is very relevant.
+However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in AdResS.
-Since in the Hamiltonian approach we have the same equilibrium of the original adaptive (and full atomistic) system  and in addition we do not need to use a thermostat, the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{Q}$.
-Moreover we have proven numerically, for the case of liquid water, that $\omega_{Q}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$, where $V_{AT}$ and $V_{CG}$ are the atomistic and coarse-grained potential.
+\recheck{In the Hamiltonian approach we have the same equilibrium of the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{Q}$ (further details about this point are given in the Appendix)}.
+Moreover we have proven numerically, for the case of liquid water, that $\omega_{extra}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$, where $V_{AT}$ and $V_{CG}$ are the atomistic and coarse-grained potential.
+\recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
+the probability distribution of the system as defined in Eq.\ref{order}}.
 The result above implies that $\omega_{Q}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
-It must be noticed that the relation we obtained for the chemical potential is the similar to that  obtained in a complementary work by Potestio {\it et al.} \cite{h-adress}.
-In \cite{h-adress} an Hamiltonian approach  (H-AdResS) was explored and the expression of the chemical potential was derived via an elegant thermodynamic procedure.
-However, H-AdResS and GC-AdResS are essentially the same up to the first order in reproducing the probability distribution in the atomistic region.
-It is not a surprise that the calculation of the chemical potential can be done in a very similar way; in fact the chemical potential of a system in equilibrium requires (essentially) that the density of molecules is the same across the simulation box.
-The differences between the two methods emerge when higher orders of the probability distribution in the atomistic region are required.
-However the intention of this paper is not to discuss the difference between the two methods but rather to show their capability in accurately calculating the chemical potential; a discussion about the difference between the two approaches of AdResS can be found in \cite{luigientropy}.
+\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxilary Hamiltonian  has been recently proposed and applied to mixtures  by Potestio {\it et al.} \cite{h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
 At this point according to \eqref{mu}, if one knows $\mu_{CG}$, then  GC-AdResS can automatically provide $\mu_{AT}$.
@@
 Regarding the kinetic part, one can notice that the contribution coming from the center of mass is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
-The kinetic part of $\mu_{AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{DOF}$ and can be calculated by hand removing $\frac{1}{2}k_{B}T$ per degree of freedom.
-Actually this calculation is not required, in fact the technical set up of AdResS considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
+The kinetic part of $\mu_{AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{DOF}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
+However such a calcualtion may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the technical set up of AdResS considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
 Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference.
@@
 \end{equation}
-In the next section we apply this procedure to several liquids and mixtures.
+\section*{Analytic eriviation of the $w_{extra}$}
+\recheck{In this section we derive analytically the equivalence: $\omega_{extra}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$ and define its limitations.\\
+We define a potential coupling the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
+\begin{align}
+  V =
+  \sum_{i<j} w(\vect r_i) w(\vect r_j)
+  V^\AT_{i,j}
+  +
+  \sum_{i<j}[1- w(\vect r_i) w(\vect r_j)]
+  V^\CG_{i,j},
+\end{align}
+where  $\vect r_i$ denotes
+the center-of-mass (COM) position of the molecule with index $i$.
+$V^\AT_{i,j}$ and $V^\CG_{i,j}$ are the atomistic and coarse-grained interaction potential between molecule $i$ and $j$, respectively, with:
+\begin{align}
+  V^\AT_{i,j} =
+  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta),\quad
+  V^\CG_{i,j} =
+  V^\CG(\vect r_i - \vect r_j).
+\end{align}
+where index $\alpha$ and $\beta$ denotes the atom position of the corresponding molecule.
+The center of mass of the molecule is defined as:
+\begin{align}
+  \vect r_i = \sum_{\alpha\in i} \frac{m_\alpha}{\sum_{\alpha\in i} m_\alpha} \vect r_\alpha,
+\end{align}
+where $m_\alpha$ is the mass of atom $\alpha$.
+The
+corresponding intermolecular force is given by:
+\begin{align}\label{eqn:interpol-f}
+  \vect F_{i,j} =
+  w(\vect r_i) w(\vect r_j)
+  \vect F^\AT_{i,j}
+  +
+  [1- w(\vect r_i) w(\vect r_j)]
+  \vect F_{i,j}^\CG
+  -
+  \nabla w(\vect r_i) w(\vect r_j)
+  (V^\AT_{i,j} - V^\CG_{i,j})
+\end{align}
+We define the force of changing representation:
+\begin{align}\label{eqn:frep}
+  \vect F_{\res,i} = 
+  \sum_j \nabla w(\vect r_i) w(\vect r_j)
+  (V^\AT_{i,j} - V^\CG_{i,j})
+\end{align}
+%An important fact is that the force of changing representation is not
+%symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
+%action-reaction law (momentum conservation) does not hold anymore for
+%the potential interpolation approach. On the other hand, the force
+%interpolation scheme does not preserve
+%energy, while the potential interpolation
+%approach has the advantage of energy conservation. In sum, both the
+%force and potential interpolation approaches do not hold all physical
+%conservation laws, because the hybrid region is artificially
+%designed. Therefore, we will take the advantage of both and
+%develop the thermodynamic relation (between the atomistic and
+%coarse-grained resolutions)  for them at the same time.\\
+
+We use the same notation as in our previous work~\cite{prx}.
+The thermodynamic variables for the atomistic and coarse-grained regions
+are denoted by $(N_1, V_1, T)$ and $(N_3, V_3, T)$, respectively.
+We assume that the hybrid region is an infinitely thin filter (that is a much smaller region than the atomistic and coarse-grained region) that allows molecules
+to change resolution as they cross it. Therefore, it is 
+reasonable to assume that:
+\begin{align}
+  V &= V_1 + V_3\\
+  N &= N_1 + N_3
+\end{align}
+where $V$ and $N$ are the total volume and total number of
+molecules of the system. In this work, we adopt the same
+assumptions as those listed in Sec.III.C of Ref.~\cite{prx},
+i.e. we assume to be in the thermodynamic limit, and molecules are short-range
+correlated (short-ranged must be intended as a range comparable to the size of the filter).
+The thermodynamic force for GC-AdResS ($\vect F_\thf$) and for the approach with the auxiliary Hamiltonian ($\vect F^\hadress_\thf$, i.e.
+potential interpolation AdResS),
+enforce the system to have a flat density:
+\begin{align}
+  \rho_\HY &= \rho_\AT = \rho_\CG = \rho_0\\
+  \rho_\HY^\hadress &= \rho_\AT = \rho_\CG = \rho_0
+\end{align}
+Where $\rho_0$ is the equilibrium number density of the system defined by $\rho_0 = N/V$.
+\
+As shown in Refs.\cite{prl12, prx} $\vect F_\thf$ provides the
+balance of the grand potential or equivalently
+\begin{align}\label{eqn:peq}
+  p_\AT = p_\CG - \rho_0 \,\omega_\thf 
+\end{align}
+where $p$ denotes the pressure, and $ \omega_\thf$ denotes the
+integral of the thermodynamic force.} \\
+
+Instead when we consider the auxiliary Hamiltonian approach,  the force of changing representation is not
+symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
+action-reaction law (momentum conservation) does not hold anymore.
+As a consequence, the pressure relation between the AT and CG
+resolution~\eqref{eqn:peq} does not hold anymore and should be derived again.
+Now assume, for simplicity, that the system changes resolution only along the $x$ direction.
+We impose an infinitesimal increment of the volume $\Delta V$ to the
+AT region, and apply the same decrement of the volume $-\Delta V$ to the CG
+region.  The volume of the hybrid region is kept constant as if an ideal ``piston'' moves toward the CG region by an amount $\Delta L$.
+We assume $\Delta V = \Delta L\cdot S$, where $S$ is the
+cutting surface area.
+For infinitesimal displacement , $\Delta L$, we mean a displacement which is much smaller than the size of the
+hybrid region. This is achievable by taking the limit of $\Delta L\rightarrow 0$,
+while keeping the system size fixed.
+It must be noticed that also the displacements of the molecules are infinitesimal, so that it can be reasonably assumed that
+the resolution of the molecules remains the same under a displacement of $\Delta L$.
+Therefore, the change of the free energy of the system is
+\begin{align}\nonumber
+  \Delta A \approx&\,
+  A_\AT(N_1, V_1+\Delta V, T) -
+  A_\AT(N_1, V_1, T)
+  +
+  A_\CG(N_3, V_3-\Delta V, T) -
+  A_\CG(N_3, V_3, T)\\\label{eqn:apptmp3}
+  &+
+  \int d r\, \rho_0 S\cdot \Delta L\cdot
+  \vect F^\hadress_\thf(r)
+  -
+  \int d r\, \rho_0 S\cdot \Delta L\cdot
+  \big\langle \vect F_\res(r)\big\rangle
+\end{align}
+where $A_\AT$ and $A_\CG$ is the free energy of the AT and CG region, respectively \recheck{HAN: why is it justified to split the free energy in free energies of subsystems and why the free energy of the HYB region is only the work and not also its kinetic component.
+I understand that since the molecule do not change resolution, their kinetic part stays the same and thus the difference is zero.
+However this formula needs either a reference or few more explanations}.
+$N_1$ and $N_3$ is the number of molecules in the AT and CG region, and
+$V_1$ and $V_3$ is the volume in the AT and CG region, respectively. $T$ is the temperature
+of the system.
+The last term comes from the work done on the piston. It is composed by
+two parts, the first is the work done by the thermodynamic force, and the
+second is due to 
+the force of changing representation, which does not vanish due to the breaking of the Newton's
+action-reaction law. The first and second part of Eq.~\eqref{eqn:interpol-f}
+do not contribute, because they obey the Newton's action-reaction law, so
+their total work is zero as long as the transition region move infinitesimally in one direction.
+The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
+It is straightforward to show that \recheck{HAN, here it must be shown} 
+\begin{align}\label{eqn:peq-d}
+  \Delta A \approx
+  -p_\AT\Delta V + p_\CG\Delta V -
+  \rho_0 \Delta V (\omega_\thf^\hadress - \omega_\res), 
+\end{align}
+where $w_\thf^\hadress$ is the integral of the potential interpolation
+thermodynamic force $\vect F_\thf^\hadress$, and
+$ \omega_\res$ is the work of changing representation,
+which can be explicitly written down as:
+\begin{align}\label{eqn:w-rep}
+  \omega_\res
+  = \int_\HY d r\,\langle \vect F_\res (r)\rangle
+  = \int_\HY d r\,\nabla\omega(r)\,
+  \big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+\end{align}
+The average is taken over all possible positions of the second molecule
+in the pairwise interaction. In case of molecules that contain
+more than one atom, the averge is also taken over all possible
+conformations of the molecules. 
+By using the same argument as the Section III.C of Ref.~\cite{prx} \recheck{Han, which ones?}, we can
+show that in the thermodynamic limit, the equilibrium volume of the AT region maxiimize the
+free energy, i.e.~$\Delta A / \Delta V
+= 0$, which yields
+\begin{align}\label{eqn:peq-h}
+  p_\CG - p_\AT =  \rho_0 (\omega_\thf^\hadress - \omega_\res).
+\end{align}
+Comparing with the result of the standard GC-AdResS~Eq.~\eqref{eqn:peq},
+we have: 
+\begin{align}\label{eqn:hd-rel}
+  \omega_\res = \omega_\thf^\hadress -   \omega_\thf,
+\end{align}
+which relates the thermodynamic force of the potential interpolation
+and force interpolation AdResS.\\
+
+In Ref.~\cite{prx} we proved that under proper assumptions,
+when the flat density profile is enforced by the thermodynamic force,
+the chemical potential difference between the different resolutions
+is given by
+\begin{align}\label{eqn:mueq-d}
+ \mu_\CG - \mu_\AT =   \omega_\thf + \omega_\dof + \omega_\ext
+\end{align}
+The same argument can be applied to the potential interpolation approach,
+and yields  the chemical potential difference between the AT and CG resolutions
+\begin{align}\label{eqn:mueq-h}
+ \mu_\CG - \mu_\AT =   \omega^\hadress_\thf + \omega_\dof 
+\end{align}
+Since we have an auxiliary Hamiltonian, by using the the potential
+interpolation, we do not have the term $w_\ext$ in the above
+fomula.
+By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-d}, we have the
+relation
+\begin{align}\label{eqn:hd-rel-2}
+  \omega_\thermo^\ext = \omega^\hadress_\thf - \omega_\thf,
+\end{align}
+which also relates the thermodynamic force of the potential interpolation
+and force interpolation AdResS.\\
+\\
+
+From Eq.~\eqref{eqn:hd-rel} and \eqref{eqn:hd-rel-2}, we
+find the extra work of the thermostat in GC-AdResS being identical to the work of changing
+representation of the Hamiltonian auxiliary approach:
+\begin{align}\label{eqn:wextra}
+  \omega_\ext = \omega_\res,
+\end{align}
+which basically proves the statement at the beginning of this section.  The ensemble
+average on the R.H.S.~of Eq.~\eqref{eqn:w-rep} is performed in the
+ensemble of the system treated with the potential interpolation approach, and the question is if the ensemble average is equivalent if it is performed in the simulation where the force
+interpolation approach is used.  It is obvious that the phase spatial probability distribution correponding to the system treated with the potential interpolation is consistent with the force
+interpolation at least up to the 1st order as defined in Eq.\ref{order}.  It is also
+possbile to systematically obtain equivalence in the ensemble average operation  at higher orders of accuracy of the probability distribution, as, for example, it is done for the radial distribution function in Ref.~\cite{jctchan}.
+However, here we do not consider higher order corrections, because it
+has been numerically shown that actually the ensemble average of
+$\vect F_\res$ dose not depend on in which ensemble it is
+calculated~\cite{prx}. Therefore, we use Eq.~\eqref{eqn:wextra} to
+calculate $\omega_\ext$, and measure the ensemble average by the
+standard AdResS.  Since in the computer implementation, the CG
+molecules also keep the atomistic degrees of freedom eventhough they
+are in the CG region, therefore, the kinetic part of $\mu_\AT$ and
+$\mu_\CG$ are identical, and $\omega_\dof$ vanishes. Therefore,
+by inserting Eq.~\eqref{eqn:wextra} into \eqref{eqn:mueq-d}, we have
+\begin{align}
+  \mu_\AT^\ext = \mu_\CG^\ext - \int_\HY dr \vect F_\thf(r)
+  -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+\end{align}
+In the next section we apply the procedure to the calculation of the excess chemical potential of several liquids and mixtures.}
 \section*{Results and Discussion}
@@
 water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.
+\subsection{Auxiliary Hamiltonian: Technical Aspects}
+\recheck{In principle when the auxiliary Hamiltonian approach is used, one can perform microcanonical simulations and thus can avoid the use of a thermostat.
+In this case the thermodynamic force of the auxiliary Hamiltonian does not have any effect of the thermostat and thus its difference from the thermodynamic force of GC-AdResS is exactly the work that the thermostat does in GC-AdResS in order to enforce the falt density profile and thus induced the correct flux of particles which are changing resolution.
+The question is whether the energy is conserved in the auxiliary Hamiltonian approach.
+We have checked that the conservation holds for systems without electrostatics (methane,ethane,propane), thus for such systems the procedure is straightforward.
+Instaed, for systems with electrostatic interactions, even for full atomistic simulations, due to the fact that the force fields are designed for employing the reaction field method, the energy cannot be conserved and the coupling to a thermostat is required.
+This is a well known problem reported in the manual of Gromacs.
+However, in our case, for both, the auxiliary Hamiltonian and GC-AdResS the energy drift due to the reaction field method is the essentially same because they have equivalent electrostatic interactions, thus the energy drift due to the use of the reaction field method is automatically removed when we consider the difference between the thermodynamic forces of the two approaches, that is the force of changing resolution.}
 
@@
 H.Wang, C.Hartmann, C.Sch\"{u}tte and L.Delle Site, Phys.Rev.X, {\bf 3}, 011018 (2013)
+\bibitem{matej-sw1}
+J.Zavadlav, M.N.Melo, S.J. Marrink and M.Praprotnik, J.Chem.Phys. {\bf 140}, 054114 (2014)
+\bibitem{matej-sw2}
+J.Zavadlav, M.N.Melo, A.Vicente Cunha, A.H. De Vries ,S.J. Marrink and M.Praprotnik, J.Chem.Th.Comp. DOI:10.1021/ct5001523 (2014)
 \bibitem{h-adress}
-R.Potestio, S.Fritsch, P.Espanol, R.Delgado-Buscalioni, K.Kremer, R.Everaers, and D.Donadio, Phys.Rev.Lett. {\bf 110}, 108301 (2013)
+R.Potestio, P.Espanol, R.Delgado-Buscalioni, R.Everaers, K.Kremer, and D.Donadio, Phys.Rev.Lett. {\bf 111}, 060601 (2013)
 \bibitem{luigientropy}

### 2014-05-08 writeDown/pub.jcp/chem-pot-jcp.tex
my revision

@@
 \newcommand{\ext}{{\textrm{extra}}}
-\newcommand{\exc}{{\textrm{exc}}}
+\newcommand{\exc}{{\textrm{ex}}}
 \newcommand{\thermo}{{\textrm{Q}}}
@@
   \item hybrid region $\rightarrow$ transition region
+  \item define COM, change all ``center of mass'' to COM
+  \item change the title of sec.III
+  \item do not be too mean, we cite BOTH of their PRL H-Adress paper...
+  \item some times, it is called GC-AdResS, sometimes original AdResS, sometimes standard AdResS, sometimes force-interpolation AdResS....
+  \item rewrite eq. 4, see if it is OK for you
   \end{itemize}
@@
 In this context, the possibility of having a quantity like the chemical potential under \bluec{what is ``explicit control''} can be used as a further argument for the validity of the method in applications to large systems of biological interest.}
-Below we provide the basic technical ingredients of GC-AdResS which are relevant for the calculation of the chemical potential, more specific details can be found in \cite{jctchan, prx}.
+Below we provide the basic technical ingredients of GC-AdResS which are relevant for the calculation of the chemical potential, more specific details can be found in~\cite{jctchan, prx}.
 
@@
 force derived from the atomistic force field and  ${\vect F}^{\CG}$
-from the corresponding coarse-grained potential, $\vect r$ is the center of mass (COM) position of
+from the corresponding coarse-grained potential, \recheck{$\vect r$ is the center of mass (COM) position of}
 the molecule and $w$ is an interpolating function which smoothly goes from $0$
-to $1$ (or vice versa) in the interface region ($\Delta$) where the lower resolution is then
+to $1$ (or vice versa) in the transition region ($\Delta$) where the lower resolution is then
 slowly transformed (according to $w$) in the high resolution (or vice versa),
-as illustrated in Fig.\ref{fig1}. .  
-\item In the interface region a thermodynamic force acting on the center of mass (CM) of each molecule and a locally acting thermostat are added to assure the overall thermodynamic equilibrium at a given temperature.
-The thermodynamic force is defined in such a way that $p_{AT}+\rho_{0}\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}=p_{CG}$, where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)\cite{prl12}.
+as illustrated in Fig.\ref{fig1}.
+\item In the transition region a thermodynamic force acting on the COM of each molecule and a locally acting thermostat are added to assure the overall thermodynamic equilibrium at a given temperature.
+The thermodynamic force is defined in such a way that
+  $p_{\AT}+\rho_{0}\int_{\Delta}{\vect F}_{th}({\vect r})d{\vect r}=p_{\CG}$,
+  where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)~\cite{prl12}.
 An additional locally acting thermostat is added to take care of the loss/gain of energy in the transition region.
@@
 the transition (hybrid) region $\Delta$, where the switching function
-$w(x)$ (in green) is defined, and the region on the left, is the high resolution region (atomistic).
-It must be noticed that differently from the original AdResS, in GC-AdResS the range of definition of $w(x)$ is extended of an amount of ${\bf R}_{c}$.
+$w(x)$ (in green.
+\recheck{Here the space is devided in $x$ direction, so it is a function of only $x$.}) is defined, and the region on the left, is the high resolution region (atomistic).
+It must be noticed that differently from the original AdResS, in GC-AdResS the range of definition of $w(x)$ is extended of an amount of ${\vect R}_{c}$.
 The extension of this additional region is equal to the cutoff radius of the atomistic interactions and $w(x)$ takes the constant value of $1$.
@@
 In \cite{prx} we have defined necessary conditions in $\Delta$ such that the spatial probability distribution of the full-atomistic reference system was reproduced up to a certain (desired) order in the atomistic region of the adaptive system.
-\recheck{We have defined the $i$th order of a spatial (configurational) probability distribution of $N$ molecules, $p({\bf r}_{1}, \cdots, {\bf r}_{N})$, as:
+\recheck{We have defined the $m$th order of a spatial (configurational) probability distribution of $N$ molecules, $p({\vect r}_{1}, \cdots, {\vect r}_{N})$, as:
 \begin{equation}
-p^{(i)}({\bf r}_{1}, \cdots, {\bf r}_{i})=\int p({\bf r}_{1}, \cdots, {\bf r}_{i},{\bf r}_{i+1}, \cdots, {\bf r}_{N}) \: d{\bf r}_{i+1}\cdots d{\bf r}_{N}
+p^{(m)}({\vect r}_{1}, \cdots, {\vect r}_{m})=\int p({\vect r}_{1}, \cdots, {\vect r}_{m},{\vect r}_{m+1}, \cdots, {\vect r}_{N}) \: d{\vect r}_{m+1}\cdots d{\vect r}_{N}
 \label{order}
 \end{equation}
-The first order, often mentioned in this work corresponds to the molecular number density $\rho({\bf r})$.}
+The first order, often mentioned in this work corresponds to the molecular number density $\rho({\vect r})$.}
 Moreover we have shown that, because of the necessary conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
- In the simulation set up, ${\bf F}_{th}$ is calculated via an iterative procedure as a function of the molecular density in $\Delta$.
-The iterative scheme consists of calculating ${\bf F}^{i+1}_{th}({\bf r})=\frac{1}{\rho_{0}\kappa_{T}}\nabla \rho^{i}({\bf r})$, ($\kappa_{T}$ the isothermal compressibility) and the force is considered converged when in $\Delta$ the target density $\rho_{0}$ is reached.
-As a result, ${\bf F}_{th}({\bf r})$, acting in $\Delta$, assures that there are no artificial density variations across the system, thus it allows to accurately reproduce the first order of the probability distribution in the atomistic region.
-Higher orders can be systematically achieved by imposing in $\Delta$ a corrective force proportional to the gradient of the corresponding higher order of the probability distribution; for example, the gradient of the CM-CM radial distribution function for the second order.
-Next it was proved that indeed the target Grand Canonical distribution, that is the probability distribution of a subsystem (of the size of the atomistic region in GC-AdResS) in a large full atomistic simulation is accurately reproduced.
+
+In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure \recheck{using} the molecular number density in $\Delta$.
+The iterative scheme consists of calculating \recheck{${\vect F}^{k+1}_{th}({\vect r}) = {\vect F}^{k}_{th}({\vect r}) + \frac{1}{\rho^2_{0}\kappa_{T}}\nabla \rho^{k}({\vect r})$} ($\kappa_{T}$ the isothermal compressibility), and the thermodynamic force is considered converged when the target density $\rho_{0}$ is reached in $\Delta$.
+As a result, ${\vect F}_{th}({\vect r})$, acting in $\Delta$, assures that there are no artificial density variations across the system, thus it allows to accurately reproduce the first order of the probability distribution in the atomistic region.
+Higher orders can be systematically achieved by imposing in $\Delta$ a corrective force.
+% proportional to the gradient of the corresponding higher order of the probability distribution;
+\recheck{For example, the COM-COM radial distribution function correction for the second order~\cite{jctchan}.} Next it was proved that indeed the target Grand Canonical distribution, that is the probability distribution of a subsystem (of the size of the atomistic region in GC-AdResS) in a large full atomistic simulation is accurately reproduced.
 A large number of tests were performed and the reproduction by GC-AdResS of the probability distribution was numerically proved up to (at least) the third order, more than sufficient in MD simulations.
-Within this framework it was finally shown that the sum of work of ${\bf F}_{th}({\bf r})$ and that of the thermostat corresponds to the difference in chemical potential between the atomistic and coarse-grained resolution; this subject is treated in the next section.
-\section{Calculation of $\mu$}
-In Ref.\cite{prx} it has been shown that the chemical potential of the atomistic and coarse-grained resolution are related by the following formula: 
+Within this framework it was finally shown that the sum of work of ${\vect F}_{th}({\vect r})$ and that of the thermostat corresponds to the difference in chemical potential between the atomistic and coarse-grained resolution; this subject is treated in the next section.
+
+\section{Calculation of Excess Chemical Potential}
+
+In Ref.~\cite{prx} it has been shown that the chemical potential of the atomistic and coarse-grained resolution are related by the following formula: 
 \begin{equation}
-\mu_{CG}=\mu_{AT}+\omega_{th}+\omega_{Q}
+\mu_{\CG}=\mu_{\AT}+\omega_{\thf}+\omega_{\thermo}
 \label{mu}
 \end{equation}
- with $\mu_{CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{AT}$  the chemical potential of the atomistic system, $\omega_{th}=\int_{\Delta}{\bf F}_{th}({\bf r})d{\bf r}$ the work of the thermodynamic force in the transition region, $\omega_{Q}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region.
-$\omega_{Q}$ is composed by two parts, one, called $\omega_{extra}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{DOF}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-\recheck{ While the determination of $\omega_{DOF}$ is not required for the our final aim (that is the calcualtion of the excess chemical potential, as explain later on), the calculation of $\omega_{Q}$ is very relevant.
+with $\mu_{\CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{\AT}$  the chemical potential of the atomistic system, $\omega_{\thf}=\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}$ the work of the thermodynamic force in the transition region, $\omega_{\thermo}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region.
+$\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
+{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calcualtion of the excess chemical potential, as explain later on), the calculation of $\omega_{\thermo}$ is very relevant.
 However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in AdResS.
-\recheck{In the Hamiltonian approach we have the same equilibrium of the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{Q}$ (further details about this point are given in the Appendix)}.
-Moreover we have proven numerically, for the case of liquid water, that $\omega_{extra}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$, where $V_{AT}$ and $V_{CG}$ are the atomistic and coarse-grained potential.
+\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the Appendix)}.
+Moreover we have proven numerically, for the case of liquid water, that
+  $\omega_{\ext}=\int_{\Delta}\nabla w(\vect r)\langle w( U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$,
+  where $U_{AT}$ and $U_{CG}$ are the atomistic and coarse-grained potential. 
   \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
 the probability distribution of the system as defined in Eq.\ref{order}}.
-The result above implies that $\omega_{Q}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
-\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxilary Hamiltonian  has been recently proposed and applied to mixtures  by Potestio {\it et al.} \cite{h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
-At this point according to \eqref{mu}, if one knows $\mu_{CG}$, then  GC-AdResS can automatically provide $\mu_{AT}$.
-However we need to do one step more, in fact the quantity of interest is not the total chemical potential, but the excess chemical potential $\mu^{ex}_{AT}$ which corresponds to the expression of \eqref{mu} where the kinetic (ideal gas) part is subtracted.
-Regarding the kinetic part, one can notice that the contribution coming from the center of mass is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
-The kinetic part of $\mu_{AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{DOF}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
-However such a calcualtion may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the technical set up of AdResS considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
+
+The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
+\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and \bluec{applied to model pure and mixture systems} by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
+At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$.
+However we need to do one step more, in fact the quantity of interest is not the total chemical potential, but the excess chemical potential $\mu^{\exc}_{\AT}$ which corresponds to the expression of \eqref{mu} where the kinetic (ideal gas) part is subtracted.
+Regarding the kinetic part, one can notice that the contribution coming from the COM is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
+The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
+However such a calcualtion may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
 Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference.
-Finally, the calculation of $\mu^{ex}_{CG}$ can be done with standard methods, TI or IPM, which for simple spherical molecules, like those of the coarse-grained system, requires a negligible computational cost.
+Finally, the calculation of $\mu^{\exc}_{\CG}$ can be done with standard methods, TI or IPM, which for simple spherical molecules, like those of the coarse-grained system, requires a negligible computational cost.
 In conclusion, we have the final expression:
 \begin{equation}
-\mu^{ex}_{AT}=\mu^{ex}_{CG}-\int_{\Delta}{F}_{th}({\bf r})d{\bf r}-\int_{\Delta}\langle w\nabla_{x} w(x) (V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}
+  \mu^{\exc}_{\AT}=
+  \mu^{\exc}_{\CG}-
+  \int_{\Delta}{F}_{th}({\vect r})d{\vect r}-
+  \int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}
 \label{finalmu}
 \end{equation}
-\section*{Analytic eriviation of the $w_{extra}$}
-\recheck{In this section we derive analytically the equivalence: $\omega_{extra}=\int_{\Delta}\langle w\nabla_{x} w(x)( V_{AT}-V_{CG})\rangle_{\bf r} d{\bf r}$ and define its limitations.\\
+
+\section{Analytic Deriviation of the $w_{\ext}$}
+{In this section we derive analytically the equivalence:
+  $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its limitations.
 We define a potential coupling the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
 \begin{align}
-  V =
+  U =
   \sum_{i<j} w(\vect r_i) w(\vect r_j)
-  V^\AT_{i,j}
+  U^\AT_{i,j}
   +
   \sum_{i<j}[1- w(\vect r_i) w(\vect r_j)]
-  V^\CG_{i,j},
+  U^\CG_{i,j},
 \end{align}
-where  $\vect r_i$ denotes
-the center-of-mass (COM) position of the molecule with index $i$.
-$V^\AT_{i,j}$ and $V^\CG_{i,j}$ are the atomistic and coarse-grained interaction potential between molecule $i$ and $j$, respectively, with:
-\begin{align}
-  V^\AT_{i,j} =
-  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta),\quad
-  V^\CG_{i,j} =
-  V^\CG(\vect r_i - \vect r_j).
+where $U^\AT_{i,j}$ and $U^\CG_{i,j}$ are the atomistic and coarse-grained interaction potential between molecule $i$ and $j$, respectively, defined by
+\begin{align}\label{eqn:pot-interpol}
+  U^\AT_{i,j} =
+  \sum_{\alpha\in i}\sum_{\beta\in j} U^\AT(\vect r_\alpha - \vect r_\beta),\quad
+  U^\CG_{i,j} =
+  U^\CG(\vect r_i - \vect r_j),
 \end{align}
 where index $\alpha$ and $\beta$ denotes the atom position of the corresponding molecule.
-The center of mass of the molecule is defined as:
+The COM of the molecule is defined as:
 \begin{align}
@@
 where $m_\alpha$ is the mass of atom $\alpha$.
-The
-corresponding intermolecular force is given by:
+\recheck{The potential interpolation~\eqref{eqn:pot-interpol} provides an auxiliary Hamiltonian to the AdResS system, and
+the
+corresponding intermolecular force is given by:}
 \begin{align}\label{eqn:interpol-f}
@@
   -
-  \nabla w(\vect r_i) w(\vect r_j)
-  (V^\AT_{i,j} - V^\CG_{i,j})
+  \nabla_{\vect r} w(\vect r_i) w(\vect r_j)
+  (U^\AT_{i,j} - U^\CG_{i,j}).
 \end{align}
-We define the force of changing representation:
+\recheck{We refer to the AdResS simulation using force scheme~\eqref{eqn:interpol-f} as
+  auxiliary Hamiltonian AdResS, and all properties of this approach will be added a superscript ``H''}.
+We define the force of changing representation by
 \begin{align}\label{eqn:frep}
   \vect F_{\res,i} = 
-  \sum_j \nabla w(\vect r_i) w(\vect r_j)
-  (V^\AT_{i,j} - V^\CG_{i,j})
+  \sum_j \nabla_{\vect r} w(\vect r_i) w(\vect r_j)
+  (U^\AT_{i,j} - U^\CG_{i,j}).
 \end{align}
@@
 are denoted by $(N_1, V_1, T)$ and $(N_3, V_3, T)$, respectively.
-We assume that the hybrid region is an infinitely thin filter (that is a much smaller region than the atomistic and coarse-grained region) that allows molecules
+We assume that the transition region is an infinitely thin filter (that is a much smaller region than the atomistic and coarse-grained region) that allows molecules
 to change resolution as they cross it. Therefore, it is 
@@
 assumptions as those listed in Sec.III.C of Ref.~\cite{prx},
-i.e. we assume to be in the thermodynamic limit, and molecules are short-range
+i.e. we assume the system to be in the thermodynamic limit, and molecules are short-range
 correlated (short-ranged must be intended as a range comparable to the size of the filter).
-The thermodynamic force for GC-AdResS ($\vect F_\thf$) and for the approach with the auxiliary Hamiltonian ($\vect F^\hadress_\thf$, i.e.
-potential interpolation AdResS),
+The thermodynamic force for GC-AdResS ($\vect F_\thf$) \recheck{and for the auxiliary Hamiltonian AdResS ($\vect F^\hadress_\thf$),}
 enforce the system to have a flat density:
@@
 Where $\rho_0$ is the equilibrium number density of the system defined by $\rho_0 = N/V$.
-\
-As shown in Refs.\cite{prl12, prx} $\vect F_\thf$ provides the
+As shown in Refs.\cite{prl12, prx}, $\vect F_\thf$ provides the
 balance of the grand potential or equivalently
@@
 \end{align}
-where $p$ denotes the pressure, and $ \omega_\thf$ denotes the
-integral of the thermodynamic force.} \\
+where $ \omega_\thf$ denotes the integral of the thermodynamic force $\vect F_\thf$. \\
 
-Instead when we consider the auxiliary Hamiltonian approach,  the force of changing representation is not
-symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
+Instead when we consider the auxiliary Hamiltonian approach, the third part of the R.H.S.~of Eq.~\eqref{eqn:interpol-f} is not
+symmetric w.r.t molecule $i$ and $j$, therefore, the Newton's
 action-reaction law (momentum conservation) does not hold anymore.
@@
 resolution~\eqref{eqn:peq} does not hold anymore and should be derived again.
-Now assume, for simplicity, that the system changes resolution only along the $x$ direction.
+Now assume, \recheck{for simplicity and without lost of generality}, that the system changes resolution only along the $x$ direction.
 We impose an infinitesimal increment of the volume $\Delta V$ to the
 AT region, and apply the same decrement of the volume $-\Delta V$ to the CG
-region.  The volume of the hybrid region is kept constant as if an ideal ``piston'' moves toward the CG region by an amount $\Delta L$.
+region.  The volume of the transition region is kept constant as if an ideal ``piston'' moves toward the CG region by an amount $\Delta L$.
 We assume $\Delta V = \Delta L\cdot S$, where $S$ is the
 cutting surface area.
-For infinitesimal displacement , $\Delta L$, we mean a displacement which is much smaller than the size of the
-hybrid region. This is achievable by taking the limit of $\Delta L\rightarrow 0$,
+The displacement $\Delta L$ should be infinitesimal, i.e.~much smaller than the size of the
+transition region. This is achievable by taking the limit of $\Delta L\rightarrow 0$,
 while keeping the system size fixed.
@@
 the resolution of the molecules remains the same under a displacement of $\Delta L$.
-Therefore, the change of the free energy of the system is
+Therefore, the change of the free energy of the system is \recheck{approximately}:
 \begin{align}\nonumber
@@
   &+
-  \int d r\, \rho_0 S\cdot \Delta L\cdot
-  \vect F^\hadress_\thf(r)
+  \int_\Delta d \vect r\, \rho_0 S\cdot \Delta L\cdot
+  \big[\vect F^\hadress_\thf(\vect r)
   -
-  \int d r\, \rho_0 S\cdot \Delta L\cdot
-  \big\langle \vect F_\res(r)\big\rangle
+  \big\langle \vect F_\res(\vect r)\big\rangle\,\big]
 \end{align}
-where $A_\AT$ and $A_\CG$ is the free energy of the AT and CG region, respectively \recheck{HAN: why is it justified to split the free energy in free energies of subsystems and why the free energy of the HYB region is only the work and not also its kinetic component.
+where $A_\AT$ and $A_\CG$ are the free energies of the AT and CG region, respectively.
+\recheck{Since the system is in the thermodynamic limit, and the interactions in the system are short-ranged,
+  the total free energy has the above splitting form.}
+% \recheck{HAN: why is it justified to split the free energy in free energies of subsystems and why the free energy of the HYB region is only the work and not also its kinetic component.
 I understand that since the molecule do not change resolution, their kinetic part stays the same and thus the difference is zero.
 However this formula needs either a reference or few more explanations}.
-$N_1$ and $N_3$ is the number of molecules in the AT and CG region, and
-$V_1$ and $V_3$ is the volume in the AT and CG region, respectively. $T$ is the temperature
+$N_1$ and $N_3$ are the numbers of molecules in the AT and CG region, and
+$V_1$ and $V_3$ are the volumes in the AT and CG region, respectively. $T$ is the temperature
 of the system.
@@
 The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
-It is straightforward to show that \recheck{HAN, here it must be shown} 
+It is straightforward to show that \recheck{HAN, here it must be shown} \bluec{No, who cannot derive it should be sent back to the graduate course of thermodynamics.} 
 \begin{align}\label{eqn:peq-d}
@@
 \end{align}
-where $w_\thf^\hadress$ is the integral of the potential interpolation
+where $w_\thf^\hadress$ is the integral of the 
 thermodynamic force $\vect F_\thf^\hadress$, and
@@
   \omega_\res
-  = \int_\HY d r\,\langle \vect F_\res (r)\rangle
-  = \int_\HY d r\,\nabla\omega(r)\,
-  \big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+  = \int_\HY d \vect r\,\langle \vect F_\res (\vect r)\rangle
+  = \int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
+  \big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
 \end{align}
-The average is taken over all possible positions of the second molecule
-in the pairwise interaction. In case of molecules that contain
+\recheck{The average is taken over all possible positions of the second molecule, provided the position of the first molecule
+in the pairwise interaction}. In case of molecules that contain
 more than one atom, the averge is also taken over all possible
 conformations of the molecules. 
-By using the same argument as the Section III.C of Ref.~\cite{prx} \recheck{Han, which ones?}, we can
-show that in the thermodynamic limit, the equilibrium volume of the AT region maxiimize the
+% By using the same argument as the Section III.C of Ref.~\cite{prx} \recheck{Han, which ones?}, we can
+% show that
+\bluec{here since we have the auxiliary Hamiltonian, then the system can be treated by the conclusions
+  that can be found in standard thermodynamic text books. If the referee does not understand, he should
+be sent back to the graduate cource. }
+In the thermodynamic limit, the equilibrium volume of the AT region maxiimize the
 free energy, i.e.~$\Delta A / \Delta V
@@
 \end{align}
-which relates the thermodynamic force of the potential interpolation
-and force interpolation AdResS.\\
+which relates the thermodynamic force of the auxiliary Hamiltonian AdResS
+and the GC-AdResS.\\
 
@@
 \end{align}
-The same argument can be applied to the potential interpolation approach,
+The same argument can be applied to the auxiliary Hamiltonian approach,
 and yields  the chemical potential difference between the AT and CG resolutions
@@
 \end{align}
-Since we have an auxiliary Hamiltonian, by using the the potential
-interpolation, we do not have the term $w_\ext$ in the above
+Since we have an auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
 fomula.
-By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-d}, we have the
+By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-h}, we have the
 relation
 \begin{align}\label{eqn:hd-rel-2}
-  \omega_\thermo^\ext = \omega^\hadress_\thf - \omega_\thf,
+  \omega_\ext = \omega^\hadress_\thf - \omega_\thf,
 \end{align}
-which also relates the thermodynamic force of the potential interpolation
-and force interpolation AdResS.\\
-\\
+which also relates the thermodynamic force of the auxiliary Hamiltonian AdResS
+and GC-AdResS.\\
 
@@
 \begin{align}
-  \mu_\AT^\ext = \mu_\CG^\ext - \int_\HY dr \vect F_\thf(r)
-  -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
+  \mu_\AT^\exc = \mu_\CG^\exc - \int_\HY d\vect r \vect F_\thf(\vect r)
+-\int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
+\big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+% -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
 \end{align}
-In the next section we apply the procedure to the calculation of the excess chemical potential of several liquids and mixtures.}
-\section*{Results and Discussion}
+In the next section we apply the procedure to the calculation of the excess chemical potential of several liquids and mixtures.
+
+\section{Results and Discussion}
 We have calculated $\mu^{ex}$ for different liquids and mixtures, choosing cases which are representative of a large class of systems.
@@
 Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; we have verified  such a supposed consistency.
-The chemical potential of $i$-th liquid's component in a mixture is calculated as:
+The chemical potential of $k$-th liquid's component in a mixture is calculated as:
 \begin{equation}
-\mu^{ex,i}_{AT}=\mu^{ex,i}_{CG}-\int_{\Delta}{F}^{i}_{th}({\bf r})d{\bf r}-\int_{\Delta}\langle w\nabla_{x_{i}} w(x)(V_{AT}-V_{CG})\rangle_{\bf r}d{\bf r}
+  \mu^{\exc,k}_{\AT}=
+  \mu^{\exc,k}_{\CG}-
+  \int_{\Delta}{\vect F}^k_{\thf}({\vect r})d{\vect r}-
+  \int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r, k} d{\vect r}
+% \mu^{ex,i}_{AT}=\mu^{ex,i}_{CG}-\int_{\Delta}{F}^{i}_{th}({\vect r})d{\vect r}-\int_{\Delta}\langle w\nabla_{x_{i}} w(x)(V_{AT}-V_{CG})\rangle_{\vect r}d{\vect r}
 \label{icomp}
 \end{equation}
-where ${F}^{i}_{th}(x)$ is the thermodynamic force applied to the molecules of the $i$-th component; this assures that, at the given concentration, the density of molecules of species $i$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
-$\nabla_{x_{i}} w(x)$ is the gradient along $x$ (in a rectangular box) applied to the switching function $w(x)$ in the center of mass of molecules of component $i$.
+where ${F}^{k}_{\thf}(x)$ is the thermodynamic force applied to the molecules of the $k$-th component; this assures that, at the given concentration, the density of molecules of species $k$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
+\recheck{The ensemble evarage is taken over the position of the second molecule, provided that the first moelcule is of species $k$, and located at postion $\vect r$}.
+% $\nabla_{x_{i}} w(x)$ is the gradient along $x$ (in a rectangular box) applied to the switching function $w(x)$ in the COM of molecules of component $i$.
+
 \begin{table}[htpb]
@@
 \end{figure}
+
 In essence, according to the results obtained, GC-AdResS allows an on-the-fly determination of $\mu^{ex}$ of each component of a liquid, whenever a simulation is performed, without extra computational costs.
@@
 It must be also noticed that the system corresponding to the figures is, among all the system considered, the case where the action of the thermodynamic force and of the thermostat produces the less accurate agreement with the reference data.
+
 \section{Current computational convenience: a critical appraisal}
@@
 
-\section*{Conclusion} 
+\section{Conclusion} 
 We have shown the accuracy of GC-AdResS in calculating the excess chemical potential for a representative class of complex liquids and mixtures. 
@@
 
-\section*{Appendix}
+\appendix
+\section{Technical details of the simulations}
 The potential energy function and the force field parameters for all the molecules
@@
 For both the AdResS and full-atom simulations, the system size was kept same. Below is a table 
-with number of solute molecules, solvent molecules, system dimensions, size of hybrid and atomistic region (in AdResS simulations)
+with number of solute molecules, solvent molecules, system dimensions, size of transition and atomistic region (in AdResS simulations)
 for each system studied. 
@@
 water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.
-\subsection{Auxiliary Hamiltonian: Technical Aspects}
-\recheck{In principle when the auxiliary Hamiltonian approach is used, one can perform microcanonical simulations and thus can avoid the use of a thermostat.
-In this case the thermodynamic force of the auxiliary Hamiltonian does not have any effect of the thermostat and thus its difference from the thermodynamic force of GC-AdResS is exactly the work that the thermostat does in GC-AdResS in order to enforce the falt density profile and thus induced the correct flux of particles which are changing resolution.
-The question is whether the energy is conserved in the auxiliary Hamiltonian approach.
-We have checked that the conservation holds for systems without electrostatics (methane,ethane,propane), thus for such systems the procedure is straightforward.
-Instaed, for systems with electrostatic interactions, even for full atomistic simulations, due to the fact that the force fields are designed for employing the reaction field method, the energy cannot be conserved and the coupling to a thermostat is required.
-This is a well known problem reported in the manual of Gromacs.
-However, in our case, for both, the auxiliary Hamiltonian and GC-AdResS the energy drift due to the reaction field method is the essentially same because they have equivalent electrostatic interactions, thus the energy drift due to the use of the reaction field method is automatically removed when we consider the difference between the thermodynamic forces of the two approaches, that is the force of changing resolution.}
+
+\section{Technical Aspects of the Auxiliary Hamiltonian AdResS}
+\recheck{In principle when the auxiliary Hamiltonian approach is used,
+  one can perform microcanonical simulations and thus can avoid the
+  use of a thermostat. \bluec{I do not understand the following sentence... cannot revise it
+    plz make it short and clear. thanks..}
+  \bluec{In this case the thermodynamic force of the
+  auxiliary Hamiltonian does not have any effect of the thermostat and
+  thus its difference from the thermodynamic force of GC-AdResS is
+  exactly the work that the thermostat does in GC-AdResS in order to
+  enforce the falt density profile and thus induced the correct flux
+  of particles which are changing resolution.} The question is whether
+  the energy is conserved in the auxiliary Hamiltonian approach. We
+  have checked that the conservation holds for systems without
+  electrostatics (methane,ethane,propane), thus for such systems the
+  procedure is straightforward. Instaed, for systems with
+  electrostatic interactions, even for full atomistic simulations, due
+  to the fact that the force fields are designed for employing the
+  reaction field method, the energy cannot be conserved and the
+  coupling to a thermostat is required. This is a well known problem
+  reported in the manual of Gromacs. However, in our case, for both,
+  the auxiliary Hamiltonian and GC-AdResS the energy drift due to the
+  reaction field method is the essentially same because they have
+  equivalent electrostatic interactions, thus the energy drift due to
+  the use of the reaction field method is automatically removed when
+  we consider the difference between the thermodynamic forces of the
+  two approaches, that is the force of changing resolution.}
 
@@
 J.Zavadlav, M.N.Melo, A.Vicente Cunha, A.H. De Vries ,S.J. Marrink and M.Praprotnik, J.Chem.Th.Comp. DOI:10.1021/ct5001523 (2014)
+\bibitem{h-adress-0}
+R.Potestio, S.Fritsch, P.Espanol, R.Delgado-Buscalioni, K.Kremer, R.Everaers and D.Donadio, Phys.Rev.Lett. {\bf 111}, 060601 (2013)
 \bibitem{h-adress}

### 2014-05-09 integate.weight/app/integrate.cpp
add files to calculate the average

@@ -1,0 +1,154 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include <time.h>
+
+#include "RandomGenerator.h"
+#include "BlockAverage.h"
+#include <boost/program_options.hpp>
+
+namespace po = boost::program_options;
+
+struct WX 
+{
+  double at;
+  double hy;
+  double cg;
+  double rcut;
+  double p0, p1, p2, p3, p4;
+public:
+  WX (const double & at,
+      const double & hy,
+      const double & rc);
+  double value (const double & xx);
+}
+    ;
+
+WX::WX (const double & at_,
+	const double & hy_,
+	const double & rc_)
+{
+  at = at_;
+  hy = hy_;
+  cg = rc_;
+  rcut = rc_;
+  p0 = cg;
+  p1 = p0 + hy - rcut;
+  p2 = p1 + rcut + at + rcut;
+  p3 = p2 + hy - rcut;
+  p4 = p3 + cg;
+}
+
+double
+WX::value (const double & xx)
+{
+  if (xx < p0){
+    return 0;
+  }
+  else if (xx < p1){
+    return .5 - 0.5 * cos( (xx - p0) / (p1 - p0) * 1. *M_PI);
+  }
+  else if (xx < p2){
+    return 1.;
+  }
+  else if (xx < p3){
+    return .5 + 0.5 * cos( (xx - p2) / (p3 - p2) * 1. * M_PI);
+  }
+  else {
+    return 0.;
+  }
+}
+
+void
+sphere (double & x, double & y, double & z)
+{
+  while (1){
+    x = RandomGenerator_MT19937::genrand_real3() - 0.5;
+    y = RandomGenerator_MT19937::genrand_real3() - 0.5;
+    z = RandomGenerator_MT19937::genrand_real3() - 0.5;
+    x *= 2.;
+    y *= 2.;
+    z *= 2.;
+    double r = x*x + y*y + z*z;
+    r = sqrt(r);
+    if (r < 1.) {
+      return;
+    }
+  }
+}
+
+
+
+int main (int argc, char * argv[])
+{
+  double at, hy, cutoff;
+  int nsphere, nposi;
+  
+  po::options_description desc ("Allow options");  
+  desc.add_options()
+      ("help,h", "print this message")
[…]

### 2014-05-09 integate.weight/app/integrate.cpp
better printing of the process

@@ -123,6 +123,10 @@ int main (int argc, char * argv[])
   BlockAverage_acc baposi (1);
 
   for (int ii = 0; ii < nposi; ++ii){
+    if (ii % 100 == 0){
+      printf ("# process: %.1f percent\r", double(double(ii) / double(nposi) * 100.0));
+      fflush (stdout);
+    }
     double posix = RandomGenerator_MT19937::genrand_real1();
     posix *= mywx.p4;
     double w1 = mywx.value (posix);
@@ -143,6 +147,7 @@ int main (int argc, char * argv[])
     basphere.calculate();
     baposi.deposite (basphere.getAvg());
   }
+  printf ("\n");
 
   baposi.calculate();
 

### 2014-05-10 writeDown/pub.jcp/chem-pot-jcp.tex
add the prove for the mixture

@@
 %\documentclass[a4paper]{article}
-\usepackage{amsmath,amssymb,amsfonts,latexsym,graphicx}
-\usepackage[dvips]{color}
+\usepackage{amsmath,amssymb,amsfonts,latexsym}
+\usepackage[dvips]{graphicx}
+\usepackage{color}
 \usepackage{indentfirst}
@@
 \newcommand{\dadress}{{\textrm{D}}}
+\newcommand{\typea}{{\textrm{A}}}
+\newcommand{\typeb}{{\textrm{B}}}
 
@@
 \maketitle
-
-\bluec{
-  Unified of terminology:
-  \begin{itemize}
-  \item interface region $\rightarrow$ transition region
-  \item hybrid region $\rightarrow$ transition region
-  \item define COM, change all ``center of mass'' to COM
-  \item change the title of sec.III
-  \item do not be too mean, we cite BOTH of their PRL H-Adress paper...
-  \item some times, it is called GC-AdResS, sometimes original AdResS, sometimes standard AdResS, sometimes force-interpolation AdResS....
-  \item rewrite eq. 4, see if it is OK for you
-  \end{itemize}
-}
 
@@
 with $\mu_{\CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{\AT}$  the chemical potential of the atomistic system, $\omega_{\thf}=\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}$ the work of the thermodynamic force in the transition region, $\omega_{\thermo}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region.
-$\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
+$\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the \bluec{non-conservative interactions} in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
 {While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calcualtion of the excess chemical potential, as explain later on), the calculation of $\omega_{\thermo}$ is very relevant.
@@
 
-\section{Analytic Deriviation of the $w_{\ext}$}
+\section{Analytic Deriviation of the $w_{\ext}$}\label{sec:tmp4}
 {In this section we derive analytically the equivalence:
@@
 The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
-It is straightforward to show that \recheck{HAN, here it must be shown} \bluec{No, who cannot derive it should be sent back to the graduate course of thermodynamics.} 
+It is straightforward to show that
+% \recheck{HAN, here it must be shown} \bluec{No, who cannot derive it should be sent back to the graduate course of thermodynamics.} 
 \begin{align}\label{eqn:peq-d}
@@
   = \int_\HY d \vect r\,\langle \vect F_\res (\vect r)\rangle
-  = \int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
-  \big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+  = \int_\HY d \vect r\,\nabla_{\vect r}w(\vect r)\,
+  \big\langle w(\vect r')\,
+  [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
 \end{align}
-\recheck{The average is taken over all possible positions of the second molecule, provided the position of the first molecule
-in the pairwise interaction}. In case of molecules that contain
+\bluec{The average is taken over all
+  possible positions of the second molecule (i.e.~$\vect r'$),
+  provided the position of the first molecule (i.e.~$\vect r$)
+  in the pairwise interaction.
+In case of molecules that contain
 more than one atom, the averge is also taken over all possible
-conformations of the molecules. 
+conformations in the atomistic resolution.}
 % By using the same argument as the Section III.C of Ref.~\cite{prx} \recheck{Han, which ones?}, we can
 % show that
-\bluec{here since we have the auxiliary Hamiltonian, then the system can be treated by the conclusions
-  that can be found in standard thermodynamic text books. If the referee does not understand, he should
-be sent back to the graduate cource. }
+% \bluec{here since we have the auxiliary Hamiltonian, then the system can be treated by the conclusions
+%   that can be found in standard thermodynamic text books. If the referee does not understand, he should
+% be sent back to the graduate cource. }
 In the thermodynamic limit, the equilibrium volume of the AT region maxiimize the
@@
 by inserting Eq.~\eqref{eqn:wextra} into \eqref{eqn:mueq-d}, we have
-\begin{align}
+\begin{align}\label{eqn:tmp24}
   \mu_\AT^\exc = \mu_\CG^\exc - \int_\HY d\vect r \vect F_\thf(\vect r)
--\int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
-\big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+-\int_\HY d \vect r\,\nabla_{\vect r}w(\vect r)\,
+\big\langle w(\vect r')\, [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
 % -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
@@
 % \mu^{ex,i}_{AT}=\mu^{ex,i}_{CG}-\int_{\Delta}{F}^{i}_{th}({\vect r})d{\vect r}-\int_{\Delta}\langle w\nabla_{x_{i}} w(x)(V_{AT}-V_{CG})\rangle_{\vect r}d{\vect r}
-\label{icomp}
+\label{eqn:tmp25}
 \end{equation}
@@
 
+\section{Extending the chemical potential expression to multi-component system}
+
+In this section we explain how to extend the chemical potential
+expresstion Eq.~\eqref{eqn:tmp24} for pure system to multi-component
+system, i.e.~\eqref{eqn:tmp25}.
+For simplicity and without lost of generality, we assume that the system
+is composed by two components, and the number of molecules are
+$N^\typea$ and $N^\typeb$, respectively. The superscript ``$\typea$'' and ``$\typeb$'' throughout this section 
+denotes the index of the components.  We further denote the number of 
+molecule $\typea$ in the atomistic, transition, and coarse-grained regions by
+$N^\typea_1$, $N^\typea_2$ and $N^\typea_3$, respectively. While those for type $\typeb$ molecules
+are $N^\typeb_1$, $N^\typeb_2$ and $N^\typeb_3$, respectively.  By
+assuming the transition region is infinitely small comparing with the
+atomistic and coarse-grained regions, we have the following
+constrains:
+\begin{align}
+  V &= V_1 + V_3\\
+  N &= N^\typea + N^\typeb\\
+  N^\typea &= N^\typea_1 + N^\typea_3\\
+  N^\typeb &= N^\typeb_1 + N^\typeb_3
+\end{align}
+By calculating the thermodynamic forces for each of the components, which
+are denoted by $\vect F^\typea_\thf$ and $\vect F^\typeb_\thf$,
+we impose the correct density profile to the system:
+\begin{align}
+  \rho_\HY^\typea &= \rho_\AT^\typea = \rho_\CG^\typea = \rho_0^\typea\\
+  \rho_\HY^\typeb &= \rho_\AT^\typeb = \rho_\CG^\typeb = \rho_0^\typeb
+\end{align}
+These can be achieved by the iterative thermodynamic force scheme for each
+component in the mixture system.\\
+
+Similar to Eq.~\eqref{eqn:peq}, we have for the force interpolation AdResS:
+\begin{align}\label{eqn:peq-d-ab}
+  p_\CG - p_\AT=\rho_0^\typea \omega^\typea_\thf + \rho_0^\typeb \omega^\typeb_\thf
+\end{align}
+Following the same argument in Sec.~\ref{sec:tmp4}, for $\typea$--$\typeb$
+mixture we have
+\begin{align}\label{eqn:peq-h-ab}
+  p_\CG - p_\AT=
+  \rho_0^\typea (\omega^{\typea,\hadress}_\thf - \omega^\typea_\res)
+  +
+  \rho_0^\typeb (\omega^{\typeb,\hadress}_\thf - \omega^\typeb_\res),
+\end{align}
+where the work of change representation for molecule $\typea$ is defined by
+\begin{align}\label{eqn:wrep-split-a}
+  \omega^\typea_\res 
+  &=
+  \omega^{\typea\typea}_\res +\omega^{\typea\typeb}_\res
+  = \int_\HY d\vect r \langle \vect F^{\typea\typea}_\res(\vect r)\rangle
+  + \int_\HY d\vect r \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle,\\
+  \label{eqn:wrep-split-b}
+  \omega^\typeb_\res 
+  &=
+  \omega^{\typeb\typea}_\res +\omega^{\typeb\typeb}_\res
+  = \int_\HY d\vect r \langle \vect F^{\typeb\typea}_\res(\vect r)\rangle
+  + \int_\HY d\vect r \langle \vect F^{\typeb\typeb}_\res(\vect r)\rangle.
+\end{align}
+Here work of changing representation is splitted based on the
+type of interaction, e.g.~$\omega_\res^{\typea\typeb}$ is due to the
+cross interaction between molecule $\typea$ and $\typeb$.
+We have the explicit expressions:
+\begin{align}
+  \langle \vect F^{\typea\typea}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typea\typea}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typea\typea}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typea; \vect r,\typea}\\
+  \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typea\typeb}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typea\typeb}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typeb; \vect r,\typea}\\
+  \langle \vect F^{\typeb\typea}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typeb\typea}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typeb\typea}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typea; \vect r,\typeb}\\
+  \langle \vect F^{\typeb\typeb}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typeb\typeb}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typeb\typeb}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typeb; \vect r,\typeb}
+\end{align}
+The notations are self-explanatory. For example $ U^\AT_{\typea\typeb}$
+denotes the atomistic interaction between molecule $\typea$ and $\typeb$.
+Notation $\langle\cdot\rangle_{\vect r',\typea; \vect r,\typeb}$ denotes the
+ensemble average taken with respect to position $\vect r'$ being molecule
+$\typea$, provided a molecule $\typeb$ taking the postion $\vect r$.
+If the molecules contain more than one atom, then the average is also taken
+over all possible conformations.
+Therefore, the physical meaning of the
+force $\langle \vect F^{\typea\typeb}_\res(\vect r)\rangle$
+is that providing a molecule of type $\typea$ at $\vect r$,
+the averaged force between this atom and all molecule type $\typeb$
+in the system.
+Although we have $U^\AT_{\typea\typeb} = U^\AT_{\typeb\typea}$ and
+$U^\CG_{\typea\typeb} = U^\CG_{\typeb\typea}$, it should
+be noted that we do not have
+$\omega_\res^{\typeb\typea} = \omega_\res^{\typea\typeb}$  in general.
+From Eq.~\eqref{eqn:peq-d-ab}, \eqref{eqn:peq-h-ab},
+\eqref{eqn:wrep-split-a} and \eqref{eqn:wrep-split-b}, we have
+\begin{align}\label{eqn:hd-rel-ab}
+  \rho_0^\typea(\omega_\thf^{\typea,\hadress} - \omega_\thf^\typea
+  - \omega^{\typea\typea}_\res - \omega^{\typea\typeb}_\res)
+  +
+  \rho_0^\typeb(\omega_\thf^{\typeb,\hadress} - \omega_\thf^\typeb
+  - \omega^{\typeb\typea}_\res - \omega^{\typeb\typeb}_\res) = 0
+\end{align}
+
+We denotes the work done by the transition region on the two types
+of molecules by $\omega_0^\typea$ and $\omega_0^\typeb$, respectively.
+To find out the chemical potential difference between AT and CG resolutions,
+the same idea as presented in Sec.III.C of Ref.5 can be extended
+to the two component system. This extension is straightforward and trivial. We do not want
+to write them down, because one can just step-by-step follow the
+deriviation for the one component system, and no new technique is needed.
+In the end, we proved
+\begin{align}\label{eqn:tmpc7}
+  \mu^\typea_\AT(N^\typea_1, N^\typeb_1, V_1, T) &= \mu^\typea_\CG(N^\typea_1, N^\typeb_1, V_1, T) - \omega^\typea_0\\\label{eqn:tmpc8}
+  \mu^\typeb_\AT(N^\typea_1, N^\typeb_1, V_1, T) &= \mu^\typeb_\CG(N^\typea_1, N^\typeb_1, V_1, T) - \omega^\typeb_0
+\end{align}
+Now, $N^\typea_1$ and $N^\typeb_1$ has the meaning of the averaged number of type $\typea$ and
+type $\typeb$ molecules in the atomistic region, respectively.  Under the thermodynamic
+limit, this number maximize the Helmholtz free energy and is the one
+of statistical importance, see more discussions in
+Ref.5. We do not distinguish these notations from
+before, because the exact meaning is clear from the context.
+The meaning of the chemical potential, e.g.~$\mu_\AT^\typea$, is clear:
+it is the free energy increament of inserting one type $\typea$ molecule
+into the infinitely large $\typea$--$\typeb$ mixture.\\
+
+Similar to the pure system, from Eq.~\eqref{eqn:tmpc7} and \eqref{eqn:tmpc8},
+we write down  for the force interpolation AdResS:
+\begin{align}\label{eqn:mueq-d-a}
+ \mu^\typea_\CG - \mu^\typea_\AT &=   \omega^\typea_\thf + \omega^\typea_\dof + \omega^\typea_\ext\\\label{eqn:mueq-d-b}
+ \mu^\typeb_\CG - \mu^\typeb_\AT &=   \omega^\typeb_\thf + \omega^\typeb_\dof + \omega^\typeb_\ext
+\end{align}
+The meaning of $ \omega^\typea_\thf$ and $ \omega^\typeb_\thf$ are clear:
+the integral of the thermodynamic force $\vect F^\typea_\thf$ and
+$\vect F^\typeb_\thf$, respectively. $\omega^\typea_\ext$ is the energy
+dissipation due to molecule $\typea$ that
+changes resolution in the transition region,
+and  $\omega^\typeb_\ext$ is defined similarly.
+The energy dissipation can be further splitted as
+\begin{align}\label{eqn:wextra-split-a}
+  \omega^\typea_\ext& = \omega^{\typea\typea}_\ext + \omega^{\typea\typeb}_\ext\\\label{eqn:wextra-split-b}
+  \omega^\typeb_\ext& = \omega^{\typeb\typea}_\ext + \omega^{\typeb\typeb}_\ext
+\end{align}
+$ \omega^{\typea\typea}_\ext$ is the energy dissipation of a molecule
+$\typea$ produced by only non-conservative interactions between
+molecule type $\typea$ and type $\typea$.
+While $\omega^{\typea\typeb}_\ext$ is
+the energy dissipation of a molecule $\typea$
+due to the non-conservative cross interaction between
+type $\typea$ and $\typeb$.  The defintions are similar for $
+\omega^{\typeb\typea}_\ext$ and $ \omega^{\typeb\typeb}_\ext$.
+It should be noticed that, we do not have
+$\omega^{\typeb\typea}_\ext = \omega^{\typea\typeb}_\ext$ in gneneral.
+The same argument is applied to the auxiliary Hamiltonian approach, and
+yields
+\begin{align}\label{eqn:mueq-h-a}
+ \mu^\typea_\CG - \mu^\typea_\AT &=   \omega^{\typea,\hadress}_\thf + \omega^\typea_\dof \\\label{eqn:mueq-h-b}
+ \mu^\typeb_\CG - \mu^\typeb_\AT &=   \omega^{\typeb,\hadress}_\thf + \omega^\typeb_\dof
+\end{align}
+By using Eq.~\eqref{eqn:mueq-d-a}, \eqref{eqn:wextra-split-a} and \eqref{eqn:mueq-h-a}, we have
+\begin{align}\label{eqn:hd-rel-2-a}
+  \omega^{\typea\typea}_\ext + \omega^{\typea\typeb}_\ext
+  = \omega^{\typea,\hadress}_\thf - \omega^\typea_\thf.
+\end{align}
+Using Eq.~\eqref{eqn:mueq-d-b}, \eqref{eqn:wextra-split-b} and \eqref{eqn:mueq-h-b}, we have
+\begin{align}\label{eqn:hd-rel-2-b}
+  \omega^{\typeb\typea}_\ext + \omega^{\typeb\typeb}_\ext
+  = \omega^{\typeb,\hadress}_\thf - \omega^\typeb_\thf.
+\end{align}
+
+By inserting Eq.~\eqref{eqn:hd-rel-2-a} and \eqref{eqn:hd-rel-2-b} into
+Eq.~\eqref{eqn:hd-rel-ab}, we have
+\begin{align}\label{eqn:hd-rel-ab-1}
+  \rho_0^\typea(\omega_\ext^{\typea\typea} + \omega_\ext^{\typea\typeb}
+  - \omega^{\typea\typea}_\res - \omega^{\typea\typeb}_\res)
+  +
+  \rho_0^\typeb(\omega_\ext^{\typeb\typea} + \omega_\ext^{\typeb\typeb}
+  - \omega^{\typeb\typea}_\res - \omega^{\typeb\typeb}_\res) = 0
+\end{align}
+It is very easy to identify
+$\omega_\ext^{\typea\typea} = \omega_\res^{\typea\typea} $  and
+because  these two terms exclusively
+involves $\typea$--$\typea$ interaction.
+The same is true for $\typeb$--$\typeb$ interaction:
+$\omega_\ext^{\typeb\typeb} = \omega_\res^{\typeb\typeb} $.
+From the physical meaning of $\omega_\ext^{\typea\typeb}$,
+$\omega_\res^{\typea\typeb}$, $\omega_\ext^{\typeb\typea}$ and
+$\omega_\res^{\typeb\typea}$, it is the most natural way to further
+identify $\omega_\ext^{\typea\typeb} = \omega_\res^{\typea\typeb}$
+and $\omega_\ext^{\typeb\typea}=\omega_\res^{\typeb\typea}$.
+In summary, we prove the extension of chemical potential expression
+for multi-component system, i.e.~Eq.~\eqref{eqn:tmp25}.
+
 \begin{thebibliography}{24}

### 2014-05-11 writeDown/pub.jcp/chem-pot-jcp.tex
Luigi's revise

--- 2014-05-08 writeDown/pub.jcp/chem-pot-jcp.tex
@@
 
-\bluec{
-  Unified of terminology:
-  \begin{itemize}
-  \item interface region $\rightarrow$ transition region
-  \item hybrid region $\rightarrow$ transition region
-  \item define COM, change all ``center of mass'' to COM
-  \item change the title of sec.III
-  \item do not be too mean, we cite BOTH of their PRL H-Adress paper...
-  \item some times, it is called GC-AdResS, sometimes original AdResS, sometimes standard AdResS, sometimes force-interpolation AdResS....
-  \item rewrite eq. 4, see if it is OK for you
-  \end{itemize}
-}
-
 \section{Introduction}
@@
 \recheck{Moreover, in recent work AdResS has been merged with the MARTINI force field \cite{matej-sw1,matej-sw2}.
-In this context, the possibility of having a quantity like the chemical potential under \bluec{what is ``explicit control''} can be used as a further argument for the validity of the method in applications to large systems of biological interest.}
+In this context, the possibility of checking the consistency of a quantity like the chemical potential can be used as a further argument for the validity of the method in applications to large systems of biological interest.}
 Below we provide the basic technical ingredients of GC-AdResS which are relevant for the calculation of the chemical potential, more specific details can be found in~\cite{jctchan, prx}.
@@
 the transition (hybrid) region $\Delta$, where the switching function
-$w(x)$ (in green.
-\recheck{Here the space is devided in $x$ direction, so it is a function of only $x$.}) is defined, and the region on the left, is the high resolution region (atomistic).
+$w(x)$ (in green) is defined, and the region on the left, is the high resolution region (atomistic).
 It must be noticed that differently from the original AdResS, in GC-AdResS the range of definition of $w(x)$ is extended of an amount of ${\vect R}_{c}$.
@@
 The consequence is that molecules in the atomistic region interact with the rest of the system always and only via well defined atomistic interactions.
-This characteristic, in turn, allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a Grand-Canonical fashion.\label{fig1}}
+This characteristic, in turn, allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a Grand-Canonical fashion \recheck{(see Eq.12 of Ref.\cite{prx})}}.
+\label{fig1}
 \end{figure} 
@@
 with $\mu_{\CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{\AT}$  the chemical potential of the atomistic system, $\omega_{\thf}=\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}$ the work of the thermodynamic force in the transition region, $\omega_{\thermo}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region.
-$\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the change of interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calcualtion of the excess chemical potential, as explain later on), the calculation of $\omega_{\thermo}$ is very relevant.
+$\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
+\recheck{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
 However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS.
-Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in AdResS.
+Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS.
 \recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the Appendix)}.
@@
   where $U_{AT}$ and $U_{CG}$ are the atomistic and coarse-grained potential.
+\recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation.
+In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the Appendix)}.
   \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
@@
 The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
-\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and \bluec{applied to model pure and mixture systems} by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
+\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids ad mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
 At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$.
@@
 The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
-However such a calcualtion may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
+However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
 Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference.
@@
 
-\section{Analytic Deriviation of the $w_{\ext}$}
-{In this section we derive analytically the equivalence:
-  $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its limitations.
+\section{Analytic Derivation of the $w_{\ext}$}\label{sec:tmp4}
+\recheck{In this section we derive analytically the equivalence:
+  $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its conceptual limitations.
 We define a potential coupling the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
@@
 \end{align}
-%An important fact is that the force of changing representation is not
-%symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
-%action-reaction law (momentum conservation) does not hold anymore for
-%the potential interpolation approach. On the other hand, the force
-%interpolation scheme does not preserve
-%energy, while the potential interpolation
-%approach has the advantage of energy conservation. In sum, both the
-%force and potential interpolation approaches do not hold all physical
-%conservation laws, because the hybrid region is artificially
-%designed. Therefore, we will take the advantage of both and
-%develop the thermodynamic relation (between the atomistic and
-%coarse-grained resolutions)  for them at the same time.\\
 
@@
 i.e. we assume the system to be in the thermodynamic limit, and molecules are short-range
-correlated (short-ranged must be intended as a range comparable to the size of the filter).
-The thermodynamic force for GC-AdResS ($\vect F_\thf$) \recheck{and for the auxiliary Hamiltonian AdResS ($\vect F^\hadress_\thf$),}
+correlated (short-ranged must be intended as a range comparable to the size of the transition region).
+The thermodynamic force for GC-AdResS ($\vect F_\thf$) and for the auxiliary Hamiltonian AdResS ($\vect F^\hadress_\thf$),
 enforce the system to have a flat density:
@@
 
-Instead when we consider the auxiliary Hamiltonian approach, the third part of the R.H.S.~of Eq.~\eqref{eqn:interpol-f} is not
+Instead when we consider the auxiliary Hamiltonian approach, the third term on the R.H.S.~of Eq.~\eqref{eqn:interpol-f} is not
 symmetric w.r.t molecule $i$ and $j$, therefore, the Newton's
@@
 the resolution of the molecules remains the same under a displacement of $\Delta L$.
-Therefore, the change of the free energy of the system is \recheck{approximately}:
+Therefore, the change of the free energy of the system is approximately:
 \begin{align}\nonumber
@@
 where $A_\AT$ and $A_\CG$ are the free energies of the AT and CG region, respectively.
-\recheck{Since the system is in the thermodynamic limit, and the interactions in the system are short-ranged,
-  the total free energy has the above splitting form.}
-% \recheck{HAN: why is it justified to split the free energy in free energies of subsystems and why the free energy of the HYB region is only the work and not also its kinetic component.
-I understand that since the molecule do not change resolution, their kinetic part stays the same and thus the difference is zero.
-However this formula needs either a reference or few more explanations}.
-$N_1$ and $N_3$ are the numbers of molecules in the AT and CG region, and
-$V_1$ and $V_3$ are the volumes in the AT and CG region, respectively. $T$ is the temperature
+The expression of Eq.\ref{eqn:apptmp3} as a sum of different terms is justified by the hypothesis of treating the system in the thermodynamic limit, and by the hypothesis that the interactions are short-ranged compared to the size of the transition region.
+$N_1$ and $N_3$ is the numbers of molecules in the AT and CG region, and
+$V_1$ and $V_3$ is the volume in the AT and CG region, respectively; $T$ is the temperature
 of the system.
-The last term comes from the work done on the piston. It is composed by
-two parts, the first is the work done by the thermodynamic force, and the
-second is due to 
-the force of changing representation, which does not vanish due to the breaking of the Newton's
-action-reaction law. The first and second part of Eq.~\eqref{eqn:interpol-f}
-do not contribute, because they obey the Newton's action-reaction law, so
-their total work is zero as long as the transition region move infinitesimally in one direction.
-The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
-It is straightforward to show that \recheck{HAN, here it must be shown} \bluec{No, who cannot derive it should be sent back to the graduate course of thermodynamics.} 
+The last term is originated by the work done of the ideal piston. This latter is composed by
+two parts, the first corresponding to the work done by the thermodynamic force, and the
+second corresponding to 
+the work done by the force of changing representation (which does not vanish due to the violation of the Newton's
+action-reaction law). The first and second term of Eq.~\eqref{eqn:interpol-f}
+being forces based on pairwise interactions only, do not contribute to the difference of energy; in fact 
+their total work is zero (as long as the transition region move infinitesimally along $x$).
+The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble average.
+It is straightforward to show that
 \begin{align}\label{eqn:peq-d}
@@
   = \int_\HY d \vect r\,\langle \vect F_\res (\vect r)\rangle
-  = \int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
-  \big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+  = \int_\HY d \vect r\,\nabla_{\vect r}w(\vect r)\,
+  \big\langle w(\vect r')\,
+  [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
 \end{align}
-\recheck{The average is taken over all possible positions of the second molecule, provided the position of the first molecule
-in the pairwise interaction}. In case of molecules that contain
-more than one atom, the averge is also taken over all possible
-conformations of the molecules. 
-% By using the same argument as the Section III.C of Ref.~\cite{prx} \recheck{Han, which ones?}, we can
-% show that
-\bluec{here since we have the auxiliary Hamiltonian, then the system can be treated by the conclusions
-  that can be found in standard thermodynamic text books. If the referee does not understand, he should
-be sent back to the graduate cource. }
-In the thermodynamic limit, the equilibrium volume of the AT region maxiimize the
+The average is performed over all
+  possible positions of the second molecule (i.e.~$\vect r'$),
+  at fixed position of the first molecule (i.e.~$\vect r$) 
+  in the pairwise interaction.
+In case of molecules containing
+more than one atom, the average is also made over all possible
+conformations in the atomistic resolution.
+In the thermodynamic limit, the equilibrium volume of the AT region maximize the
 free energy, i.e.~$\Delta A / \Delta V
@@
 \end{align}
-Comparing with the result of the standard GC-AdResS~Eq.~\eqref{eqn:peq},
+Comparing the expression above with that obtained for GC-AdResS~(Eq.~\eqref{eqn:peq}),
 we have: 
@@
 \end{align}
-Since we have an auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
-fomula.
+In the auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
+formula (being this latter, in GC-AdResS, generated by the non conservative effect of the force interpolation).
 By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-h}, we have the
@@
 ensemble of the system treated with the potential interpolation approach, and the question is if the ensemble average is equivalent if it is performed in the simulation where the force
-interpolation approach is used.  It is obvious that the phase spatial probability distribution correponding to the system treated with the potential interpolation is consistent with the force
+interpolation approach is used.  It is obvious that the spatial probability distribution corresponding to the system treated with the potential interpolation is consistent with the force
 interpolation at least up to the 1st order as defined in Eq.\ref{order}.  It is also
-possbile to systematically obtain equivalence in the ensemble average operation  at higher orders of accuracy of the probability distribution, as, for example, it is done for the radial distribution function in Ref.~\cite{jctchan}.
+possible to systematically obtain equivalence in the ensemble average operation  at higher orders of accuracy of the probability distribution, as, for example, it is done for the radial distribution function in Ref.~\cite{jctchan}.
 However, here we do not consider higher order corrections, because it
@@
 calculate $\omega_\ext$, and measure the ensemble average by the
-standard AdResS.  Since in the computer implementation, the CG
-molecules also keep the atomistic degrees of freedom eventhough they
+standard AdResS.  As previously reported, in the computer implementation, the CG
+molecules also keep the atomistic degrees of freedom even though they
 are in the CG region, therefore, the kinetic part of $\mu_\AT$ and
@@
 by inserting Eq.~\eqref{eqn:wextra} into \eqref{eqn:mueq-d}, we have
-\begin{align}
+\begin{align}\label{eqn:tmp24}
   \mu_\AT^\exc = \mu_\CG^\exc - \int_\HY d\vect r \vect F_\thf(\vect r)
--\int_\HY d \vect r\,\nabla_{\vect r}\omega(\vect r)\,
-\big\langle \omega(\vect r')\, [U^\AT(\vect r-\vect r') - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+-\int_\HY d \vect r\,\nabla_{\vect r}w(\vect r)\,
+\big\langle w(\vect r')\, [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
 % -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
 \end{align}
-In the next section we apply the procedure to the calculation of the excess chemical potential of several liquids and mixtures.
+The extension of Eq.\ref{eqn:tmp24} to multicomponent systems is reported in the Appendix, while in the next section we apply the method to the calculation of $\mu^{ex}$ to liquids and mixtures.}
 
@@
 Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; we have verified  such a supposed consistency.
-The chemical potential of $k$-th liquid's component in a mixture is calculated as:
+The chemical potential of $k$-th liquid's component in a mixture is calculated as \recheck{(see Appendix)}:
 \begin{equation}
@@
 % \mu^{ex,i}_{AT}=\mu^{ex,i}_{CG}-\int_{\Delta}{F}^{i}_{th}({\vect r})d{\vect r}-\int_{\Delta}\langle w\nabla_{x_{i}} w(x)(V_{AT}-V_{CG})\rangle_{\vect r}d{\vect r}
-\label{icomp}
+\label{eqn:tmp25}
 \end{equation}
 where ${F}^{k}_{\thf}(x)$ is the thermodynamic force applied to the molecules of the $k$-th component; this assures that, at the given concentration, the density of molecules of species $k$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
-\recheck{The ensemble evarage is taken over the position of the second molecule, provided that the first moelcule is of species $k$, and located at postion $\vect r$}.
+\recheck{The ensemble average is taken over the position of the second molecule, provided that the first molecule is of species $k$, and located at position $\vect r$}.
 % $\nabla_{x_{i}} w(x)$ is the gradient along $x$ (in a rectangular box) applied to the switching function $w(x)$ in the COM of molecules of component $i$.
@@
 However in the successive version of GROMACS 4.6.1 the performance of atomistic simulations (above all of SPC/E water) has been highly improved while the corresponding implementation of AdResS is not optimized yet.
-At the current state, AdResS can only assure a speed up factor between 1.5 and 1.9 for large systems (30000 molecules) compared to full atomistic simulations without SPC/E water.
+At the current state, AdResS can only assure a speed up factor between \recheck{2 and 3} for large systems (30000 molecules) compared to full atomistic simulations \recheck{( for systems without SPC/E water)}.
 As a consequence for the calculation of $\mu^{ex}$, TI is computationally less demanding than AdResS.
@@
 (grant code DE 1140/4-2).H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
+\recheck{We thank Christoph Junghans and Debashish Mukherji for contributing to the information reported in section IV about the speed up factor}.
 
@@
   one can perform microcanonical simulations and thus can avoid the
-  use of a thermostat. \bluec{I do not understand the following sentence... cannot revise it
-    plz make it short and clear. thanks..}
-  \bluec{In this case the thermodynamic force of the
-  auxiliary Hamiltonian does not have any effect of the thermostat and
-  thus its difference from the thermodynamic force of GC-AdResS is
-  exactly the work that the thermostat does in GC-AdResS in order to
-  enforce the falt density profile and thus induced the correct flux
-  of particles which are changing resolution.} The question is whether
+  use of a thermostat. In this case the thermodynamic force of the
+  auxiliary Hamiltonian would not carry any effect of the thermostat and thus the difference between the work of the thermodynamic force of GC-AdResS and that of the auxiliary Hamiltonian is
+  exactly the work that the thermostat does in GC-AdResS in order to compensate energy dissipation. The question is whether
   the energy is conserved in the auxiliary Hamiltonian approach. We
@@
   electrostatics (methane,ethane,propane), thus for such systems the
-  procedure is straightforward. Instaed, for systems with
+  procedure is straightforward. Instead, for systems with
   electrostatic interactions, even for full atomistic simulations, due
@@
   two approaches, that is the force of changing resolution.}
+
+\section{Extension of the chemical potential derivation to multi-component systems}
+
+\recheck{In this section we  extend the chemical potential
+expression of Eq.~\eqref{eqn:tmp24} to multi-component
+systems, i.e. we show the derivation (and limitations) of Eq.~\eqref{eqn:tmp25}.
+For simplicity and without lost of generality, we assume that the system
+is formed by two components $\typea$ and $\typeb$, and the number of molecules are
+$N^\typea$ and $N^\typeb$, respectively.  We further denote the number of 
+molecules $\typea$ in the atomistic, transition, and coarse-grained regions by
+$N^\typea_1$, $N^\typea_2$ and $N^\typea_3$, respectively and equivalently for type $\typeb$, $N^\typeb_1$, $N^\typeb_2$ and $N^\typeb_3$.  By
+assuming, as usual, that the size of the transition region is negligible compared with the
+atomistic and coarse-grained regions, we have the following
+constrains:
+\begin{align}
+  V &= V_1 + V_3\\
+  N &= N^\typea + N^\typeb\\
+  N^\typea &= N^\typea_1 + N^\typea_3\\
+  N^\typeb &= N^\typeb_1 + N^\typeb_3
+\end{align}
+We determine and apply the thermodynamic forces to each component, which
+are denoted by $\vect F^\typea_\thf$ and $\vect F^\typeb_\thf$; thus we  impose the correct density profile to the system:
+\begin{align}
+  \rho_\HY^\typea &= \rho_\AT^\typea = \rho_\CG^\typea = \rho_0^\typea\\
+  \rho_\HY^\typeb &= \rho_\AT^\typeb = \rho_\CG^\typeb = \rho_0^\typeb
+\end{align}
+
+Similarly to Eq.~\eqref{eqn:peq}, for pure systems, for a mixture in GC-AdResS we have:
+\begin{align}\label{eqn:peq-d-ab}
+  p_\CG - p_\AT=\rho_0^\typea \omega^\typea_\thf + \rho_0^\typeb \omega^\typeb_\thf
+\end{align}
+Following the same argument of Sec.~\ref{sec:tmp4}, we have
+\begin{align}\label{eqn:peq-h-ab}
+  p_\CG - p_\AT=
+  \rho_0^\typea (\omega^{\typea,\hadress}_\thf - \omega^\typea_\res)
+  +
+  \rho_0^\typeb (\omega^{\typeb,\hadress}_\thf - \omega^\typeb_\res),
+\end{align}
+where the work of changing representation for molecule $\typea$ is defined by
+\begin{align}\label{eqn:wrep-split-a}
+  \omega^\typea_\res 
+  &=
+  \omega^{\typea\typea}_\res +\omega^{\typea\typeb}_\res
+  = \int_\HY d\vect r \langle \vect F^{\typea\typea}_\res(\vect r)\rangle
+  + \int_\HY d\vect r \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle,\\
+  \label{eqn:wrep-split-b}
+  \omega^\typeb_\res 
+  &=
+  \omega^{\typeb\typea}_\res +\omega^{\typeb\typeb}_\res
+  = \int_\HY d\vect r \langle \vect F^{\typeb\typea}_\res(\vect r)\rangle
+  + \int_\HY d\vect r \langle \vect F^{\typeb\typeb}_\res(\vect r)\rangle.
+\end{align}
+Where ~$\omega_\res^{\typea\typea}$ denotes the work of changing representation for a molecule of $\typea$, due to the interaction with molecules of type $\typea$ only.
+Instead $\omega_\res^{\typea\typeb}$ denotes the work of changing representation for a molecule of $\typea$, due to the interaction with molecules of type $\typeb$ only.
+The same terminology holds for $\omega_\res^{\typeb\typea}$ and $\omega_\res^{\typeb\typeb}$.
+The explicit expressions are:
+\begin{align}
+  \langle \vect F^{\typea\typea}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typea\typea}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typea\typea}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typea; \vect r,\typea}\\
+  \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typea\typeb}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typea\typeb}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typeb; \vect r,\typea}\\
+  \langle \vect F^{\typeb\typea}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typeb\typea}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typeb\typea}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typea; \vect r,\typeb}\\
+  \langle \vect F^{\typeb\typeb}_\res(\vect r)\rangle
+  &=
+  \nabla_{\vect r} w(\vect r)\,
+  \big\langle w(\vect r')
+  \big[\, \sum_{\alpha,\beta} U^\AT_{\typeb\typeb}(\vect r_\alpha- \vect r'_\beta)
+  - U^\CG_{\typeb\typeb}(\vect r- \vect r') \,\big]
+  \big\rangle_{\vect r',\typeb; \vect r,\typeb}
+\end{align}
+The notations are self-explanatory; for example $ U^\AT_{\typea\typeb}$
+denotes the expression for atomistic interactions between a molecule of type $\typea$ and one of type $\typeb$ (similarly $ U^\AT_{\typea\typea}$ and$ U^\AT_{\typeb\typeb}$) while $ U^\CG_{\typea\typeb}$ is the equivalent for coarse-grained interactions.
+Notation $\langle\cdot\rangle_{\vect r',\typeb; \vect r,\typea}$ denotes the
+ensemble average performed with respect to position $\vect r'$ of molecule
+$\typeb$, provided that a molecule $\typea$ takes the position $\vect r$ (the same applies for other combinations on indices ${\vect r'}, {\vect r}, {\typea}, {\typeb}$.
+If molecules contain more than one atom, then the average is also taken
+over all possible conformations.
+Therefore, the physical meaning of (for example) 
+force $\langle \vect F^{\typea\typeb}_\res(\vect r)\rangle$
+is that of an average force at $\vect r$ acting on a molecule of type $\typea$  due to the interaction with molecules of type $\typeb$.
+Although we have $U^\AT_{\typea\typeb} = U^\AT_{\typeb\typea}$ and
+$U^\CG_{\typea\typeb} = U^\CG_{\typeb\typea}$, it should
+be noted that we do not have
+$\omega_\res^{\typeb\typea} = \omega_\res^{\typea\typeb}$  in general.
+From Eq.~\eqref{eqn:peq-d-ab}, \eqref{eqn:peq-h-ab},
+\eqref{eqn:wrep-split-a} and \eqref{eqn:wrep-split-b}, we have
+\begin{align}\label{eqn:hd-rel-ab}
+  \rho_0^\typea(\omega_\thf^{\typea,\hadress} - \omega_\thf^\typea
+  - \omega^{\typea\typea}_\res - \omega^{\typea\typeb}_\res)
+  +
+  \rho_0^\typeb(\omega_\thf^{\typeb,\hadress} - \omega_\thf^\typeb
+  - \omega^{\typeb\typea}_\res - \omega^{\typeb\typeb}_\res) = 0
+\end{align}
+We denote the work done in the transition region on the two types
+of molecules by $\omega_0^\typea$ and $\omega_0^\typeb$, respectively.
+The chemical potential difference between the AT and CG resolution,
+can be derived following the same procedure presented in Sec.III.C of Ref.5 which can be extended
+to the two component system in a straightforward way.
+Such a procedure leads to:
+\begin{align}\label{eqn:tmpc7}
+  \mu^\typea_\AT(N^\typea_1, N^\typeb_1, V_1, T) &= \mu^\typea_\CG(N^\typea_3, N^\typeb_3, V_3, T) - \omega^\typea_0\\\label{eqn:tmpc8}
+  \mu^\typeb_\AT(N^\typea_1, N^\typeb_1, V_1, T) &= \mu^\typeb_\CG(N^\typea_3, N^\typeb_3, V_3, T) - \omega^\typeb_0
+\end{align}
+where, $N^\typea_1$ and $N^\typeb_1$ denote the number of type $\typea$ and
+type $\typeb$ molecules in the atomistic region ($N^\typea_3$ and $N^\typeb_3$ in the CG region instead).  In the thermodynamic
+limit, these numbers maximize the Helmholtz free energy.
+In this context the chemical potential, e.g.~$\mu_\AT^\typea$, is the free energy increment due to the insertion of one molecule of type $\typea$ 
+into the infinitely large $\typea$--$\typeb$ mixture.\\
+Similarly to the case of the one component system, from Eq.~\eqref{eqn:tmpc7} and \eqref{eqn:tmpc8},
+we write down  for GC-AdResS:
+\begin{align}\label{eqn:mueq-d-a}
+ \mu^\typea_\CG - \mu^\typea_\AT &=   \omega^\typea_\thf + \omega^\typea_\dof + \omega^\typea_\ext\\\label{eqn:mueq-d-b}
+ \mu^\typeb_\CG - \mu^\typeb_\AT &=   \omega^\typeb_\thf + \omega^\typeb_\dof + \omega^\typeb_\ext
+\end{align}
+$ \omega^\typea_\thf$ and $ \omega^\typeb_\thf$ are 
+the integral of the thermodynamic force $\vect F^\typea_\thf$ and
+$\vect F^\typeb_\thf$, respectively. $\omega^\typea_\ext$ is the energy
+dissipation due to molecule $\typea$ that
+changes resolution in the transition region,
+and  $\omega^\typeb_\ext$ is defined similarly.
+The energy dissipation can be further divided as:
+\begin{align}\label{eqn:wextra-split-a}
+  \omega^\typea_\ext& = \omega^{\typea\typea}_\ext + \omega^{\typea\typeb}_\ext\\\label{eqn:wextra-split-b}
+  \omega^\typeb_\ext& = \omega^{\typeb\typea}_\ext + \omega^{\typeb\typeb}_\ext
+\end{align}
+$ \omega^{\typea\typea}_\ext$ is the energy dissipation of a molecule
+$\typea$ produced by  non-conservative interactions between
+molecule type $\typea$ and type $\typea$ only.
+Similarly $\omega^{\typea\typeb}_\ext$ is
+the energy dissipation of a molecule $\typea$
+due to the non-conservative interactions with molecules of type $\typeb$.  The definitions are similar for $
+\omega^{\typeb\typea}_\ext$ and $ \omega^{\typeb\typeb}_\ext$.
+It should be noticed that, we do not have
+$\omega^{\typeb\typea}_\ext = \omega^{\typea\typeb}_\ext$ in general.
+For the expression of the chemical potential, the same argument as above, is applied to the auxiliary Hamiltonian approach, and
+yields
+\begin{align}\label{eqn:mueq-h-a}
+ \mu^\typea_\CG - \mu^\typea_\AT &=   \omega^{\typea,\hadress}_\thf + \omega^\typea_\dof \\\label{eqn:mueq-h-b}
+ \mu^\typeb_\CG - \mu^\typeb_\AT &=   \omega^{\typeb,\hadress}_\thf + \omega^\typeb_\dof
+\end{align}
+By using Eq.~\eqref{eqn:mueq-d-a}, \eqref{eqn:wextra-split-a} and \eqref{eqn:mueq-h-a}, we have
+\begin{align}\label{eqn:hd-rel-2-a}
+  \omega^{\typea\typea}_\ext + \omega^{\typea\typeb}_\ext
+  = \omega^{\typea,\hadress}_\thf - \omega^\typea_\thf.
+\end{align}
+Using Eq.~\eqref{eqn:mueq-d-b}, \eqref{eqn:wextra-split-b} and \eqref{eqn:mueq-h-b}, we have
+\begin{align}\label{eqn:hd-rel-2-b}
+  \omega^{\typeb\typea}_\ext + \omega^{\typeb\typeb}_\ext
+  = \omega^{\typeb,\hadress}_\thf - \omega^\typeb_\thf.
+\end{align}
+
+By inserting Eq.~\eqref{eqn:hd-rel-2-a} and \eqref{eqn:hd-rel-2-b} into
+Eq.~\eqref{eqn:hd-rel-ab}, we have
+\begin{align}\label{eqn:hd-rel-ab-1}
+  \rho_0^\typea(\omega_\ext^{\typea\typea} + \omega_\ext^{\typea\typeb}
+  - \omega^{\typea\typea}_\res - \omega^{\typea\typeb}_\res)
+  +
+  \rho_0^\typeb(\omega_\ext^{\typeb\typea} + \omega_\ext^{\typeb\typeb}
+  - \omega^{\typeb\typea}_\res - \omega^{\typeb\typeb}_\res) = 0
+\end{align}
+It is natural to conclude that
+$\omega_\ext^{\typea\typea} = \omega_\res^{\typea\typea} $  
+because  these two terms exclusively
+involves $\typea$--$\typea$ interaction.
+The same is true for $\typeb$--$\typeb$ interaction:
+$\omega_\ext^{\typeb\typeb} = \omega_\res^{\typeb\typeb} $.
+The physical meaning of $\omega_\ext^{\typea\typeb}$,
+$\omega_\res^{\typea\typeb}$, $\omega_\ext^{\typeb\typea}$ and
+$\omega_\res^{\typeb\typea}$, leads to 
+identify $\omega_\ext^{\typea\typeb}$ with $\omega_\res^{\typea\typeb}$
+and $\omega_\ext^{\typeb\typea}=\omega_\res^{\typeb\typea}$.
+It follows that (for example) for component $\typea$:
+\begin{equation}
+\mu^{A}_{CG}-\mu^{A}_{AT}=\int _{\Delta}{\bf F}^{A}_{th}({\bf r})d{\bf r}+\int_{\Delta} \langle \vect F^{\typea\typea}_\res(\vect r)\rangle d{\bf r}+\int_{\Delta} \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle d{\bf r}
+\label{fineq}
+\end{equation}
+ and this proves ~Eq.~\eqref{eqn:tmp25}.}
 

### 2014-05-11 writeDown/pub.jcp/chem-pot-jcp.tex
my revise

@@
 \begin{itemize}
-\item divide the space in three regions, one with atomistic resolution (AT) and one with coarse-grained (spherical) resolution (CG) interfaced by a smaller region with an hybrid treatment, which is usually called transition region or hybrid region.
-\item couple the molecules in the different regions through a spatial interpolation formula on the forces:
+\item Divide the space in three regions, one with atomistic resolution (AT) and one with coarse-grained (spherical) resolution (CG) interfaced by a smaller region with an hybrid treatment, which is usually called transition region or hybrid region.
+\item Couple the molecules in the different regions through a spatial interpolation formula on the forces:
 \begin{equation}
@@
 The thermodynamic force is defined in such a way that
-  $p_{\AT}+\rho_{0}\int_{\Delta}{\vect F}_{th}({\vect r})d{\vect r}=p_{\CG}$,
-  where $p_{AT}$  is the target pressure of the atomistic system (region), $p_{CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)~\cite{prl12}.
+  $p_{\AT}+\rho_{0}\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}=p_{\CG}$,
+  where $p_{\AT}$  is the target pressure of the atomistic system (region), $p_{\CG}$ is the pressure of the coarse-grained model, $\rho_{0}$ is the target molecular density of the atomistic system (region)~\cite{prl12}.
 An additional locally acting thermostat is added to take care of the loss/gain of energy in the transition region.
@@
 \recheck{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
-However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in AdResS.
+However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \bluec{the original} AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS.
-\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the Appendix)}.
+\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the \bluec{Appendix~\ref{app:tmp2}})}.
 Moreover we have proven numerically, for the case of liquid water, that
   $\omega_{\ext}=\int_{\Delta}\nabla w(\vect r)\langle w( U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$,
-  where $U_{AT}$ and $U_{CG}$ are the atomistic and coarse-grained potential.
+  where $U_{\AT}$ and $U_{\CG}$ are the atomistic and coarse-grained potential.
 \recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation.
-In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the Appendix)}.
+In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the \bluec{Appendix~\ref{app:tmp2}})}.
   \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
@@
 The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
-\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids ad mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
+\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids and mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
 At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$.
@@
 The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
-However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway \cite{simon-ch}.
+However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway~\cite{simon-ch}.
 Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference.
@@
   $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its conceptual limitations.
-We define a potential coupling the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
+We consider a potential coupling between the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
 \begin{align}
@@
 \end{align}
-where index $\alpha$ and $\beta$ denotes the atom position of the corresponding molecule.
+where  $\alpha$ and $\beta$ denotes the atom indexes of the corresponding molecule.
 The COM of the molecule is defined as:
@@
 \end{align}
-where $m_\alpha$ is the mass of atom $\alpha$.
+where $m_\alpha$ is the mass of atom $\alpha$ of molecule $i$.
 \recheck{The potential interpolation~\eqref{eqn:pot-interpol} provides an auxiliary Hamiltonian to the AdResS system, and
@@
 As a consequence, the pressure relation between the AT and CG
-resolution~\eqref{eqn:peq} does not hold anymore and should be derived again.
+resolution~\eqref{eqn:peq} does not hold and should be derived again.
 Now assume, \recheck{for simplicity and without lost of generality}, that the system changes resolution only along the $x$ direction.
@@
 AT region, and apply the same decrement of the volume $-\Delta V$ to the CG
-region.  The volume of the transition region is kept constant as if an ideal ``piston'' moves toward the CG region by an amount $\Delta L$.
+region.  The volume of the transition region is kept constant as if it is an ideal ``piston'' that moves toward the CG region by an amount $\Delta L$.
 We assume $\Delta V = \Delta L\cdot S$, where $S$ is the
@@
 while keeping the system size fixed.
-It must be noticed that also the displacements of the molecules are infinitesimal, so that it can be reasonably assumed that
+It must be noticed that also the displacements of the molecules are infinitesimal, so it can be reasonably assumed that
 the resolution of the molecules remains the same under a displacement of $\Delta L$.
@@
 their total work is zero (as long as the transition region move infinitesimally along $x$).
-The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble average.
+The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble average, which
+will be specified soon.
 It is straightforward to show that
@@
 In the auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
-formula (being this latter, in GC-AdResS, generated by the non conservative effect of the force interpolation).
+formula \bluec{(being this latter, in GC-AdResS, generated by the non conservative effect of the force interpolation).}
 By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-h}, we have the
@@
 find the extra work of the thermostat in GC-AdResS being identical to the work of changing
-representation of the Hamiltonian auxiliary approach:
+representation of the auxiliary Hamiltonian approach:
 \begin{align}\label{eqn:wextra}
@@
 interpolation approach is used.  It is obvious that the spatial probability distribution corresponding to the system treated with the potential interpolation is consistent with the force
-interpolation at least up to the 1st order as defined in Eq.\ref{order}.  It is also
+interpolation at least up to the first order.  It is also
 possible to systematically obtain equivalence in the ensemble average operation  at higher orders of accuracy of the probability distribution, as, for example, it is done for the radial distribution function in Ref.~\cite{jctchan}.
@@
 calculate $\omega_\ext$, and measure the ensemble average by the
-standard AdResS.  As previously reported, in the computer implementation, the CG
+standard AdResS.  As previously discussed, in the Gromacs implementation, the CG
 molecules also keep the atomistic degrees of freedom even though they
@@
 \end{align}
-The extension of Eq.\ref{eqn:tmp24} to multicomponent systems is reported in the Appendix, while in the next section we apply the method to the calculation of $\mu^{ex}$ to liquids and mixtures.}
+The extension of Eq.\ref{eqn:tmp24} to multicomponent systems is reported in the Appendix~\ref{app:tmp3}, while in the next section we apply the method to the calculation of $\mu^{ex}$ to liquids and mixtures.}
 
@@
 Moreover, systems as water/urea are commonly used as cosolvent of biological molecules \cite{nico-debashish} while systems as tert-Butyl alcohol/water play a key role in modern technology \cite{irata}, thus they are of high interest {\it per se}.
-All technical details of each simulation are presented in the Appendix.
+All technical details of each simulation are presented in the Appendix~\ref{app:tmp1}.
 Results are reported in Table \ref{table} where the comparison with values obtained using full atomistic TI and available experiments, at the same concentrations, of our calculation is made; in our previous work we have already shown that value of the chemical potential of liquid water obtained with IPM is well reproduced by GC-AdResS, however the computational cost of IMP was very large, thus we do not consider calculations done with IPM in this paper.
@@
 Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; we have verified  such a supposed consistency.
-The chemical potential of $k$-th liquid's component in a mixture is calculated as \recheck{(see Appendix)}:
+The chemical potential of $k$-th liquid's component in a mixture is calculated as \recheck{(see Appendix~\ref{app:tmp3})}:
 \begin{equation}
@@
 \appendix
-\section{Technical details of the simulations}
+\section{Technical details of the simulations}\label{app:tmp1}
 The potential energy function and the force field parameters for all the molecules
@@
 $\lambda$ allow to plot a $\frac{\partial H}{\partial \lambda}$ curve, from which 
-$\mu^{excess}$ is derived \cite{mu}. 
+$\mu^{\exc}$ is derived \cite{mu}. 
 \begin{equation}
- \mu_{iB} - \mu_{iA} = \int_{0}^{1} \left \langle \frac{\partial H}{\partial \lambda} \right \rangle_{\lambda} d\lambda 
+ \mu^\exc_{iB} - \mu^\exc_{iA} = \int_{0}^{1} \left \langle \frac{\partial H}{\partial \lambda} \right \rangle_{\lambda} d\lambda 
 \end{equation}
-where $U_{i}$ is the interaction energy of particle $i$ with the remaining particles and $\langle . \rangle$
+\bluec{where $U_{i}$ is the interaction energy of particle $i$ with the remaining particles} and $\langle \cdot \rangle$
 denotes the canonical (NVT) or isobaric-isothermal (NPT) ensemble average. We computed the excess 
@@
 \end{equation}
-where $\Delta G_{ele}$ is the free energy change associated with introducing the van der Waals interactions and 
-$\Delta G_{vdw}$ is the free energy change associated with introducing Coulomb interactions. 
+where $\Delta G_{vdw}$ is the free energy change associated with introducing the van der Waals interactions and 
+$\Delta G_{ele}$ is the free energy change associated with introducing Coulomb interactions. 
 We evaluated the above integral for 21 values of $\lambda$ (evenly spaced between 0 and 1) in both the procedures.
@@
 
-\section{Technical Aspects of the Auxiliary Hamiltonian AdResS}
+\section{Technical Aspects of the Auxiliary Hamiltonian AdResS}\label{app:tmp2}
 \recheck{In principle when the auxiliary Hamiltonian approach is used,
   one can perform microcanonical simulations and thus can avoid the
-  use of a thermostat. In this case the thermodynamic force of the
-  auxiliary Hamiltonian would not carry any effect of the thermostat and thus the difference between the work of the thermodynamic force of GC-AdResS and that of the auxiliary Hamiltonian is
+  use of a thermostat. In this case, the thermodynamic force of the
+  auxiliary Hamiltonian would not carry any effect of the thermostat, and thus the difference between the work of the thermodynamic force of GC-AdResS and that of the auxiliary Hamiltonian is
   exactly the work that the thermostat does in GC-AdResS in order to compensate energy dissipation. The question is whether
@@
 
-\section{Extension of the chemical potential derivation to multi-component systems}
+\section{Extension of the chemical potential derivation to multi-component systems}\label{app:tmp3}
 
@@
 The notations are self-explanatory; for example $ U^\AT_{\typea\typeb}$
-denotes the expression for atomistic interactions between a molecule of type $\typea$ and one of type $\typeb$ (similarly $ U^\AT_{\typea\typea}$ and$ U^\AT_{\typeb\typeb}$) while $ U^\CG_{\typea\typeb}$ is the equivalent for coarse-grained interactions.
+denotes the expression for atomistic interactions between one molecule of type $\typea$ and one of type $\typeb$ ($U^\AT_{\typea\typea}$ and$ U^\AT_{\typeb\typeb}$ are similar),
+while $ U^\CG_{\typea\typeb}$ is the equivalent for coarse-grained interactions.
 Notation $\langle\cdot\rangle_{\vect r',\typeb; \vect r,\typea}$ denotes the
 ensemble average performed with respect to position $\vect r'$ of molecule
-$\typeb$, provided that a molecule $\typea$ takes the position $\vect r$ (the same applies for other combinations on indices ${\vect r'}, {\vect r}, {\typea}, {\typeb}$.
+$\typeb$, provided that a molecule $\typea$ takes the position $\vect r$ (the same applies for other combinations on indices ${\vect r'}, {\vect r}, {\typea}, {\typeb}$).
 If molecules contain more than one atom, then the average is also taken
@@
 \end{align}
-where, $N^\typea_1$ and $N^\typeb_1$ denote the number of type $\typea$ and
-type $\typeb$ molecules in the atomistic region ($N^\typea_3$ and $N^\typeb_3$ in the CG region instead).  In the thermodynamic
-limit, these numbers maximize the Helmholtz free energy.
+In the thermodynamic limit, these numbers maximize the Helmholtz free energy.
 In this context the chemical potential, e.g.~$\mu_\AT^\typea$, is the free energy increment due to the insertion of one molecule of type $\typea$ 
@@
 It is natural to conclude that
-$\omega_\ext^{\typea\typea} = \omega_\res^{\typea\typea} $  
+$\omega_\ext^{\typea\typea} = \omega_\res^{\typea\typea} $,
 because  these two terms exclusively
@@
 $\omega_\res^{\typeb\typea}$, leads to 
-identify $\omega_\ext^{\typea\typeb}$ with $\omega_\res^{\typea\typeb}$
-and $\omega_\ext^{\typeb\typea}=\omega_\res^{\typeb\typea}$.
+identify of $\omega_\ext^{\typea\typeb}$ with $\omega_\res^{\typea\typeb}$,
+and $\omega_\ext^{\typeb\typea}$ with $\omega_\res^{\typeb\typea}$.
 It follows that (for example) for component $\typea$:

### 2014-05-14 writeDown/pub.jcp/chem-pot-jcp.tex
a few small changes

@@
 \recheck{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
-However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \bluec{the original} AdResS.
+However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS.
-\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the \bluec{Appendix~\ref{app:tmp2}})}.
+\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}.
 Moreover we have proven numerically, for the case of liquid water, that
@@
 \recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation.
-In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the \bluec{Appendix~\ref{app:tmp2}})}.
+In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the {Appendix~\ref{app:tmp2}})}.
   \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
@@
 In the auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
-formula \bluec{(being this latter, in GC-AdResS, generated by the non conservative effect of the force interpolation).}
+formula {(being the term $w_\ext$ in GC-AdResS, generated by the non-conservative effect of the force interpolation).}
 By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-h}, we have the
@@
 and $\omega_\ext^{\typeb\typea}$ with $\omega_\res^{\typeb\typea}$.
-It follows that (for example) for component $\typea$:
+It follows that (for example) for component $\typea$, the excess chemical potential difference is:
 \begin{equation}
-\mu^{A}_{CG}-\mu^{A}_{AT}=\int _{\Delta}{\bf F}^{A}_{th}({\bf r})d{\bf r}+\int_{\Delta} \langle \vect F^{\typea\typea}_\res(\vect r)\rangle d{\bf r}+\int_{\Delta} \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle d{\bf r}
+\mu^{\typea,\exc}_{\CG}-\mu^{\typea,\exc}_{\AT}=\int _{\Delta}{\vect F}^{\typea}_{\thf}({\vect r})d{\vect r}+\int_{\Delta} \langle \vect F^{\typea\typea}_\res(\vect r)\rangle d{\vect r}+\int_{\Delta} \langle \vect F^{\typea\typeb}_\res(\vect r)\rangle d{\vect r}
 \label{fineq}
 \end{equation}
- and this proves ~Eq.~\eqref{eqn:tmp25}.}
+ and this proves Eq.~\eqref{eqn:tmp25}.}
 

### 2014-05-19 writeDown/pub.jcp/resubmission.tex
add missing resubmission.tex

\documentclass[12pt]{article}
\usepackage{german}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage[]{color}
\usepackage{amsmath,amssymb,amsfonts,latexsym,graphicx}

\pagestyle{empty}
\parindent0cm
% \addtolength{\textheight}{2cm}
% \addtolength{\textwidth}{1cm}
\renewcommand{\sfdefault}{cmss}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\redc}[1]{{\color{red} #1}}            
\newcommand{\recheck}[1]{{\color{red} #1}}

\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\AT}{{\textrm{{AT}}}}
\newcommand{\EX}{{\textrm{EX}}}
\newcommand{\CG}{{\textrm{CG}}}
\newcommand{\HY}{{\Delta}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\res}{{\textrm{rep}}}
\newcommand{\ext}{{\textrm{extra}}}
\newcommand{\exc}{{\textrm{exc}}}
\newcommand{\thermo}{{\textrm{Q}}}
\newcommand{\hadress}{{\textrm{H}}}
\newcommand{\dadress}{{\textrm{D}}}

\newcommand{\kopf}{\noindent
\raisebox{2.5cm}[0cm][0cm]
{
\parbox[c]{0.88\textwidth}
{
\begin{center}
\textsc{\large Institute for Mathematics, Freie Universit\"{a}t Berlin}\\
\textsc{ PD Dr. Luigi Delle Site}
\end{center}
}
}}
%\raisebox{2cm}[0cm][0cm]{\rule{\textwidth}{0.2mm}}}
\begin{document}

\kopf
\vspace{2cm}
\hfill\raisebox{1.5cm}[0cm][0cm]
{\parbox[t]{0.34\textwidth}
{e-mail:\\
{\small luigi.dellesite@fu-berlin.de}\\
Arnimallee 6\\
D-14195 Berlin\\
Tel:\ +49 (0)30 838 75775 \\
Fax:\ + 49 (0)30 838 75412 \\
}}

\vspace{3cm}
\noindent\raisebox{1.5cm}[0cm][0cm]
{\fbox{\parbox[t]{0.6\textwidth}
{Editor of {\it The Journal of Chemical Physics}\\
}}}
\vspace{1cm}

\textbf{Resubmission of the paper: ``Chemical potential of liquids and mixtures via Adaptive Resolution Simulation''}

\vspace{1cm}
\parskip 2ex
Dear Editor\\
We would like to thank both referees for the criticisms and suggestions.
We agree on several points, however tend to strongly disagree on some crucial ones.\\
Below please find a reply to each of the concerns raised by the referees and the
corresponding modification of the manuscript (where required).\\
Moreover one section is dedicated to comments that are for you and are properly labeled.\\

{\bf For the Editor:}

Regarding the comment of {\bf Reviewer 1}:

{\it  It is not easy to judge the relevance of this
  work because it might contain enough simulations, but not new information. In fact, its main contribution is a table, with comparison with reported data.}

In the previous paper published about one year ago in Physical Review X,
we have developed what we have {\bf openly} proposed in that paper as a {\bf very rigorous approach} where all the formulas were derived analytically and checked mathematically.

The whole theory is based on two assumptions:

(1) Thermodynamic limit for the \redc{atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}

(2) Hybrid region considered as a thin filter compared to the size of the two other regions.

In a simulation of course these conditions cannot be met at the ideal
level, 
thus the idea of this paper was that of treating real systems
in order to explore the numerical {\bf accuracy} that the formulas can
provide. Thirteen systems were studied with both AdResS and with the
thermodynamic integration, this {\it per se} is a major numerical
effort, \recheck{I would delete ``even for large computer facilities'', see the reason below}, however, the systems were
carefully chosen as representative of different classes of liquids and
mixtures characterized by different physics. The {\bf new information}
consists of thirteen values of the chemical potential which are
reproduced by AdResS, thus showing that the method is trustable for
such kind of calculations and that the hypothesis (1) and (2) above
can be easily met in \recheck{systems of relatively small sizes (see Table~II of the manuscript). Actually
  all simulations reported were performed on a 8-core workstation.}
\recheck{Comment from HAN: the thermodynamic limit does not imply extremely large system,
  rather, comparatively small systems that can be simulated on desktop-workstations.
  This is actully the advantage of our method, and one of the important information
  delievered by the paper.}

Moreover, regarding the comment below:

{\it On the other hand, the paper lacks important pieces of
  information and many incomplete statements and definitions (see
  below). There is also a theoretical weakness in the sense that the
  main equation used to evaluate the chem. potential seems to be
  derived in an ad hoc fashion, and ``proven numerically'', as the
  authors wrote. It is not easy to rely on an equation/method which
  lacks a solid theoretical background (mostly in statistical
  physics)}

Some of the information asked from the referee is indeed missing,
i.e.~description of the coarse-grained model. \recheck{Actually  this is} a
further advantage of our approach: One does NOT need to derive the
\recheck{coarse-grained models}, but simply takes spherical models interacting via a WCA
potential. It is in fact the thermodynamic force which makes them
compatible with the corresponding full atomistic models. We will add this part in
the Appendix.

However, we tend to strongly disagree on the comment about the lack of
solid theoretical background. \recheck{One can refer to all details of
  the theoretical developement that has alreadly been published in
  Phys.Rev.X.,} and we would like very much to avoid to report again
the whole derivation \recheck{ in this paper, since it would be redundant.}

If, instead, the referee means that he found our paper on Phys.Rev.X
was not solid enough or wrong, then clear scientific arguments must be
brought forward and eventually a comment to the PRX paper should be
done. We did not find helpful the \recheck{words like ``{\bf seems to
    be derived}''}. In the PRX paper, we claimed that the equations
were \recheck{derived \textbf{rigorously} and {\bf exactly}},
\recheck{thus either the referee had found some mistakes in our
  previous paper (then this should be made clear), or he did not read
  the PRX paper.}

In conclusion, we will take several suggestions from {\bf Reviewer 1},
\recheck{however, we will reduce the additions about the
derivation of the formulas to the minimum. Mostly we refer to the exact
equations in the PRX paper}. \recheck{Indeed, we intend} that people focus on
the numerical calculations rather then on the analytical derivations
which can be found in full details in the PRX paper.

We are confident that regarding these points we have your understanding.

\vskip 2cm

Below we report the reply to each referee. The comment of the referees
are in italics.  In order to facilitate the work of the referee, the
additions/modifications in the text will be in red.

{\bf Reply to Reviewer 1:}

{\it ``..... The idea of calculating excess
  chemical potentials from adaptive resolution techniques is appealing}

We are pleased that the referee recognizes that the overall idea is interesting; we take this comment as a positive basis of our work.

{\it ``This work is in fact a sort of extension of Ref. 5, and its contribution is just to offer a check of the
statements, hypothesis and calculations made on that previous paper. It is not easy to judge the relevance of this
work because it might contain enough simulations, but not new information. In fact, its main contribution is a table, with comparison with reported data.}

In Ref.5, we claim to have developed a rigorous approach from the
point of view of physics, and gone even further by exploring how far
one could make it mathematically rigorous/exact. We have found that
under the hypothesis:

(1) Thermodynamic limit for the \redc{atomistic and the coarse-grained
  region. (i.e. the number of molecules in both of the two regions are
  infinitely large, and the coarse-grained region is infinitely larger
  than the atomistic region)}

(2) Hybrid region considered as a thin filter compared to the size of
the two other regions.

The method is mathematically rigorous and for some aspects even
exact. Conditions (1) and (2) are ideal, so it was important to know
how they can be met in \recheck{practical simulations, especially in
the mixture systems that the solute concentration is dilute.} The aim of this
paper is: {\bf to explore the numerical accuracy of the theory (for
  the chemical potential) proposed in Ref.5}.

We have done it for thirteen representative \recheck{I would remove ``and computationally expensive'', reason as before} systems.
We hope the referee can recognize that this effort is a non trivial one.

{\it On the other hand, the paper lacks important pieces of information and many incomplete statements and definitions (see below). There is also a theoretical
weakness in the sense that the main equation used to evaluate the chem. potential seems to be derived in an ad hoc fashion, and ``proven numerically'', as the authors wrote. It is not easy to rely on an equation/method which lacks a solid theoretical background (mostly in statistical physics)}

The sentence {\bf ``proven numerically''} has been used by the referee
as argument for an {\it ad hoc} formulation of the method, and our
impression is that he/she means that we constructed it based on
\recheck{what we see numerically}. \recheck{ In fact, it is not. In
  Ref.5, the theory was ({\bf explicitly}) derived from thermodynamic
  priciples, and was proved in a rigorous and exact way (in the due
  limits). The conclusion itself does not need further numerical verfication.
  The referee is legitimate to think that it is not rigorous, but
  then he/she should point out explicitly the weak points of Ref.5 and
  provide solid arguments.  However, in this case the referee should 
  correct/comment the paper of Ref.5. The numerical tests
  presented by this manuscript provide extra information on how our
  theory works in practial pure/mixutre systems, in which
  thermodynamic limit can only be approached, but never be reached. We believe this is a plus
  rather than a minus of our work. We are confident that the referee
  sees our point.
}

The sentence {\bf ``proven numerically''} has been used by the referee
as argument for an {\it ad hoc} formulation of the method, and our
impression is that he/she means that we constructed it in order to get
what we wanted. In fact it is not, the formula we have proven
numerically is actually an extra information. We do not need to use
it, in fact we have a technically rigorous way to check the heat given
by the thermostat; this formula just gives an interesting insight,
this is explicitly written in Ref.5. In this paper we have explored it
further and proved that works for other twelve systems. We believe
this is a plus rather than a minus of our work.

In general, as we have said above, we have presented our approach in
Ref.5 ({\bf explicitly}) as rigorous and exact (in the due limits).
The referee is legitimate to think that it is not, but then he/she
should point out explicitly the weak points of Ref.5 and provide solid
arguments.  However, in this case should be corrected/commented the
paper of Ref.5, the numerical result of this paper suggest that at the
simulation level the method cannot be that bad. We are confident that
the referee sees our point.

We found several comments extremely useful to improve the quality of the paper and performed several additional calculations in order to fulfill the request of the referee, we report below the description of all of them.

{\it (1) A description of the cg model is lacking. Please specify how
  do you treat and the interaction potential for cg molecules of
  solvent and solute. I suppose that both types of molecules (solvent
  and solute) free to cross the hybrid layer.  Please confirm. Please
  add a section about the cg model.}

We added it in the appendix. It must be noticed that we actually do
not need to derive a cg model. In fact our approach allows us to use
simple spherical models \recheck{(e.g.~interacting via the WCA potential)} whose size is about the vdW radius of the
specific molecule. It is
then the thermodynamic force that makes the thermodynamics of the cg
models compatible with the atomistic one. Molecules change their
resolution when they pass from one region to another.

{\it (2) Definitions of $V_{AT}$ and $V_{CG}$ are also lacking in terms of particle indexes. The model definition is important to distinguish between total energies and pair-wise terms, e.g. $V_{AT}(xij)$.}

\recheck{we can refer to the new appendix}

{\it (3) Figure 1. ``allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a GC fashion.'' This phrase is
difficult to understand. The AT region is connected with the CG domain (via a transition layer which is not small, but much thicker than the
molecular size). Thus either one has a complete Hamiltonian for the whole AT+HYB+CG system, or else, there is no Hamiltonian. In other words, if
the interactions between AT and HYB, and CG molecules are not derived from H, then there is no Hamiltonian. Also, ``...treat the system in a GC
fashion'' is also difficult to understand (maybe the authors mean ``...consider the AT region as an open subsystem''). I would suggest
deleting this phrase and refer in the text to their theoretical findings in Ref. 5 about particle number distributions p(N),etc.}

Actually this is the very core of our derivation. If the referee think
that this is wrong, then Ref.5 is entirely wrong.

In fact we have extended the hybrid region adding a region equal to
the interaction cut off where the resolution is full atomistic, but
such a region is not considered part of the full atomistic region. As
a consequence all the molecules of the atomistic region will interact
with the hybrid region {\bf ONLY} at atomistic level (coarse-grained
molecules are in the region beyond the cut off one). In fact beyond
the cut off radius there is no interaction or better the interaction
is zero. As a consequence the molecules of the atomistic region have a
well defined Hamiltonian. This is the Hamiltonian of an open system,
\recheck{and is parametrized by the the coordinate of the molecules
  that are interacting with the atomistic region}. \recheck{It is comparable with  a
subsystem of a large full atomistic simulation}; the Hamiltonian of the
subsystem is well defined, without any artificial interpolation.  This
is clearly reported in Eq.12 of Ref.5.

Although we believe it is redundant we have reported the explicit form
of the Hamiltonian of the atomistic region also in this paper.

\recheck{{\bf HAN can you write it for me in Latex}}.
\recheck{{\bf See below}}
\begin{align}
  \mathcal H^{\AT}_{N_1} (\vect x_1; \vect x_2, N_2)
  =
  \sum_{i=1}^{N_1}\frac12 m_i\vect v_i^2
  + \sum_{i,j=1}^{N_1}\frac 12 V^\AT_{i,j}
  + \sum_{i=1}^{N_1}\sum_{j=N_1+1}^{N_1+N_2} V^\AT_{i,j},
\end{align}
where $V^\AT_{i,j}$ is the atomistic molecular potential, which is given by
\begin{align}
  V^\AT_{i,j} =
  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta).
\end{align}
where index $\alpha$ and $\beta$ denotes the atoms on the
corresponding molecule.  $N_1$ and $N_2$ are the number of molecules
in the AT and atomistic part of the HY region, respectively. $\vect x_1$
and $\vect x_2$ are the phase space variables (joint of velocity and position)
in the  AT and atomistic part of the HY region, respectively.

{\it (4) Page 4. ``...reproduce the first order of the
  probability...'' and ``Higher orders...'' Could the authors specify
  what (small) quantity the order is referred to?, I think it could be
  orders in the density of solute molecules, or maybe in density
  variation with respect the average. Please be more clear when
  referring to ``orders'' elsewhere in the manuscript.}

\recheck{comment from HAN: why not add your short description on the
  orders to the paper? It is concise and would be convenient for the
  readers who are only interested in the numerical result, and do not
  have time to read Ref.5.}

This is clearly described in Ref.5 and we felt it would be redundant
to write it here once again; we have defined the first order of the
probability distribution of a system as its molecular density, a
function in three-dimension. The second order is the two-body
distribution (6-dimensional function) of which the radial distribution
function is a specific expression; the third order is the three-body
distribution (in 9-dimension) etc etc. The full probability is a
3N-dimensional function of which the different orders are a lower
dimensional approximation.

If the referee put this as a condition of rejection, then we would add
it, but we strongly believe that it is not needed for this paper.

{\it (5) Page 5. Auxiliary Hamiltonian. For the sake of clarity, the
  authors should write down this Hamiltonian they refer to, with full
  index details. Also, please write down the form of thermodynamic
  force in the auxiliary Hamiltonian. They mention that simulations
  using the auxiliary Hamiltonian were made with no thermostat. Did
  the authors check that the ``energy'' of this Hamiltonian is
  conserved? Please comment on this important issue.}

\recheck{Comment from HAN: Wo DO use a thermostat for the potential-interpolation
  simulation.  we should be honest on this point. And the prove in the
  appendix also assumes that ths thstem is thermostated. Tell me why you wrote ``
  we do not need to use a thermostat''? Or you simply mean that we in principle we
  do not need, but in practice, to generate the Boltzmann distribution we use it.}

  As before, it is reported in all details in Ref.5 and we thought it
  was redundant. The thermodynamic force must have exactly the same
  numerical formula of the standard AdResS, otherwise it would not
  work for our purposes: if two expressions are formally identical but
  one has the effect of the thermostat and the other not then the
  difference isolates the effect of the thermostat. For the
  Hamiltonian system we use the same formula and impose artificially
  the same density of the AdResS system thus we get a condition on the
  gradient of the molecular density in the transition region.

  Yes, we have checked the conservation of the energy. However this
  was preliminary to everything, in fact it must be clear that if the
  energy was not conserved, then we would also get completely wrong
  results (the heat would either be too low or too high and anyway
  would not converge).

  {\it (6) ``Keeps the density of particles across the system as in
    AdResS''. Do you mean at constant density?}

Yes

{\it (7) ``It must be noticed that the relation we obtained form the
  chem. pot. is similar to that obtained in... Ref[6]''. This
  statement is not clear. The equation this method proposes seems not
  similar to that of Ref. 6. In particular the term is quite different
  from which is the corresponding free energy difference appearing in
  Ref. 6. The authors should explicitly write out this essential term
  of the calculation, indicating summations with particle indexes. It
  would seem from the (not-written auxiliary Hamiltonian) that the
  particles index of the first ``w'' is not the same as that of the
  ``nabla w''. Please derive and clarify this term so anybody could
  understand it.

  The effect of discrepancies with Ref.6 are not simple to trace, but
  certainly not zero. The authors state: ``H-Adress and CG-Adress are
  the same up to first order'' (please again, in what?). A reference
  proving this statement is not mentioned, but I guess the authors
  refer to Ref. 7 for that prove. However after reading that paper
  (Ref. 7) I saw no prove of this (just essentially the same phrase,
  without prove). The authors should prove this statement here or
  delete this phrase, or comment about the lack of comparisons, at
  present.}

We see the point of the referee, perhaps we should do a paper with
explicit formulas and data to show similarity and differences between
the two methods.

However since this is not a relevant part of the paper, we decided to
remove any reference to similarities and differences with Ref.6.  We
will cite their second paper dealing with a mixture. We hope that the
referee is happy with the deletion of Ref.6 and addition of a new
reference.

{\it (8) Fig. 2. Please indicate the locations of the HYB domain. A
  difference of about 20 percent in density is not small, although
  *inside* the AT domain, the g(r) might not be too sensible to such
  density difference (as shown in the fig.). On the other hand,
  contrary with what the authors state below, a large transition
  region is beneficial, because molecules have larger space to adapt
  to the change in resolution. Please correct this.}

We disagree with the referee.
\recheck{The large deviation is due to the sampling error, because the
  number of TBA molecules in the system is very small (80, see the Table II).
  We could reach a much better accuracy of the density if we do longer simulations,
  but it would require much more computer time.}
% We could reach a much higher accuracy if
% we set the level of accuracy of the thermodynamic force higher (but
% requires more computer time)
However, we wanted to show that even with 20 percent of (maximum)
difference we get the chemical potential accurate and the density in
the AT region flat.
\recheck{comment from HAN: is the HY region goes
  from 0.5 nm to 3.2 nm, i.e.~the whole range of the figure 2? Then we
  do not show the density in the AT region is flat.}

Regarding the point
that a larger region is beneficial, we must disagree. This is based on
arguments (which we will give next) and long experience with such
systems. What is important in AdResS is that the AT and CG region are
large, in fact if they are large they are going to thermalize and in
general equilibrate substantially the hybrid region.  We have recently
made tests on related issues and found that if one uses a large
thermalized reservoir then small regions where the density or the the
temperature are not targeted, are automatically equilibrated by the
large reservoir. Moreover our analytic derivation suggests the same.
On the contrary a HYB region is charaterized by non physical
description of the potentials and thus it does not have as a reference
any thermodynamic state point. As a consequence the larger the HYB
region the larger the perturbation. Of course there is a minimal size
that is a region equal to the interaction cut off.  These aspects have
been explored and described in details in several previous papers
among which:

(1) Matej Praprotnik, Luigi Delle Site, and Kurt Kremer, .J.Chem.Phys. 123, 224106 (2005).

(2)Silvina Matysiak, Cecilia Clementi, Matej Praprotnik, Kurt Kremer and Luigi Delle Site, J.Chem.Phys. 128, 024503 (2008).

(3) S.Poblete, M.Praprotnik, K.Kremer and L.Delle Site,  J.Chem.Phys. 132, 114101 (2010).

{\it (9) Table I. What results of Ref. 15 corresponds to table I?,
  this is not mentioned. Results in Ref 12 and 15 were made at lower
  concentration, but the authors state that the excess chem pot is not
  sensible to the solute concentration in this regime. And say that
  ``we have verified that such consistency holds''. This is important
  though, and the authors should include a graph with the calculated
  excess chem. pot. against the solute concentration, showing that it
  goes to a plateau at low concentration consistent with the
  experimental value reported (at least for some of the cases
  considered). Error bars are crucial, but means nothing without the
  simulation times required to obtain them. The authors should include
  a more clear measure of this. A possible one could be showing the
  accumulated standard error against the simulation time and compare
  the IPM, the TI (free energy estimate using Bennet's method) and
  their own method. With the specification of the system size (table
  II) this already gives an idea of the computational costs.}

We do understand the concerns of the referee about the values referred
to paper in Ref.15, however all the values in the table for TI were
obtained by us.  We have checked (the sentence {\it ``we have verified
  such a consistency''}) that our values are close to those at lower
concentration.  We have also made the (expensive) calculation of the
concentration dependence and show that indeed goes towards a plateau
added the error etc etc.  The figure and related comments have been
added in the revised version of the manuscript.

However, at the current stage the comparison about the computational time required by AdResS and TI would not be fair.
In fact for this reason we have {\bf honestly} reported current numerical limitations in Section IV.

This paper is about the capability and numerical accuracy of the approach.

{\it (10) Sec. IV. ...a critical appraisal. This comment is connected with 8). In this section the authors state that their method is not as fast as TI if dilute systems are considered. I would just like to comment that this observation seems to conflict with the comment made in Ref. 7 (``orders of magnitude faster than IPM''). Indeed, Widom method is not very good for large molecules in liquids, this is well known. So, as far I understand, the author's conclusion is that the best option is to use TI for dilute systems while adaptive resolution pays off when dealing with many solute molecules. This observation is important and should be shown in a graph (e.g. standard error vs. simulation time for TI and CG-Adress, in the dilute case and less diluted case)}

NO, we only say that in the future, AdResS, once its implementation is optimized, may even offer a better way to calculate the chemical potential in some situations, at the moment, although in very recent work we have reached a speed up factor of more than two w.r.t. full atomistic simulation, the computational implementation of AdResS in Gromacs is still not optimal. What we instead claim (for sure) is that if you do in any case an AdResS simulation, you automatically get the chemical potential, that is this is an automatic feature of the simulation method. This is reported clearly in the paper and we believe that it does not need further clarifications.\\

{\it (11) Recent works: an extension to the Hamiltonian based method the authors refer to, appeared in ``Phys. Rev. Lett. 2013, 111, 060601''. This work should be cited because it precisely deal with mixtures being in close relation with this work.}

OK, as said before we cite this instead of Ref.6.

{\bf Reply to Reviewer 2}:\\

 {\it I would recommend that the authors consider the following minor revisions. Most significantly, it would be very helpful for the authors to discuss the apparently systematic errors that arise in their estimation of the chemical potentials. The following provides further details and minor comments.

Table 1 compares the chemical potentials determined from GC-AdResS and thermodynamic integration (TI). (It would be helpful to know the basis for estimating the uncertainty of these calculations.) The results indicate that there is a fairly small, but systematic discrepancy between the two methods. In particular, in almost all cases, GC-AdResS underestimates the magnitude of the chemical potential. It would be very interesting and helpful if the authors could investigate and provide insight into the origin of this discrepancy.}

The only reason that came to our mind is that such a systematic difference may come from the interaction cut off.
In fact, currently, we are using the reaction field method for electrostatics and thus the accuracy may indeed depend on that.\\
We found this point very interesting and studied the dependence of our results from the cut off. Indeed it seems that, etc etc...... {\bf WHEN ANIMESH IS READY}\\

{\it  I am somewhat confused by the notation for $F_{th}$. Is this a vector quantity? Is the integral on page 3 giving a vector or a scalar? The notation seems confusing and inconsistent. Also, I am confused by the first equality sign after $F_{th}$. It would be helpful if the authors could clarify this.}

We apologize for the misprint, the term $F_{th}=$ has been removed\\

{\it On page 5, the authors indicate that equipartition implies a
  contribution to the chemical potential of 1/2 kT for each atomic
  degree of freedom (dof). I would expect that this would be true if
  each atomic dof contributes quadratically to the Hamiltonian. It
  would be helpful if the authors could clarify why this would be so
  for dof's that do not contribute quadratically to the Hamiltonian.}

We must again apologize, we reported the same written in Ref.5 where
we gave a general explanation in case molecules had also vibrational
degrees of freedom. Of course here we have rigid model and rotational
DOF's are not quadratic. The kinetic part related to rotations can
actually be written analytically, however we found out that it is not
very practical and thus the numerical trick of double resolution also
in the GC region simplifies the procedure.  For this reason we have
left only this part and removed the comment about the equipartition
theorem.

{\it  It would be helpful if the authors could clarify why/how eq 3 generalizes to eq 4 in the case of a multicomponent system}

\recheck{\bf Added below... I do not really know what to write for him/her.}

 We denote the volume of the system by $V$ and the temperature by
$T$. It is divided into atomistic~($\AT$), hybrid~($\HY$), and
coarse-grained~($\CG$) region, the volume of which are denoted by
$V_1$, $V_2$ and $V_3$, respectively.  We assume two different types
of molecules are mixed in the system, and the number of molecules are
$N^1$ and $N^2$, respectively. The superscript ``1'' and ``2'' in the
paper denotes the two component.  We further denote the number of type
1 molecules in the atomistic, hybrid, and coarse-grained regions by
$N^1_1$, $N^1_2$ and $N^1_3$, respectively. While for type 2 molecules
the notations are $N^2_1$, $N^2_2$ and $N^2_3$, respectively.  By
assuming the hybrid region is infinitely small comparing with the
atomistic and coarse-grained regions, we have the following
constrains:
\begin{align}
  V &= V_1 + V_3\\
  N &= N^1 + N^2\\
  N^1 &= N^1_1 + N^1_3\\
  N^2 &= N^2_1 + N^2_3
\end{align}
By calculating the thermodynamic forces for both of the components, which
are denoted by $\vect F^1_\thf$ and $\vect F^2_\thf$,
we impose the correct density profile to the system:
\begin{align}
  \rho_\HY^1 &= \rho_\AT^1 = \rho_\CG^1\\
  \rho_\HY^2 &= \rho_\AT^2 = \rho_\CG^2
\end{align}
We further denotes the work done by the hybrid region on the two types
of molecules by $\omega_0^1$ and $\omega_0^2$, respectively.
To find out the chemical potential difference between AT and CG resolutions,
the same idea as presented in Sec.III.C of Ref.5 can be extended
to the two component system. This extension is straightforward and trivial. We do not want
to write them down, because one can just step-by-step follow the
deriviation for the one component system, and no new technique is needed.
In the end, we proved
\begin{align}
  \mu^1_\AT(N^1_1, N^2_1, V_1, T) &= \mu^1_\CG(N^1_1, N^2_1, V_1, T) - \omega^1_0\\
  \mu^2_\AT(N^1_1, N^2_1, V_1, T) &= \mu^2_\CG(N^1_1, N^2_1, V_1, T) - \omega^2_0
\end{align}
Now, $N^1_1$ and $N^2_1$ denotes the averaged number of type 1 and
type 2 molecules in the atomistic region.  Under the thermodynamic
limit, this number maximize the Helmholtz free energy and is the one
of statistical importance, see more discussions in
Ref.5. We do not distinguish these notations from
before, because the meaning is clear from the context.

Sincerely\\

Luigi Delle Site

\end{document}

### 2014-05-19 writeDown/pub.jcp/resubmission.tex
resubmission letter imporoved

@@
 \usepackage{pslatex}
-\usepackage[]{color}
-\usepackage{amsmath,amssymb,amsfonts,latexsym,graphicx}
-
+\usepackage{color}
 \pagestyle{empty}
@@
 % \addtolength{\textheight}{2cm}
-% \addtolength{\textwidth}{1cm}
 \renewcommand{\sfdefault}{cmss}
 \renewcommand{\familydefault}{\sfdefault}
-\newcommand{\redc}[1]{{\color{red} #1}}            
 \newcommand{\recheck}[1]{{\color{red} #1}}
-
-\newcommand{\vect}[1]{\textbf{\textit{#1}}}
-\newcommand{\dof}{{\textrm{DOF}}}
-\newcommand{\AT}{{\textrm{{AT}}}}
-\newcommand{\EX}{{\textrm{EX}}}
-\newcommand{\CG}{{\textrm{CG}}}
-\newcommand{\HY}{{\Delta}}
-\newcommand{\rdf}{{\textrm{rdf}}}
-\newcommand{\thf}{{\textrm{th}}}
-\newcommand{\res}{{\textrm{rep}}}
-\newcommand{\ext}{{\textrm{extra}}}
-\newcommand{\exc}{{\textrm{exc}}}
-\newcommand{\thermo}{{\textrm{Q}}}
-\newcommand{\hadress}{{\textrm{H}}}
-\newcommand{\dadress}{{\textrm{D}}}
 
@@
 \begin{document}
-
 \kopf
@@
 }}
-
 \vspace{3cm}
@@
 \parskip 2ex
-Dear Editor\\
+Dear Editor
+
 We would like to thank both referees for the criticisms and suggestions.
-We agree on several points, however tend to strongly disagree on some crucial ones.\\
 Below please find a reply to each of the concerns raised by the referees and the
-corresponding modification of the manuscript (where required).\\
-Moreover one section is dedicated to comments that are for you and are properly labeled.\\
+corresponding modification of the manuscript (where required).
+In order to facilitate the work of the referees we have highlighted in red, the additions/modifications in the manuscript.
 
-{\bf For the Editor:}
+\vskip 1cm
+Sincerely,
 
-Regarding the comment of {\bf Reviewer 1}:
+Luigi Delle Site
 
-{\it  It is not easy to judge the relevance of this
+\newpage
+
+{\bf For the Editor only:}
+
+Regarding the comment of {\bf Reviewer 1}:\\
+{\color{blue} \it  It is not easy to judge the relevance of this
   work because it might contain enough simulations, but not new information. In fact, its main contribution is a table, with comparison with reported data.}
@@
 In the previous paper published about one year ago in Physical Review X,
-we have developed what we have {\bf openly} proposed in that paper as a {\bf very rigorous approach} where all the formulas were derived analytically and checked mathematically.
-
+we have developed what we have {\bf openly} proposed in that paper as a {\bf rigorous approach} where all the formulas were derived analytically and checked mathematically.
 The whole theory is based on two assumptions:
 
-(1) Thermodynamic limit for the \redc{atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
+(1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).
+
+(2) Hybrid region considered as a thin filter compared to the size of the two other regions.
+
+In a simulation of course these conditions cannot be met at the ideal level, thus the original idea of this paper was that of treating real systems in order to explore the numerical {\bf accuracy} that the formulas can provide.
+Thirteen systems (about 300 simulations) were studied with both AdResS and with the thermodynamic integration, this {\it per se} is a major numerical effort, even for large computer facilities, however, the systems were carefully chosen as representative of different classes of liquids and mixtures characterized by different physics.
+The {\bf new information} consists of thirteen values of the chemical potential which are reproduced by GC-AdResS, thus showing that the method is trustable for such kind of calculations and that the hypothesis (1) and (2) above can be easily met in standard simulations.
+In the paper, we have made clear the intention described above, but it seems that the first referee has missed it.
+Moreover, the request of the first referee about showing concentration dependent behaviors in order to show that we are consistent with previous work at very low concentrations was actually not of major interest, since we always compare each GC-AdResS calculation with the corresponding TI at the same concentrations.
+{\bf In our view this was clear also to the referee and it was also clear to him/her the amount of additional computational effort he/she was asking for}.
+
+However, independently from the referee's comment, we decided to do the study about the concentration dependent.
+In fact, in case of positive outcome, we would show that our method is very robust over different thermodynamic state points (and, as minor point, we would make happy the referee about the consistency with previous work).
+Indeed our results strongly support such a conclusion.
+However the computational cost was massive (about 300 additional simulations!), for this reason we ask you to consider this point in case the referee requires additional simulations.
+
+In addition, we did not like the comment of the referee:\\
+{\color{blue}\it ``There is also a theoretical
+  weakness in the sense that the main equation used to evaluate the chem. potential seems to be derived in an ad hoc fashion, and ``proven numerically'', as the authors wrote.}
+
+It was not the aim of the paper to have an analytic derivation of the formula, this does not mean that the approach is weak and above all the referee gave the impression that we obtained something by manipulating formulas and computational tools in order to ``force'' our results.
+
+Given our major effort over the last 2-3 years to merge analytic/mathematical work with numerical applications to realistic chemical systems, the opinion of the referee is quite discouraging. 
+However, our impression is that the first referee did not really read our previous paper and/or he/she may not have the background for catching analytic/mathematical derivations of formulas in full.
+In any case, in this revised version we have added the analytic derivation of the formula, (and in order to address the point raised by the second referee, we have added also the analytic derivation of the extension of the formula to multicomponent component systems).
+We have tried to be not too much mathematical, in order to reach the whole community interested in the subject.
+However, to merge computational results about chemical systems and analytic derivation of the formulas in one coherent paper is not easy, we made a strong effort in such direction and we hope that you will appreciate it.
+
+We have also added two very recent references related to the use of AdResS with the MARTINI force field.
+The senior authors of such publications pointed out to us the importance of calculating the chemical potential as a test of thermodynamical consistency of the whole system, especially for systems of the kind they are treating (large bio-systems).
+
+\recheck{do not say that...}
+Finally, the referee asked us to ``{\it ameliorate} the language; we are fully aware of not being mother tongue Oxford academics, but we asked several colleagues to read the paper and tell us if it was understandable; we got only positive comments, we cannot do more than that.
+
+We have added all the calculations/information asked by the referees and we are confident that now the paper is ready for publication.
+
+\newpage
+
+{\bf Reply to Reviewer 1:}
+
+{\color{blue}{\it ``..... The idea of calculating excess
+    chemical potentials from adaptive resolution techniques is appealing}}
+
+We are pleased that the referee recognizes that the overall idea is interesting; we take this comment as a positive basis of our work.
+
+{\color{blue}{\it ``This work is in fact a sort of extension of Ref. 5, and its contribution is just to offer a check of the
+statements, hypothesis and calculations made on that previous paper. It is not easy to judge the relevance of this
+work because it might contain enough simulations, but not new information. In fact, its main contribution is a table, with comparison with reported data.}}
+
+In Ref.5, we claim to have developed a rigorous approach from the
+point of view of physics and went even further by exploring how far
+one could make it mathematically rigorous/exact. We have found that
+under the hypothesis:
+
+(1) Thermodynamic limit for the \recheck{atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
   regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}
@@
 
-In a simulation of course these conditions cannot be met at the ideal
-level, 
-thus the idea of this paper was that of treating real systems
-in order to explore the numerical {\bf accuracy} that the formulas can
-provide. Thirteen systems were studied with both AdResS and with the
-thermodynamic integration, this {\it per se} is a major numerical
-effort, \recheck{I would delete ``even for large computer facilities'', see the reason below}, however, the systems were
-carefully chosen as representative of different classes of liquids and
-mixtures characterized by different physics. The {\bf new information}
-consists of thirteen values of the chemical potential which are
-reproduced by AdResS, thus showing that the method is trustable for
-such kind of calculations and that the hypothesis (1) and (2) above
-can be easily met in \recheck{systems of relatively small sizes (see Table~II of the manuscript). Actually
-  all simulations reported were performed on a 8-core workstation.}
-\recheck{Comment from HAN: the thermodynamic limit does not imply extremely large system,
-  rather, comparatively small systems that can be simulated on desktop-workstations.
-  This is actully the advantage of our method, and one of the important information
-  delievered by the paper.}
-
-Moreover, regarding the comment below:
-
-{\it On the other hand, the paper lacks important pieces of
-  information and many incomplete statements and definitions (see
-  below). There is also a theoretical weakness in the sense that the
-  main equation used to evaluate the chem. potential seems to be
-  derived in an ad hoc fashion, and ``proven numerically'', as the
-  authors wrote. It is not easy to rely on an equation/method which
-  lacks a solid theoretical background (mostly in statistical
-  physics)}
-
-Some of the information asked from the referee is indeed missing,
-i.e.~description of the coarse-grained model. \recheck{Actually  this is} a
-further advantage of our approach: One does NOT need to derive the
-\recheck{coarse-grained models}, but simply takes spherical models interacting via a WCA
-potential. It is in fact the thermodynamic force which makes them
-compatible with the corresponding full atomistic models. We will add this part in
-the Appendix.
-
-However, we tend to strongly disagree on the comment about the lack of
-solid theoretical background. \recheck{One can refer to all details of
-  the theoretical developement that has alreadly been published in
-  Phys.Rev.X.,} and we would like very much to avoid to report again
-the whole derivation \recheck{ in this paper, since it would be redundant.}
-
-If, instead, the referee means that he found our paper on Phys.Rev.X
-was not solid enough or wrong, then clear scientific arguments must be
-brought forward and eventually a comment to the PRX paper should be
-done. We did not find helpful the \recheck{words like ``{\bf seems to
-    be derived}''}. In the PRX paper, we claimed that the equations
-were \recheck{derived \textbf{rigorously} and {\bf exactly}},
-\recheck{thus either the referee had found some mistakes in our
-  previous paper (then this should be made clear), or he did not read
-  the PRX paper.}
-
-In conclusion, we will take several suggestions from {\bf Reviewer 1},
-\recheck{however, we will reduce the additions about the
-derivation of the formulas to the minimum. Mostly we refer to the exact
-equations in the PRX paper}. \recheck{Indeed, we intend} that people focus on
-the numerical calculations rather then on the analytical derivations
-which can be found in full details in the PRX paper.
-
-We are confident that regarding these points we have your understanding.
-
-\vskip 2cm
-
-Below we report the reply to each referee. The comment of the referees
-are in italics.  In order to facilitate the work of the referee, the
-additions/modifications in the text will be in red.
-
-{\bf Reply to Reviewer 1:}
-
-{\it ``..... The idea of calculating excess
-  chemical potentials from adaptive resolution techniques is appealing}
-
-We are pleased that the referee recognizes that the overall idea is interesting; we take this comment as a positive basis of our work.
-
-{\it ``This work is in fact a sort of extension of Ref. 5, and its contribution is just to offer a check of the
-statements, hypothesis and calculations made on that previous paper. It is not easy to judge the relevance of this
-work because it might contain enough simulations, but not new information. In fact, its main contribution is a table, with comparison with reported data.}
-
-In Ref.5, we claim to have developed a rigorous approach from the
-point of view of physics, and gone even further by exploring how far
-one could make it mathematically rigorous/exact. We have found that
-under the hypothesis:
-
-(1) Thermodynamic limit for the \redc{atomistic and the coarse-grained
-  region. (i.e. the number of molecules in both of the two regions are
-  infinitely large, and the coarse-grained region is infinitely larger
-  than the atomistic region)}
-
-(2) Hybrid region considered as a thin filter compared to the size of
-the two other regions.
-
 The method is mathematically rigorous and for some aspects even
@@
 how they can be met in \recheck{practical simulations, especially in
-the mixture systems that the solute concentration is dilute.} The aim of this
-paper is: {\bf to explore the numerical accuracy of the theory (for
-  the chemical potential) proposed in Ref.5}.
+the mixture systems that the solute concentration is dilute.} The aim of this paper is: {\bf to
+  explore the numerical accuracy of the theory (for the chemical
+  potential) proposed in Ref.5}.  We have done it for thirteen
+representative and computationally expensive systems.  We hope the
+referee can recognize that this effort is a non-trivial one. However
+as asked by him/her, we have added all the simulations requested (see
+below).
 
-We have done it for thirteen representative \recheck{I would remove ``and computationally expensive'', reason as before} systems.
-We hope the referee can recognize that this effort is a non trivial one.
-
-{\it On the other hand, the paper lacks important pieces of information and many incomplete statements and definitions (see below). There is also a theoretical
+{\color{blue}{\it On the other hand, the paper lacks important pieces of information and many incomplete statements and definitions (see below). There is also a theoretical
     weakness in the sense that the main equation used to evaluate the chem.
 potential seems to be derived in an ad hoc fashion, and ``proven numerically'', as the authors wrote.
-It is not easy to rely on an equation/method which lacks a solid theoretical background (mostly in statistical physics)}
+It is not easy to rely on an equation/method which lacks a solid theoretical background (mostly in statistical physics)}}
 
-The sentence {\bf ``proven numerically''} has been used by the referee
-as argument for an {\it ad hoc} formulation of the method, and our
-impression is that he/she means that we constructed it based on
-\recheck{what we see numerically}. \recheck{ In fact, it is not. In
-  Ref.5, the theory was ({\bf explicitly}) derived from thermodynamic
-  priciples, and was proved in a rigorous and exact way (in the due
-  limits). The conclusion itself does not need further numerical verfication.
-  The referee is legitimate to think that it is not rigorous, but
-  then he/she should point out explicitly the weak points of Ref.5 and
-  provide solid arguments.  However, in this case the referee should 
-  correct/comment the paper of Ref.5. The numerical tests
-  presented by this manuscript provide extra information on how our
-  theory works in practial pure/mixutre systems, in which
-  thermodynamic limit can only be approached, but never be reached. We believe this is a plus
-  rather than a minus of our work. We are confident that the referee
-  sees our point.
-}
+% \recheck{
+%   The main purpose of the paper was to show the numerical accuracy of the theory, so we did not provide the theoretical derivation of
+% }
+% We have taken such a comment as a motivation to make an effort and finalize a derivation of the formula defined {\it ``weak''} by the referee.
+The derivation is presented as one of the results of this paper and has got its own section.
+We have taken such a comment as a motivation to \recheck{provide the} derivation of the formula defined {\it ``weak''} by the referee.
+The derivation is presented as one of the results of this paper and has got its own section.
 
-The sentence {\bf ``proven numerically''} has been used by the referee
-as argument for an {\it ad hoc} formulation of the method, and our
-impression is that he/she means that we constructed it in order to get
-what we wanted. In fact it is not, the formula we have proven
-numerically is actually an extra information. We do not need to use
-it, in fact we have a technically rigorous way to check the heat given
-by the thermostat; this formula just gives an interesting insight,
-this is explicitly written in Ref.5. In this paper we have explored it
-further and proved that works for other twelve systems. We believe
-this is a plus rather than a minus of our work.
+{\color{blue}{\it (1) A description of the cg model is lacking. Please specify how do you treat and the interaction potential for
+cg molecules of solvent and solute. I suppose that both types of molecules (solvent and solute) free to cross the hybrid layer.
+Please confirm. Please add a section about the cg model.}}
 
-In general, as we have said above, we have presented our approach in
-Ref.5 ({\bf explicitly}) as rigorous and exact (in the due limits).
-The referee is legitimate to think that it is not, but then he/she
-should point out explicitly the weak points of Ref.5 and provide solid
-arguments.  However, in this case should be corrected/commented the
-paper of Ref.5, the numerical result of this paper suggest that at the
-simulation level the method cannot be that bad. We are confident that
-the referee sees our point.
+We added the procedure in the appendix. It must be noticed that, as a
+major result of Ref.5, we actually do not need to derive a detailed cg
+model. In fact our approach allows us to use simple spherical models
+whose size is about the vdW radius of the specific molecule. The spheres
+interact via the simple WCA potentials. It is then the thermodynamic force
+that makes the thermodynamics of the cg models compatible with the
+atomistic one. Both types of molecules change their resolution when they pass from
+one region to another.
 
-We found several comments extremely useful to improve the quality of the paper and performed several additional calculations in order to fulfill the request of the referee, we report below the description of all of them.
+{\color{blue}{\it (2) Definitions of $V_{AT}$ and $V_{CG}$ are also lacking in terms of particle indexes.
+The model definition is important to distinguish between total energies and pair-wise terms, e.g.
+$V_AT(xij)$.}}
 
-{\it (1) A description of the cg model is lacking. Please specify how
-  do you treat and the interaction potential for cg molecules of
-  solvent and solute. I suppose that both types of molecules (solvent
-  and solute) free to cross the hybrid layer.  Please confirm. Please
-  add a section about the cg model.}
+Done. See the new Section IV for a detailed description.
 
-We added it in the appendix. It must be noticed that we actually do
-not need to derive a cg model. In fact our approach allows us to use
-simple spherical models \recheck{(e.g.~interacting via the WCA potential)} whose size is about the vdW radius of the
-specific molecule. It is
-then the thermodynamic force that makes the thermodynamics of the cg
-models compatible with the atomistic one. Molecules change their
-resolution when they pass from one region to another.
-
-{\it (2) Definitions of $V_{AT}$ and $V_{CG}$ are also lacking in terms of particle indexes.
-The model definition is important to distinguish between total energies and pair-wise terms, e.g.
-$V_{AT}(xij)$.}
-
-\recheck{we can refer to the new appendix}
-
-{\it (3) Figure 1. ``allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a GC fashion.'' This phrase is
+{\color{blue}{\it (3) Figure 1. ``allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a GC fashion.'' This phrase is
 difficult to understand. The AT region is connected with the CG domain (via a transition layer which is not small, but much thicker than the
@@
 fashion'' is also difficult to understand (maybe the authors mean ``...consider the AT region as an open subsystem''). I would suggest
-deleting this phrase and refer in the text to their theoretical findings in Ref. 5 about particle number distributions p(N),etc.}
+deleting this phrase and refer in the text to their theoretical findings in Ref. 5 about particle number distributions p(N),etc.}}
 
-Actually this is the very core of our derivation. If the referee think
-that this is wrong, then Ref.5 is entirely wrong.
+Actually this is the very core of our derivation. If the referee think that this is wrong, then Ref.5 is entirely wrong.
 
@@
 is zero. As a consequence the molecules of the atomistic region have a
-well defined Hamiltonian. This is the Hamiltonian of an open system,
-\recheck{and is parametrized by the the coordinate of the molecules
-  that are interacting with the atomistic region}. \recheck{It is comparable with  a
-subsystem of a large full atomistic simulation}; the Hamiltonian of the
-subsystem is well defined, without any artificial interpolation.  This
-is clearly reported in Eq.12 of Ref.5.
+well defined Hamiltonian: The Hamiltonian of an open system.
+It is as we take a subsystem of a full atomistic simulation; the Hamiltonian of the subsystem is well defined, without any artificial interpolation.
+Moreover an open subsystem of a much larger system is naturally Grand Canonical.
+This is clearly reported in Ref.5 and Eq.12 provides the exact definition of the Hamiltonian.
+We have added the exact reference for the equation with the specific Hamiltonian, and we do not believe it should be explicitly reported and discussed in the current paper because it would be redundant and anyway it is not crucial to any of the derivations of this work.
 
-Although we believe it is redundant we have reported the explicit form
-of the Hamiltonian of the atomistic region also in this paper.
+{\color{blue}{\it (4) Page 4. ``...reproduce the first order of the
+    probability...'' and ``Higher orders...'' Could the authors
+    specify what (small) quantity the order is referred to?, I think
+    it could be orders in the density of solute molecules, or maybe in
+    density variation with respect the average. Please be more clear
+    when referring to ``orders'' elsewhere in the manuscript.}}
 
-\recheck{{\bf HAN can you write it for me in Latex}}.
-\recheck{{\bf See below}}
-\begin{align}
-  \mathcal H^{\AT}_{N_1} (\vect x_1; \vect x_2, N_2)
-  =
-  \sum_{i=1}^{N_1}\frac12 m_i\vect v_i^2
-  + \sum_{i,j=1}^{N_1}\frac 12 V^\AT_{i,j}
-  + \sum_{i=1}^{N_1}\sum_{j=N_1+1}^{N_1+N_2} V^\AT_{i,j},
-\end{align}
-where $V^\AT_{i,j}$ is the atomistic molecular potential, which is given by
-\begin{align}
-  V^\AT_{i,j} =
-  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta).
-\end{align}
-where index $\alpha$ and $\beta$ denotes the atoms on the
-corresponding molecule.  $N_1$ and $N_2$ are the number of molecules
-in the AT and atomistic part of the HY region, respectively. $\vect x_1$
-and $\vect x_2$ are the phase space variables (joint of velocity and position)
-in the  AT and atomistic part of the HY region, respectively.
-
-{\it (4) Page 4. ``...reproduce the first order of the
-  probability...'' and ``Higher orders...'' Could the authors specify
-  what (small) quantity the order is referred to?, I think it could be
-  orders in the density of solute molecules, or maybe in density
-  variation with respect the average. Please be more clear when
-  referring to ``orders'' elsewhere in the manuscript.}
-
-\recheck{comment from HAN: why not add your short description on the
-  orders to the paper? It is concise and would be convenient for the
-  readers who are only interested in the numerical result, and do not
-  have time to read Ref.5.}
-
-This is clearly described in Ref.5 and we felt it would be redundant
-to write it here once again; we have defined the first order of the
-probability distribution of a system as its molecular density, a
-function in three-dimension. The second order is the two-body
+This is clearly described in Ref.5; we have defined the first order of
+the probability distribution of a system as its molecular density, a
+function in three-dimensions. The second order is the two-body
 distribution (6-dimensional function) of which the radial distribution
 function is a specific expression; the third order is the three-body
-distribution (in 9-dimension) etc etc. The full probability is a
+distribution (in 9 dimensions) etc etc. The full probability is a
 3N-dimensional function of which the different orders are a lower
@@
 
-If the referee put this as a condition of rejection, then we would add
-it, but we strongly believe that it is not needed for this paper.
+We have added the explicit definition in the revised version of the paper.
 
-{\it (5) Page 5. Auxiliary Hamiltonian. For the sake of clarity, the
-  authors should write down this Hamiltonian they refer to, with full
-  index details. Also, please write down the form of thermodynamic
-  force in the auxiliary Hamiltonian. They mention that simulations
-  using the auxiliary Hamiltonian were made with no thermostat. Did
-  the authors check that the ``energy'' of this Hamiltonian is
-  conserved? Please comment on this important issue.}
-
-\recheck{Comment from HAN: Wo DO use a thermostat for the potential-interpolation
-  simulation.  we should be honest on this point. And the prove in the
-  appendix also assumes that ths thstem is thermostated. Tell me why you wrote ``
-  we do not need to use a thermostat''? Or you simply mean that we in principle we
-  do not need, but in practice, to generate the Boltzmann distribution we use it.}
+{\color{blue}{\it (5) Page 5. Auxiliary Hamiltonian. For the sake of
+    clarity, the authors should write down this Hamiltonian they refer
+    to, with full index details. Also, please write down the form of
+    thermodynamic force in the auxiliary Hamiltonian. They mention
+    that simulations using the auxiliary Hamiltonian were made with no
+    thermostat. Did the authors check that the ``energy'' of this
+    Hamiltonian is conserved? Please comment on this important
+    issue.}}
 
 As before, it is reported in all details in Ref.5 and we thought it
-  was redundant. The thermodynamic force must have exactly the same
-  numerical formula of the standard AdResS, otherwise it would not
-  work for our purposes: if two expressions are formally identical but
-  one has the effect of the thermostat and the other not then the
-  difference isolates the effect of the thermostat. For the
-  Hamiltonian system we use the same formula and impose artificially
-  the same density of the AdResS system thus we get a condition on the
-  gradient of the molecular density in the transition region.
+was redundant, but we have added it in the revised version. The
+thermodynamic force must have exactly the same numerical formula of
+the standard AdResS, otherwise it would not work for our purposes: if
+two expressions are formally identical but one has the effect of the
+thermostat and the other not then the difference isolates the effect
+of the thermostat. For the Hamiltonian system we use the same formula
+and impose artificially the same density of the AdResS system thus we
+get a condition on the gradient of the molecular density in the
+transition region, this is now reported in the paper.
 
-  Yes, we have checked the conservation of the energy. However this
-  was preliminary to everything, in fact it must be clear that if the
-  energy was not conserved, then we would also get completely wrong
-  results (the heat would either be too low or too high and anyway
-  would not converge).
+Yes, we have checked the conservation of the energy and added a
+section dedicated to this issue in the Appendix. There we report the
+advantage and limitations of such an approach (i.e. when we can
+consider pure conservation and when the coupling to a thermostat is
+anyway needed).
 
-  {\it (6) ``Keeps the density of particles across the system as in
-    AdResS''. Do you mean at constant density?}
+{\color{blue}{\it (6) ``Keeps the density of particles across the system as in AdResS''. Do you mean at constant density?}}
 
@@
 
-{\it (7) ``It must be noticed that the relation we obtained form the
-  chem. pot. is similar to that obtained in... Ref[6]''. This
-  statement is not clear. The equation this method proposes seems not
-  similar to that of Ref. 6. In particular the term is quite different
-  from which is the corresponding free energy difference appearing in
-  Ref. 6. The authors should explicitly write out this essential term
-  of the calculation, indicating summations with particle indexes. It
-  would seem from the (not-written auxiliary Hamiltonian) that the
-  particles index of the first ``w'' is not the same as that of the
-  ``nabla w''. Please derive and clarify this term so anybody could
+{\color{blue}{\it (7) ``It must be noticed that the relation we
+    obtained form the chem. pot. is similar to that obtained
+    in... Ref[6]''. This statement is not clear. The equation this
+    method proposes seems not similar to that of Ref. 6. In particular
+    the term is quite different from which is the corresponding free
+    energy difference appearing in Ref. 6. The authors should
+    explicitly write out this essential term of the calculation,
+    indicating summations with particle indexes. It would seem from
+    the (not-written auxiliary Hamiltonian) that the particles index
+    of the first ``w'' is not the same as that of the ``nabla
+    w''. Please derive and clarify this term so anybody could
     understand it.
 
-  The effect of discrepancies with Ref.6 are not simple to trace, but
-  certainly not zero. The authors state: ``H-Adress and CG-Adress are
-  the same up to first order'' (please again, in what?). A reference
-  proving this statement is not mentioned, but I guess the authors
-  refer to Ref. 7 for that prove. However after reading that paper
-  (Ref. 7) I saw no prove of this (just essentially the same phrase,
-  without prove). The authors should prove this statement here or
-  delete this phrase, or comment about the lack of comparisons, at
-  present.}
+    The effect of discrepancies with Ref.6 are not
+    simple to trace, but certainly not zero. The authors state:
+    ``H-Adress and CG-Adress are the same up to first order'' (please
+    again, in what?). A reference proving this statement is not
+    mentioned, but I guess the authors refer to Ref. 7 for that
+    prove. However after reading that paper (Ref. 7) I saw no prove of
+    this (just essentially the same phrase, without prove). The
+    authors should prove this statement here or delete this phrase, or
+    comment about the lack of comparisons, at present.}}
 
-We see the point of the referee, perhaps we should do a paper with
-explicit formulas and data to show similarity and differences between
-the two methods.
+We see the point of the referee, perhaps we should do a paper with explicit formulas and data to show similarity and differences between the two methods.
+However since this is not a relevant part of the paper, we decided to remove any reference to similarities and differences with Ref.6.
+and add the reference from the same authors on mixtures.
 
-However since this is not a relevant part of the paper, we decided to
-remove any reference to similarities and differences with Ref.6.  We
-will cite their second paper dealing with a mixture. We hope that the
-referee is happy with the deletion of Ref.6 and addition of a new
-reference.
+{\color{blue}{\it (8) Fig. 2. Please indicate the locations of the HYB
+    domain. A difference of about 20 percent in density is not small,
+    although *inside* the AT domain, the g(r) might not be too
+    sensible to such density difference (as shown in the fig.). On the
+    other hand, contrary with what the authors state below, a large
+    transition region is beneficial, because molecules have larger
+    space to adapt to the change in resolution. Please correct this.}}
 
-{\it (8) Fig. 2. Please indicate the locations of the HYB domain. A
-  difference of about 20 percent in density is not small, although
-  *inside* the AT domain, the g(r) might not be too sensible to such
-  density difference (as shown in the fig.). On the other hand,
-  contrary with what the authors state below, a large transition
-  region is beneficial, because molecules have larger space to adapt
-  to the change in resolution. Please correct this.}
-
-We disagree with the referee.
-\recheck{The large deviation is due to the sampling error, because the
-  number of TBA molecules in the system is very small (80, see the Table II).
+\recheck{The Fig.2 (Fig.4 in the revision) plots the density profile only for the HYB region, as the caption states.}
+% We disagree.
+\recheck{The relatively large deviation is due to the sampling error, because the
+  number of TBA molecules in the system is very small (80, see the Table II, i.e.~the Table IV in the revision).
   We could reach a much better accuracy of the density if we do longer simulations,
   but it would require much more computer time.}
-% We could reach a much higher accuracy if
-% we set the level of accuracy of the thermodynamic force higher (but
-% requires more computer time)
-However, we wanted to show that even with 20 percent of (maximum)
-difference we get the chemical potential accurate and the density in
-the AT region flat.
-\recheck{comment from HAN: is the HY region goes
-  from 0.5 nm to 3.2 nm, i.e.~the whole range of the figure 2? Then we
-  do not show the density in the AT region is flat.}
+% We could reach a much higher accuracy if we set the level
+% of accuracy of the thermodynamic force higher (but requires more
+% computer time).
+However, we wanted to show that even with 20 percent of
+(maximum) difference we get the chemical potential accurate and the
+density in the AT region flat.
 
-Regarding the point
-that a larger region is beneficial, we must disagree. This is based on
-arguments (which we will give next) and long experience with such
-systems. What is important in AdResS is that the AT and CG region are
-large, in fact if they are large they are going to thermalize and in
-general equilibrate substantially the hybrid region.  We have recently
-made tests on related issues and found that if one uses a large
-thermalized reservoir then small regions where the density or the the
-temperature are not targeted, are automatically equilibrated by the
-large reservoir. Moreover our analytic derivation suggests the same.
-On the contrary a HYB region is charaterized by non physical
-description of the potentials and thus it does not have as a reference
-any thermodynamic state point. As a consequence the larger the HYB
-region the larger the perturbation. Of course there is a minimal size
-that is a region equal to the interaction cut off.  These aspects have
-been explored and described in details in several previous papers
-among which:
+Regarding the point that a larger
+region is beneficial, we must disagree. This is based on arguments
+(which we will give next) and long experience with such systems. What
+is important in AdResS is that the AT and CG region are large, in fact
+if they are large they are going to thermalize and in general
+equilibrate substantially the hybrid region.  We have recently made
+tests on related issues and found that if one uses a large thermalized
+reservoir then small regions where the density or the the temperature
+are not targeted, are automatically equilibrated by the large
+reservoir. Moreover our analytic derivation suggests the same.  On the
+contrary a HYB region is characterized by non-physical description of
+the potentials and thus it does not have as a reference any
+thermodynamic state point. As a consequence the larger the HYB region
+the larger the perturbation. Of course there is a minimal size that is
+a region equal to the interaction cut off.  These aspects have been
+explored and described in details in several previous papers among
+which:
+\begin{itemize}
+\item (1) Matej Praprotnik, Luigi Delle Site, and Kurt Kremer, .J.Chem.Phys. 123, 224106 (2005).
+\item (2)Silvina Matysiak, Cecilia Clementi, Matej Praprotnik, Kurt Kremer and Luigi Delle Site, J.Chem.Phys. 128, 024503 (2008).
+\item (3) S.Poblete, M.Praprotnik, K.Kremer and L.Delle Site,  J.Chem.Phys. 132, 114101 (2010).
+\end{itemize}
 
-(1) Matej Praprotnik, Luigi Delle Site, and Kurt Kremer, .J.Chem.Phys. 123, 224106 (2005).
+{\color{blue}{\it (9) Table I. What results of Ref. 15 corresponds to
+    table I?, this is not mentioned. Results in Ref 12 and 15 were
+    made at lower concentration, but the authors state that the excess
+    chem pot is not sensible to the solute concentration in this
+    regime. And say that ``we have verified that such consistency
+    holds''. This is important though, and the authors should include
+    a graph with the calculated excess chem. pot. against the solute
+    concentration, showing that it goes to a plateau at low
+    concentration consistent with the experimental value reported (at
+    least for some of the cases considered). Error bars are crucial,
+    but means nothing without the simulation times required to obtain
+    them. The authors should include a more clear measure of this. A
+    possible one could be showing the accumulated standard error
+    against the simulation time and compare the IPM, the TI (free
+    energy estimate using Bennet's method) and their own method. With
+    the specification of the system size (table II) this already gives
+    an idea of the computational costs.}}
 
-(2)Silvina Matysiak, Cecilia Clementi, Matej Praprotnik, Kurt Kremer and Luigi Delle Site, J.Chem.Phys. 128, 024503 (2008).
+We have added a plot (for one system) of $\mu^{ex}$
+v.s. concentration, we have shown that the chemical potential
+converges to the experimental value for very dilute
+concentrations. Moreover our plot is consistent with that of Lee and
+van der Vegt, (ref.18) which is supposed to be {\it ``state of the
+  art''} result in the field.  For computational costs, see below.
 
-(3) S.Poblete, M.Praprotnik, K.Kremer and L.Delle Site,  J.Chem.Phys. 132, 114101 (2010).
+{\color{blue}{\it (10) Sec. IV. ...a critical appraisal. This comment
+    is connected with 8). In this section the authors state that their
+    method is not as fast as TI if dilute systems are considered. I
+    would just like to comment that this observation seems to conflict
+    with the comment made in Ref. 7 (``orders of magnitude faster than
+    IPM''). Indeed, Widom method is not very good for large molecules
+    in liquids, this is well known. So, as far I understand, the
+    author's conclusion is that the best option is to use TI for
+    dilute systems while adaptive resolution pays off when dealing
+    with many solute molecules. This observation is important and
+    should be shown in a graph (e.g. standard error vs. simulation
+    time for TI and CG-Adress, in the dilute case and less diluted
+    case)}}
 
-{\it (9) Table I. What results of Ref. 15 corresponds to table I?,
-  this is not mentioned. Results in Ref 12 and 15 were made at lower
-  concentration, but the authors state that the excess chem pot is not
-  sensible to the solute concentration in this regime. And say that
-  ``we have verified that such consistency holds''. This is important
-  though, and the authors should include a graph with the calculated
-  excess chem. pot. against the solute concentration, showing that it
-  goes to a plateau at low concentration consistent with the
-  experimental value reported (at least for some of the cases
-  considered). Error bars are crucial, but means nothing without the
-  simulation times required to obtain them. The authors should include
-  a more clear measure of this. A possible one could be showing the
-  accumulated standard error against the simulation time and compare
-  the IPM, the TI (free energy estimate using Bennet's method) and
-  their own method. With the specification of the system size (table
-  II) this already gives an idea of the computational costs.}
+We have added a table where we show the total time needed to calculate
+$\mu^{ex}$ with GC-AdResS and with TI.  The table show that the total time
+needed for obtaining the plot of $\mu^{ex}$ v.s. concentration is
+slightly shorter with our method than with TI.  Moreover one must add
+the fact that we use relatively small system (5000 molecules) and that
+GC-AdResS is not yet optimized in Gromacs.  We hope that this is a
+good argument to convince the referee that maybe it is worth to look
+at GC-AdResS as a potential complementary (not substitutive) method
+for calculating $\mu^{ex}$.
 
-We do understand the concerns of the referee about the values referred
-to paper in Ref.15, however all the values in the table for TI were
-obtained by us.  We have checked (the sentence {\it ``we have verified
-  such a consistency''}) that our values are close to those at lower
-concentration.  We have also made the (expensive) calculation of the
-concentration dependence and show that indeed goes towards a plateau
-added the error etc etc.  The figure and related comments have been
-added in the revised version of the manuscript.
+{\color{blue}{\it (11) Recent works: an extension to the Hamiltonian
+    based method the authors refer to, appeared in
+    ``Phys. Rev. Lett. 2013, 111, 060601''. This work should be cited
+    because it precisely deal with mixtures being in close relation
+    with this work.}}
 
-However, at the current stage the comparison about the computational time required by AdResS and TI would not be fair.
-In fact for this reason we have {\bf honestly} reported current numerical limitations in Section IV.
+Done.
 
-This paper is about the capability and numerical accuracy of the approach.
+\newpage
 
-{\it (10) Sec.
-IV.
-...a critical appraisal.
-This comment is connected with 8).
-In this section the authors state that their method is not as fast as TI if dilute systems are considered.
-I would just like to comment that this observation seems to conflict with the comment made in Ref.
-7 (``orders of magnitude faster than IPM'').
-Indeed, Widom method is not very good for large molecules in liquids, this is well known.
-So, as far I understand, the author's conclusion is that the best option is to use TI for dilute systems while adaptive resolution pays off when dealing with many solute molecules.
-This observation is important and should be shown in a graph (e.g.
-standard error vs.
-simulation time for TI and CG-Adress, in the dilute case and less diluted case)}
+{\bf Reply to Reviewer 2}:
 
-NO, we only say that in the future, AdResS, once its implementation is optimized, may even offer a better way to calculate the chemical potential in some situations, at the moment, although in very recent work we have reached a speed up factor of more than two w.r.t.
-full atomistic simulation, the computational implementation of AdResS in Gromacs is still not optimal.
-What we instead claim (for sure) is that if you do in any case an AdResS simulation, you automatically get the chemical potential, that is this is an automatic feature of the simulation method.
-This is reported clearly in the paper and we believe that it does not need further clarifications.\\
-
-{\it (11) Recent works: an extension to the Hamiltonian based method the authors refer to, appeared in ``Phys.
-Rev.
-Lett.
-2013, 111, 060601''.
-This work should be cited because it precisely deal with mixtures being in close relation with this work.}
-
-OK, as said before we cite this instead of Ref.6.
-
-{\bf Reply to Reviewer 2}:\\
-
- {\it I would recommend that the authors consider the following minor revisions.
-Most significantly, it would be very helpful for the authors to discuss the apparently systematic errors that arise in their estimation of the chemical potentials.
-The following provides further details and minor comments.
-
-Table 1 compares the chemical potentials determined from GC-AdResS and thermodynamic integration (TI).
-(It would be helpful to know the basis for estimating the uncertainty of these calculations.) The results indicate that there is a fairly small, but systematic discrepancy between the two methods.
-In particular, in almost all cases, GC-AdResS underestimates the magnitude of the chemical potential.
-It would be very interesting and helpful if the authors could investigate and provide insight into the origin of this discrepancy.}
+{\color{blue}{\it I would recommend that the authors consider the
+    following minor revisions. Most significantly, it would be very
+    helpful for the authors to discuss the apparently systematic
+    errors that arise in their estimation of the chemical
+    potentials. The following provides further details and minor
+    comments. Table 1 compares the chemical potentials determined from
+    GC-AdResS and thermodynamic integration (TI). (It would be helpful
+    to know the basis for estimating the uncertainty of these
+    calculations.) The results indicate that there is a fairly small,
+    but systematic discrepancy between the two methods. In particular,
+    in almost all cases, GC-AdResS underestimates the magnitude of the
+    chemical potential. It would be very interesting and helpful if
+    the authors could investigate and provide insight into the origin
+    of this discrepancy.}}
 
 The only reason that came to our mind is that such a systematic difference may come from the interaction cut off.
-In fact, currently, we are using the reaction field method for electrostatics and thus the accuracy may indeed depend on that.\\
-We found this point very interesting and studied the dependence of our results from the cut off. Indeed it seems that, etc etc...... {\bf WHEN ANIMESH IS READY}\\
+In fact, currently, we are using the reaction field method for electrostatics and thus the accuracy may indeed depend on that.
 
-{\it  I am somewhat confused by the notation for $F_{th}$.
-Is this a vector quantity?
-Is the integral on page 3 giving a vector or a scalar?
-The notation seems confusing and inconsistent.
-Also, I am confused by the first equality sign after $F_{th}$.
-It would be helpful if the authors could clarify this.}
+In the revised version we have added a plot that shows the convergence
+of $\mu^{ex}$ as a function of the interaction cut-off.  Indeed we can
+systematically improve our results if we go to higher cut-off (for
+systems whose electrostatics is particularly relevant).  However, we
+also show that for a cut-off of 1.4 nm (standard in full atom
+simulations) we already reach a quite accurate value.  This is
+reported and commented in the revised version.
 
-We apologize for the misprint, the term $F_{th}=$ has been removed\\
+{\color{blue}{\it I am somewhat confused by the notation for
+    $F_{th}$. Is this a vector quantity? Is the integral on page 3
+    giving a vector or a scalar? The notation seems confusing and
+    inconsistent. Also, I am confused by the first equality sign after
+    $F_{th}$. It would be helpful if the authors could clarify this.}
+}
 
-{\it On page 5, the authors indicate that equipartition implies a
-  contribution to the chemical potential of 1/2 kT for each atomic
-  degree of freedom (dof). I would expect that this would be true if
-  each atomic dof contributes quadratically to the Hamiltonian. It
-  would be helpful if the authors could clarify why this would be so
-  for dof's that do not contribute quadratically to the Hamiltonian.}
+We apologize for the misprint, the term $F_{th}=$ has been removed, and now the quantity is well defined.
+
+{\color{blue}{\it On page 5, the authors indicate that equipartition
+    implies a contribution to the chemical potential of 1/2 kT for
+    each atomic degree of freedom (dof). I would expect that this
+    would be true if each atomic dof contributes quadratically to the
+    Hamiltonian. It would be helpful if the authors could clarify why
+    this would be so for dof's that do not contribute quadratically to
+    the Hamiltonian.}}
 
@@
 
-{\it  It would be helpful if the authors could clarify why/how eq 3 generalizes to eq 4 in the case of a multicomponent system}
+{\color{blue}{\it  It would be helpful if the authors could clarify why/how eq 3 generalizes to eq 4 in the case of a multicomponent system}}
 
-\recheck{\bf Added below... I do not really know what to write for him/her.}
-
- We denote the volume of the system by $V$ and the temperature by
-$T$. It is divided into atomistic~($\AT$), hybrid~($\HY$), and
-coarse-grained~($\CG$) region, the volume of which are denoted by
-$V_1$, $V_2$ and $V_3$, respectively.  We assume two different types
-of molecules are mixed in the system, and the number of molecules are
-$N^1$ and $N^2$, respectively. The superscript ``1'' and ``2'' in the
-paper denotes the two component.  We further denote the number of type
-1 molecules in the atomistic, hybrid, and coarse-grained regions by
-$N^1_1$, $N^1_2$ and $N^1_3$, respectively. While for type 2 molecules
-the notations are $N^2_1$, $N^2_2$ and $N^2_3$, respectively.  By
-assuming the hybrid region is infinitely small comparing with the
-atomistic and coarse-grained regions, we have the following
-constrains:
-\begin{align}
-  V &= V_1 + V_3\\
-  N &= N^1 + N^2\\
-  N^1 &= N^1_1 + N^1_3\\
-  N^2 &= N^2_1 + N^2_3
-\end{align}
-By calculating the thermodynamic forces for both of the components, which
-are denoted by $\vect F^1_\thf$ and $\vect F^2_\thf$,
-we impose the correct density profile to the system:
-\begin{align}
-  \rho_\HY^1 &= \rho_\AT^1 = \rho_\CG^1\\
-  \rho_\HY^2 &= \rho_\AT^2 = \rho_\CG^2
-\end{align}
-We further denotes the work done by the hybrid region on the two types
-of molecules by $\omega_0^1$ and $\omega_0^2$, respectively.
-To find out the chemical potential difference between AT and CG resolutions,
-the same idea as presented in Sec.III.C of Ref.5 can be extended
-to the two component system. This extension is straightforward and trivial. We do not want
-to write them down, because one can just step-by-step follow the
-deriviation for the one component system, and no new technique is needed.
-In the end, we proved
-\begin{align}
-  \mu^1_\AT(N^1_1, N^2_1, V_1, T) &= \mu^1_\CG(N^1_1, N^2_1, V_1, T) - \omega^1_0\\
-  \mu^2_\AT(N^1_1, N^2_1, V_1, T) &= \mu^2_\CG(N^1_1, N^2_1, V_1, T) - \omega^2_0
-\end{align}
-Now, $N^1_1$ and $N^2_1$ denotes the averaged number of type 1 and
-type 2 molecules in the atomistic region.  Under the thermodynamic
-limit, this number maximize the Helmholtz free energy and is the one
-of statistical importance, see more discussions in
-Ref.5. We do not distinguish these notations from
-before, because the meaning is clear from the context.
-
-Sincerely\\
-
-Luigi Delle Site
+We have added an analytic derivation of the extension to
+multicomponent systems in the appendix.  We have tried to give the
+essential physical arguments, but cannot avoid the lengthy discussion
+otherwise crucial point may be missed.
 

### 2014-05-20 writeDown/pub.jcp/chem-pot-jcp.tex
revise...

@@
 \newcommand{\typeb}{{\textrm{B}}}
+\newcommand{\concenttba}{x_{\textrm{TBA}}}
 
@@
 It must be noticed that differently from the original AdResS, in GC-AdResS the range of definition of $w(x)$ is extended of an amount of ${\vect R}_{c}$.
-The extension of this additional region is equal to the cutoff radius of the atomistic interactions and $w(x)$ takes the constant value of $1$.
+The extension of this additional region is equal to the cut-off radius of the atomistic interactions and $w(x)$ takes the constant value of $1$.
 The consequence is that molecules in the atomistic region interact with the rest of the system always and only via well defined atomistic interactions.
@@
 Moreover we have shown that, because of the necessary conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
-
 In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure \recheck{using} the molecular number density in $\Delta$.
@@
 $\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-\recheck{While the determination of $\omega_{\dof}$ is not required for the our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
+\recheck{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
 However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS.
@@
 \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
-the probability distribution of the system as defined in Eq.\ref{order}}.
+the probability distribution of the system as defined in Eq.\ref{order}}.\\
 
@@
 
-\section{Analytic Derivation of the $w_{\ext}$}\label{sec:tmp4}
+\section{Analytic Derivation of  $w_{\ext}$}\label{sec:tmp4}
 \recheck{In this section we derive analytically the equivalence:
@@
 Moreover, systems as water/urea are commonly used as cosolvent of biological molecules \cite{nico-debashish} while systems as tert-Butyl alcohol/water play a key role in modern technology \cite{irata}, thus they are of high interest {\it per se}.
-All technical details of each simulation are presented in the Appendix~\ref{app:tmp1}.
-Results are reported in Table \ref{table} where the comparison with values obtained using full atomistic TI and available experiments, at the same concentrations, of our calculation is made; in our previous work we have already shown that value of the chemical potential of liquid water obtained with IPM is well reproduced by GC-AdResS, however the computational cost of IMP was very large, thus we do not consider calculations done with IPM in this paper.
+All technical details of each simulation are presented in the Appendix~\ref{app:tmp1}.\\
+
+Results are reported in Table \ref{table}, where the comparison with values obtained using full atomistic TI and available experiments, at the same concentrations, of our calculation is made; in our previous work we have already shown that value of the chemical potential of liquid water obtained with IPM is well reproduced by GC-AdResS, however the computational cost of IMP was very large, thus we do not consider calculations done with IPM in this paper.
 The agreement with full atomistic TI simulations is satisfactory in all cases, and thus it proves the solidity of GC-AdResS in describing the essential thermodynamics of a large class of systems.
 We also compare the obtained values with those available in literature \cite{vang,nico}.
-Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; we have verified  such a supposed consistency.
+Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; \recheck{we have verified  such a supposed consistency for one relevant system (see discussion about Fig.\ref{concentration})}.
 The chemical potential of $k$-th liquid's component in a mixture is calculated as \recheck{(see Appendix~\ref{app:tmp3})}:
@@
 \end{equation}
-where ${F}^{k}_{\thf}(x)$ is the thermodynamic force applied to the molecules of the $k$-th component; this assures that, at the given concentration, the density of molecules of species $k$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
-\recheck{The ensemble average is taken over the position of the second molecule, provided that the first molecule is of species $k$, and located at position $\vect r$}.
-% $\nabla_{x_{i}} w(x)$ is the gradient along $x$ (in a rectangular box) applied to the switching function $w(x)$ in the COM of molecules of component $i$.
+where $\vect{F}^{k}_{\thf}(x)$ is the thermodynamic force applied to the molecules of the $k$-th component; this assures that, at the given concentration, the density of molecules of species $k$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
+\recheck{The ensemble average is taken over the position of the second molecule, provided that the first molecule is of species $k$, and located at position $\vect r$}.\\
 
-\begin{table}[htpb]
+\begin{table}[]
 \begin{center}
@@
 \hline
-water    & -- & -22.8 $\pm$ 0.2  & -22.1 $\pm$ 0.3 & -23.5 \cite{florian} \\
+\recheck{water} & -- & -22.1 $\pm$ 0.2  & -- & -23.5 \cite{florian} \\
 methane  & -- & -4.6 $\pm$ 0.1  & -5.2 $\pm$ 0.1 & -- \\
@@
 propane  & -- & -8.5 $\pm$ 0.1 & -9.5 $\pm$ 0.2 & -- \\
-methanol  & -- & -20.1 $\pm$ 0.1 & -20.6 $\pm$ 0.4 & -20.5 \cite{vang}  \\
+\recheck{methanol}  & -- & -20.3 $\pm$ 0.2 & -20.9 $\pm$ 0.3 & -20.5 \cite{vang}  \\
 DMSO & -- & -32.2 $\pm$ 0.3 & -34.7 $\pm$ 0.7 & -32.2 \cite{dmso}  \\
-methanol in methanol/water mixture & 0.01 & -18.1 $\pm$ 0.2 & -19.7 $\pm$ 0.2 & -- \\
-methane in methane/water mixture & 0.006 & 9.1 $\pm$ 0.1  & 8.5 $\pm$ 0.2 & -- \\
+\recheck{methanol in methanol/water mixture} & 0.01 & -19.0 $\pm$ 0.2 & -- & -- \\
+\recheck{methane in methane/water mixture} & 0.006 & 9.3 $\pm$ 0.2  & -- & -- \\
 urea in urea/water mixture & 0.02 & -56.1 $\pm$ 0.6 & -58.2 $\pm$ 0.5 & -57.8 $\pm$ 2.5 \cite{urea} \\
-ethane in ethane/water mixture & 0.006 & 7.2 $\pm$ 0.2 & 7.4 $\pm$ 0.3 & -- \\ 
-TBA in water/TBA mixture & 0.02 & -20.5 $\pm$ 0.6 & -21.4 $\pm$ 0.5 & -- \\
+\recheck{ethane in ethane/water mixture} & 0.006 & 7.2 $\pm$ 0.2 & -- & -- \\ 
+\recheck{TBA in water/TBA mixture} & 0.001 & -19.5 $\pm$ 0.5 & -20.8 $\pm$ 0.6 & -19.0 \cite{nico} \\
 DMSO in DMSO/water mixture & 0.01 & -31.4 $\pm$ 0.5 & -33.2 $\pm$ 0.3 & -- \\
@@
 \end{tabular}
-\caption{The excess chemical potential of different liquids and mixtures in $kJ/mol$ calculated from GC-AdResS and TI of full atomistic simulations.
+\caption{The excess chemical potential of different liquids and mixtures in kJ/mol calculated from GC-AdResS and TI of full atomistic simulations.
 Experimental values for systems at the same concentrations used in simulation are also reported for comparison.
 For pure systems (water and methanol) we compare our values with those obtained in literature using the same force field and computational code.
-For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); however since we are always in a very dilute regime the chemical potential does not change significantly; we have verified that such consistency holds.
+For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); However, since we are always in a very dilute regime the chemical potential does not change significantly.
+\recheck{We have provided evidence for the TBA/water misture that such consistency holds (see Fig.\ref{concentration})}.
 Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
@@
 \end{table}
+
+\begin{figure}
+\center
+\includegraphics[width=0.475\textwidth]{convergence.eps}
+\caption{ \recheck{Excess chemical potential of Dimethyl sulfoxide (DMSO) in water as a function of cut-off radius calculated using GC-AdResS.
+The value obtained from thermodynamic integration calculation in also shown, with a gray region indicating the standard deviation.
+This value was calculated using a cut-off radius of $1.4$~nm.
+It was seen that the value does not change significantly if the cut-off radius is varied.}}
+\label{convergence}
+\end{figure}
+
+\begin{figure}
+\center
+\includegraphics[width=0.475\textwidth]{concentration.eps}
+\caption{ \recheck{Excess chemical potential of t-butyl alcohol (TBA) in water for different concentrations (in logarithmic scale), calculated using GC-AdResS.
+The results are compared with thermodynamic integration values.
+At mole-fraction $\concenttba=0.001$, the experiment value is shown.
+\label{concentration}}}
+\end{figure}
+
+\recheck{A complementary information to Table~\ref{table} is
+  Fig.\ref{convergence}. In
+  Table~\ref{table}, there is a systematic difference of
+  $1.2 \sim 2.0$~kJ/mol between our values and those of TI
+  calculations. In order to understand the possible origin of such a
+  discrepancy and provide a way to eventually improve the accuracy of
+  results, we have studied the behavior of $\mu^{ex}$ as a function of
+  the interaction cut-off. In fact the current version of GC-AdResS,
+  employs the reaction field method for treating electrostatic
+  interactions in the atomistic region, and the cut off is likely to
+  play a role. Fig.\ref{convergence}, for the case of DMSO/water
+  mixture, confirms our intuition and suggests that we could
+  systematically improve the accuracy by increasing the cut-off,
+  however at a value of about $1.5$~nm, $\mu^{ex}$ converges. In any
+  case, at a values of $1.4$~nm, which is the one routinely used in
+  full atomistic simulations and used by us in all calculations, the
+  value obtained with GC-AdResS is already satisfactory.\\
+
+  A further
+  question that may arise is the capability of our method to predict
+  the behavior of $\mu^{ex}$ as a function of the concentration, above
+  all in the very dilute regime. In Fig.\ref{concentration} we have
+  performed such a study for the case of TBA/water mixture, we show a
+  good agreement between GC-AdResS and TI and show that at a very
+  dilute concentration our calculated value is close to that of
+  experiments, moreover the trend, regarding the TI calculations, is
+  consistent with that reported in Ref.\cite{nico}.\\}
 
@@
 \end{figure}
-
 In essence, according to the results obtained, GC-AdResS allows an on-the-fly determination of $\mu^{ex}$ of each component of a liquid, whenever a simulation is performed, without extra computational costs.
@@
 The agreement with data from a full atomistic simulation is highly satisfactory.
-Moreover, it must be underlined that, on purpose, we have chosen extreme technical conditions, that is, a very small atomistic and coarse-grained region ($0.5 nm$) and a relatively large transition region ($2.7 nm$).
+Moreover, it must be underlined that, on purpose, we have chosen extreme technical conditions, that is, a very small atomistic and coarse-grained region ($0.5$~nm) and a relatively large transition region ($2.7$~nm).
 Even in these conditions we prove that local properties as those of Fig.\ref{urea-TBA} and Fig.\ref{gr}, together with a relevant thermodynamics quantity as $\mu^{ex}$ are well reproduced.
@@
 
+\section{Efficiency}
+
+\recheck{In order to show the numerical efficiency of our approach, we compare the time taken to do a full GC-AdResS simulation and the time for a thermodynamic integration calculation for
+different systems with varied concentration of TBA in water. The total time required for an GC-AdResS simulation consists of 
+the time taken to obtain a converged thermodynamic force and the time taken to obtain the coarse-grained chemical potential. 
+The time taken to complete TI procedure at each value of $\lambda$ is summed up to obtain the total time. In this work, the TI 
+is done in two stages, first the van der Waals  interactions are coupled followed by the electrostatic coupling. At each stage, 21 
+equally distributed values of $\lambda$ are used,
+therefore, in total 42 simulations were performed to calculate each TI chemical potential value.
+% However, in literature, a single stage procedure which consists of coupling 
+%  van der Waals and electrostatic interactions together is followed. In order to have a fair comparison, we have compared GC-AdResS time
+% to the single-stage TI procedure. Also, GC-AdResS calculations have been done in a more optimized way, by using a spherical atomistic region and 
+% a transition region of $1.4 nm$ each. 
+In an AdResS simulation, the initial guess of the thermodynamic force largely determines the time for convergence. 
+We started with a randomly chosen initial guess
+($-42$~kJ/mol, we picked a very small value because the TBA molecule is highly hydrophilic)
+for system with the highest mole fraction of TBA. For all the other systems, 
+we used the converged thermodynamic force obtained from the first system as an initial guess. The convergence was much 
+faster in all the other cases using this approach. Table~\ref{table3} shows the number of iterations required for 
+the thermodynamic force convergence in GC-AdResS and total time required for GC-AdResS and TI calculation.
+% The total time for the all the calculations is 66 hours in GC-AdResS and 72 hours in TI.
+The advantage of GC-AdResS over TI
+is that we get two values of excess chemical potential for both solute and solvent in a single calculation, while 
+in TI, the whole process has to be repeated to get the excess chemical potential of other component. For very dilute systems ($\concenttba=0.001$), 
+however, one has to take a very large systems in GC-AdResS (see the Appendix~\ref{app:tmp1} for system size).
+It takes a large amount of time for the thermodynamic force to reach convergence, and hence TI is always a better option at such low concentrations with a much
+smaller system size at the same mole fraction.
+
+\begin{table}[htpb]
+\begin{center}
+\begin{tabular}{|l|c|r|r|}
+\hline
+ &\multicolumn{2}{c|}{GC-AdResS}&\multicolumn{1}{l|}{TI}\\
+ \hline
+$\concenttba$ &No. of iterations&Time(hrs.)&Time(hrs.)\\
+\hline
+0.200 & 20 & 52.4 & 30.8 \\
+0.160 & 5 & 15.1 & 31.0 \\
+0.120 & 5 & 16.3 & 29.9 \\
+0.040 & 8 & 27.2 & 26.7 \\
+0.020 & 8 & 28.8 & 26.6 \\  
+0.001* & 20 & 252 & 202 \\
+\hline
+\end{tabular}
+\caption{Time required for a full GC-AdResS and thermodynamic
+  integration (TI) calculation for tbutyl-alcohol(TBA) in water at
+  different mole-fractions.
+  The ``*'' means that a larger system was used for  the very dilute system ($\concenttba=0.001$), see Appendix~\ref{app:tmp1} for details.
+  All the simulations were performed on a
+  workstation that has two Quad-Core AMD Opteron(tm) 2376 Processors.
+  % Quad-Core AMD machine on the same number of processors.
+}
+\label{table3}
+\end{center}
+\end{table}
+}
+
 \section{Current computational convenience: a critical appraisal}
 The natural question arising from the discussion above is whether or not GC-AdResS is a more convenient technical tool for calculating $\mu^{ex}$ compared to TI.
-Currently the answer is negative although the current work is the first step towards a potentially positive answer for the future.
+Currently the answer is \recheck{neither negative nor positive}, although the current work is the first step towards a potentially positive answer for the future.
 In fact, the fastest version of AdResS is implemented in the GROMACS code \cite{gromacs}; using the Gromacs version 4.5.1 a speedup of a factor four with respected to full atomistic simulations has been reported for aqueous mixtures~\cite{debashish1,nico-debashish}.
@@
 However in the successive version of GROMACS 4.6.1 the performance of atomistic simulations (above all of SPC/E water) has been highly improved while the corresponding implementation of AdResS is not optimized yet.
-At the current state, AdResS can only assure a speed up factor between \recheck{2 and 3} for large systems (30000 molecules) compared to full atomistic simulations \recheck{( for systems without SPC/E water)}.
-As a consequence for the calculation of $\mu^{ex}$, TI is computationally less demanding than AdResS.
+At the current state, AdResS can only assure a speed up factor between \recheck{2 and 3} for large systems (30000 molecules) compared to full atomistic simulations \recheck{(except for pure SPC/E water systems)}.
+As a consequence for the calculation of $\mu^{ex}$, TI is in general computationally less demanding than AdResS .
 Another point that must be considered (in perspective) for a fair comparison between TI and GC-AdResS, is the following: even if AdResS is optimized, in any code, TI has the advantage that one can use one single molecule in the simulation box to mimic the minor component of a mixture.
@@
 of both components in one simulation run, whereas in TI, one needs to run two separate simulations in order to get the chemical potential of both components.
-However, at the current state, the technical aspects of code optimization must be reported and we must make clear that the aim of this work is to show that  the automatic calculation of $\mu^{ex}$, independently from the simulation code in which is implemented and its computational cost, is a ``conceptual'' feature of GC-AdResS.
+\recheck{The results reported in the previous section about the current efficiency of GC-AdResS are rather encouraging, however currently there is not a clear convenience in using GC-AdResS instead of TI for calculating $\mu^{ex}$;
+in any case the technical aspects of code optimization must be reported and we must make clear that the aim of this work is to show that  the automatic calculation of $\mu^{ex}$, independently from the simulation code in which is implemented and its computational cost, is a ``conceptual'' feature of GC-AdResS}.
 
@@
 model~\cite{spc}, methanol was described by the model developed by Walser et al~\cite{walser},
-urea by the model described in~\cite{urea}, tert-butyl alcohol by the parameter set of~\cite{tba}
+urea by the model described in~\cite{urea}, tert-butyl alcohol by the parameter set of~\cite{nico}
 and DMSO was described by the model given by Geerke et.al.~\cite{dmso1}. For liquid methanol simulations, 
 GROMOS43A1 parameter set was used, as it was shown to be more accurate for calculating excess free energy of 
-solvation of methanol in methanol~\cite{vang}.
+solvation of methanol in methanol~\cite{vang}. \\
 
@@
 at 298 K. Simulations of liquid methane and ethane were performed at
-111.66 K and 184.52 K respectively. To obtain the chemical potential of coarse-grained component, 
-insertion particle method was used, where a trajectory of 8 ns was obtained and the coordinates were written
-after every 0.4 ps. The insertions of the molecule were performed 4,000,000 times in each 
-frame at random locations and with random orientations of the molecule. The chemical potential value and
-the error were calculated by taking the average and standard deviation of the last ten iterations.
+111.66 K and 184.52 K respectively. \recheck{As it was discussed in~\cite{prx}, there is no requirement 
+of a coarse-grained model that resembles the structural and thermodynamic properties of a full atomistic
+model. It was shown numerically that the proper exchange of energy and molecules was independent from the 
+molecular model used in the coarse-grained region, showing the convenience of GC-AdResS. In this work, a generic WCA potential was used in the 
+coarse-grained region. The interaction potential between the coarse-grained particles is given by 
+\begin{equation}
+  U(r) = 4 \epsilon \left[\left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^{6}\right] + \epsilon,
+  \quad
+  r \leq 2^{1/6}\sigma. 
+\end{equation}
+The parameters $\sigma$ and $\epsilon$ were chosen such that the radial distribution functions of particles 
+reproduce a liquid structure. For water molecule, the parameters used in this study are $\epsilon=0.65$~kJ/mol
+and $\sigma=0.30$~nm. Table~\ref{cg} shows the WCA parameters for other molecules used in this work.
+For interactions between solute and solvent, $\sigma$ values were obtained by 
+averaging over the individual parameters.
+The solute-solvent $\epsilon$ is the same as the solute-solute  $\epsilon$.
+\\
+}
+
+\begin{table}[]
+\begin{center}
+\begin{tabular}{ccc}
+\hline \hline
+ System & $\epsilon (kJ/mol)$ & $\sigma (nm)$ \\
+\hline
+methane & 0.65 & 0.40 \\
+ethane & 0.20 & 0.50 \\
+propane & 0.65 & 0.55 \\
+methanol & 0.65 & 0.40 \\
+DMSO & 0.30 & 0.50 \\
+methanol in methanol/water & 0.65 & 0.40 \\
+methane in methane/water & 0.65 & 0.40 \\
+urea in urea/water & 0.65 & 0.40 \\
+ethane in ethane/water & 0.65 & 0.45 \\
+TBA in TBA/water & 0.65 & 0.60\\
+DMSO in DMSO/water & 0.65 & 0.50 \\
+TBA in TBA/DMSO & 0.40 & 0.60 \\
+DMSO in TBA/DMSO & 0.30 & 0.50 \\
+\hline \hline
+\end{tabular}
+\caption{WCA parameters for different coarse-grained molecules used in this work}
+\label{cg}
+\end{center}
+\end{table}
+
+To obtain the chemical potential of coarse-grained component, 
+insertion particle method was used, where a trajectory of 8~ns was obtained and the coordinates were written
+after every 0.4~ps. The insertions of the molecule were performed 4,000,000 times in each 
+frame at random locations and with random orientations of the molecule.  
+\recheck{The excess chemical potential value was calculated by averaging over the last ten iterations after 
+the thermodynamic force has converged and the statistical uncertainty is determined by the standard deviation in the data. \\}
 
@@
 continuously decreased in the stepwise manner. Simulations conducted at different values of 
-$\lambda$ allow to plot a $\frac{\partial H}{\partial \lambda}$ curve, from which 
+$\lambda$ allow to plot a \recheck{$\frac{\partial U_{i}(\lambda)}{\partial \lambda}$} curve, from which 
 $\mu^{\exc}$ is derived \cite{mu}. 
+\recheck{
 \begin{equation}
- \mu^\exc_{iB} - \mu^\exc_{iA} = \int_{0}^{1} \left \langle \frac{\partial H}{\partial \lambda} \right \rangle_{\lambda} d\lambda 
+ \mu^\exc_{iB} - \mu^\exc_{iA} = \int_{0}^{1} \left \langle \frac{\partial U_{i}(\lambda)}{\partial \lambda} \right \rangle_{\lambda} d\lambda 
 \end{equation}
-\bluec{where $U_{i}$ is the interaction energy of particle $i$ with the remaining particles} and $\langle \cdot \rangle$
+}
+where $U_{i}$ is the interaction energy of particle $i$ with the remaining particles and $\langle \cdot \rangle$
 denotes the canonical (NVT) or isobaric-isothermal (NPT) ensemble average. We computed the excess 
@@
 were calculated through Bennet's acceptance ratio method (BAR)~\cite{bar}. 
-For both the AdResS and full-atom simulations, the system size was kept same. Below is a table 
-with number of solute molecules, solvent molecules, system dimensions, size of transition and atomistic region (in AdResS simulations)
-for each system studied. 
-\begin{table}[!ht]
+For both the AdResS and full-atom simulations, the system size was kept same.
+\recheck{Table~\ref{table2} gives a detailed summary of each system studied}.\\
+
+\begin{table}[]
 \begin{center}
@@
 \hline \hline
- System & $N_{solute}$ & $N_{solvent}$ & System size ($nm^{3}$) &  AT + HY region ($nm^{3}$)  \\
+ System & $N_{solute}$ & $N_{solvent}$ & System size ($\textrm{nm}^{3}$) &  AT + HY region ($\textrm{nm}^{3}$)  \\
 \hline
-water    & --- & 13824 & $29.9 \times 3.7 \times 3.7$ & $6.7 \times 3.7 \times 3.7$ \\
+\recheck{water} & --- & 13824 & $30.2 \times 3.8 \times 3.8$ & $14.6 \times 3.8 \times 3.8$ \\
 methane & --- & 2000 & $9.0 \times  3.7 \times 3.6$ & $6.0 \times 3.7 \times 3.6$ \\
@@
 propane & --- & 1433 & $10.0 \times 4.5 \times 4.5$ & $7.0 \times 4.5 \times 4.5$ \\
-methanol & --- & 3200 & $9.6 \times 4.8 \times 4.8$ & $6.8 \times 4.8 \times 4.8$ \\
+\recheck{methanol} & --- & 4000 & $12.0 \times 4.6 \times 4.5$ & $7.4 \times 4.6 \times 4.5$ \\
 DMSO & --- & 1500 & $15.0 \times 3.6 \times 3.3$ &  $7.0 \times 3.6 \times 3.3$ \\
-methanol/water mixture & 40 & 3960 & $9.2 \times 3.7 \times 3.7$ & $6.5 \times 3.7 \times 3.7$ \\
-methane/water mixture & 40  & 6960 & $10.0 \times 4.8 \times 4.7$ & $6.5 \times 4.8 \times 4.7$ \\
-urea/water mixture & 50 & 2500 & $9.7 \times 2.9 \times 2.8$ & $6.8 \times 2.9 \times 2.8$ \\
-ethane/water mixture & 40 & 6960 & $10.0 \times 4.7 \times 4.6$ & $6.5 \times 4.7 \times 4.6$ \\ 
-TBA/water mixture & 80 & 4400 & $10 \times 3.9 \times 3.8$ & $6.5 \times 3.9 \times 3.8$  \\
-DMSO/water mixture & 50 & 4950 & $12.0 \times 4.0 \times 3.3$ & $7.0 \times 4.0 \times 3.3$ \\
-TBA/DMSO mixture & 80 & 4400 & $10.0 \times 7.3 \times 7.2$ &  $7.0 \times 7.3 \times 7.2$ \\
+\recheck{methanol/water} & 128 & 12672 & $29.5 \times 3.7 \times 3.7$ & $14.6 \times 3.7 \times 3.7$ \\
+\recheck{methane/water} & 40  & 6960 & $10.0 \times 4.8 \times 4.7$ & $7.0 \times 4.8 \times 4.7$ \\
+urea/water & 50 & 2500 & $9.7 \times 2.9 \times 2.8$ & $6.8 \times 2.9 \times 2.8$ \\
+\recheck{ethane/water} & 40 & 6960 & $10.0 \times 4.7 \times 4.6$ & $7.0 \times 4.7 \times 4.6$ \\
+\recheck{TBA/water ($\concenttba=0.001$)} & 40 & 39960 & $50.1 \times 5.8 \times 4.3$ & $7.0 \times 5.8 \times 4.3$  \\
+\recheck{TBA/water ($\concenttba=0.02$)} & 80 & 4400 & $10 \times 3.6 \times 4.2$ & $7.0 \times 3.6 \times 4.2$  \\
+\recheck{TBA/water ($\concenttba=0.04$)} & 180 & 4300 & $10 \times 4.3 \times 3.7$ & $7.0 \times 4.3 \times 3.7$  \\
+\recheck{TBA/water ($\concenttba=0.12$)} & 538 & 3942 & $10 \times 4.4 \times 4.6$ & $7.0 \times 4.4 \times 4.6$  \\
+\recheck{TBA/water ($\concenttba=0.16$)} & 717 & 3763 & $10 \times 4.9 \times 4.6$ & $7.0 \times 4.9 \times 4.6$  \\
+\recheck{TBA/water ($\concenttba=0.20$)} & 896 & 3584 & $12 \times 4.6 \times 4.5$ & $7.0 \times 4.6 \times 4.5$  \\
+DMSO/water & 50 & 4950 & $12.0 \times 4.0 \times 3.3$ & $7.0 \times 4.0 \times 3.3$ \\
+TBA/DMSO & 80 & 4400 & $10.0 \times 7.3 \times 7.2$ &  $7.0 \times 7.3 \times 7.2$ \\
 \hline \hline
 \end{tabular}
-\caption{Summary of AdResS and full-atom simulations.}
+\caption{Summary of AdResS and full-atom systems.}
 \label{table2}
@@
 In all the simulations, a leap-frog stochastic dynamics integrator with a time step
-of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS 
-algorithm. In AdResS simulations, it was 
-seen that the excess chemical potential values converge after a specific cut-off radius value. Hence, a different 
-cut-off radius was used for different simulations in order to obtain a converged value. The full-atom simulations 
-were performed using the same cut-off value to have a fair comparison. For liquid water, methanol/water, methane/water, ethane/water
-and TBA/water systems, a cut-off radius of 0.9 nm was used for van der Waals and Coulomb interactions, while for rest 
-of the systems, a cut-off radius of 1.4 nm was used. Electrostatic 
-interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
-permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{tba}, 61 for other solutes in SPC
+of 2~fs and an inverse friction coefficient of 0.1~ps was used. All bond-lengths were constrained using the LINCS 
+algorithm. \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
+in AdResS and full-atom simulations}. 
+Electrostatic interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
+permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{nico}, 61 for other solutes in SPC
 water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.
@@
 R. Walser, A. E. Mark, W. F. van Gunsteren, M. Lauterbach, G. Wipff, J. Chem. Phys. {\bf 112}, 10450 (2000)
-\bibitem{tba}
-M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
 \bibitem{dmso1}

### 2014-05-20 writeDown/pub.jcp/resubmission.tex
revise...

@@
 
-(1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).
+(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
+  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
+% (1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).
 
@@
 
-\recheck{do not say that...}
-Finally, the referee asked us to ``{\it ameliorate} the language; we are fully aware of not being mother tongue Oxford academics, but we asked several colleagues to read the paper and tell us if it was understandable; we got only positive comments, we cannot do more than that.
+Finally, the referee asked us to {\it ameliorate} the language; we are fully aware of not being mother tongue Oxford academics, but we asked several colleagues to read the paper and tell us if it was understandable; we got only positive comments, we cannot do more than that.
 
@@
 
-(1) Thermodynamic limit for the \recheck{atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
-  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}
+(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
+  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
 
@@
 exact. Conditions (1) and (2) are ideal, so it was important to know
-how they can be met in \recheck{practical simulations, especially in
+how they can be met in {practical simulations, especially in
 the mixture systems that the solute concentration is dilute.} The aim of this paper is: {\bf to
@@
 The derivation is presented as one of the results of this paper and has got its own section.
-We have taken such a comment as a motivation to \recheck{provide the} derivation of the formula defined {\it ``weak''} by the referee.
+We have taken such a comment as a motivation to {provide the} derivation of the formula defined {\it ``weak''} by the referee.
 The derivation is presented as one of the results of this paper and has got its own section.
+Although developed before the submission of this paper, this result was not presented, because the paper was intended to investigate only the numerical accuracy.
 
@@
 
-\recheck{The Fig.2 (Fig.4 in the revision) plots the density profile only for the HYB region, as the caption states.}
+{The Fig.2 (Fig.4 in the revision) plots the density profile only for the HYB region, as the caption states.}
 % We disagree.
-\recheck{The relatively large deviation is due to the sampling error, because the
-  number of TBA molecules in the system is very small (80, see the Table II, i.e.~the Table IV in the revision).
+{The relatively large deviation is due to the sampling error, because the
+  number of TBA molecules in the system is very small (80 for mole-fraction 0.02, see the Table II, i.e.~the Table IV in the revision).
   We could reach a much better accuracy of the density if we do longer simulations,

### 2014-05-20 writeDown/pub.jcp/chem-pot-jcp.tex
update the values in the table. change small things

@@
 \recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
-the probability distribution of the system as defined in Eq.\ref{order}}.\\
-
+the probability distribution of the system as defined in Eq.\ref{order}}.
 The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
@@
 %\begin{tabular}{ccccc}
-\begin{tabular}{ccccc}
+\begin{tabular}{ccrrc}
 \hline \hline
@@
 \hline
-\recheck{water} & -- & -22.1 $\pm$ 0.2  & -- & -23.5 \cite{florian} \\
-methane  & -- & -4.6 $\pm$ 0.1  & -5.2 $\pm$ 0.1 & -- \\
-ethane   & -- & -8.2 $\pm$ 0.3  &  -8.8 $\pm$ 0.1 & -- \\
-propane  & -- & -8.5 $\pm$ 0.1 & -9.5 $\pm$ 0.2 & -- \\
-\recheck{methanol}  & -- & -20.3 $\pm$ 0.2 & -20.9 $\pm$ 0.3 & -20.5 \cite{vang}  \\
-DMSO & -- & -32.2 $\pm$ 0.3 & -34.7 $\pm$ 0.7 & -32.2 \cite{dmso}  \\
-\recheck{methanol in methanol/water mixture} & 0.01 & -19.0 $\pm$ 0.2 & -- & -- \\
-\recheck{methane in methane/water mixture} & 0.006 & 9.3 $\pm$ 0.2  & -- & -- \\
-urea in urea/water mixture & 0.02 & -56.1 $\pm$ 0.6 & -58.2 $\pm$ 0.5 & -57.8 $\pm$ 2.5 \cite{urea} \\
-\recheck{ethane in ethane/water mixture} & 0.006 & 7.2 $\pm$ 0.2 & -- & -- \\ 
-\recheck{TBA in water/TBA mixture} & 0.001 & -19.5 $\pm$ 0.5 & -20.8 $\pm$ 0.6 & -19.0 \cite{nico} \\
-DMSO in DMSO/water mixture & 0.01 & -31.4 $\pm$ 0.5 & -33.2 $\pm$ 0.3 & -- \\
-TBA in TBA/DMSO mixture & 0.02 & -24.8 $\pm$ 0.4 & -24.0 $\pm$ 0.5 & -- \\
+\recheck{water} & -- & $-23.9 \pm 0.3$  & $-22.3 \pm 0.6$ & $-23.5$~\cite{florian} \\
+methane  & -- & $-4.6 \pm 0.1$  & $-5.2 \pm 0.1$ & -- \\
+ethane   & -- & $-8.2 \pm 0.3$  & $-8.8 \pm 0.1$ & -- \\
+propane  & -- & $-8.5 \pm 0.1$ & $-9.5 \pm 0.2$ & -- \\
+\recheck{methanol}  & -- & $-20.3 \pm 0.2$ & $-20.9 \pm 0.3$ & $-20.5$ \cite{vang}  \\
+DMSO & -- & $-32.2 \pm 0.3$ & $-34.7 \pm 0.7$ & $-32.2$ \cite{dmso}  \\
+\recheck{methanol in methanol/water mixture} & 0.01 & $-19.0 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
+\recheck{methane in methane/water mixture} & 0.006 & $9.3 \pm 0.2$  & $8.2 \pm 0.3$ & -- \\
+urea in urea/water mixture & 0.02 & $-56.1 \pm 0.6$ & $-58.2 \pm 0.5$ & $-57.8 \pm 2.5$ \cite{urea} \\
+\recheck{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.3 \pm 0.3$ & -- \\ 
+\recheck{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.5$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
+DMSO in DMSO/water mixture & 0.01 & $-31.4 \pm 0.5$ & $-33.2 \pm 0.3$ & -- \\
+TBA in TBA/DMSO mixture & 0.02 & $-24.8 \pm 0.4$ & $-24.0 \pm 0.5$ & -- \\
 \hline \hline
@@
 We started with a randomly chosen initial guess
-($-42$~kJ/mol, we picked a very small value because the TBA molecule is highly hydrophilic)
+($-42$~kJ/mol, we picked a small value because the TBA molecule is hydrophilic)
 for system with the highest mole fraction of TBA. For all the other systems, 
@@
 
-In all the AdResS simulations, 30 iterations were performed to obtain a 
+In all the AdResS simulations, the resolution changes only on $x$ direction.
+For each system, 30 iterations were performed to obtain a 
 converged thermodynamic force and a flat density profile. Each iteration consisted 
@@
 in AdResS and full-atom simulations}. 
-Electrostatic interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
+Electrostatic interactions  were calculated using the reaction-field term \cite{rf} with a dielectric 
 permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{nico}, 61 for other solutes in SPC

### 2014-05-20 writeDown/pub.jcp/resubmission.tex
update the values in the table. change small things

@@
 
-(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
+(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the numbers of molecules in both of the two
   regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
@@
 The derivation is presented as one of the results of this paper and has got its own section.
-Although developed before the submission of this paper, this result was not presented, because the paper was intended to investigate only the numerical accuracy.
+Although developed before the submission of the manuscript, this result was not presented because the paper was intended to investigate only the numerical accuracy.
 

### 2014-05-20 writeDown/pub.jcp/chem-pot-jcp.tex
switch back to cut-off 0.9nm

@@
 \hline
-\recheck{water} & -- & $-23.9 \pm 0.3$  & $-22.3 \pm 0.6$ & $-23.5$~\cite{florian} \\
+\recheck{water} & -- & $-22.8 \pm 0.2$  & $-22.1 \pm 0.3$ & $-23.5$~\cite{florian} \\
 methane  & -- & $-4.6 \pm 0.1$  & $-5.2 \pm 0.1$ & -- \\
@@
 propane  & -- & $-8.5 \pm 0.1$ & $-9.5 \pm 0.2$ & -- \\
-\recheck{methanol}  & -- & $-20.3 \pm 0.2$ & $-20.9 \pm 0.3$ & $-20.5$ \cite{vang}  \\
+\recheck{methanol}  & -- & $-20.1 \pm 0.1$ & $-20.6 \pm 0.4$ & $-20.5$ \cite{vang}  \\
 DMSO & -- & $-32.2 \pm 0.3$ & $-34.7 \pm 0.7$ & $-32.2$ \cite{dmso}  \\
-\recheck{methanol in methanol/water mixture} & 0.01 & $-19.0 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
-\recheck{methane in methane/water mixture} & 0.006 & $9.3 \pm 0.2$  & $8.2 \pm 0.3$ & -- \\
+\recheck{methanol in methanol/water mixture} & 0.01 & $-18.1 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
+\recheck{methane in methane/water mixture} & 0.006 & $9.1 \pm 0.1$  & $8.5 \pm 0.2$ & -- \\
 urea in urea/water mixture & 0.02 & $-56.1 \pm 0.6$ & $-58.2 \pm 0.5$ & $-57.8 \pm 2.5$ \cite{urea} \\
-\recheck{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.3 \pm 0.3$ & -- \\ 
-\recheck{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.5$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
+\recheck{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.4 \pm 0.3$ & -- \\ 
+\recheck{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.3$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
 DMSO in DMSO/water mixture & 0.01 & $-31.4 \pm 0.5$ & $-33.2 \pm 0.3$ & -- \\
@@
 For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); However, since we are always in a very dilute regime the chemical potential does not change significantly.
-\recheck{We have provided evidence for the TBA/water misture that such consistency holds (see Fig.\ref{concentration})}.
+\recheck{We have provided evidence for the TBA/water mixture that such consistency holds (see Fig.\ref{concentration})}.
 Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
@@
 \includegraphics[width=0.475\textwidth]{concentration.eps}
-\caption{ \recheck{Excess chemical potential of t-butyl alcohol (TBA) in water for different concentrations (in logarithmic scale), calculated using GC-AdResS.
+\caption{ \recheck{Excess chemical potential of tert-butyl alcohol (TBA) in water for different concentrations (in logarithmic scale), calculated using GC-AdResS.
 The results are compared with thermodynamic integration values.
@@
 
-\recheck{A complementary information to Table~\ref{table} is
-  Fig.\ref{convergence}. In
-  Table~\ref{table}, there is a systematic difference of
-  $1.2 \sim 2.0$~kJ/mol between our values and those of TI
-  calculations. In order to understand the possible origin of such a
-  discrepancy and provide a way to eventually improve the accuracy of
-  results, we have studied the behavior of $\mu^{ex}$ as a function of
+\recheck{A complementary information to Table~\ref{table} are 
+  Fig.~\ref{convergence} and~\ref{concentration}.
+  % In
+  % Table~\ref{table}, there is a systematic difference of
+  % $1.2 \sim 2.0$~kJ/mol between our values and those of TI
+  % calculations. In order to understand the possible origin of such a
+  % discrepancy and provide a way to eventually improve the accuracy of
+  % results,
+  In Fig.~\ref{convergence} we have studied the behavior of $\mu^{ex}$ as a function of
   the interaction cut-off. In fact the current version of GC-AdResS,
@@
   interactions in the atomistic region, and the cut off is likely to
-  play a role. Fig.\ref{convergence}, for the case of DMSO/water
+  play a role in some of the systems investigated. Fig.\ref{convergence}, for the case of DMSO/water
   mixture, confirms our intuition and suggests that we could
   systematically improve the accuracy by increasing the cut-off,
-  however at a value of about $1.5$~nm, $\mu^{ex}$ converges. In any
+  and at a value of about $1.5$~nm, $\mu^{ex}$ converges. In any
   case, at a values of $1.4$~nm, which is the one routinely used in
-  full atomistic simulations and used by us in all calculations, the
-  value obtained with GC-AdResS is already satisfactory.\\
-
+  full atomistic simulations and used by us, the
+  value obtained with GC-AdResS is already satisfactory.
+  The cut-off radii used for other systems are reported in Appendix~\ref{app:tmp1}.
   A further
@@
   experiments, moreover the trend, regarding the TI calculations, is
-  consistent with that reported in Ref.\cite{nico}.\\}
+  consistent with that reported in Ref.\cite{nico}.\\
+}
 
@@
 \includegraphics[width=0.475\textwidth]{water_rho.eps}
-\caption{Top: Molecular density profile in $\Delta$ for TBA/water mixture; bottom, the same plot for water.
-Among all the systems considered, in this case the action of the thermodynamic force and that of the thermostat leads to the largest deviation from the reference all atomistic average density; however even in this case the discrepancy is negligible.\label{urea-TBA}}
+\caption{Top: Molecular density profile in $\Delta$ for TBA/water mixture; Bottom, the same plot for water.
+  Among all the systems considered, in this case the action of the thermodynamic force and that of the thermostat leads to the largest deviation from the reference all atomistic average density;
+  however even in this case the discrepancy is negligible. The mole-fraction is $\concenttba=0.02$, and the cut-off radius is 0.9~nm.}
+\label{urea-TBA}
 \end{figure}
+
 \begin{figure}
@@
 \includegraphics[width=0.475\textwidth]{water-water.eps}
-\caption{Top: TBA-TBA radial distribution function; middle: the same plot for TBA-water; bottom: for water-water.
+\caption{Top: TBA-TBA radial distribution function; Middle: the same plot for TBA-water; Bottom: for water-water.
+  Red: the results of the AdResS simulation.
   The $g(r)$ is calculated only in the atomistic region.
-Molecules located beyond a distance equal to the interactions' cut off, $0.9 nm$, are not considered since would include hybrid and coarse-grained molecules.
-\label{gr}}
+  Blue: the results of a full-atomistic reference simulation that has the same simulation region as AdResS.
+  The mole-fraction is $\concenttba=0.02$, and the cut-off radius is 0.9~nm.}
+\label{gr}
 \end{figure}
+
 In essence, according to the results obtained, GC-AdResS allows an on-the-fly determination of $\mu^{ex}$ of each component of a liquid, whenever a simulation is performed, without extra computational costs.
@@
 \caption{Time required for a full GC-AdResS and thermodynamic
-  integration (TI) calculation for tbutyl-alcohol(TBA) in water at
+  integration (TI) calculation for tert-butyl-alcohol(TBA) in water at
   different mole-fractions.
@@
 \recheck{TBA/water ($\concenttba=0.001$)} & 40 & 39960 & $50.1 \times 5.8 \times 4.3$ & $7.0 \times 5.8 \times 4.3$  \\
-\recheck{TBA/water ($\concenttba=0.02$)} & 80 & 4400 & $10 \times 3.6 \times 4.2$ & $7.0 \times 3.6 \times 4.2$  \\
-\recheck{TBA/water ($\concenttba=0.04$)} & 180 & 4300 & $10 \times 4.3 \times 3.7$ & $7.0 \times 4.3 \times 3.7$  \\
-\recheck{TBA/water ($\concenttba=0.12$)} & 538 & 3942 & $10 \times 4.4 \times 4.6$ & $7.0 \times 4.4 \times 4.6$  \\
-\recheck{TBA/water ($\concenttba=0.16$)} & 717 & 3763 & $10 \times 4.9 \times 4.6$ & $7.0 \times 4.9 \times 4.6$  \\
-\recheck{TBA/water ($\concenttba=0.20$)} & 896 & 3584 & $12 \times 4.6 \times 4.5$ & $7.0 \times 4.6 \times 4.5$  \\
+\recheck{TBA/water ($\concenttba=0.02$)} & 80 & 4400 & $10.0 \times 3.6 \times 4.2$ & $7.0 \times 3.6 \times 4.2$  \\
+\recheck{TBA/water ($\concenttba=0.04$)} & 180 & 4300 & $10.0 \times 4.3 \times 3.7$ & $7.0 \times 4.3 \times 3.7$  \\
+\recheck{TBA/water ($\concenttba=0.12$)} & 538 & 3942 & $10.0 \times 4.4 \times 4.6$ & $7.0 \times 4.4 \times 4.6$  \\
+\recheck{TBA/water ($\concenttba=0.16$)} & 717 & 3763 & $10.0 \times 4.9 \times 4.6$ & $7.0 \times 4.9 \times 4.6$  \\
+\recheck{TBA/water ($\concenttba=0.20$)} & 896 & 3584 & $12.0 \times 4.6 \times 4.5$ & $7.0 \times 4.6 \times 4.5$  \\
 DMSO/water & 50 & 4950 & $12.0 \times 4.0 \times 3.3$ & $7.0 \times 4.0 \times 3.3$ \\
@@
 of 2~fs and an inverse friction coefficient of 0.1~ps was used. All bond-lengths were constrained using the LINCS 
-algorithm. \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
-in AdResS and full-atom simulations}. 
+algorithm.
+For liquid water, methanol,
+methanol/water, methane/water and ethane/water  a cut-off radius of
+0.9 nm was used for van der Waals and Coulomb interactions, while for rest of the systems,
+a cut-off radius of 1.4 nm was used.
+\recheck{
+  For the TBA/water system, the chemical potential converges at cut-off 0.9~nm for mole-fraction $\concenttba=0.02$.
+  Since it would be too expensive to do the convergence tests for
+  all concentrations, we simply use a large cut-off 1.4~nm for the concentration dependency study of TBA/water.}
+% \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
+% in AdResS and full-atom simulations}. 
 Electrostatic interactions  were calculated using the reaction-field term \cite{rf} with a dielectric 

### 2014-06-28 writeDown/pub.jcp/arxiv.rev/chem-pot-jcp.tex
version go to arxiv

--- 2014-05-20 writeDown/pub.jcp/chem-pot-jcp.tex
@@
 \newcommand{\recheck}[1]{{\color{red} #1}}
-\newcommand{\redc}[1]{{\color{red} #1}}            
-\newcommand{\bluec}[1]{{\color{blue} #1}}            
+\newcommand{\redc}[1]{{\color{black} #1}}            
+\newcommand{\bluec}[1]{{\color{black} #1}}            
 \newcommand{\vect}[1]{\textbf{\textit{#1}}}
@@
 This agreement allows us to conclude that every time a multiscale GC-AdResS is performed, $\mu^{ex}$ is automatically calculated for each liquid component and implicitly confirm that the basic thermodynamics of the system is well described by the method.
-\recheck{Moreover, in recent work AdResS has been merged with the MARTINI force field \cite{matej-sw1,matej-sw2}.
+{Moreover, in recent work AdResS has been merged with the MARTINI force field \cite{matej-sw1,matej-sw2}.
 In this context, the possibility of checking the consistency of a quantity like the chemical potential can be used as a further argument for the validity of the method in applications to large systems of biological interest.}
@@
 force derived from the atomistic force field and  ${\vect F}^{\CG}$
-from the corresponding coarse-grained potential, \recheck{$\vect r$ is the center of mass (COM) position of}
+from the corresponding coarse-grained potential, {$\vect r$ is the center of mass (COM) position of}
 the molecule and $w$ is an interpolating function which smoothly goes from $0$
@@
 The consequence is that molecules in the atomistic region interact with the rest of the system always and only via well defined atomistic interactions.
-This characteristic, in turn, allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a Grand-Canonical fashion \recheck{(see Eq.12 of Ref.\cite{prx})}}.
+This characteristic, in turn, allows to write an exact Hamiltonian for the atomistic region and thus treat the system in a Grand-Canonical fashion {(see Eq.12 of Ref.\cite{prx})}}.
 \label{fig1}
@@
 In \cite{prx} we have defined necessary conditions in $\Delta$ such that the spatial probability distribution of the full-atomistic reference system was reproduced up to a certain (desired) order in the atomistic region of the adaptive system.
-\recheck{We have defined the $m$th order of a spatial (configurational) probability distribution of $N$ molecules, $p({\vect r}_{1}, \cdots, {\vect r}_{N})$, as:
+{We have defined the $m$th order of a spatial (configurational) probability distribution of $N$ molecules, $p({\vect r}_{1}, \cdots, {\vect r}_{N})$, as:
 \begin{equation}
@@
 Moreover we have shown that, because of the necessary conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
-In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure \recheck{using} the molecular number density in $\Delta$.
-The iterative scheme consists of calculating \recheck{${\vect F}^{k+1}_{th}({\vect r}) = {\vect F}^{k}_{th}({\vect r}) + \frac{1}{\rho^2_{0}\kappa_{T}}\nabla \rho^{k}({\vect r})$} ($\kappa_{T}$ the isothermal compressibility), and the thermodynamic force is considered converged when the target density $\rho_{0}$ is reached in $\Delta$.
+In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure {using} the molecular number density in $\Delta$.
+The iterative scheme consists of calculating {${\vect F}^{k+1}_{th}({\vect r}) = {\vect F}^{k}_{th}({\vect r}) + \frac{1}{\rho^2_{0}\kappa_{T}}\nabla \rho^{k}({\vect r})$} ($\kappa_{T}$ the isothermal compressibility), and the thermodynamic force is considered converged when the target density $\rho_{0}$ is reached in $\Delta$.
 As a result, ${\vect F}_{th}({\vect r})$, acting in $\Delta$, assures that there are no artificial density variations across the system, thus it allows to accurately reproduce the first order of the probability distribution in the atomistic region.
@@
 % proportional to the gradient of the corresponding higher order of the probability distribution;
-\recheck{For example, the COM-COM radial distribution function correction for the second order~\cite{jctchan}.} Next it was proved that indeed the target Grand Canonical distribution, that is the probability distribution of a subsystem (of the size of the atomistic region in GC-AdResS) in a large full atomistic simulation is accurately reproduced.
+{For example, the COM-COM radial distribution function correction for the second order~\cite{jctchan}.} Next it was proved that indeed the target Grand Canonical distribution, that is the probability distribution of a subsystem (of the size of the atomistic region in GC-AdResS) in a large full atomistic simulation is accurately reproduced.
 A large number of tests were performed and the reproduction by GC-AdResS of the probability distribution was numerically proved up to (at least) the third order, more than sufficient in MD simulations.
@@
 $\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-\recheck{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
-However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS.
+{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
+However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in {the original} AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS.
-\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}.
+{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}.
 Moreover we have proven numerically, for the case of liquid water, that
@@
   where $U_{\AT}$ and $U_{\CG}$ are the atomistic and coarse-grained potential.
-\recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation.
+{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation.
 In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the {Appendix~\ref{app:tmp2}})}.
-\recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t.
-the probability distribution of the system as defined in Eq.\ref{order}}.
+{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t. the probability distribution of the system as defined in Eq.\ref{order}}.
 The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
-\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids and mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
+{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids and mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}.
 At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$.
@@
 Regarding the kinetic part, one can notice that the contribution coming from the COM is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
-The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules).
-However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway~\cite{simon-ch}.
+The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and {in principle can be calculated by hand (chemical potential of an isolated molecules).
+However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the {Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway~\cite{simon-ch}.
 Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference.
@@
 \section{Analytic Derivation of  $w_{\ext}$}\label{sec:tmp4}
-\recheck{In this section we derive analytically the equivalence:
+{In this section we derive analytically the equivalence:
   $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its conceptual limitations.
@@
 where $m_\alpha$ is the mass of atom $\alpha$ of molecule $i$.
-\recheck{The potential interpolation~\eqref{eqn:pot-interpol} provides an auxiliary Hamiltonian to the AdResS system, and
+{The potential interpolation~\eqref{eqn:pot-interpol} provides an auxiliary Hamiltonian to the AdResS system, and
 the
@@
 \end{align}
-\recheck{We refer to the AdResS simulation using force scheme~\eqref{eqn:interpol-f} as
+{We refer to the AdResS simulation using force scheme~\eqref{eqn:interpol-f} as
   auxiliary Hamiltonian AdResS, and all properties of this approach will be added a superscript ``H''}.
@@
 resolution~\eqref{eqn:peq} does not hold and should be derived again.
-Now assume, \recheck{for simplicity and without lost of generality}, that the system changes resolution only along the $x$ direction.
+Now assume, {for simplicity and without lost of generality}, that the system changes resolution only along the $x$ direction.
 We impose an infinitesimal increment of the volume $\Delta V$ to the
@@
   &+
-  \int_\Delta d \vect r\, \rho_0 S\cdot \Delta L\cdot
-  \big[\vect F^\hadress_\thf(\vect r)
+  \recheck{\int_{\Delta_{x}} d x\, \rho_0 S\cdot \Delta L\cdot
+  \big[\vect F^\hadress_\thf(x)
   -
-  \big\langle \vect F_\res(\vect r)\big\rangle\,\big]
+  \big\langle \vect F_\res(x)\big\rangle\,\big]}
 \end{align}
 where $A_\AT$ and $A_\CG$ are the free energies of the AT and CG region, respectively.
+\recheck{
+$\Delta_{x}$ is the linear dimension of the transition region along $x$. 
+Since the resolution changes only along $x$,
+the two one-particle forces depend only on $x$, and only have the component along $x$.
+This can be easily generalized to changing resolution in any direction, i.e., replacing $x$ by ${\vect r}$.}
 The expression of Eq.\ref{eqn:apptmp3} as a sum of different terms is justified by the hypothesis of treating the system in the thermodynamic limit, and by the hypothesis that the interactions are short-ranged compared to the size of the transition region.
@@
 $ \omega_\res$ is the work of changing representation,
-which can be explicitly written down as:
+which can be explicitly written down \recheck{in a general form} as:
 \begin{align}\label{eqn:w-rep}
@@
   \big\langle w(\vect r')\,
-  [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r}
+  [\sum_{\alpha,\beta}U^\AT(\vect r_\alpha-\vect r'_\beta) - U^\CG(\vect r-\vect r')]\big\rangle_{\vect r'; \vect r},
 \end{align}
@@
 \end{align}
-The extension of Eq.\ref{eqn:tmp24} to multicomponent systems is reported in the Appendix~\ref{app:tmp3}, while in the next section we apply the method to the calculation of $\mu^{ex}$ to liquids and mixtures.}
+The extension of Eq.\ref{eqn:tmp24} to multicomponent systems is
+reported in the Appendix~\ref{app:tmp3}, while in the next section we
+apply the method to the calculation of $\mu^{ex}$ to liquids and
+mixtures.}
 
@@
 We also compare the obtained values with those available in literature \cite{vang,nico}.
-Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; \recheck{we have verified  such a supposed consistency for one relevant system (see discussion about Fig.\ref{concentration})}.
-The chemical potential of $k$-th liquid's component in a mixture is calculated as \recheck{(see Appendix~\ref{app:tmp3})}:
+Although the concentration of the minor component in the mixtures that we consider, is higher than the concentrations considered in Refs.\cite{vang,nico}, we are anyway in the very dilute regime and thus the chemical potential should not change in a significant way; {we have verified  such a supposed consistency for one relevant system (see discussion about Fig.\ref{concentration})}.
+The chemical potential of $k$-th liquid's component in a mixture is calculated as {(see Appendix~\ref{app:tmp3})}:
 \begin{equation}
@@
 where $\vect{F}^{k}_{\thf}(x)$ is the thermodynamic force applied to the molecules of the $k$-th component; this assures that, at the given concentration, the density of molecules of species $k$, in the transition region, is equivalent to the density of the same liquid's component in a reference full atomistic simulation.
-\recheck{The ensemble average is taken over the position of the second molecule, provided that the first molecule is of species $k$, and located at position $\vect r$}.\\
+{The ensemble average is taken over the position of the second molecule, provided that the first molecule is of species $k$, and located at position $\vect r$}.\\
 
@@
 \hline
-\recheck{water} & -- & $-22.8 \pm 0.2$  & $-22.1 \pm 0.3$ & $-23.5$~\cite{florian} \\
+{water} & -- & $-22.8 \pm 0.2$  & $-22.1 \pm 0.3$ & $-23.5$~\cite{florian} \\
 methane  & -- & $-4.6 \pm 0.1$  & $-5.2 \pm 0.1$ & -- \\
@@
 propane  & -- & $-8.5 \pm 0.1$ & $-9.5 \pm 0.2$ & -- \\
-\recheck{methanol}  & -- & $-20.1 \pm 0.1$ & $-20.6 \pm 0.4$ & $-20.5$ \cite{vang}  \\
+{methanol}  & -- & $-20.1 \pm 0.1$ & $-20.6 \pm 0.4$ & $-20.5$ \cite{vang}  \\
 DMSO & -- & $-32.2 \pm 0.3$ & $-34.7 \pm 0.7$ & $-32.2$ \cite{dmso}  \\
-\recheck{methanol in methanol/water mixture} & 0.01 & $-18.1 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
-\recheck{methane in methane/water mixture} & 0.006 & $9.1 \pm 0.1$  & $8.5 \pm 0.2$ & -- \\
+{methanol in methanol/water mixture} & 0.01 & $-18.1 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
+{methane in methane/water mixture} & 0.006 & $9.1 \pm 0.1$  & $8.5 \pm 0.2$ & -- \\
 urea in urea/water mixture & 0.02 & $-56.1 \pm 0.6$ & $-58.2 \pm 0.5$ & $-57.8 \pm 2.5$ \cite{urea} \\
-\recheck{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.4 \pm 0.3$ & -- \\ 
-\recheck{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.3$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
+{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.4 \pm 0.3$ & -- \\ 
+{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.3$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
 DMSO in DMSO/water mixture & 0.01 & $-31.4 \pm 0.5$ & $-33.2 \pm 0.3$ & -- \\
@@
 For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); However, since we are always in a very dilute regime the chemical potential does not change significantly.
-\recheck{We have provided evidence for the TBA/water mixture that such consistency holds (see Fig.\ref{concentration})}.
+{We have provided evidence for the TBA/water mixture that such consistency holds (see Fig.\ref{concentration})}.
 Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
@@
 \includegraphics[width=0.475\textwidth]{convergence.eps}
-\caption{ \recheck{Excess chemical potential of Dimethyl sulfoxide (DMSO) in water as a function of cut-off radius calculated using GC-AdResS.
+\caption{ {Excess chemical potential of Dimethyl sulfoxide (DMSO) in water as a function of cut-off radius calculated using GC-AdResS.
 The value obtained from thermodynamic integration calculation in also shown, with a gray region indicating the standard deviation.
@@
 \includegraphics[width=0.475\textwidth]{concentration.eps}
-\caption{ \recheck{Excess chemical potential of tert-butyl alcohol (TBA) in water for different concentrations (in logarithmic scale), calculated using GC-AdResS.
+\caption{ {Excess chemical potential of tert-butyl alcohol (TBA) in water for different concentrations (in logarithmic scale), calculated using GC-AdResS.
 The results are compared with thermodynamic integration values.
@@
 
-\recheck{A complementary information to Table~\ref{table} are 
+{A complementary information to Table~\ref{table} are 
   Fig.~\ref{convergence} and~\ref{concentration}.
@@
 
-\recheck{In order to show the numerical efficiency of our approach, we compare the time taken to do a full GC-AdResS simulation and the time for a thermodynamic integration calculation for
+{In order to show the numerical efficiency of our approach, we compare the time taken to do a full GC-AdResS simulation and the time for a thermodynamic integration calculation for
 different systems with varied concentration of TBA in water. The total time required for an GC-AdResS simulation consists of 
@@
 The natural question arising from the discussion above is whether or not GC-AdResS is a more convenient technical tool for calculating $\mu^{ex}$ compared to TI.
-Currently the answer is \recheck{neither negative nor positive}, although the current work is the first step towards a potentially positive answer for the future.
+Currently the answer is {neither negative nor positive}, although the current work is the first step towards a potentially positive answer for the future.
 In fact, the fastest version of AdResS is implemented in the GROMACS code \cite{gromacs}; using the Gromacs version 4.5.1 a speedup of a factor four with respected to full atomistic simulations has been reported for aqueous mixtures~\cite{debashish1,nico-debashish}.
@@
 However in the successive version of GROMACS 4.6.1 the performance of atomistic simulations (above all of SPC/E water) has been highly improved while the corresponding implementation of AdResS is not optimized yet.
-At the current state, AdResS can only assure a speed up factor between \recheck{2 and 3} for large systems (30000 molecules) compared to full atomistic simulations \recheck{(except for pure SPC/E water systems)}.
+At the current state, AdResS can only assure a speed up factor between {2 and 3} for large systems (30000 molecules) compared to full atomistic simulations {(except for pure SPC/E water systems)}.
 As a consequence for the calculation of $\mu^{ex}$, TI is in general computationally less demanding than AdResS .
@@
 of both components in one simulation run, whereas in TI, one needs to run two separate simulations in order to get the chemical potential of both components.
-\recheck{The results reported in the previous section about the current efficiency of GC-AdResS are rather encouraging, however currently there is not a clear convenience in using GC-AdResS instead of TI for calculating $\mu^{ex}$;
+{The results reported in the previous section about the current efficiency of GC-AdResS are rather encouraging, however currently there is not a clear convenience in using GC-AdResS instead of TI for calculating $\mu^{ex}$;
 in any case the technical aspects of code optimization must be reported and we must make clear that the aim of this work is to show that  the automatic calculation of $\mu^{ex}$, independently from the simulation code in which is implemented and its computational cost, is a ``conceptual'' feature of GC-AdResS}.
@@
 (grant code DE 1140/4-2).H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
-\recheck{We thank Christoph Junghans and Debashish Mukherji for contributing to the information reported in section IV about the speed up factor}.
+{We thank Christoph Junghans and Debashish Mukherji for contributing to the information reported in section IV about the speed up factor}.
 
@@
 at 298 K. Simulations of liquid methane and ethane were performed at
-111.66 K and 184.52 K respectively. \recheck{As it was discussed in~\cite{prx}, there is no requirement 
+111.66 K and 184.52 K respectively. {As it was discussed in~\cite{prx}, there is no requirement 
 of a coarse-grained model that resembles the structural and thermodynamic properties of a full atomistic
@@
 frame at random locations and with random orientations of the molecule.  
-\recheck{The excess chemical potential value was calculated by averaging over the last ten iterations after 
+{The excess chemical potential value was calculated by averaging over the last ten iterations after 
 the thermodynamic force has converged and the statistical uncertainty is determined by the standard deviation in the data. \\}
@@
 continuously decreased in the stepwise manner. Simulations conducted at different values of 
-$\lambda$ allow to plot a \recheck{$\frac{\partial U_{i}(\lambda)}{\partial \lambda}$} curve, from which 
+$\lambda$ allow to plot a {$\frac{\partial U_{i}(\lambda)}{\partial \lambda}$} curve, from which 
 $\mu^{\exc}$ is derived \cite{mu}. 
-\recheck{
+{
 \begin{equation}
@@
 For both the AdResS and full-atom simulations, the system size was kept same.
-\recheck{Table~\ref{table2} gives a detailed summary of each system studied}.\\
+{Table~\ref{table2} gives a detailed summary of each system studied}.\\
 
@@
 \hline
-\recheck{water} & --- & 13824 & $30.2 \times 3.8 \times 3.8$ & $14.6 \times 3.8 \times 3.8$ \\
+{water} & --- & 13824 & $30.2 \times 3.8 \times 3.8$ & $14.6 \times 3.8 \times 3.8$ \\
 methane & --- & 2000 & $9.0 \times  3.7 \times 3.6$ & $6.0 \times 3.7 \times 3.6$ \\
@@
 propane & --- & 1433 & $10.0 \times 4.5 \times 4.5$ & $7.0 \times 4.5 \times 4.5$ \\
-\recheck{methanol} & --- & 4000 & $12.0 \times 4.6 \times 4.5$ & $7.4 \times 4.6 \times 4.5$ \\
+{methanol} & --- & 4000 & $12.0 \times 4.6 \times 4.5$ & $7.4 \times 4.6 \times 4.5$ \\
 DMSO & --- & 1500 & $15.0 \times 3.6 \times 3.3$ &  $7.0 \times 3.6 \times 3.3$ \\
-\recheck{methanol/water} & 128 & 12672 & $29.5 \times 3.7 \times 3.7$ & $14.6 \times 3.7 \times 3.7$ \\
-\recheck{methane/water} & 40  & 6960 & $10.0 \times 4.8 \times 4.7$ & $7.0 \times 4.8 \times 4.7$ \\
+{methanol/water} & 128 & 12672 & $29.5 \times 3.7 \times 3.7$ & $14.6 \times 3.7 \times 3.7$ \\
+{methane/water} & 40  & 6960 & $10.0 \times 4.8 \times 4.7$ & $7.0 \times 4.8 \times 4.7$ \\
 urea/water & 50 & 2500 & $9.7 \times 2.9 \times 2.8$ & $6.8 \times 2.9 \times 2.8$ \\
-\recheck{ethane/water} & 40 & 6960 & $10.0 \times 4.7 \times 4.6$ & $7.0 \times 4.7 \times 4.6$ \\
-\recheck{TBA/water ($\concenttba=0.001$)} & 40 & 39960 & $50.1 \times 5.8 \times 4.3$ & $7.0 \times 5.8 \times 4.3$  \\
-\recheck{TBA/water ($\concenttba=0.02$)} & 80 & 4400 & $10.0 \times 3.6 \times 4.2$ & $7.0 \times 3.6 \times 4.2$  \\
-\recheck{TBA/water ($\concenttba=0.04$)} & 180 & 4300 & $10.0 \times 4.3 \times 3.7$ & $7.0 \times 4.3 \times 3.7$  \\
-\recheck{TBA/water ($\concenttba=0.12$)} & 538 & 3942 & $10.0 \times 4.4 \times 4.6$ & $7.0 \times 4.4 \times 4.6$  \\
-\recheck{TBA/water ($\concenttba=0.16$)} & 717 & 3763 & $10.0 \times 4.9 \times 4.6$ & $7.0 \times 4.9 \times 4.6$  \\
-\recheck{TBA/water ($\concenttba=0.20$)} & 896 & 3584 & $12.0 \times 4.6 \times 4.5$ & $7.0 \times 4.6 \times 4.5$  \\
+{ethane/water} & 40 & 6960 & $10.0 \times 4.7 \times 4.6$ & $7.0 \times 4.7 \times 4.6$ \\
+{TBA/water ($\concenttba=0.001$)} & 40 & 39960 & $50.1 \times 5.8 \times 4.3$ & $7.0 \times 5.8 \times 4.3$  \\
+{TBA/water ($\concenttba=0.02$)} & 80 & 4400 & $10.0 \times 3.6 \times 4.2$ & $7.0 \times 3.6 \times 4.2$  \\
+{TBA/water ($\concenttba=0.04$)} & 180 & 4300 & $10.0 \times 4.3 \times 3.7$ & $7.0 \times 4.3 \times 3.7$  \\
+{TBA/water ($\concenttba=0.12$)} & 538 & 3942 & $10.0 \times 4.4 \times 4.6$ & $7.0 \times 4.4 \times 4.6$  \\
+{TBA/water ($\concenttba=0.16$)} & 717 & 3763 & $10.0 \times 4.9 \times 4.6$ & $7.0 \times 4.9 \times 4.6$  \\
+{TBA/water ($\concenttba=0.20$)} & 896 & 3584 & $12.0 \times 4.6 \times 4.5$ & $7.0 \times 4.6 \times 4.5$  \\
 DMSO/water & 50 & 4950 & $12.0 \times 4.0 \times 3.3$ & $7.0 \times 4.0 \times 3.3$ \\
@@
 a cut-off radius of 1.4 nm was used.
-\recheck{
+{
   For the TBA/water system, the chemical potential converges at cut-off 0.9~nm for mole-fraction $\concenttba=0.02$.
@@
   all concentrations, we simply use a large cut-off 1.4~nm for the concentration dependency study of TBA/water.}
-% \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
+% {As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
 % in AdResS and full-atom simulations}. 
@@
 \section{Technical Aspects of the Auxiliary Hamiltonian AdResS}\label{app:tmp2}
-\recheck{In principle when the auxiliary Hamiltonian approach is used,
+{In principle when the auxiliary Hamiltonian approach is used,
   one can perform microcanonical simulations and thus can avoid the
@@
 
-\recheck{In this section we  extend the chemical potential
+{In this section we  extend the chemical potential
 expression of Eq.~\eqref{eqn:tmp24} to multi-component

### 2014-07-03 writeDown/pub.jcp/chem-pot-jcp.tex
fix bugs, final version

@@
 \setlength\parindent{2em} 
-\newcommand{\recheck}[1]{{\color{red} #1}}
-\newcommand{\redc}[1]{{\color{red} #1}}            
-\newcommand{\bluec}[1]{{\color{blue} #1}}            
+\newcommand{\recheck}[1]{{\color{black} #1}}
+\newcommand{\redc}[1]{{\color{black} #1}}            
+\newcommand{\bluec}[1]{{\color{black} #1}}            
 \newcommand{\vect}[1]{\textbf{\textit{#1}}}
@@
 \end{equation}
-The first order, often mentioned in this work corresponds to the molecular number density $\rho({\vect r})$.}
+The first order, often mentioned in this work, corresponds to the molecular number density $\rho({\vect r})$.}
 Moreover we have shown that, because of the necessary conditions, the accuracy in the atomistic region is independent of the accuracy of the coarse-grained model, thus, in the coarse-grained region, one can use a generic liquid of spheres whose only requirement is that it has the same molecular density of the reference system.
-In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure \recheck{using} the molecular number density in $\Delta$.
-The iterative scheme consists of calculating \recheck{${\vect F}^{k+1}_{th}({\vect r}) = {\vect F}^{k}_{th}({\vect r}) + \frac{1}{\rho^2_{0}\kappa_{T}}\nabla \rho^{k}({\vect r})$} ($\kappa_{T}$ the isothermal compressibility), and the thermodynamic force is considered converged when the target density $\rho_{0}$ is reached in $\Delta$.
+In the simulation set up, ${\vect F}_{th}$ is calculated via an iterative procedure {using} the molecular number density in $\Delta$.
+The iterative scheme consists of calculating {${\vect F}^{k+1}_{th}({\vect r}) = {\vect F}^{k}_{th}({\vect r}) + \frac{1}{\rho^2_{0}\kappa_{T}}\nabla \rho^{k}({\vect r})$} ($\kappa_{T}$ the isothermal compressibility), and the thermodynamic force is considered converged when the target density $\rho_{0}$ is reached in $\Delta$.
 As a result, ${\vect F}_{th}({\vect r})$, acting in $\Delta$, assures that there are no artificial density variations across the system, thus it allows to accurately reproduce the first order of the probability distribution in the atomistic region.
@@
 $\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational).
-\recheck{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}.
-However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS.
+{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\ext}$ is very relevant}.
+However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in {the original} AdResS.
 Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS.
-\recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}.
+{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}.
 Moreover we have proven numerically, for the case of liquid water, that
@@
 
-\section{Analytic Derivation of  $w_{\ext}$}\label{sec:tmp4}
-\recheck{In this section we derive analytically the equivalence:
+\section{Analytic Derivation of  $\omega_{\ext}$}\label{sec:tmp4}
+{In this section we derive analytically the equivalence:
   $\omega_{\ext}=\int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$ and define its conceptual limitations.
-We consider a potential coupling between the atomistic and coarse-grained resolution as the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
+We consider a potential coupling between the atomistic and coarse-grained resolution, that is the spatial interpolation of the atomistic and coarse-grained potential, as done instead for the forces in the standard AdResS:
 \begin{align}
@@
 \end{align}
-where  $\alpha$ and $\beta$ denotes the atom indexes of the corresponding molecule.
+where  $\alpha$ and $\beta$ denotes the atom indices of the corresponding molecule.
 The COM of the molecule is defined as:
@@
 \end{align}
-\recheck{We refer to the AdResS simulation using force scheme~\eqref{eqn:interpol-f} as
+{We refer to the AdResS simulation using potential scheme~\eqref{eqn:interpol-f} as
   auxiliary Hamiltonian AdResS, and all properties of this approach will be added a superscript ``H''}.
@@
 \end{align}
-where $ \omega_\thf$ denotes the integral of the thermodynamic force $\vect F_\thf$. \\
+where $ \omega_\thf$ denotes the work of the thermodynamic force $\vect F_\thf$. \\
 
 Instead when we consider the auxiliary Hamiltonian approach, the third term on the R.H.S.~of Eq.~\eqref{eqn:interpol-f} is not
-symmetric w.r.t molecule $i$ and $j$, therefore, the Newton's
+symmetric w.r.t molecules $i$ and $j$, therefore, the Newton's
 action-reaction law (momentum conservation) does not hold anymore.
@@
   A_\CG(N_3, V_3, T)\\\label{eqn:apptmp3}
-  &+
-  \int_\Delta d \vect r\, \rho_0 S\cdot \Delta L\cdot
-  \big[\vect F^\hadress_\thf(\vect r)
+  &-
+  \recheck{\int_{\Delta_{x}} d x\, \rho_0 S\cdot \Delta L\cdot
+  \big[\vect F^\hadress_\thf(x)
   -
-  \big\langle \vect F_\res(\vect r)\big\rangle\,\big]
+  \big\langle \vect F_\res(x)\big\rangle\,\big]}
 \end{align}
 where $A_\AT$ and $A_\CG$ are the free energies of the AT and CG region, respectively.
+\recheck{
+$\Delta_{x}$ is the linear dimension of the transition region along $x$. 
+Since the resolution changes only along $x$,
+the two one-particle forces depend only on $x$, and only have the component along $x$.
+This can be easily generalized to changing resolution in any direction, i.e., replacing $x$ by ${\vect r}$.}
 The expression of Eq.\ref{eqn:apptmp3} as a sum of different terms is justified by the hypothesis of treating the system in the thermodynamic limit, and by the hypothesis that the interactions are short-ranged compared to the size of the transition region.
@@
 of the system.
-The last term is originated by the work done of the ideal piston. This latter is composed by
+The last term is originated by the work done by the ideal piston. This term is composed by
 two parts, the first corresponding to the work done by the thermodynamic force, and the
@@
 being forces based on pairwise interactions only, do not contribute to the difference of energy; in fact 
-their total work is zero (as long as the transition region move infinitesimally along $x$).
+their total work is zero (as long as the transition region moves infinitesimally along $x$).
 The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble average, which
@@
 \end{align}
-where $w_\thf^\hadress$ is the integral of the 
+where $\omega_\thf^\hadress$ is the work of the 
 thermodynamic force $\vect F_\thf^\hadress$, and
 $ \omega_\res$ is the work of changing representation,
-which can be explicitly written down as:
+which can be explicitly written down \recheck{in a general form} as:
 \begin{align}\label{eqn:w-rep}
@@
 conformations in the atomistic resolution.
-In the thermodynamic limit, the equilibrium volume of the AT region maximize the
+In the thermodynamic limit, the equilibrium volume of the AT region maximizes the
 free energy, i.e.~$\Delta A / \Delta V
@@
 \end{align}
-In the auxiliary Hamiltonian, we do not have the term $w_\ext$ in the above
-formula {(being the term $w_\ext$ in GC-AdResS, generated by the non-conservative effect of the force interpolation).}
+In the auxiliary Hamiltonian, we do not have the term $\omega_\ext$ in the above
+formula {(being the term $\omega_\ext$ in GC-AdResS, generated by the non-conservative effect of the force interpolation).}
 By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-h}, we have the
@@
 is that we get two values of excess chemical potential for both solute and solvent in a single calculation, while 
-in TI, the whole process has to be repeated to get the excess chemical potential of other component. For very dilute systems ($\concenttba=0.001$), 
+in TI, the whole process has to be repeated to get the excess chemical potential of the other component. For very dilute systems ($\concenttba=0.001$), 
 however, one has to take a very large systems in GC-AdResS (see the Appendix~\ref{app:tmp1} for system size).
@@
 
-In all the AdResS simulations, the resolution changes only on $x$ direction.
+In all the AdResS simulations, the resolution changes only along the $x$ direction.
 For each system, 30 iterations were performed to obtain a 
@@
   the auxiliary Hamiltonian and GC-AdResS the energy drift due to the
-  reaction field method is the essentially same because they have
+  reaction field method is  essentially the same because they have
   equivalent electrostatic interactions, thus the energy drift due to
@@
 $ \omega^\typea_\thf$ and $ \omega^\typeb_\thf$ are 
-the integral of the thermodynamic force $\vect F^\typea_\thf$ and
+the work of the thermodynamic force $\vect F^\typea_\thf$ and
 $\vect F^\typeb_\thf$, respectively. $\omega^\typea_\ext$ is the energy
@@
 \bibitem{luigientropy}
-L.Delle Site, Entropy {\bf 15} (2013); doi:10.3390
+L.Delle Site, Entropy {\bf 15}, 23-40 (2013); doi:10.3390/e16010023
 \bibitem{simon-ch}
@@
 \bibitem{spc}
-H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans, Reidel, Dordrecht, 331 (1981)
+H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans, Interaction Models for Water in Relation to Protein Hydration, in Intermolecular Forces, Reidel, Dordrecht, p.331 (1981)
 \bibitem{walser}

### 2014-10-14 writeDown/pub.epj/paper.tex
add paper.tex

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for The European Physical Journal Special Topics
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[epjST]{svjour}
%
\usepackage{graphics}
\usepackage{color, colortbl}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{tabularx}

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mh}[0]{\mathcal {H}}
\newcommand{\dist}[0]{\textrm {dist}}
\newcommand{\AT}[0]{\textrm{AT}}
\newcommand{\HY}[0]{\textrm{HY}}
\newcommand{\CG}[0]{\textrm{CG}}
\newcommand{\EX}[0]{\textrm{EX}}
\newcommand{\moleidxone}[0]{i}
\newcommand{\moleidxtwo}[0]{j}
\newcommand{\atomidxone}[0]{\alpha}
\newcommand{\atomidxtwo}[0]{\beta}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\rep}{{\textrm{rep}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\exc}{{\textrm{extra}}}
\newcommand{\inv}{{\textrm{equi}}}

% \usepackage{amsfonts}
% \newcommand{\tickYes}{\checkmark}
% \usepackage{pifont}
% \newcommand{\tickNo}{\hspace{1pt}\ding{55}}
% \definecolor{MyGray}{gray}{0.85}

%
\begin{document}
%
\title{Adaptive Resolution Simulation: Theoretical Fundations and Open Questions}
\author{Han Wang\inst{1}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}}
%
\institute{Zuse Institut Berlin}
%
\abstract{
Insert your abstract here.
} %end of abstract
%
\maketitle
%

\section{The two ways  of designing the hybrid region}

The AdResS uses a weighting function $w(\vect r)$ that is a scalor
function defined over the simulation region to denote the resolution
of the system. In the atomistic region the value of the
weighting function is usually set to 1, while in the coarse-grained
region it is usually set to 0. In between, there is a bybrid region
that is denoted by $\Omega_\HY$
(or called transition region), where the molecules
has both the atomistic and coarse-grained resolutions, and the weighting function
goes smoothly from 1 to 0. The way of designing the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
Since all interactions (including the electrostatic interction) are treated
by cut-off method, the weighting function requires the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$). 
The benefite of this setting is that the atomistic
region is not directly interacting with the coarse-grained region,
so there is no extra work for modeling the interactions between the atomistic
and coarse-grained resolutions.

Both the atomistic and coarse-grained intermolecular interactions are
well defined in the atomistic region and coarse-grained regions,
respectively.  To setup an AdResS simulation, one needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (saying $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$, from the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

The potential interpolation approach defines the hybrid energy by the same idea:
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
The intermolecular force is therefore calculated by
\begin{align}\nonumber
  {\vect F}^V_{\moleidxone \moleidxtwo}&= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo} \\ \label{eqn:f-v-interpol}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscipt ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
It should be noted that
the last term breaks the Newton's third law, therefore the force of potential interpolation
does not conserves the momentum.

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}). The choice of the interpolation scheme depends on
the practical requirement, for example, in some systems it is crucial to have the momentum
conservation, then the force interpolation is prefered, and vice versa.
In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonial ensamble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exserts on one molecule is given by the normal adding up rule:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
On the force on the atomistic DOFs of a hybrid molecules is distributed 
by, taking atom $\atomidxone$ on molecule $\moleidxone$ for example,
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where $m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

Before discussing the statistical and thermodynamic properties of AdResS, a few comments on the
choice of the weighting function should be added. 
In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function that
introduce a buffer region so that the molecules with the atomistic resolution
interacts with the hybrid region via the atomistic intermolecular interaction:
\begin{equation}\label{eqn:new-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &1 && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c \\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT) - r_c}{d_{{\HY}} - r_c}\,\Big] && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) \geq r_c\\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
The minimum thickness of the hybrid region is therefore $2r_c$.
It worth noting that the coarse-grained region does not requires a buffer in the hybrid region, because
by definition the coarse-grained region interacts with the hybrid region via the coarse-grained intermolecular interaction.
The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
however, the extra cost of is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
which is treated in atomistic resolution. This cost is relatively small for systems with large atomistic region.

\section{Equilibrium statistical properties of adaptive resolution simulation}
\label{sec:statistical}

To consider the accuracy of the AdResS simulation, we always compare it with a
atomistic reference system, which is of the same size as the AdResS system, and contains the same number of molecules.
If the statistal properties of the atomistic region in the AdResS simulation
is same as the corresponding subregion in the atomistic reference, then
the atomistic region is embeded into the AdResS system as if it were embeded in to
an atomistic environment, and the AdResS simulation is of good accuracy.

We denote the number of molecules, volume and temperture of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the desired equilibrium.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables for subregions are specified by the subscript,
for example, the those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All DOFs of the system is denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
generality, the first molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ in hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
\redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/system.thermo/system.eps}
  \caption{A schematic plot of the AdResS system in thermodynamic
    equilibrium. The number of molecules, volume and temperature of
    the atomistic and coarse-grained regions are denoted by $\{N_\AT,
    V_\AT, T\}$ and $\{N_\AT, V_\AT, T\}$, respectively. The filter
    allows free exchange of molecules between atomistic and
    coarse-grained regions.}
  \label{fig:system-thermo}
\end{figure}

We consider the system in the thermodynamic limit: both the atomistic
and the coarse-grained regions are infinitely large, and at the same
time, the atomistic region is much larger than the coarse-grained
region. The hybrid region is much smaller than both the atomistic and
coarse-grained regions.  Therefore, the number of molecules in the
three regions satisfies $N_\CG\gg N_\AT\gg N_\HY$.  The coarse-grained
region can be treated as an infinitely large particle and energy
reservior of the atomistic region, and the hybrid region is an
infinitely thin filter that changes molecular resolution when a
molecule passes by (see Fig.~\ref{fig:system-thermo}). In the
thermodynamic limit, if there were no change of resolution (or
considering the full atomistic reference system), it is obvious that
the subregion corresponds to the atomistic region samples the
grand-canonial ensemble.  The question regarding the accuracy of
AdResS can be asked by: How accurately the atomistic region samples
the grand-canonial ensemble in the thermodynamic limit. Being more
specifically, we want to prove the probability density of the atomistic region satisfies
\begin{align}\label{eqn:dist-0}
  p(\vect x_\AT, N_\AT) \approx \frac{1}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT - \beta \mh^\AT(\vect x_\AT)} \Big\}
\end{align}
where $\mu^\ast_\AT$ is the chemical potential of reference system in
desired equilibrium, $\mathcal Z$ is the partition function
normalizing the probability density, and $\mh^\AT$ is the atomistic
Hamiltonian defined in the the subregion of the reference system that
corresponds to the atomistic region of the AdResS system.

In stead of directly proving Eq.~\eqref{eqn:dist-0}, Ref.~\cite{wang2013grand}
suggest investigating the following equivalent equations:
\begin{align}\label{eqn:dist-1-0}
  p(\vect x_\AT \vert N_\AT) &\approx \frac{1}{Z_{N_\AT}} \exp\Big\{{- \beta \mh^\AT(\vect x_\AT)}\Big\}  \\\label{eqn:dist-1-1}
  p(N_\AT) & \approx \frac{ Z_{N_\AT}}{\mathcal Z} \exp\Big\{{\beta\mu^\ast_\AT N_\AT}\Big\}
\end{align}
where $Z_{N_\AT}$ is the canonical partition function for an atomistic
system with $N_\AT$ molecules
\begin{align}
  Z_{N_\AT} = \int d\vect x_{\AT} \exp\Big\{{- \beta \mh^\AT(\vect x_\AT)}\Big\}.
\end{align}
The identity of the conditional probability holds: $ p(\vect x_\AT, N_\AT)  = p(\vect x_\AT \vert N_\AT) \, p(N_\AT) $.

Eq.~\ref{eqn:dist-1-0} is further splitted as
\begin{align}
  p(\vect x_\AT \vert N_\AT) =
  \sum_{N_\HY} \int {d}\vect x_\HY\,
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)\cdot
  p(\vect x_\HY, N_\HY\vert N_\AT)  
\end{align}
The first probability density in the integral is the probability density
of atomistic DOFs conditioned on the number of atomistic molecules and all
hybrid DOFs.
It can shown that if
(1) all interactions in the system are cut-offed;
(2) The atomistic region interacts with the bybrid region only in an atomistic way;
(3) The system is short-range correlated, and the correlation between the atomistic
and the coarse-grained regions is negligible, then the probability density $p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)$
is approximated by
\begin{align}\label{eqn:dist-conf-0}
  p(\vect x_\AT \vert N_\AT; \vect x_\HY, N_\HY)
  \propto
  \exp\Big\{-\beta \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY) \Big\},
\end{align}
where 
\begin{align}
  \mh^\AT(\vect x_\AT; \vect x_\HY, N_\HY)
  =
  \sum_{i=1}^{N_\AT}\frac12 m_i\vect v_i^2 +
  \sum_{i,j=1}^{N_\AT} \frac12 V^\AT(\vect r_{ij}) +
  \sum_{i=1}^{N_\AT}\sum_{j=N_\AT+1}^{N_\AT + N_\HY} V^\AT(\vect r_{ij})
\end{align}
is the atomistic Hamiltonian with parameters $\vect x_\HY, N_\HY$. It
should be noted that the probability density~\eqref{eqn:dist-conf-0}
is identical to that of the reference system with a subregion that
corresponds to the hybrid region.

In general, the probability density $p(\vect x_\HY, N_\HY\vert N_\AT)$
is not the same as the reference system.  For example, it has been
shown that the density distribution in the hybrid region deviates from
the desired one, even if the coarse-grained side is modelled to
reporduce the atomistic pressure~\cite{poblete2010coupling}.  However,
it is possible to raise necessary conditions that systematically
improves the accuracy of the probability density. The first necessary
condition is that the density profile of the hybrid region should be a
constant that is identical to the density of the atomistic reference
at desired equilibrium:
\begin{align}
  \rho_\HY(\vect r) = \rho_\AT^\ast = \frac NV
\end{align}
The second necessary condition is that the two body probability
density in the hybrid region is the same as the full atomistic
reference, In homogeneous and isotropic system, it is equivalent to
ask that the hybrid radial distribution function (RDF) should be the
same as that of the reference system:
\begin{align}
  g_\HY(r) = g^\ast_\AT(r).
\end{align}
It is fully justified to systematically raise the necessary conditions
upto $m$-th multibody probability density, however, it is not convenient in
numerics, because the correction to the $m$-th multibody probability density
needs a $m$-body correction force in general, which is computationally
too expensive.

In practice, the density in the hybrid region is correct by the
thermodynamic force, which is applied on top of the AdResS intermolecular interactions:
\begin{align}
  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf  \\
  \vect F^V_\moleidxone &= \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V}
\end{align}
calculated by a iterative scheme:

Therefore
certain manipulation in the hybrid region is need improve the accuracy
of $p(\vect x_\HY, N_\HY\vert N_\AT)$. However, it is still not clear
what is the sufficient conditions to achieve good accuracy in $p(\vect x_\HY, N_\HY\vert N_\AT)$.
It is easy to raise necessary conditions: The marginal distributions
of the hybrid cooridnates
\begin{align}
  p(\vect x_\HY) = \sum_{N_\HY = 0}^\infty \sum_{N_\AT = 0}^\infty p(\vect x_\HY, N_\HY\vert N_\AT) p(N_\AT)
\end{align}
should be the same as the reference system. Here we use the fact that
the probability $ p(N_\AT)$ should be of good accuracy, which will be
discussed later. This approach is validated because the discussion of
accuracy of $ p(N_\AT)$ does not require a good accuracy of $ p(\vect
x_\HY, N_\HY\vert N_\AT)$.  The $m$th marginal distribution of a probability density saying $p(\vect x_\HY)$ is defined
by
\begin{align}
  p_\HY^{(m)}(\vect x_1, \cdots \vect x_m) = \int\cdots\int d\vect x_{m+1}\cdots d\vect x_{N_\HY}
  p (\vect x_1, \cdots, \vect x_m, \vect x_{m+1}, \cdots \vect x_{N_\HY})
\end{align}
In a homogeneous system, the first marginal distribution is the
density profile in the

% It is not desirable to explicitly write the

% Eq.~\eqref{eqn:dist-1-0} and \eqref{eqn:dist-1-1} are equivalent to

% In 
% A good accuracy means that the atomistic region is embeded into the AdResS
% To answer what is an accurate equilibrium AdResS simulation,
% To understand the statistical properties of an AdResS system,

\section{Thermodynamic properties of adaptive resolution simulation}
\label{sec:thermodynamic}

\section{Test}
citation~\cite{wang2014exploring}

\bibliography{ref}{}
\bibliographystyle{unsrt}

% \begin{thebibliography}{}
% % and use \bibitem to create references.
% \bibitem{RefJ}
% % Format for Journal Reference
% Author, Journal \textbf{Volume}, (year) page numbers
% % Format for books
% \bibitem{RefB}
% Author, \textit{Book title} (Publisher, place year) page numbers
% % etc
% \end{thebibliography}

\end{document}

% end of file template.tex

### 2014-10-15 writeDown/pub.epj/paper.tex
back up before thermodynamics

@@
 \end{align}
-The intermolecular force is therefore calculated by
-\begin{align}\nonumber
-  {\vect F}^V_{\moleidxone \moleidxtwo}&= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo} \\ \label{eqn:f-v-interpol}
+The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
+which is explicitly written as
+\begin{align}\label{eqn:f-v-interpol}
+  {\vect F}^V_{\moleidxone \moleidxtwo}
   &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
@@
 
-Eq.~\ref{eqn:dist-1-0} is further splitted as
+\subsection{The accuracy of the configurational probability density}
+The configurational probability density~\ref{eqn:dist-1-0} is further splitted as
 \begin{align}
@@
 corresponds to the hybrid region.
+The probability density and local Hamiltonian
+can be written down for the coarse-grained region analogically.
 
@@
 at desired equilibrium:
-\begin{align}
+\begin{align}\label{eqn:necessary-1st}
   \rho_\HY(\vect r) = \rho_\AT^\ast = \frac NV
@@
 same as that of the reference system:
-\begin{align}
+\begin{align}\label{eqn:necessary-2nd}
   g_\HY(r) = g^\ast_\AT(r).
@@
 It is fully justified to systematically raise the necessary conditions
-upto $m$-th multibody probability density, however, it is not convenient in
-numerics, because the correction to the $m$-th multibody probability density
-needs a $m$-body correction force in general, which is computationally
-too expensive.
+upto $m$-th multibody probability density, for example the third necessary condition would be
+\begin{align}
+  C^{(3)}_\HY = C^{(3)\ast}_\AT
+\end{align}
+where $C^{(3)}$ is the three-body correlation.
+Since the system is homogeneous
+and isotropic, the three-body probability density is equivalent to
+three-body correlation function. 
+% However, it is not convenient in
+% numerics, because the correction to the $m$-th multibody probability density
+% needs a $m$-body correction force in general, which is computationally
+% too expensive.
 
 In practice, the density in the hybrid region is correct by the
-thermodynamic force, which is applied on top of the AdResS intermolecular interactions:
+thermodynamic force~\cite{fritsch2012adaptive}, which is applied on top of the AdResS intermolecular interactions:
 \begin{align}
-  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf  \\
-  \vect F^V_\moleidxone &= \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V}
+  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf,  \\
+  \vect F^V_\moleidxone& = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V},
 \end{align}
-calculated by a iterative scheme:
+where the thermodynamic forces is a one-body force defined over space,
+i.e.~$\vect F^\thf_i = \vect F^\thf(\vect r_\moleidxone)$ and $\vect F^{\thf, V}_\moleidxone = \vect F^{\thf,V}(\vect r_\moleidxone)$,
+for force and potential interpolations, respectively.
+The thermodynamic force is applied only in the hybrid region, and is
+calculated by the following iterative scheme:
+\begin{align}
+  \vect F_{k+1}^{\thf(, V)} (\vect r) = \vect F_k^{\thf(, V)} (\vect r)-
+  \frac{M}{\kappa(\rho^\ast_\AT)^2} \nabla\rho_k(\vect r)
+\end{align}
+where $k$ denotes the step of iteration. $\kappa$ is the
+isothermo-compressibility. In equilibrium the density profile $\rho(\vect r)$ in the
+atomistic and coarse-grained regions are constants, so the thermodynamic force
+is updated only in the hybrid region. When the hybrid density is flat, the thermodynamic
+force converges. An important subsequence of a flat hybrid density is that
+\begin{align}
+  \rho_\AT(\vect r) = \rho_\HY(\vect r) = \rho_\CG(\vect r) = \rho_\AT^\ast,
+\end{align}
+because the density profiles match at the atomistic-hybrid and
+hybrid-coarse-grained boundaries.
 
-Therefore
-certain manipulation in the hybrid region is need improve the accuracy
-of $p(\vect x_\HY, N_\HY\vert N_\AT)$. However, it is still not clear
-what is the sufficient conditions to achieve good accuracy in $p(\vect x_\HY, N_\HY\vert N_\AT)$.
-It is easy to raise necessary conditions: The marginal distributions
-of the hybrid cooridnates
+In a numerical example of SPC/E water~\cite{berendsen1987missing}
+system, it has been shown in Ref.~\cite{wang2013grand} that when the
+thermodynamic force is applied, the AdResS atomistic region reporduces
+mulit-body configurational probability density of the reference system
+upto three-body correlation.
+In principle, higher order of mulit-body correlation can be investigated in
+a similar way. A surprising numerical observation is that although
+only the thermodynamic force is applied, the second order necessary condition~\eqref{eqn:necessary-2nd}
+is automatically fulfilled, because the RDF is identical to the reference system in the buffer hybrid region
+$\{\vect r \,:\, \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$ that is interacting with
+the atomistic region. While the third necessary condition is not satisfied because deviation
+in the three-body correlation presents in the buffer bybrid region.
+It should be noted that there is no theoretical background why the second necessary
+condition is satisfied by only using the thermodynamic force,
+so one cannot expect the same benefit in other systems.
+
+The second necessary condition~\eqref{eqn:necessary-2nd} is fulfilled by the
+RDF correction $\vect F^\rdf$~\cite{wang2012adaptive}, which is a conservative two-body force added to the force interpolation~\eqref{eqn:f-f-interpol} as an extra term
+that applies only in the hybrid region:
+\begin{align}\label{eqn:rdf-corr-f}
+  {\vect F}_{\moleidxone \moleidxtwo}
+  =
+  w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}
+  +
+  (1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}
+  +
+  w_\moleidxone w_\moleidxtwo(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\rdf}_{\moleidxone\moleidxtwo}.
+\end{align}
+The RDF correction force is constructed from a RDF correction potential $V^\rdf$ by
 \begin{align}
-  p(\vect x_\HY) = \sum_{N_\HY = 0}^\infty \sum_{N_\AT = 0}^\infty p(\vect x_\HY, N_\HY\vert N_\AT) p(N_\AT)
+  \vect F_{\moleidxone\moleidxtwo}^\rdf = \vect F^\rdf(\vect r_{\moleidxone\moleidxtwo})
+  = -\nabla_{\vect r} V^\rdf(r_{\moleidxone\moleidxtwo}),
 \end{align}
-should be the same as the reference system. Here we use the fact that
-the probability $ p(N_\AT)$ should be of good accuracy, which will be
-discussed later. This approach is validated because the discussion of
-accuracy of $ p(N_\AT)$ does not require a good accuracy of $ p(\vect
-x_\HY, N_\HY\vert N_\AT)$.  The $m$th marginal distribution of a probability density saying $p(\vect x_\HY)$ is defined
-by
+which is calculated by the iterative Boltzmann inversion:
 \begin{align}
-  p_\HY^{(m)}(\vect x_1, \cdots \vect x_m) = \int\cdots\int d\vect x_{m+1}\cdots d\vect x_{N_\HY}
-  p (\vect x_1, \cdots, \vect x_m, \vect x_{m+1}, \cdots \vect x_{N_\HY})
+  V_{k+1}^\rdf(r) = V_k^\rdf(r) + k_BT \ln \Big[\frac{g_k(r)}{g^\ast_\AT(r)}\Big] 
 \end{align}
-In a homogeneous system, the first marginal distribution is the
-density profile in the
+where $k$ is the step of iteration. When the RDF of $k$th iteration is
+identical to that of the full atomistic reference $g^\ast_\AT(r)$, the
+iteration converges. It has been shown that the iterative scheme of
+thermodynamic force coupled with the iterative Boltzmann inversion RDF
+is effective in correcting the density profile $g_\HY(\vect r)$ and
+RDF $g_\HY(r)$ simultaneously~\cite{wang2012adaptive}.
+For SPC/E water system when the RDF correction is applied, the third
+necessary condition is automatically satisfied~\cite{wang2013grand}. Again, there is no
+theoretical prove behind this phenomenum, and one cannot expect the same
+benefit for other systems.
+
+\noindent\textbf{Remark:} The RDF correction is developed only for the force interpolation scheme,
+and a natural extension to the potential interpolation seems to be
+\begin{align}
+  {V}_{\moleidxone \moleidxtwo}
+  =
+  w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}
+  +
+  (1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}
+  +
+  w_\moleidxone w_\moleidxtwo(1-w_\moleidxone w_\moleidxtwo){V}^{\rdf}_{\moleidxone\moleidxtwo}.  
+\end{align}
+The effectiveness of this proposal has never been tested, and is still an open question.
+
+\subsection{The accuracy of the number probability}
+
+The accuracy of number probability $p(N_\AT)$ is investigated by a
+Taylor expansion w.r.t.~the relative size of the atomistic region to
+the whole system, which vanishes in the thermodynamic limit. The sufficient condition for the first order accuracy
+asks for a balance of the chemical potential~\cite{wang2013grand}:
+\begin{align}\label{eqn:mu-eq}
+  \mu_\CG - \mu_\AT = \omega_0,
+\end{align}
+where $\omega_0$ corresponds to the work from the filter, on each
+molecule that enters the atomistic region. An important conclusion
+form Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
+holds when the thermodynamic force is applied so that the atomistic
+and coarse-grained densities match. The conclusion is derived under
+the assumption of thermodynamic limit and the decorrlation between the
+atomistic and coarse-grained regions.
+
+The second order accuracy is achieved if the isothermo-compressibilty of the atomistic and coarse-grained sizes matches:
+\begin{align}
+  \kappa_\AT = \kappa_\CG
+\end{align}
+This is achieved by coarse-grained modeling, for example, the
+structure based coarse-grained models that reproduces the atomistic
+RDF~\cite{wang2009comparative}.
+
+\subsection{The WCA potential as a generic energy and particle reservior}
+
+From the accuracy analysis one surprising fact is that if the
+requirement for the accuracy is not very high, and only applying the
+thermodynamic force is acceptable, then there is actually no
+restriction on the coarse-grained model. One can even use ideal gas as
+a coarse-grained model, but the computational difficulty lies in the
+sudden switching on of the atomistic interaction when a coarse-grained
+molecule enters the hybrid region. If two molecules are entering at
+the same time and the same location, then the atomistic contribution
+to the intermolecular interaction~\eqref{eqn:f-f-interpol} or
+\eqref{eqn:f-v-interpol} is infinity, which drives the simulation
+unstable. This numerical difficulty can be avoided by using capped
+atomistic interaction~\cite{praprotnik2005adaptive}, or by using a
+gradually switching-on core-softened atomistic
+interaction~\cite{heyes2010thermodynamic}.
+In Ref.~\cite{wang2013grand}, the authors instead tested with
+Weeks-Chandler-Andersen (WCA) potential~\cite{weeks1971role} as the
+coarse-grained model, which is a short-ranged and pure repulsive
+interaction.  For a SPC/E water system, the cut-off radius of WCA potential
+can be 2.4 time smaller than the cut-off used in the atomistic
+region. Since the computational cost with is of order $\mo(r_c^3)$,
+the computational cost spent on each pair interaction
+is 19 times cheaper. For each pair of molecules the atomistic model computes
+10 pairwise interactions (9 electrostatic + 1 van der Waals), while the
+WCA model computes only one, therefore the WCA model in total costs $1/190$ 
+computational effort on force computation than atomistic model.
+The WCA approach has been successfully used in calculating the
+chemical potential of various complex fluids and mixtures~\cite{agarwal2014chemical}.
+
+% Therefore
+% certain manipulation in the hybrid region is need improve the accuracy
+% of $p(\vect x_\HY, N_\HY\vert N_\AT)$. However, it is still not clear
+% what is the sufficient conditions to achieve good accuracy in $p(\vect x_\HY, N_\HY\vert N_\AT)$.
+% It is easy to raise necessary conditions: The marginal distributions
+% of the hybrid cooridnates
+% \begin{align}
+%   p(\vect x_\HY) = \sum_{N_\HY = 0}^\infty \sum_{N_\AT = 0}^\infty p(\vect x_\HY, N_\HY\vert N_\AT) p(N_\AT)
+% \end{align}
+% should be the same as the reference system. Here we use the fact that
+% the probability $ p(N_\AT)$ should be of good accuracy, which will be
+% discussed later. This approach is validated because the discussion of
+% accuracy of $ p(N_\AT)$ does not require a good accuracy of $ p(\vect
+% x_\HY, N_\HY\vert N_\AT)$.  The $m$th marginal distribution of a probability density saying $p(\vect x_\HY)$ is defined
+% by
+% \begin{align}
+%   p_\HY^{(m)}(\vect x_1, \cdots \vect x_m) = \int\cdots\int d\vect x_{m+1}\cdots d\vect x_{N_\HY}
+%   p (\vect x_1, \cdots, \vect x_m, \vect x_{m+1}, \cdots \vect x_{N_\HY})
+% \end{align}
+% In a homogeneous system, the first marginal distribution is the
+% density profile in the
 
@@
 
-\section{Test}
+For the 
+In Ref.~\cite{wang2013grand}, it has been shown that
+
+\section{Dynamical properties: adaptive resolution simulation beyond equilibrium}
 citation~\cite{wang2014exploring}

### 2014-10-17 writeDown/pub.epj/paper.tex
add results of dynamical properties of alanine system

@@
 \newcommand{\exc}{{\textrm{extra}}}
-\newcommand{\inv}{{\textrm{equi}}}
+\newcommand{\equi}{{\textrm{eq}}}
 
@@
 It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
-exist a potential so that the force interpolation is derived by taking the negative gradient of the potential~\cite{praprotnik2011comment,dellesite2007some}.
+exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
+unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
 It is easy to show that the force interpolation satisfies the momentum conservation: Since
@@
 acting along the direction of decreasing weighting function.
+This force is defined as the force of changing representation:
 It should be noted that
@@
 does not conserves the momentum.
+We define the accumulative effect of this term by the force of changing representation:
+\begin{align}
+  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
+\end{align}
 
@@
 
+\recheck{Remark, add the remark of inversed weighting function}
+
 \section{Equilibrium statistical properties of adaptive resolution simulation}
@@
 an atomistic environment, and the AdResS simulation is of good accuracy.
+\recheck{comments on the ``atomistic region'' of the reference system}
 
@@
 \subsection{The accuracy of the configurational probability density}
-The configurational probability density~\ref{eqn:dist-1-0} is further splitted as
+The configurational probability density~\eqref{eqn:dist-1-0} is further splitted as
 \begin{align}
@@
 
-For the 
-In Ref.~\cite{wang2013grand}, it has been shown that
+In the reference system, if the equilibrium state is achieved, then
+the temperature, pressure and chemical potential of the atomistic and
+coarse-grained subregions match. In AdResS system, the global uniform
+temperture distrubution in equilibrium is impoosed by the Langevin
+thermostat.  However, extra term appear in the pressure or chemical
+potential relation when the momentum or energy conservation is absent
+(see Tab.~\ref{tab:conv-laws}), respectively.
+
+The chemical potential balance can be investigated from the fact that
+when the uniform density distribution is guaranteed by thermodynamic force in equilibrium, the chemical potential
+difference between the resolutions is compensited by $\omega_0$, which
+is the work per molecule from the filter when a molecule leaves the
+coarse-grained region and enters the atomistic region (see
+relation~\eqref{eqn:mu-eq}).  Now the question turns out to be what
+contributes to the work $\omega_0$.  For the potential interpolation,
+the work of the filter is nothing but the work of the thermodynamic
+force plus the extra kinetic energy corresponding to the extra DOFs
+when a molecule obtains higher resolution:
+\begin{align}\label{eqn:mu0-v}
+  \omega_0 = \omega^{\thf,V} + \omega^\dof,
+\end{align}
+where $ \omega^{\thf,V}$ denotes the work of the thermodynamic force
+of potential interpolation.
+This work is path independent if the thermodynamic force is defined as a function of the distance to the atomistic region, and applies along the gradient of the weighting function.
+We always assume the thermodynamic force satisfies these conditions.
+For the force interpolation, 
+we denote the extra contribution due to the absence of the enregy conservation
+by $\omega^\exc$, then
+\begin{align}\label{eqn:mu0-f}
+  \omega_0 = \omega^{\thf} + \omega^\exc + \omega^\dof,
+\end{align}
+where $\omega^{\thf}$ is the work of the thermodynamic force of force interpolation.
+The magnitude of the extra term $\omega^\exc$ is unclear up to now,
+however, it is easy to computewith the help of the pressure relations.
+
+For the force interpolation, the pressure of different resolutions
+is related by~\cite{fritsch2012adaptive}
+\begin{align}\label{eqn:p-eq-f}
+  p_\CG - p_\AT = \rho_0 \:\omega^{\thf},
+\end{align}
+in which the work of the thermodynamic force again plays an important
+role.  For the potential interpolation, the pressure relation can be
+investigated by an imaginary infiniesimal volume increment of the atomistic
+region, and the same amount of volume decrement of the coarse-grained
+region. Following this idea, Ref.~\cite{agarwal2014chemical} proves that in
+equilibrium the pressure between the resolutions is related by
+\begin{align}\label{eqn:p-eq-v}
+  p_\CG - p_\AT = \rho_0 (\omega^{\thf,V} - \omega^\rep)  
+\end{align}
+where $\omega^\rep$ is the work done by the average force of change representation:
+\begin{align}\label{eqn:work-rep}
+  \omega^\rep = \int \langle \vect F^\rep(\vect r)\rangle_V\circ d\vect r
+\end{align}
+where ``$\circ$'' means that the integral should be understood as along the path.
+Since the force of changing representation acts always along the gradient of the weighting
+function, therefore, if the system is homogeneous in the hybrid region, then the integral
+is path independent. The ensemble average  can be estimated by sampling.
+The force of changing representation merges from the last term of potential
+interpolation~\eqref{eqn:f-v-interpol}, and contributes to the
+pressure relation~\eqref{eqn:p-eq-v} because it does not satisfies the Newton's third
+law.
+
+Using Eq.~\eqref{eqn:mu0-v} and \eqref{eqn:mu0-f} one has $\omega^{\thf,V} - \omega^\thf = \omega^\exc$,
+while using \eqref{eqn:p-eq-f} and \eqref{eqn:p-eq-v} one has $\omega^{\thf,V} - \omega^\thf = \omega^\rep$.
+Therefore, we have 
+\begin{align}
+  \omega^\exc = \omega^\rep
+\end{align}
+which gives a explicit expression for the extra energy contribution
+due to the absence of energy conservation in the force
+interpolation. It should be noted that the ensemble averge in the work
+of changing representation~\eqref{eqn:work-rep} is defined for the
+potential interpolation, however, the estimate of the term
+$\omega^\rep$ does not depend on the ensemble, at least up to the
+``first order approximation''~\cite{agarwal2014chemical}, because the
+hybrid region of the potential and force interpolation have the same
+density. In Ref.~\cite{wang2013grand} an even strong conclusion is shown numerically in the SPC/E water system: The
+averge force of changing representation estimated from potential
+interpolation is pointwisly identical to that estimated from the force
+interpolation. The thermodynamic relation discoved in
+force and potential interpolation AdResS schemes are summarized
+in Tab.~\ref{tab:thermodynamic}.
+
+\begin{table}
+  \centering
+  \caption{A summary of the thermodynamic relations satisfied in force and potential interpolation AdResS.}
+  \label{tab:thermodynamic}
+  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}lll}\hline\hline
+    &         Force interp. AdResS     &       Potential interp. AdResS \\
+    Temperature    &   {$T_\AT = T_\CG$}                                                & {$T_\AT = T_\CG$}                                        \\
+    Pressure       &   {$p_\CG - p_\AT = \rho_0\, \omega^\thf$}                          & {$p_\CG - p_\AT = \rho_0(\omega^{\thf,V} - \omega^\rep)$} \\
+    Chemical pot.  &   {$\mu_\CG - \mu_\AT = (\omega^\thf + \omega^\dof +\omega^\rep)$}   & {$\mu_\CG - \mu_\AT = \omega^{\thf,V}+ \omega^\dof$}      \\\hline\hline
+  \end{tabular*}
+\end{table}
 
 \section{Dynamical properties: adaptive resolution simulation beyond equilibrium}
-citation~\cite{wang2014exploring}
+
+\recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
+}
+
+\subsection{Velocity auto-correlation of water}
+
+\subsection{Alanine dipeptide dissolved in water: equilibrium and dynamical properties}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.99\textwidth]{figs/system.alanine/all.eps}
+  \caption{(a): A schematic plot of the alanine dipeptide molecule,
+    and the two dihedral angles $\phi$ and $\psi$ that are used to
+    represent the conformations of the molecule. (b) and (c): The free
+    energy landscape plotted using variables $\phi$ and $\psi$.  (b)
+    is for full atomistic reference simulation, while (c) is for
+    AdResS simulation.}
+  \label{fig:ala}
+\end{figure}
+
+The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
+used as a testing case for computational method in simulating real
+biomolecular system.
+The system presents a very clear time-scale seperation: There are fast
+motions like bond and angle vibration that happens on the time-scale of tens of femtoseconds, while
+there are slow conformational changes that happens on the time-scale of hundreds of picoseconds.
+The dihedral angles $\phi$ and $\psi$ (see
+Fig.~\ref{fig:ala}~(a)) are usually chosen as slow variables that  describles
+the molecular conformation and its transitions of the moelcules, which are of
+general biological interest.
+
+The free energy defined as the logrithm of equilibrium probability density over
+$\phi$--$\psi$ space:
+\begin{align}
+  F(\phi,\psi) = -k_BT \ln p_\equi(\phi,\psi)
+\end{align}
+is plotted in Fig.~\ref{fig:ala}~(b) and (c). The AdResS free energy is
+in good consistency with the full atomistic reference system. This is expected
+at least in equilibrium, because as discussed in Sec.~\ref{sec:statistical}, the
+AdResS sampling approximates the atomistic grand-canonical ensemble.
+
+In pratice, not only the equilibrium probability density if of interest,
+sometimes how the system relax to equilibrium is also of interest.
+A direct analysis of the MD trajectories for these properties is not easy.
+% Or equivalently
+% at which timescale the slow dynamics  happens and from which conformation to which it corresponds to.
+One possible solution is the Markov state model (MSM), which
+approximate the original high-dimensional dynamics by a finite-state
+Markov process (also called reduced dynamics),
+and the original time-dependent probability density define on the phase
+space $p_t(\vect x)$ is approximated by a  temporal discrete $\vect p_{k\tau}$ probability defined on the finite-state space.
+The step of the temporal discretization $\tau$ is called the lag-time.
+We always assume the reduced
+dynamics is Markovian, although uaually it is not so in practice, and may become one of the main sources of the error.
+It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
+Due to the Markovianity of the reduced dynamics, the
+probability at time $k\tau$ is given by
+\begin{align}
+\vect p_{k\tau} = \mathcal Q^k(\tau)\circ \vect p_0,
+\end{align}
+where $\mathcal Q(\tau)$ is the transfer operator
+associated to the reduced dynamics. In equilibrium, the transfer operator is time-homogeneous.
+Due to the Markovianity, for any $k$, we have
+$p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t (\vect x)$.
+If the propagator is irreducible and aperiodic, than according to Perron-Frobenius theorem, the maximum
+eigenvalue is single and equal to 1.
+If the dynamics
+is further assumed to be reversible, then all eigenvalues of the propagator are
+real valued.
+The first $m$ largest eigenvalues are denoted by $1 = \lambda_1 > \lambda_2 \geq \lambda_3 \geq \cdots \geq \lambda_m$, and
+the corresponding eigenvetors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$. The leading eigenvector is nothing but the
+equilibrium probability that satisfies $\Phi_1 = \mathcal Q(\tau)\circ \Phi_1$.
+The time evolution of the reduced probability density can be expaned by 
+\begin{align}\label{eqn:expan}
+  \vect p_{k\tau} = \Phi_1 + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} \,a_i\Phi_i + \textrm{fast decaying dynamics},
+\end{align}
+where $t_i$ is the timescale that corresponds to the $i$th eigenvalue:
+\begin{align}\label{eqn:time-scale}
+  t_i  = -\frac{\tau}{\log\lambda_i}, \quad i=2, \cdots, m,
+\end{align}
+and $a_i$ are constant that are determined by the initial state. As can be seen from Eq.~\eqref{eqn:expan}, the
+time-dependent probability  converges to the equilibrium probability as time goes to infinity.
+The timescale of the slow part of the relaxation is govenerned by the leanding eigenvectors through Eq.~\eqref{eqn:time-scale},
+while the conformational change corresponds to each timescale is indicated by the eigenvector.
+We assume a gap in the spectrum between $\lambda_m$ and the rest of the spectrum $\lambda_{m+1}, \cdots$,
+therefore, the dynamics of the rest of the spectrum decays out very fast, and is not of particular interest.
+
+The accuracy analysis of the MSM can be find in literature e.g.~\cite{}.
+
+% The spectral anaysis of the MSM will reveal the
+% implied timescales, and corresponding conformational changes.
+% It has
+% been proved that MSM is a good approximation to the original dynamics.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{figs/system.alanine/fig-eig-val.png}
+  \caption{The non-trivial leading timescale calculated from the
+    Markov state modeling for the system of alanine dipeptide
+    dissolved in water. In this figure, $t_2$ $t_3$ and $t_4$
+    correspond to the first, second and third non-trivial leading
+    timescale, respectively. The horizontal axis $\tau$ is the
+    lag-time used to build the Markov state model. For a sufficient
+    large $\tau$ the values of the timescales should be independent on
+    the lag-time. The shadowing regions around the lines indicate the
+    statistical uncertainty of the result. }
+  \label{fig:ala-msm-t}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-2.eps}
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-3.eps}
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-4.eps}\\
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-2.eps}
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-3.eps}
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-4.eps}\\
+  \caption{The eigenvectors corresponding to the first three leading timescales.
+    The first row presents the eigenvectors of the full atomistic reference, while the second
+    row presents those of the AdResS simulation. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
+    timescales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
+    denoted by the color. 
+    The conformational
+    changes indicated by the eigenvectors are noted on the plots.}
+  \label{fig:ala-msm-v}
+\end{figure}
+
+Here we present the eigenvalues and eigenvectors in
+Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}, respectively. The
+eigenvalue should be $\tau$ independent if the MSM is of good
+accuracy. From the Fig.~\ref{fig:ala-msm-t}, the full atomistic
+reference and the AdResS result are consistent within the statistical
+uncertainty.  The eigenvectors of the AdResS are also consistent with
+those of the full atomistic reference. Although calculated from the
+equilibrium MD simulations, the leading timescales and the
+corresponding eigenvectors are not the equilibrium properties, because
+the transition probability (or the propagator) are actually
+time-correlation functions, which are called dynamical properties in
+this context. A good reproduction of the equilibrium properties does
+not necessary implies a reproduction of the dynamical properties.
+Although currently there is still no theoretical answer why AdResS is
+so good in reproducing the dynamical properties, the provided
+numercial example suggests that AdResS is promising in the applications
+beyond equilibrium.
 

### 2014-10-27 writeDown/pub.epj/paper.tex
back up the changes to the MSM, adding intro

@@
 
+\newcommand{\confa}[0]{{\alpha_{\textrm{R}}}}
+\newcommand{\confb}[0]{{\textrm{C}7_{\textrm{eq}}}}
+\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}
+\newcommand{\confd}[0]{{\textrm{C}7_{\textrm{ax}}}}
+
 % \usepackage{amsfonts}
@@
 %
+
+\section{Introduction}
+
+Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,praprotnik2011statistical,fritsch2012adaptive} is a concurrent multiscale simulation method for molecular system.
+The terminology ``concurrent multiscale simulation'' means that
+part of the system is simulated with higher resolution molecular models for the
+purpose of accuracy, and \emph{in the meanwhile} the rest of the system is
+simulated with lower resolution models for the purpose of saving computational cost.
+The AdResS is, therefore, suitable for the systems that different physcial
+phenomena happen concurrently at different time and length scales. For example,
+the structure of a protein and its solvation shell
+should be resolved at the atomistic level, while far away form the protein,
+the only the hydrodynamic properties are of interest, which can be studied with satisfactory
+accuracy with very coarse-grained or even continum
+models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
+Similar  
+techniques sharing the ``concurrent'' idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.
+
+Traditionally the
 
@@
 
-\subsection{Velocity auto-correlation of water}
+\subsection{Velocity and dipole auto-correlation of water}
 
@@
     is for full atomistic reference simulation, while (c) is for
-    AdResS simulation.}
+    AdResS simulation. The metastable conformations coded by $\confa$, $\confb$, $\confc$ and $\confd$
+    are noted on plot (b).}
   \label{fig:ala}
@@
 The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
-used as a testing case for computational method in simulating real
-biomolecular system.
-The system presents a very clear time-scale seperation: There are fast
-motions like bond and angle vibration that happens on the time-scale of tens of femtoseconds, while
-there are slow conformational changes that happens on the time-scale of hundreds of picoseconds.
+used as a testing case for evaluating the new computational method in simulating 
+biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
+The system presents a very clear timescale seperation: There are fast
+motions like bond and angle vibration that happens in tens of femtoseconds, while
+there are slow conformational transformations that happens in hundreds of picoseconds.
 The dihedral angles $\phi$ and $\psi$ (see
@@
 
-The free energy defined as the logrithm of equilibrium probability density over
+The free energy defined as the logrithm of the projected equilibrium probability density on the
 $\phi$--$\psi$ space:
 \begin{align}
-  F(\phi,\psi) = -k_BT \ln p_\equi(\phi,\psi)
+  F(\phi,\psi) = -k_BT \ln p_\equi(\phi,\psi).
 \end{align}
-is plotted in Fig.~\ref{fig:ala}~(b) and (c). The AdResS free energy is
-in good consistency with the full atomistic reference system. This is expected
-at least in equilibrium, because as discussed in Sec.~\ref{sec:statistical}, the
-AdResS sampling approximates the atomistic grand-canonical ensemble.
+The free energy of the full atomistic reference system is showed in
+Fig.~\ref{fig:ala}~(b), which clearly presents the metastablity in the
+system: several highly populated regions that correspond to metastable
+conformations are seperated by lowly populated regions that are
+identified as transition regions.
+The AdResS free energy is in good
+consistency with the full atomistic reference system, and
+reproduces the metastable conformations and their populations
+with satisfactory accuracy.
+This is expected in equilibrium, because as discussed in
+Sec.~\ref{sec:statistical}, the AdResS sampling approximates the
+atomistic grand-canonical ensemble.
 
-In pratice, not only the equilibrium probability density if of interest,
-sometimes how the system relax to equilibrium is also of interest.
-A direct analysis of the MD trajectories for these properties is not easy.
+In pratice, not only the equilibrium properties like the free energy are of interest,
+but also the dynamical properties like the conformational transitions and the corresponding timescales
+are of highly biological importance.
+% sometimes how the system relaxes to equilibrium is also of interest,
+% e.g.~
+% A direct analysis of the MD trajectories for these properties is not easy.
 % Or equivalently
 % at which timescale the slow dynamics  happens and from which conformation to which it corresponds to.
-One possible solution is the Markov state model (MSM), which
-approximate the original high-dimensional dynamics by a finite-state
-Markov process (also called reduced dynamics),
-and the original time-dependent probability density define on the phase
-space $p_t(\vect x)$ is approximated by a  temporal discrete $\vect p_{k\tau}$ probability defined on the finite-state space.
+When the system presents metastablity,
+one powerful tool for this purpose
+is the Markov state model (MSM)~\cite{prinz2011probing,prinz2011markov,schuette2011markov}, which
+approximate the original high-dimensional dynamics by a finite-state reduced
+Markov process.
+The accuracy analysis regarding  this approximation is well-founded~\cite{sarich2010approximation,djurdjevac2012estimating}.
+The MSM has found successfully applications in various fileds, for example studying complex protein systems
+(two of the hundreds examples are Ref.~\cite{noe2009constructing,kohlhoff2014cloud}).
+
+In a standard MSM approach, the full phase space is firstly deomposed in to a union of finite number of states
+(not necessarily identical to the metastable conformations),
+then
+the original time-dependent probability density define on the phase
+space ($p_t(\vect x)$) is approximated by a temporal discrete $\vect p_{k\tau}$ probability defined on the finite-state space.
 The step of the temporal discretization $\tau$ is called the lag-time.
-We always assume the reduced
-dynamics is Markovian, although uaually it is not so in practice, and may become one of the main sources of the error.
-It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
-Due to the Markovianity of the reduced dynamics, the
-probability at time $k\tau$ is given by
+The reduced
+dynamics is always assumed to be Markovian,
+although uaually it is not,  and in practice it becomes one of the main sources of the error.
+% It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
+% Due to the Markovianity of the reduced dynamics, the
+Under this assumption, the original continuous dynamics is approximated by the Markov processes governed by
+% probability at time $k\tau$ is given by
 \begin{align}
-\vect p_{k\tau} = \mathcal Q^k(\tau)\circ \vect p_0,
+\vect p^\top_{k\tau} = \vect p^\top_0 \cdot \vect T^k(\tau),
 \end{align}
-where $\mathcal Q(\tau)$ is the transfer operator
-associated to the reduced dynamics. In equilibrium, the transfer operator is time-homogeneous.
-Due to the Markovianity, for any $k$, we have
-$p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t (\vect x)$.
-If the propagator is irreducible and aperiodic, than according to Perron-Frobenius theorem, the maximum
-eigenvalue is single and equal to 1.
+where $\vect T(\tau)$ is the transition maxtix that
+associates to the reduced dynamics. The matrix element, for example $T_{ij}$
+is defined as the probability of the system being in state
+$j$ at $\tau$,  provided the system being in state $i$ at time 0.
+% The ``$\cdot$'' denotes the matrix-vector multiplication.
+In equilibrium, the transition matrix is time-homogeneous, i.e.~$\vect T(\tau)$ does not depend on time $t$.
+% Due to the Markovianity, for any $k$, we have
+% $p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t (\vect x)$.
+If the transition matrix is irreducible and aperiodic, than according to Perron-Frobenius theorem, the maximum
+eigenvalue is reached and single. Due to the stochaticity of the matrix, the maximal eigenvalue is equal to 1.
 If the dynamics
-is further assumed to be reversible, then all eigenvalues of the propagator are
+is further assumed to be reversible, then all eigenvalues of the transition are
 real valued.
 The first $m$ largest eigenvalues are denoted by $1 = \lambda_1 > \lambda_2 \geq \lambda_3 \geq \cdots \geq \lambda_m$, and
-the corresponding eigenvetors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$. The leading eigenvector is nothing but the
-equilibrium probability that satisfies $\Phi_1 = \mathcal Q(\tau)\circ \Phi_1$.
-The time evolution of the reduced probability density can be expaned by 
-\begin{align}\label{eqn:expan}
-  \vect p_{k\tau} = \Phi_1 + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} \,a_i\Phi_i + \textrm{fast decaying dynamics},
-\end{align}
-where $t_i$ is the timescale that corresponds to the $i$th eigenvalue:
-\begin{align}\label{eqn:time-scale}
-  t_i  = -\frac{\tau}{\log\lambda_i}, \quad i=2, \cdots, m,
-\end{align}
-and $a_i$ are constant that are determined by the initial state. As can be seen from Eq.~\eqref{eqn:expan}, the
-time-dependent probability  converges to the equilibrium probability as time goes to infinity.
-The timescale of the slow part of the relaxation is govenerned by the leanding eigenvectors through Eq.~\eqref{eqn:time-scale},
-while the conformational change corresponds to each timescale is indicated by the eigenvector.
-We assume a gap in the spectrum between $\lambda_m$ and the rest of the spectrum $\lambda_{m+1}, \cdots$,
-therefore, the dynamics of the rest of the spectrum decays out very fast, and is not of particular interest.
+the corresponding left eigenvetors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$.
+The leading eigenvector is non-negative, and satisfies $\Phi^\top_1 = \Phi^\top_1\cdot\vect T(\tau)$.
+With proper normalization the leanding eigenvector is identical to the 
+equilibrium probability density.
+At inifinitely long time, the probability density $p_{k\tau}$ converges to the equilibrium probability.
+The speed of the convergence is characterized by the non-trivial leading timescales that are
+determined by the leading eigenvalues:  $t_i  = -{\tau}/{\log\lambda_i}, \ i=2, \cdots, m$.
+Since the eigenvectors are orthorgonal and the first eigenvectors is non-negative, the reset
+of the eigenvectors have a vanished sum over all elements: Their
+value is positive at some states and negative at some other states.
+The different signs in the eigenvectors denote the conformational transition corresponding to the
+timescale $t_i$.
 
-The accuracy analysis of the MSM can be find in literature e.g.~\cite{}.
+% If the leading eigenvector is normalized to 1.
+% The  reduced probability
+
+% The time evolution of the reduced probability density can be expaned by 
+% \begin{align}\label{eqn:expan}
+%   \vect p_{k\tau} = \Phi_1 + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} \,a_i\Phi_i + \textrm{fast decaying dynamics},
+% \end{align}
+% where $t_i$ is the timescale that corresponds to the $i$th eigenvalue:
+% \begin{align}\label{eqn:timescale}
+%   t_i  = -\frac{\tau}{\log\lambda_i}, \quad i=2, \cdots, m,
+% \end{align}
+% and $a_i$ are constant that are determined by the initial state. As can be seen from Eq.~\eqref{eqn:expan}, the
+% time-dependent probability  converges to the equilibrium probability as time goes to infinity.
+% The timescale of the slow part of the relaxation is govenerned by the leanding eigenvalues through Eq.~\eqref{eqn:timescale},
+% while the conformational change corresponds to each timescale is indicated by the eigenvector.
+% We assume a gap in the spectrum between $\lambda_m$ and the rest of the spectrum $\lambda_{m+1}, \cdots$,
+% therefore, the dynamics of the rest of the spectrum decays out very fast, and is not of particular interest.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figs/system.alanine/fig-eig-val.png}
+  \includegraphics[width=0.5\textwidth]{figs/system.alanine/fig-eig-val.png}
   \caption{The non-trivial leading timescale calculated from the
@@
   \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-3.eps}
-  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-4.eps}\\
+  \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-atom-4.eps}\\[-.4cm]
   \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-2.eps}
@@
   \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-4.eps}\\
-  \caption{The eigenvectors corresponding to the first three leading timescales.
+  \caption{The eigenvectors corresponding to the first three leading timescales computed using lag-time $20$~ps.
     The first row presents the eigenvectors of the full atomistic reference, while the second
@@
 
-Here we present the eigenvalues and eigenvectors in
-Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}, respectively. The
-eigenvalue should be $\tau$ independent if the MSM is of good
-accuracy. From the Fig.~\ref{fig:ala-msm-t}, the full atomistic
+In the example of alanine dipeptide dissoved in water, the states in the MSM
+is defined by uniformly dividing the $\phi$-$\psi$ space in to $20\times 20$ bins.
+Each bin presents a state in MSM, and the transition matrix is sampled by equilibrium
+MD simulations with the local thermostating scheme.
+The MSM and the leading eigen properties are built and analyzed by the software EMMA~\cite{senne2012emma}.
+The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference in
+Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
+eigenvalues should be $\tau$ independent if the MSM is of good
+accuracy, and from Fig.~\ref{fig:ala-msm-t} they are so for $\tau \geq 20$~ps.
+Also from the Fig.~\ref{fig:ala-msm-t}, the full atomistic
 reference and the AdResS result are consistent within the statistical
-uncertainty.  The eigenvectors of the AdResS are also consistent with
+uncertainty.
+From Fig.~\ref{fig:ala-msm-v}, the conformational transitions corrsponds
+to $t_2$, $t_3$ and $t_4$ are $\{\confa \} \leftrightarrow \{\confc,\confd\}$,
+$\{\confa, \confc \} \leftrightarrow \{\confb\}$ and $\{\confc \} \leftrightarrow \{\confd\}$, respectively.
+The eigenvectors and the indicated conformational transitions of the AdResS are also consistent with
 those of the full atomistic reference. Although calculated from the
@@
 corresponding eigenvectors are not the equilibrium properties, because
-the transition probability (or the propagator) are actually
-time-correlation functions, which are called dynamical properties in
+the transition probability (elements of the transition matrix) are actually
+time-correlation functions of the characteristic functions, which are called dynamical properties in
 this context. A good reproduction of the equilibrium properties does
 not necessary implies a reproduction of the dynamical properties.
-Although currently there is still no theoretical answer why AdResS is
-so good in reproducing the dynamical properties, the provided
-numercial example suggests that AdResS is promising in the applications
-beyond equilibrium.
+Although currently there is still no theoretical answer why AdResS works,
+the provided numercial example suggests that AdResS being promising in the applications beyond equilibrium,
+and  worth further theoretical studies.
+
+\section{Open problems of the adaptive resolution simulation}
 

### 2014-10-28 writeDown/pub.epj/paper.tex
finish the first write of the intro

@@
 \title{Adaptive Resolution Simulation: Theoretical Fundations and Open Questions}
-\author{Han Wang\inst{1}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}}
+\author{Han Wang\inst{1}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{2}}
 %
-\institute{Zuse Institut Berlin}
+\institute{Zuse Institut Berlin, \and Institut f\"ur Mathematik, Freie Universit\"at Berlin}
 %
@@
 
-Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,praprotnik2011statistical,fritsch2012adaptive} is a concurrent multiscale simulation method for molecular system.
+Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
 The terminology ``concurrent multiscale simulation'' means that
@@
 
-Traditionally the
+The time evolution of a classical molecular systems
+is modeled with Newtonian dynamics, and fundamental conservation laws
+are satisfied, i.e.~the momentum and energy conservations.
+However, in the AdResS system,
+due to the spacial change of molecular resolution,
+the two conservation laws cannot be satisfied in the same system~\cite{praprotnik2011comment,dellesite2007some}.
+Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
+that preserves the momentum conservation while breaks the energy
+conservation.
+Recently,
+alternative approaches based on \emph{potential interpolation},
+which preserve energy conservation while break momentum conservation,
+were designed~\cite{wang2013grand,potestio2013hamiltonian}.
+The choice between the two AdResS branches therefore depends on the application. For example, in the
+cases of studying hydrodynamic the momentum conservation is prefered to the energy conservation.
+However, if only the equilibrium properties are of interest,
+the question should be asked on the ensemble that AdResS samples,
+rather than directly on the mechanical conservation laws.
+In this context,
+it worth noting that the energy conservation is not a must for theoretical analysis on the equilibrium statistical properties,
+although out of the energy conservation
+one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
+(not a physical one~\cite{dellesite2013multiscale}),
+which reduces the mathematical difficulties of the theoretical analysis.
+In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
+under the same theoretical framework (GC-AdResS)~\cite{wang2013grand} that raises necessary conditions
+for a grand-canonical sampling with AdResS scheme.
+In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
+provided for both branches of the AdResS scheme.
+From these relations, it is noticed that the abscence of mechanical conservation laws 
+modifies the way of thermodynamic equilibrium between the resolutions.
 
-\section{The two ways  of designing the hybrid region}
+The GC-AdResS framework answers of how to accurately compute the  equilibrium properties.
+However, although the system is in equilibrium,
+some properties, which are called dynamical properties, cannot be simply computed from the equilibrium averages.
+% These properties are called dynamical properties.
+A typical example is the velocity auto-correlation.
+% that describs the infiniesimal response of the system
+% to external perturbation.
+Moreoever, the time-scales of conformational transformations
+of bio-macromolecules (e.g.~protein and DNA)
+are, again, not equilibrium averages.
+The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
+and to the best of our knowledge, there is no theoretical answers on how accurately does AdResS reproduce
+dynamical properties of a system.
+Therefore, it is of practical significance to  provide numerical
+evidence on the performance of AdResS in computing the dynamical properties.
+In Sec.~\ref{sec:dynamical}, we investigate the
+velocity auto-correlation in an AdResS water system, and the
+leading time-scales and corresponding conformational dynamics of
+a model dipeptide system.
+The importance of designing the thermostat in these simulations
+is also discussed.
+The paper is closed by a concluding section~\ref{sec:conclusion}
+that mainly discusses the opening problems in AdResS from both theoretical
+and practical point of view.
 
+\section{The hybrid region: bridging the molecular models of different resolutions}
+\label{sec:design}
 The AdResS uses a weighting function $w(\vect r)$ that is a scalor
@@
 In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
-that both approaches approximately sample the grand-canonial ensamble.
+that both approaches approximately sample the grand-canonial ensemble.
 
@@
 \section{Dynamical properties: adaptive resolution simulation beyond equilibrium}
+\label{sec:dynamical}
 
@@
 \section{Open problems of the adaptive resolution simulation}
+\label{sec:conclusion}
 

### 2014-11-10 writeDown/pub.epj/paper.tex
add the velocity auto-correlation

@@
 %
-\title{Adaptive Resolution Simulation: Theoretical Fundations and Open Questions}
-\author{Han Wang\inst{1}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{2}}
+\title{Adaptive Resolution Simulation in Equilibrium and Beyond}
+\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
 %
-\institute{Zuse Institut Berlin, \and Institut f\"ur Mathematik, Freie Universit\"at Berlin}
+\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
+  \and Zuse Institute Berlin (ZIB), Germany
+  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
 %
@@
 
-Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
+Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
 The terminology ``concurrent multiscale simulation'' means that
@@
 \label{sec:design}
-The AdResS uses a weighting function $w(\vect r)$ that is a scalor
-function defined over the simulation region to denote the resolution
-of the system. In the atomistic region the value of the
-weighting function is usually set to 1, while in the coarse-grained
-region it is usually set to 0. In between, there is a bybrid region
-that is denoted by $\Omega_\HY$
-(or called transition region), where the molecules
-has both the atomistic and coarse-grained resolutions, and the weighting function
-goes smoothly from 1 to 0. The way of designing the weighting function
+
+In most cases discussed in this work, we refer to higher resolution as the classical atomistic model, while
+the lower resolution as the coarse-grained molecular model. However,
+one should keep in mind that the ``atomistic'' and ``coarse-grained'' resolutions
+may refer to more general molecular models, e.g.~the higher resolution can be
+path-integral representation~\cite{poma2010classical}, and lower resolution can be continuous
+hydrodynamic description~\cite{delgado2009coupling}.
+
+In AdResS scheme, the simulation region $\Omega$ is 
+is decomposed without overlapping into 3 regions:
+the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
+a hybrid region $\Omega_\HY$ bridging the former two regions
+That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
+The names of the atomistic and coarse-grained regions are self-explanatory, while
+in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
+The AdResS uses a scalor weighting function $w(\vect r),\ \vect r\in\Omega$ 
+to denote the resolution of the molecule at position $\vect r$.
+% In the atomistic region the value of the
+% weighting function is usually set to 1, while in the coarse-grained
+% region it is usually set to 0. In between, there is a bybrid region
+% that is denoted by $\Omega_\HY$
+% (or called transition region), where the molecules
+% has both the atomistic and coarse-grained resolutions, and the weighting function
+% goes smoothly from 1 to 0.
+The definition of the weighting function
 is not unique, one possible and perhaps the most popular choice is
@@
 at the boundary between the hybrid and the coarse-grained regions.
-Since all interactions (including the electrostatic interction) are treated
+Since all interactions (including the electrostatic interction) in AdResS are treated
 by cut-off method, the weighting function requires the thickness of
@@
 region is not directly interacting with the coarse-grained region,
-so there is no extra work for modeling the interactions between the atomistic
-and coarse-grained resolutions.
-
-Both the atomistic and coarse-grained intermolecular interactions are
-well defined in the atomistic region and coarse-grained regions,
-respectively.  To setup an AdResS simulation, one needs to define the
+so there is no extra work for modeling the cross-scale interactions.
+
+The intermolecular interactions are
+well defined in the atomistic and coarse-grained regions by the corresponding models.
+To setup an AdResS simulation, one only needs to define the
 interactions in the hybrid region. There are in general two
@@
 The force interpolation approach defines the hybrid force between two
-molecules (saying $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
+molecules (indexed by $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
 between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
@@
 both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
-and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$, from the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.
-
-The potential interpolation approach defines the hybrid energy by the same idea:
+and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$.
+From the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.
+
+The potential interpolation approach defines the hybrid energy by
 \begin{align}\label{eqn:v-v-interpol}
-  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo} 
+  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
 \end{align}
@@
 the last term breaks the Newton's third law, therefore the force of potential interpolation
-does not conserves the momentum.
+does not conserve the momentum.
 We define the accumulative effect of this term by the force of changing representation:
@@
 properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}). The choice of the interpolation scheme depends on
-the practical requirement, for example, in some systems it is crucial to have the momentum
-conservation, then the force interpolation is prefered, and vice versa.
+the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
+conservation, then the force interpolation is prefered.
 In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
@@
 \end{align}
-On the force on the atomistic DOFs of a hybrid molecules is distributed 
-by, taking atom $\atomidxone$ on molecule $\moleidxone$ for example,
+The force on the atomistic DOFs of a hybrid molecules is distributed 
+by, 
 \begin{align}
@@
 \end{align}
-where $m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.
-
-Before discussing the statistical and thermodynamic properties of AdResS, a few comments on the
+where  $\atomidxone$ is the indexes of atoms in molecule $\moleidxone$.
+$m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.
+
+Before discussing the statistical and thermodynamic properties of AdResS, a remark on the
 choice of the weighting function should be added. 
-In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function that
-introduce a buffer region so that the molecules with the atomistic resolution
+In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function with
+a buffer region so that the atomistic region
 interacts with the hybrid region via the atomistic intermolecular interaction:
@@
 
-\recheck{Remark, add the remark of inversed weighting function}
+% \recheck{Remark, add the remark of inversed weighting function}
+% \vskip .2cm
+% \noindent\textbf{Remark}: In the case where the high-resolution simulation
+% is extremely expensive, e.g.~the path-integral AdResS~\cite{poma2010classical},
+% the extra cost for simulating with buffer region is therefore not desirable.
+% One possible solution is to assign the value of weighting function in an reversed way:
+% it taks 0 in high-resolution region, while takes 1 in low-resolution region.
+% With the reversed weighting, the buffer region is on the coarse-grained side,
 
@@
 
-To consider the accuracy of the AdResS simulation, we always compare it with a
-atomistic reference system, which is of the same size as the AdResS system, and contains the same number of molecules.
-If the statistal properties of the atomistic region in the AdResS simulation
+In order to consider the accuracy of the AdResS from statistical point of view, we always compare it with a full
+atomistic reference system, which is of the same size as the AdResS system,
+and contains the same number of molecules.
+If the configuration of the atomistic region in the AdResS 
 is same as the corresponding subregion in the atomistic reference, then
-the atomistic region is embeded into the AdResS system as if it were embeded in to
-an atomistic environment, and the AdResS simulation is of good accuracy.
-\recheck{comments on the ``atomistic region'' of the reference system}
+the AdResS  is of good accuracy (see the comparision indicated by the red arrow in Fig.~\ref{fig:compare}).
+A well-known conclusion of the standard statistical mechanics is that
+when the reference system approximate the thermodynamic limit, the subsystem is
+subject to the grand-canonial ensemble. Therefore, it is natural to investigate
+if the atomistic region of AdResS is also subject to the grand-canonial ensemble
+in the same thermodynamic limit. The theoretical framework presented in this section works for
+both the force and potential interpolations.
+
+% the atomistic region is embeded into the AdResS system as if it were embeded in to an atomistic environment,
+% and the AdResS  is of good accuracy (see the red arrow in Fig.~\ref{fig:compare}).
+% Here the corresponding atomistic region in the reference sys
+% \recheck{comments on the ``atomistic region'' of the reference system}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
+  \caption{A schematic plot of the comparision between the AdResS system (left) and the full atomistic reference system (right).}
+  \label{fig:compare}
+\end{figure}
 
@@
 The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
-the desired equilibrium.
+the \emph{desired equilibrium} of AdResS.
 % The word ``desired'' means that
@@
 % system.
-The thermodynamic variables for subregions are specified by the subscript,
+The thermodynamic variables of the subregions are specified by the subscript,
 for example, the those of the atomistic region are 
@@
 the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
-\redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/system.thermo/system.eps}
-  \caption{A schematic plot of the AdResS system in thermodynamic
-    equilibrium. The number of molecules, volume and temperature of
-    the atomistic and coarse-grained regions are denoted by $\{N_\AT,
-    V_\AT, T\}$ and $\{N_\AT, V_\AT, T\}$, respectively. The filter
-    allows free exchange of molecules between atomistic and
-    coarse-grained regions.}
-  \label{fig:system-thermo}
-\end{figure}
-
-We consider the system in the thermodynamic limit: both the atomistic
+It should be noted that for simplicity, we do not explicitly consider the number of DOFs are different for an atomistic
+and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
+% so it is acutally 
+% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.3\textwidth]{figs/system.thermo/system.eps}
+%   \caption{A schematic plot of the AdResS system in thermodynamic
+%     equilibrium. The number of molecules, volume and temperature of
+%     the atomistic and coarse-grained regions are denoted by $\{N_\AT,
+%     V_\AT, T\}$ and $\{N_\AT, V_\AT, T\}$, respectively. The filter
+%     allows free exchange of molecules between atomistic and
+%     coarse-grained regions.}
+%   \label{fig:system-thermo}
+% \end{figure}
+
+The thermodynamic limit is taken in the sense that both the atomistic
 and the coarse-grained regions are infinitely large, and at the same
@@
 region. The hybrid region is much smaller than both the atomistic and
-coarse-grained regions.  Therefore, the number of molecules in the
-three regions satisfies $N_\CG\gg N_\AT\gg N_\HY$.  The coarse-grained
+coarse-grained regions.  Therefore, the volumes of the
+three regions satisfies $V_\CG\gg V_\AT\gg V_\HY$.  The coarse-grained
 region can be treated as an infinitely large particle and energy
@@
 infinitely thin filter that changes molecular resolution when a
-molecule passes by (see Fig.~\ref{fig:system-thermo}). In the
+molecule passes by. In the
 thermodynamic limit, if there were no change of resolution (or
@@
 where $\mu^\ast_\AT$ is the chemical potential of reference system in
-desired equilibrium, $\mathcal Z$ is the partition function
-normalizing the probability density, and $\mh^\AT$ is the atomistic
+the desired equilibrium, $\mathcal Z$ is the partition function
+normalizing the probability density, and $\mh^\AT$ is the \emph{atomistic}
 Hamiltonian defined in the the subregion of the reference system that
@@
 The configurational probability density~\eqref{eqn:dist-1-0} is further splitted as
-\begin{align}
+\begin{align}\label{eqn:conf-split}
   p(\vect x_\AT \vert N_\AT) =
@@
 hybrid DOFs.
-It can shown that if
+It can be shown that if
 (1) all interactions in the system are cut-offed;
@@
 should be noted that the probability density~\eqref{eqn:dist-conf-0}
-is identical to that of the reference system with a subregion that
-corresponds to the hybrid region.
+is identical to that of the reference system.
+% with a subregion that
+% corresponds to the hybrid region.
 The probability density and local Hamiltonian
@@
 
-In general, the probability density $p(\vect x_\HY, N_\HY\vert N_\AT)$
+In general, the second probability density $p(\vect x_\HY, N_\HY\vert N_\AT)$ in Eq.~\eqref{eqn:conf-split} 
 is not the same as the reference system.  For example, it has been
@@
 reporduce the atomistic pressure~\cite{poblete2010coupling}.  However,
-it is possible to raise necessary conditions that systematically
-improves the accuracy of the probability density. The first necessary
+it is possible to raise necessary conditions
+for the AdResS system, with which the accuracy can be improved
+systematically.
+% improve the accuracy of the probability density.
+The first necessary
 condition is that the density profile of the hybrid region should be a
@@
 ask that the hybrid radial distribution function (RDF) should be the
-same as that of the reference system:
+same as that of the reference system (see the green arrow in Fig.~\ref{fig:compare}):
 \begin{align}\label{eqn:necessary-2nd}
@@
 
-In practice, the density in the hybrid region is correct by the
+In practice, the density in the hybrid region is corrected by the
 thermodynamic force~\cite{fritsch2012adaptive}, which is applied on top of the AdResS intermolecular interactions:
-\begin{align}
-  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf,  \\
+\begin{align}\label{eqn:thf-f}
+  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf,  \\\label{eqn:thf-p}
   \vect F^V_\moleidxone& = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V},
@@
 calculated by the following iterative scheme:
-\begin{align}
+\begin{align}\label{eqn:tfi}
   \vect F_{k+1}^{\thf(, V)} (\vect r) = \vect F_k^{\thf(, V)} (\vect r)-
@@
 is updated only in the hybrid region. When the hybrid density is flat, the thermodynamic
-force converges. An important subsequence of a flat hybrid density is that
+force converges. An important consequence is that
 \begin{align}
@@
 
-In a numerical example of SPC/E water~\cite{berendsen1987missing}
+By using a numerical example of SPC/E water~\cite{berendsen1987missing}
 system, it has been shown in Ref.~\cite{wang2013grand} that when the
-thermodynamic force is applied, the AdResS atomistic region reporduces
-mulit-body configurational probability density of the reference system
+thermodynamic force is applied, the AdResS atomistic region reporduces (with satisfory accuracy)
+mulit-body configurational probability densities of the reference system
 upto three-body correlation.
-In principle, higher order of mulit-body correlation can be investigated in
-a similar way. A surprising numerical observation is that although
+% In principle, higher order of mulit-body correlation can be investigated in
+% a similar way.
+A surprising numerical observation is that although
 only the thermodynamic force is applied, the second order necessary condition~\eqref{eqn:necessary-2nd}
@@
 which is calculated by the iterative Boltzmann inversion:
-\begin{align}
+\begin{align}\label{eqn:ibi}
   V_{k+1}^\rdf(r) = V_k^\rdf(r) + k_BT \ln \Big[\frac{g_k(r)}{g^\ast_\AT(r)}\Big] 
@@
 iteration converges. It has been shown that the iterative scheme of
-thermodynamic force coupled with the iterative Boltzmann inversion RDF
+thermodynamic force~\eqref{eqn:tfi} coupled with the iterative Boltzmann inversion~\eqref{eqn:ibi}
 is effective in correcting the density profile $g_\HY(\vect r)$ and
@@
 \end{align}
-The effectiveness of this proposal has never been tested, and is still an open question.
+The effectiveness of this proposal has never been tested, and is still an open problem.
 
@@
 \end{align}
-where $\omega_0$ corresponds to the work from the filter, on each
-molecule that enters the atomistic region. An important conclusion
+where $\omega_0$ corresponds to the work from the filter on each
+molecule that leaves the coarse-grained region and  enters the atomistic region. An important conclusion
 form Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
-holds when the thermodynamic force is applied so that the atomistic
+holds automatically when the thermodynamic force is applied so that the atomistic
 and coarse-grained densities match. The conclusion is derived under
@@
 
-The second order accuracy is achieved if the isothermo-compressibilty of the atomistic and coarse-grained sizes matches:
+The second order accuracy is achieved if the isothermo-compressibilty of the atomistic and coarse-grained resolutions match:
 \begin{align}
@@
 This is achieved by coarse-grained modeling, for example, the
-structure based coarse-grained models that reproduces the atomistic
+structure based coarse-grained models that reproduce the atomistic
 RDF~\cite{wang2009comparative}.
@@
 
-From the accuracy analysis one surprising fact is that if the
-requirement for the accuracy is not very high, and only applying the
-thermodynamic force is acceptable, then there is actually no
+From the analysis on statistical mechanics one surprising fact is that if the
+requirement for the accuracy is not very high (only applying the
+thermodynamic force is acceptable), then there is actually no
 restriction on the coarse-grained model. One can even use ideal gas as
-a coarse-grained model, but the computational difficulty lies in the
-sudden switching on of the atomistic interaction when a coarse-grained
-molecule enters the hybrid region. If two molecules are entering at
+a coarse-grained model.  The computational difficulty lies in the
+sudden switching on of the atomistic interactions when a coarse-grained
+molecule enters the hybrid region. If two molecules enters at
 the same time and the same location, then the atomistic contribution
-to the intermolecular interaction~\eqref{eqn:f-f-interpol} or
-\eqref{eqn:f-v-interpol} is infinity, which drives the simulation
+to the intermolecular interaction
+% ~\eqref{eqn:f-f-interpol} or
+% \eqref{eqn:f-v-interpol}
+is infinity, which drives the simulation
 unstable. This numerical difficulty can be avoided by using capped
@@
 coarse-grained model, which is a short-ranged and pure repulsive
-interaction.  For a SPC/E water system, the cut-off radius of WCA potential
+interaction.  For an SPC/E water system, the cut-off radius of WCA potential
 can be 2.4 time smaller than the cut-off used in the atomistic
-region. Since the computational cost with is of order $\mo(r_c^3)$,
-the computational cost spent on each pair interaction
-is 19 times cheaper. For each pair of molecules the atomistic model computes
+region. Since the computational cost of cut-off scheme is of order $\mo(r_c^3)$,
+the pair interaction of WCA
+is 19 times cheaper. Moreover, for each pair of molecules the atomistic model computes
 10 pairwise interactions (9 electrostatic + 1 van der Waals), while the
-WCA model computes only one, therefore the WCA model in total costs $1/190$ 
-computational effort on force computation than atomistic model.
+WCA model computes only one. Therefore the WCA model in total costs only $1/190$ 
+on force computation than atomistic model.
 The WCA approach has been successfully used in calculating the
@@
 
-In the reference system, if the equilibrium state is achieved, then
-the temperature, pressure and chemical potential of the atomistic and
-coarse-grained subregions match. In AdResS system, the global uniform
-temperture distrubution in equilibrium is impoosed by the Langevin
+In the reference system (full atomistic), if the equilibrium state is achieved, then
+the temperature, pressure and chemical potential of different regions are identical.
+In AdResS system, the global uniform
+temperture distrubution in equilibrium is equilibriated by the Langevin
 thermostat.  However, extra term appear in the pressure or chemical
-potential relation when the momentum or energy conservation is absent
+potential relations when the momentum or energy conservation is absent
 (see Tab.~\ref{tab:conv-laws}), respectively.
@@
 The chemical potential balance can be investigated from the fact that
-when the uniform density distribution is guaranteed by thermodynamic force in equilibrium, the chemical potential
+when the uniform density distribution is guaranteed, the chemical potential
 difference between the resolutions is compensited by $\omega_0$, which
@@
 force plus the extra kinetic energy corresponding to the extra DOFs
-when a molecule obtains higher resolution:
+that a molecule obtains in higher resolution region:
 \begin{align}\label{eqn:mu0-v}
@@
 This work is path independent if the thermodynamic force is defined as a function of the distance to the atomistic region, and applies along the gradient of the weighting function.
-We always assume the thermodynamic force satisfies these conditions.
+We always use the thermodynamic force that satisfies these conditions.
 For the force interpolation, 
@@
 where $\omega^{\thf}$ is the work of the thermodynamic force of force interpolation.
-The magnitude of the extra term $\omega^\exc$ is unclear up to now,
-however, it is easy to computewith the help of the pressure relations.
+The magnitude of the extra term $\omega^\exc$ is unclear up to now.
+% however, it is easy to computewith the help of the pressure relations.
 
@@
 region. Following this idea, Ref.~\cite{agarwal2014chemical} proves that in
-equilibrium the pressure between the resolutions is related by
+equilibrium the pressure is related by
 \begin{align}\label{eqn:p-eq-v}
@@
 Since the force of changing representation acts always along the gradient of the weighting
-function, therefore, if the system is homogeneous in the hybrid region, then the integral
+function, therefore, if the system is homogeneous in the hybrid region, then the integral~\eqref{eqn:work-rep}
 is path independent. The ensemble average  can be estimated by sampling.
@@
 \end{align}
-which gives a explicit expression for the extra energy contribution
-due to the absence of energy conservation in the force
-interpolation. It should be noted that the ensemble averge in the work
+% which gives a explicit expression for the extra energy contribution
+% due to the absence of energy conservation in the force
+% interpolation.
+It should be noted that the ensemble averge in the work
 of changing representation~\eqref{eqn:work-rep} is defined for the
@@
 hybrid region of the potential and force interpolation have the same
-density. In Ref.~\cite{wang2013grand} an even strong conclusion is shown numerically in the SPC/E water system: The
+density. In Ref.~\cite{wang2013grand} an even stronger conclusion is shown numerically in the SPC/E water system: The
 averge force of changing representation estimated from potential
@@
 
-\recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
-}
-
-\subsection{Velocity and dipole auto-correlation of water}
+\subsection{Velocity auto-correlation of water}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{local-thermostat/fig-vac.eps}
+  \caption{The oxygen velocity auto-correlation by atomistic
+    simulation compared with AdResS simulation.  The solid cyan and
+    red lines compares the atomistic simulation with and without
+    Langevin thermostat, respectively.  The square and cross points
+    present the potential and force interpolation AdResS with local
+    thermostat, respectively.  The time-scales of the global- and local- Langevin
+  thermostat are both $\tau_T = 0.1$~ps.}
+  \label{fig:vac}
+\end{figure}
+
+In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
+in sampling the equilibrium ensemble. Therefore, all quantities that
+can be written down in terms of ensemble averages should have good
+when using AdResS. However, not all quantities are in the form
+of ensemble averages, for example, the velocity auto-correlation function
+(in the normalized form):
+\begin{align}
+  C_v(t) = \frac{\langle \vect v(0)\cdot \vect v(t) \rangle}{\langle \vect v(0)\cdot \vect v(0) \rangle}
+\end{align}
+where the averages $\langle\cdot\rangle$ are still taken with respect
+to the equilibrium ensemble, and the term
+$\langle \vect v(0)\cdot \vect v(t)\rangle$ computes the correlation
+between the velocity at time $0$ and $t$.  In the context of molecular
+dynamics simulation, these quantities does depends on how the dynamics
+of the system is implemented, so they are called dynamical properties
+of the system.  An illustrative example, presented in
+Fig.~\ref{fig:vac}, is computing the oxygen velocity auto-correlation
+in a TIP3P~\cite{jorgensen1983comparison} water system: If the system
+is coupled to a Langevin thermostat, the result is quanlitatively
+differed from that without any thermostat coupling, i.e.~Hamiltonian
+dynamics. Although by using milder thermostats (increased time-scales)
+will improve the result, it is in general difficult to know \emph{a priori}
+the strength of the thermostat.
+The standard AdResS simulations, since the Langevin thermostat
+is coupled,  is thus not suitable to reproduce the dynamical
+quantities of the system.
+
+The solution is to adopt the local-thermostat method that was initially
+developed for non-equilibrium MD simulations~\cite{wang2014exploring}.
+The idea is to leave the atomistic region uncoupled to any thermostat, so the dynamics 
+is preserved as Hamiltonian dynamics.
+The region without thermostating is called the dynamics region. In this case the dynamical region
+is identical to the atomistic region.
+In the meanwhile, the hybrid and
+coarse-grained regions, which are serving as particle and energy reservior, are coupled to Langevin thermostat in order to keep the system
+at the desired  thermodynamic state. In this context, the dynamical quantities
+should be measured only in the atomistic region.
+
+The local thermostat is validated by an AdResS simulation of pure TIP3P
+water system.
+The simulation is performed by the Gromacs~\cite{pronk2013gromacs} version 4.6.5 with AdResS support.
+The system contains 5000 water molecules.  The dimension of the simulation region is $14.7\times3.2\times3.2~\textrm{nm}^3$,
+in which the resolution changes only on $x$-direction.
+The atomistic region is of size $1.5\times3.2\times3.2~\textrm{nm}^3$, and governed by Hamiltonian dynamics.
+The rest of the system (hybrid + coarse-grained
+regions) is coupled to Langevin thermostat of time-scale 
+$\tau_T = 0.1$~ps.
+The WCA potential
+% with parameter $\sigma = 0.3~$nm and $\epsilon = 0.65$~kJ/mol
+is adopted as generic coarse-grained water,
+and the weighting function of form Eq.~\eqref{eqn:new-w} is used to couple different resolutions with
+two hybrid regions of width $d_{\HY} = 2.85$~nm.
+The thermodynamic forces of force and potential interpolations are iteratively computed by
+Eq.~\eqref{eqn:thf-f} and \eqref{eqn:thf-p}, respectively.
+The electrocstatic interaction is treated by the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized},
+with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$, which conserves the energy, and
+is proved to be a special case of the more
+accurate Zero-multiple method~\cite{fukuda2011molecular,fukuda2013zero}.
+The cut-off radius is 1.2~nm, and the van der Waals interaction is smoothed by the ``\texttt{switch}'' method provided by
+Gromacs.
+
+The Fig.~\ref{fig:vac} presents the velocity auto-correlation
+functions computed by fully equilibriated of length 1~ns, with the
+velocities recored every 0.04~ps.  Here full equilibriation means
+uniform temperature and density distributions in the system.
+In the Figure, both the force and potential interpolations are presented along with the
+atomistic simulation, and show almost perfect consistency.
+This indicates that the AdResS with the local thermostat
+is a promising method to investigate the dynamics quantities
+in the concurrent multiscale simulation.
+
+% In the next subsection, we investigate the accuracy AdResS reprduces not only
+% the equilibrium, but also the dynamical properties of a model
+% poly-peptide system: Alanine dipeptide dissolved in water.
+
+% \recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
+% }
 
@@
     is for full atomistic reference simulation, while (c) is for
-    AdResS simulation. The metastable conformations coded by $\confa$, $\confb$, $\confc$ and $\confd$
+    AdResS. The metastable conformations coded by $\confa$, $\confb$, $\confc$ and $\confd$
     are noted on plot (b).}
@@
 biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
+We investiage a system composed of
+7235 TIP3P water molecules, and
+one alanine dipeptide described by the CHARMM27 force field~\cite{foloppe2000all} with
+grid-based energy correction map (CMAP)~\cite{mackerell2004extending}. 
+The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
+a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a hybrid shell-shaped region of width 2.0~nm.
+The rest of the system is treated coarse-grainly by the WCA potential.
+The dynamical region (no thermostating region) is
+also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
+It has been proved that the conformational dynamics of alanine dipeptide is not sensitive to the size of
+the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
+In this case, part of the hybrid region is not thermostated, so
+when using force interpolation, the extra energy production might not be effectively equilibriated.
+To this end, we only investiage the potential interpolation. The corresponding
+thermodynamic force is iteratively computed by
+Eq.~\eqref{eqn:thf-p}.
+The electrocstatic interaction is computed by the Reaction-Field with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
+Both the electrocstatic and the van der Waals intercations (smoothed by ``\texttt{switch}'' method in Gromacs)
+are cut-offed at 1.0~nm.
+
 The system presents a very clear timescale seperation: There are fast
-motions like bond and angle vibration that happens in tens of femtoseconds, while
-there are slow conformational transformations that happens in hundreds of picoseconds.
+motions like bond and angle vibrations that happen in tens of femtoseconds, while
+there are slow conformational transformations that happen in hundreds of picoseconds.
 The dihedral angles $\phi$ and $\psi$ (see
-Fig.~\ref{fig:ala}~(a)) are usually chosen as slow variables that  describles
-the molecular conformation and its transitions of the moelcules, which are of
-general biological interest.
+Fig.~\ref{fig:ala}~(a)) are usually chosen as collective variables that  describe
+the molecular conformation and its transitions.
 
@@
 identified as transition regions.
-The AdResS free energy is in good
+The AdResS free energy (Fig.~\ref{fig:ala}~(c)) is in good
 consistency with the full atomistic reference system, and
@@
 In pratice, not only the equilibrium properties like the free energy are of interest,
-but also the dynamical properties like the conformational transitions and the corresponding timescales
+but also the dynamical properties like the conformational transitions and the corresponding relaxation timescales
 are of highly biological importance.
@@
 Markov process.
-The accuracy analysis regarding  this approximation is well-founded~\cite{sarich2010approximation,djurdjevac2012estimating}.
+The accuracy analysis regarding  this approximation is well-established~\cite{sarich2010approximation,djurdjevac2012estimating}.
 The MSM has found successfully applications in various fileds, for example studying complex protein systems
@@
 
-In a standard MSM approach, the full phase space is firstly deomposed in to a union of finite number of states
+In a standard MSM approach, the full phase space is firstly deomposed into a non-overlapping union of finite number of states
 (not necessarily identical to the metastable conformations),
@@
 % The ``$\cdot$'' denotes the matrix-vector multiplication.
-In equilibrium, the transition matrix is time-homogeneous, i.e.~$\vect T(\tau)$ does not depend on time $t$.
+In equilibrium, the transition matrix~$\vect T(\tau)$ does not depend on time when the state $i$ is investigated, and only the
+lag-time $\tau$ matters.
 % Due to the Markovianity, for any $k$, we have
 % $p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t (\vect x)$.
-If the transition matrix is irreducible and aperiodic, than according to Perron-Frobenius theorem, the maximum
-eigenvalue is reached and single. Due to the stochaticity of the matrix, the maximal eigenvalue is equal to 1.
+If the transition matrix is irreducible and aperiodic, then according to Perron-Frobenius theorem, the maximum
+eigenvalue is reached and single. Due to the stochaticity of the matrix, this eigenvalue is equal to 1.
 If the dynamics
-is further assumed to be reversible, then all eigenvalues of the transition are
+is further assumed to be reversible, then all eigenvalues of the transition matrix are
 real valued.
@@
 equilibrium probability density.
-At inifinitely long time, the probability density $p_{k\tau}$ converges to the equilibrium probability.
+At inifinitely long time, the probability density $\vect p_{k\tau}$ converges to the equilibrium probability.
 The speed of the convergence is characterized by the non-trivial leading timescales that are
@@
     The first row presents the eigenvectors of the full atomistic reference, while the second
-    row presents those of the AdResS simulation. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
+    row presents those of the AdResS. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
     timescales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
@@
 Each bin presents a state in MSM, and the transition matrix is sampled by equilibrium
-MD simulations with the local thermostating scheme.
-The MSM and the leading eigen properties are built and analyzed by the software EMMA~\cite{senne2012emma}.
+MD simulations with the local thermostating scheme~\cite{wang2014exploring}.
+The MSM is built and analyzed by the software EMMA~\cite{senne2012emma}.
 The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference in
 Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
-eigenvalues should be $\tau$ independent if the MSM is of good
+eigenvalues should be $\tau$ independent for sufficiently large $\tau$ if the MSM is of good
 accuracy, and from Fig.~\ref{fig:ala-msm-t} they are so for $\tau \geq 20$~ps.
 Also from the Fig.~\ref{fig:ala-msm-t}, the full atomistic
-reference and the AdResS result are consistent within the statistical
+reference and the AdResS eigenvalues are consistent within the statistical
 uncertainty.
@@
 corresponding eigenvectors are not the equilibrium properties, because
-the transition probability (elements of the transition matrix) are actually
-time-correlation functions of the characteristic functions, which are called dynamical properties in
-this context. A good reproduction of the equilibrium properties does
-not necessary implies a reproduction of the dynamical properties.
+the transition probabilities (elements of the transition matrix) are actually
+auto-correlation functions of the characteristic functions that are not equilibrium ensemble averages.
+A good reproduction of the equilibrium probability density does
+not necessary implies a reproduction of the auto-correlation functions.
 Although currently there is still no theoretical answer why AdResS works,
@@
 
-\section{Open problems of the adaptive resolution simulation}
+\section{Concluding remarks and open problems}
 \label{sec:conclusion}

### 2014-11-11 writeDown/pub.epj/paper.tex
finishing the conclusions

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{figs/system.alanine/system-region-1.eps}
+  \caption{A schematic plot of an AdResS simulation.
+In side the red circle is the atomistic region.
+Between the red and blue circles is the hybrid region.
+Outside the blue circle is the coarse-grained region.}
+  \label{fig:sys-region}
+\end{figure}
+
 In AdResS scheme, the simulation region $\Omega$ is 
@@
 the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
-a hybrid region $\Omega_\HY$ bridging the former two regions
+a hybrid region $\Omega_\HY$ bridging the former two regions.
 That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
@@
 in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
+A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
 The AdResS uses a scalor weighting function $w(\vect r),\ \vect r\in\Omega$ 
@@
 
+% In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
+% in sampling the equilibrium ensemble.
+In principle, all quantities that
+can be written down in terms of equilibrium ensemble averages should
+be computed with high accuracy accuracy when using an AdResS simulation that approximately samples the grand-canonial ensemble.
+However, under this framework one has little knowledge regarding the quantities
+that are not ensemble averages.
+For example, the non-equilibrium response of the system
+with respect to an external perturbation, which is 
+either computed by brute force non-equilibrium simulations~\cite{wang2014exploring}, or by
+equilibrium time-correlation function via the Green-Kubo
+relation~\cite{green1954markoff,kubo1957statistical} if the perturbation is small. The
+time-correlation function, although measured in equilibrium
+simulations, depends on how the dynamics
+of the system is implemented.
+The quantities of this type are called \emph{dynamical properties} of the system.
+In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
+however, due to the trunction error in computer simulations, it
+is technically difficult to conserve the energy in very long MD simulations.
+To this end thermostats are sometime coupled to keep the system at desired thermodynamic
+state.
+It worth noting that the thermostats are designed to bring the system to equilibrium distributions, and 
+disturb the Hamiltonian dynamics in an artificial way.
+Therefore, when applying the thermostats
+in computing the dynamical properties, the potential artifacts
+should be check carefully.
+In the context of AdResS, we propose an alternative way of thermostating
+the system, the local thermostat method~\cite{wang2014exploring},
+which is proved to be free of the artifacts in computing the dynamical properties in the following sections.
+
+% \footnote{In principle, 
+%   whether the dynamical properties are disturbed by the thermostat should
+%   be checked systematically with respect to the coupling parameters.}.
+% Therefore, in the context of molecular dynamics simulation,
+
 \subsection{Velocity auto-correlation of water}
@@
     red lines compares the atomistic simulation with and without
-    Langevin thermostat, respectively.  The square and cross points
+    Langevin thermostat, respectively.
+    In the simulation of Hamiltonian dynamics, the energy drift is only 0.01\%.
+    The square and cross points
     present the potential and force interpolation AdResS with local
@@
 
-In Sec.~\ref{sec:statistical}, we investigated the accuracy of AdResS
-in sampling the equilibrium ensemble. Therefore, all quantities that
-can be written down in terms of ensemble averages should have good
-when using AdResS. However, not all quantities are in the form
-of ensemble averages, for example, the velocity auto-correlation function
-(in the normalized form):
+In this section we take the normalized velocity auto-correlation function
+for example:
 \begin{align}
@@
 $\langle \vect v(0)\cdot \vect v(t)\rangle$ computes the correlation
-between the velocity at time $0$ and $t$.  In the context of molecular
-dynamics simulation, these quantities does depends on how the dynamics
-of the system is implemented, so they are called dynamical properties
-of the system.  An illustrative example, presented in
-Fig.~\ref{fig:vac}, is computing the oxygen velocity auto-correlation
-in a TIP3P~\cite{jorgensen1983comparison} water system: If the system
-is coupled to a Langevin thermostat, the result is quanlitatively
-differed from that without any thermostat coupling, i.e.~Hamiltonian
+between the velocity at time $0$ and $t$. 
+An illustrative example of the thermostating artifact is 
+the oxygen velocity auto-correlation
+in a TIP3P~\cite{jorgensen1983comparison} water system presented in Fig.~\ref{fig:vac}: If the system
+is coupled to a Langevin thermostat, the result is qualitatively
+different from that without any thermostat coupling, i.e.~Hamiltonian
 dynamics. Although by using milder thermostats (increased time-scales)
 will improve the result, it is in general difficult to know \emph{a priori}
-the strength of the thermostat.
+the strength of the thermostat coupling.
 The standard AdResS simulations, since the Langevin thermostat
-is coupled,  is thus not suitable to reproduce the dynamical
-quantities of the system.
+is globally coupled to the system,  is not suitable to reproduce the dynamical
+properties of the system.
 
@@
 developed for non-equilibrium MD simulations~\cite{wang2014exploring}.
-The idea is to leave the atomistic region uncoupled to any thermostat, so the dynamics 
-is preserved as Hamiltonian dynamics.
-The region without thermostating is called the dynamics region. In this case the dynamical region
-is identical to the atomistic region.
-In the meanwhile, the hybrid and
-coarse-grained regions, which are serving as particle and energy reservior, are coupled to Langevin thermostat in order to keep the system
-at the desired  thermodynamic state. In this context, the dynamical quantities
-should be measured only in the atomistic region.
-
-The local thermostat is validated by an AdResS simulation of pure TIP3P
+This method divide the system in to two regions.
+The dynamical region of out of which the dynamical properties are calculated is not coupled
+to any thermostat, so the dynamics there is preserved as Hamiltonian dynamics.
+The thermostated region is coupled to Langevin thermostat in order to keep the system
+at the desired thermodynamic state.
+In the context of AdResS, we let the dynamical region identical to the atomistic region,
+and
+the hybrid and coarse-grained regions, which serve as particle and energy reservior, coupled to thermostat.
+% The idea is to leave the atomistic region uncoupled to any thermostat, so the dynamics 
+% is preserved as Hamiltonian dynamics.
+% The region without thermostating is called the dynamics region. In this case the dynamical region
+% is identical to the atomistic region.
+% In the meanwhile, the hybrid and
+% coarse-grained regions, which are serving as particle and energy reservior, are coupled to Langevin thermostat in order to keep the system
+% at the desired  thermodynamic state. In this AdResS simulation, the dynamical properties
+% should be measured only in the atomistic region.
+
+This local thermostat method is validated by an AdResS simulation of pure TIP3P
 water system.
-The simulation is performed by the Gromacs~\cite{pronk2013gromacs} version 4.6.5 with AdResS support.
-The system contains 5000 water molecules.  The dimension of the simulation region is $14.7\times3.2\times3.2~\textrm{nm}^3$,
+The simulation is performed by the Gromacs~\cite{pronk2013gromacs} version 4.6.5.
+The system contains 5000 water molecules.  The dimension of the periodic
+simulation region is $14.7\times3.2\times3.2~\textrm{nm}^3$,
 in which the resolution changes only on $x$-direction.
-The atomistic region is of size $1.5\times3.2\times3.2~\textrm{nm}^3$, and governed by Hamiltonian dynamics.
-The rest of the system (hybrid + coarse-grained
-regions) is coupled to Langevin thermostat of time-scale 
-$\tau_T = 0.1$~ps.
-The WCA potential
-% with parameter $\sigma = 0.3~$nm and $\epsilon = 0.65$~kJ/mol
-is adopted as generic coarse-grained water,
-and the weighting function of form Eq.~\eqref{eqn:new-w} is used to couple different resolutions with
-two hybrid regions of width $d_{\HY} = 2.85$~nm.
+The atomistic region is of size $1.5\times3.2\times3.2~\textrm{nm}^3$, and the width of the hybrid region is $d_{\HY} = 2.85$~nm.
+The rest of the system is coarse-grained region modeled by the WCA interaction.
+The weighting function of form Eq.~\eqref{eqn:new-w} is used to couple different resolutions.
+The Langevin thermostat coupled to the hybrid and coarse-grained regions is of time-scale $\tau_T = 0.1$~ps.
 The thermodynamic forces of force and potential interpolations are iteratively computed by
@@
 The Fig.~\ref{fig:vac} presents the velocity auto-correlation
-functions computed by fully equilibriated of length 1~ns, with the
+functions computed by fully equilibriated MD trajectories of length 1~ns, with the
 velocities recored every 0.04~ps.  Here full equilibriation means
@@
 In the Figure, both the force and potential interpolations are presented along with the
-atomistic simulation, and show almost perfect consistency.
+NVE atomistic simulation, and show almost perfect consistency.
 This indicates that the AdResS with the local thermostat
-is a promising method to investigate the dynamics quantities
+is a promising method to investigate the dynamical properties
 in the concurrent multiscale simulation.
@@
 The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
-a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a hybrid shell-shaped region of width 2.0~nm.
-The rest of the system is treated coarse-grainly by the WCA potential.
-The dynamical region (no thermostating region) is
+a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
+The rest of the system is treated coarse-grainly by the WCA interpolation.
+The dynamical region  is
 also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
@@
 the original time-dependent probability density define on the phase
-space ($p_t(\vect x)$) is approximated by a temporal discrete $\vect p_{k\tau}$ probability defined on the finite-state space.
+space ($p_t(\vect x)$) is approximated by a temporal discrete probability $\vect p_{k\tau}$ defined on the finite-state space.
 The step of the temporal discretization $\tau$ is called the lag-time.
 The reduced
-dynamics is always assumed to be Markovian,
-although uaually it is not,  and in practice it becomes one of the main sources of the error.
+dynamics is assumed to be Markovian,
+although uaually it is not (or not perfectly Markovian),  and in practice it becomes one of the main sources of the error.
+We will not discuss the accuracy issue of the MSM in this paper,
+because it is not very relavant to the performance of the AdResS method.
 % It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
 % Due to the Markovianity of the reduced dynamics, the
-Under this assumption, the original continuous dynamics is approximated by the Markov processes governed by
+Under the assumption of Markovianity, the original continuous dynamics is approximated by the Markov processes governed by
 % probability at time $k\tau$ is given by
@@
 where $\vect T(\tau)$ is the transition maxtix that
-associates to the reduced dynamics. The matrix element, for example $T_{ij}$
+associates to the reduced dynamics of $\vect p^\top_{k\tau}$. The matrix element, for example $T_{ij}$
 is defined as the probability of the system being in state
@@
 The leading eigenvector is non-negative, and satisfies $\Phi^\top_1 = \Phi^\top_1\cdot\vect T(\tau)$.
-With proper normalization the leanding eigenvector is identical to the 
+With proper normalization (integrate to 1) the leanding eigenvector is identical to the 
 equilibrium probability density.
 At inifinitely long time, the probability density $\vect p_{k\tau}$ converges to the equilibrium probability.
-The speed of the convergence is characterized by the non-trivial leading timescales that are
+The speed of the convergence is characterized by the leading relaxation timescales that are
 determined by the leading eigenvalues:  $t_i  = -{\tau}/{\log\lambda_i}, \ i=2, \cdots, m$.
-Since the eigenvectors are orthorgonal and the first eigenvectors is non-negative, the reset
+Since the eigenvectors are orthorgonal and the first eigenvector is non-negative, the reset
 of the eigenvectors have a vanished sum over all elements: Their
@@
 The MSM is built and analyzed by the software EMMA~\cite{senne2012emma}.
-The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference in
+The resulting eigenvalues and eigenvectors of AdResS are compared with the full atomistic reference under the same local thermostat in
 Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
@@
 uncertainty.
-From Fig.~\ref{fig:ala-msm-v}, the conformational transitions corrsponds
+From Fig.~\ref{fig:ala-msm-v}, the conformational transitions corrspond
 to $t_2$, $t_3$ and $t_4$ are $\{\confa \} \leftrightarrow \{\confc,\confd\}$,
@@
 those of the full atomistic reference. Although calculated from the
-equilibrium MD simulations, the leading timescales and the
+equilibrium MD simulations, it sould be noted that the leading timescales and the
 corresponding eigenvectors are not the equilibrium properties, because
@@
 auto-correlation functions of the characteristic functions that are not equilibrium ensemble averages.
-A good reproduction of the equilibrium probability density does
-not necessary implies a reproduction of the auto-correlation functions.
-Although currently there is still no theoretical answer why AdResS works,
-the provided numercial example suggests that AdResS being promising in the applications beyond equilibrium,
-and  worth further theoretical studies.
-
-\section{Concluding remarks and open problems}
+
+% A good reproduction of the equilibrium probability density does
+% not necessary implies a reproduction of the auto-correlation functions.
+% Although currently there is still no theoretical answer why AdResS works,
+% the provided numercial example suggests that AdResS being promising in the applications beyond equilibrium,
+% and  worth further theoretical studies.
+
+\section{Concluding remarks and open questions}
 \label{sec:conclusion}
+
+In this paper, we investigated both the potential and force
+interpolation under a uniform theoretical framework of GC-AdResS. The
+necessary conditions for the grand-canonical like equilibrium
+simulation are provided. However, it sould be noticed that these
+conditions are not sufficient, and the very-high accuracy in the  numerical simulations indicate
+that these conditions tend to be too ``strong''.  Take the AdResS
+water simulation for example, when only the thermodynamic force is
+applied to impose the first necessary condition (density consistency),
+the configuration of the atomistic region is almost identical to the
+full atomistic reference up to the three-body
+correlation\footnote{
+  The three-body correlation is the highest order correlation function that we could reach.
+  The four-body correlation is out of the capability of numerical
+investigation, so it was not studied.}, and the second necessary condition (RDF consistency)
+is automatically fulfilled.  If the necessary conditions were not
+sufficient, it might also be possible that the errors in the numercial simulations are too
+small to be observed.  In this context, it would be helpful
+to provide error estimates on the ensemble  sampled by AdResS with respect to the full atomistic
+grand-canonical ensemble.
+To the knowledge of the authors,
+neither the sufficient condition nor the error estimate has ever been investigated.
+
+If one were able to answer the questions regarding the accuracy of the equilibrium
+ensemble of AdResS, the accuracy of quantities that are equilibrium ensemble
+averages would be automatically answered. However, the dynamical properties, which are
+not equilibrium ensemble averages, are out of the scope of the current
+theoretical framework. In order to numerically check the accuracy of AdResS
+in computing the dynamical properties, we investigated the velocity auto-correlation
+function of pure water and the leading relaxation time-scales of alanine dipeptide
+dissoved in water.
+The vanishing time-scale of the time-correlations ranges from 1~ps in the case of velocity auto-correlation
+to almost 600~ps in the case of conformational relaxation of alanine dipeptide.
+In both systems the AdResS reproduces the atomistic result
+with a satisfactory agreement.
+Although these positive numerically evidences cannot answer the open questions
+on the reason behind the high accuracy or the error estimates of the dynamical properties,
+they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
+and suggests a direction of theoretical investigations.
+
+% These numerical result cannot answer the question
+% of the theoretical reason behind the high accuracy, however,
+
+Currently the AdResS method has only been applied to model systems and small scale
+applications. The advantage in the efficiency is not very obvious.
+One important reason that prevents the AdResS method from
+large scale applications is the software implementation~\cite{agarwal2014chemical}.
+The software we used in the simulations is Gromacs\footnote{Verions higher than 4.6 support
+AdResS}.
+Currently the force computation kernel for the hybrid region is written in C language~\cite{kernighan1988c}.
+Comparing to the highly optimized assembly force computation kernels in Gromacs,
+the AdResS kernel is not competitive. Moreover, the current AdResS implementation
+keeps double resolution everywhere in the system\footnote{In the coarse-grained region,
+  the atomistic DOFs are not used in the force computations, but they are kept and updated
+  in every numerical integration step.
+}.
+Since in the coarse-grained region the force computation is very cheap, majority
+of the computational cost is actually spent on keeping and integrating the atomistic DOFs.
+On straightforward solution is the remove the atomistic DOFs in the coarse-grained
+region, which was actually proposed by the very original paper of AdResS~\cite{praprotnik2005adaptive}.
+Owing to the fact that the coarse-grained interactions are usually ``softer''
+than the atomistic interactions, one way of futher boost the performance is
+to integrate the coarse-grained molecules with larger time-steps.
+If possible, the theoretical analyses on the
+consistency and the corresponding
+error estimates should be developed along the application this adaptive time-step idea.
+All these technical difficulties would hopfully be solved in the near futher.
 

### 2014-11-12 writeDown/pub.epj/paper.tex
add abstract

@@
 %
-\abstract{
-Insert your abstract here.
+\abstract{ In this paper, we discuss the necessary conditions for
+  accurate adaptive resolution simulation (AdResS) in equilibrium.
+  The statistical and thermodynamical properties of two AdResS
+  branches, i.e.~the force and the potential interpolations, are
+  discussed and compared in parallel.  We further demonstrate the
+  accuracy of AdResS in computing dynamical properties, which are not
+  equilibrium ensemble averages, by the velocity auto-correlation of pure water
+  and conformational relaxation of alanine dipeptide dissolved in water.
+  Open questions are discussed in the end of the paper.
 } %end of abstract

### 2014-11-13 writeDown/pub.epj/paper.tex
go through again, new abstract

--- 2014-11-11 writeDown/pub.epj/paper.tex
@@
 %
-\abstract{
-Insert your abstract here.
+\abstract{ In this paper,
+  we investigate the equilibrium statistical properties of both the force and potential interpolations of
+  adaptive resolution simulation (AdResS) under the theoretical framework of
+  grand-canonical like AdResS (GC-AdResS).
+  The thermodynamic relations between the higher and lower resolutions are
+  derived by considering the absence of fundamental conservation laws in mechanics for both branches of AdResS.
+  % we discuss the necessary conditions for
+  % accurate adaptive resolution simulation (AdResS) in equilibrium.
+  % The statistical and thermodynamical properties of two AdResS
+  % branches, i.e.~the force and the potential interpolations, are
+  % discussed and compared in parallel.
+  In order to investigate the applicability of AdResS method in studying the properties
+  beyond the equilibrium, we demonstrate the accuracy of AdResS in computing the dynamical properties in
+  two numerical examples: The velocity auto-correlation of pure water
+  and the conformational relaxation of alanine dipeptide dissolved in water.
+  Theoretical and technical open questions of the AdResS method are discussed in the end of the paper.
 } %end of abstract
@@
 simulated with lower resolution models for the purpose of saving computational cost.
-The AdResS is, therefore, suitable for the systems that different physcial
+The AdResS is, therefore, suitable for the systems that different physical
 phenomena happen concurrently at different time and length scales. For example,
@@
 should be resolved at the atomistic level, while far away form the protein,
-the only the hydrodynamic properties are of interest, which can be studied with satisfactory
-accuracy with very coarse-grained or even continum
+the only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
+accuracy with very coarse-grained or even continuum
 models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
 Similar  
-techniques sharing the ``concurrent'' idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.
+techniques sharing the concurrent idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.
 
@@
 is modeled with Newtonian dynamics, and fundamental conservation laws
-are satisfied, i.e.~the momentum and energy conservations.
+are satisfied, i.e.~the momentum and energy conservation.
 However, in the AdResS system,
@@
 alternative approaches based on \emph{potential interpolation},
-which preserve energy conservation while break momentum conservation,
+which preserve energy conservation while break the momentum conservation,
 were designed~\cite{wang2013grand,potestio2013hamiltonian}.
 The choice between the two AdResS branches therefore depends on the application. For example, in the
-cases of studying hydrodynamic the momentum conservation is prefered to the energy conservation.
+cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
 However, if only the equilibrium properties are of interest,
@@
 In this context,
-it worth noting that the energy conservation is not a must for theoretical analysis on the equilibrium statistical properties,
+it worth noting that the energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
 although out of the energy conservation
@@
 (not a physical one~\cite{dellesite2013multiscale}),
-which reduces the mathematical difficulties of the theoretical analysis.
+which reduces the mathematical difficulties.
 In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
-under the same theoretical framework (GC-AdResS)~\cite{wang2013grand} that raises necessary conditions
+under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
 for a grand-canonical sampling with AdResS scheme.
 In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
-provided for both branches of the AdResS scheme.
-From these relations, it is noticed that the abscence of mechanical conservation laws 
+provided for both branches of the AdResS.
+From these relations, it is noticed that the absence of mechanical conservation laws 
 modifies the way of thermodynamic equilibrium between the resolutions.
@@
 However, although the system is in equilibrium,
-some properties, which are called dynamical properties, cannot be simply computed from the equilibrium averages.
+some properties, which are called dynamical properties, cannot be simply computed from the equilibrium ensemble averages.
 % These properties are called dynamical properties.
@@
 % to external perturbation.
-Moreoever, the time-scales of conformational transformations
+Moreover, the time-scales of conformational transformations
 of bio-macromolecules (e.g.~protein and DNA)
@@
 The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
-and to the best of our knowledge, there is no theoretical answers on how accurately does AdResS reproduce
+and to the best of our knowledge, there is no theoretical answers on how accurately  AdResS reproduces the 
 dynamical properties of a system.
@@
 velocity auto-correlation in an AdResS water system, and the
-leading time-scales and corresponding conformational dynamics of
+leading relaxation time-scales and corresponding conformational dynamics of
 a model dipeptide system.
@@
 is also discussed.
-The paper is closed by a concluding section~\ref{sec:conclusion}
+The paper is closed by a concluding section
 that mainly discusses the opening problems in AdResS from both theoretical
-and practical point of view.
-
-\section{The hybrid region: bridging the molecular models of different resolutions}
+and practical perspectives.
+
+\section{The hybrid resolution: bridging the molecular models of different resolutions}
 \label{sec:design}
@@
 In AdResS scheme, the simulation region $\Omega$ is 
-is decomposed without overlapping into 3 regions:
+is decomposed without overlapping into three regions:
 the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
@@
 A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
-The AdResS uses a scalor weighting function $w(\vect r),\ \vect r\in\Omega$ 
+The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
 to denote the resolution of the molecule at position $\vect r$.
@@
 at the boundary between the hybrid and the coarse-grained regions.
-Since all interactions (including the electrostatic interction) in AdResS are treated
-by cut-off method, the weighting function requires the thickness of
+AdResS requires 
+all interactions\footnote{The long-range electrostatic interactions
+  are also treated by the cut-off method, e.g.~the Reaction-Field method.
+} being treated
+by the cut-off method, and the thickness of
 the hybrid region being at least one cut-off radius (denoted by $r_c$).
-The benefite of this setting is that the atomistic
-region is not directly interacting with the coarse-grained region,
-so there is no extra work for modeling the cross-scale interactions.
+Moreover, owing to the double-resolution of hybrid molecules,
+an atomistic molecule only interacts with the 
+atomistic resolution of a hybrid molecule,
+while a coarse-grained molecule only interacts with the coarse-grained resolution
+of a hybrid molecule.
+The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
+The benefit of these settings is that
+there is no extra work for modeling the cross-scale interactions.
 
@@
 Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
-and the superscipt ``$V$'' denotes that the force is defined
+and the superscript ``$V$'' denotes that the force is defined
 by the potential interpolation.
@@
 acting along the direction of decreasing weighting function.
-This force is defined as the force of changing representation:
+% This force is defined as \emph{the force of changing representation}.
 It should be noted that
-the last term breaks the Newton's third law, therefore the force of potential interpolation
+this force breaks the Newton's third law, therefore the force of potential interpolation
 does not conserve the momentum.
-We define the accumulative effect of this term by the force of changing representation:
+We define the accumulative effect of this term by the \emph{force of changing representation}:
 \begin{align}
@@
 both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
-properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}). The choice of the interpolation scheme depends on
-the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
-conservation, then the force interpolation is prefered.
-In equilibrium case, we will show later in Sec.~\ref{sec:statistical}
-that both approaches approximately sample the grand-canonial ensemble.
+properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
+% The choice of the interpolation scheme depends on
+% the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
+% conservation, then the force interpolation is prefered.
+Regarding the equilibrium statistical properties, we will show later in Sec.~\ref{sec:statistical}
+that both approaches approximately sample the grand-canonical ensemble.
 
@@
 Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
-force exserts on one molecule is given by the normal adding up rule:
+force exerts on one molecule is the sum of all pairwise forces:
 \begin{align}
@@
 \end{align}
-The force on the atomistic DOFs of a hybrid molecules is distributed 
+The force on the atomistic degrees of freedom (DOFs) of a hybrid molecules is distributed 
 by, 
@@
 a buffer region so that the atomistic region
-interacts with the hybrid region via the atomistic intermolecular interaction:
+interacts with the hybrid region only via the atomistic intermolecular interaction:
 \begin{equation}\label{eqn:new-w}
@@
 The minimum thickness of the hybrid region is therefore $2r_c$.
-It worth noting that the coarse-grained region does not requires a buffer in the hybrid region, because
-by definition the coarse-grained region interacts with the hybrid region via the coarse-grained intermolecular interaction.
+It worth noting that the coarse-grained region does not require a buffer in the hybrid region, because
+by definition the coarse-grained region interacts with the hybrid region only via the coarse-grained intermolecular interaction.
 The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
 however, the extra cost of is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
-which is treated in atomistic resolution. This cost is relatively small for systems with large atomistic region.
+which is treated in atomistic resolution. This cost is relatively small for systems with a large atomistic region.
 
@@
 
-In order to consider the accuracy of the AdResS from statistical point of view, we always compare it with a full
+In order to consider the accuracy of the AdResS from statistical perspective, we always compare it with a full
 atomistic reference system, which is of the same size as the AdResS system,
@@
 is same as the corresponding subregion in the atomistic reference, then
-the AdResS  is of good accuracy (see the comparision indicated by the red arrow in Fig.~\ref{fig:compare}).
+the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
 A well-known conclusion of the standard statistical mechanics is that
 when the reference system approximate the thermodynamic limit, the subsystem is
-subject to the grand-canonial ensemble. Therefore, it is natural to investigate
-if the atomistic region of AdResS is also subject to the grand-canonial ensemble
+subject to the grand-canonical ensemble. Therefore, it is natural to investigate
+if the atomistic region of AdResS is also subject to the grand-canonical ensemble
 in the same thermodynamic limit. The theoretical framework presented in this section works for
@@
   \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
-  \caption{A schematic plot of the comparision between the AdResS system (left) and the full atomistic reference system (right).}
+  \caption{A schematic plot of the comparison between the AdResS system (left) and the full atomistic reference system (right).}
   \label{fig:compare}
@@
 
-We denote the number of molecules, volume and temperture of the system by $N$, $V$ and $T$, respectively.
+We denote the number of molecules, volume and temperature of the system by $N$, $V$ and $T$, respectively.
 The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
@@
 The thermodynamic variables of the subregions are specified by the subscript,
-for example, the those of the atomistic region are 
+for example, those of the atomistic region are 
 $N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
-are denoted by adding ``$\HY$'' and ``$\CG$'', respectively.
+are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
 Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
@@
 All DOFs of the system is denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
-generality, the first molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ in hybrid region, and
+generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
 the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
-It should be noted that for simplicity, we do not explicitly consider the number of DOFs are different for an atomistic
+It should be noted that for simplicity, we do not explicitly consider that the number of DOFs are different for an atomistic
 and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
@@
 region can be treated as an infinitely large particle and energy
-reservior of the atomistic region, and the hybrid region is an
+reservoir of the atomistic region, and the hybrid region is an
 infinitely thin filter that changes molecular resolution when a
@@
 the subregion corresponds to the atomistic region samples the
-grand-canonial ensemble.  The question regarding the accuracy of
+grand-canonical ensemble.  The question regarding the accuracy of
 AdResS can be asked by: How accurately the atomistic region samples
-the grand-canonial ensemble in the thermodynamic limit. Being more
+the grand-canonical ensemble in the thermodynamic limit. Being more
 specifically, we want to prove the probability density of the atomistic region satisfies
@@
 normalizing the probability density, and $\mh^\AT$ is the \emph{atomistic}
-Hamiltonian defined in the the subregion of the reference system that
-corresponds to the atomistic region of the AdResS system.
+Hamiltonian.
+% defined in the the subregion of the reference system that
+% corresponds to the atomistic region of the AdResS system.
 
@@
 \subsection{The accuracy of the configurational probability density}
-The configurational probability density~\eqref{eqn:dist-1-0} is further splitted as
+The configurational probability density~\eqref{eqn:dist-1-0} is further split as
 \begin{align}\label{eqn:conf-split}
@@
 It can be shown that if
-(1) all interactions in the system are cut-offed;
-(2) The atomistic region interacts with the bybrid region only in an atomistic way;
+(1) All interactions in the system are cut-offed;
+(2) The atomistic region interacts with the hybrid region only in an atomistic way;
 (3) The system is short-range correlated, and the correlation between the atomistic
@@
 shown that the density distribution in the hybrid region deviates from
-the desired one, even if the coarse-grained side is modelled to
-reporduce the atomistic pressure~\cite{poblete2010coupling}.  However,
+the desired one, even if the coarse-grained side is modeled to
+reproduce the atomistic pressure~\cite{poblete2010coupling}.  However,
 it is possible to raise necessary conditions
 for the AdResS system, with which the accuracy can be improved
-systematically.
+systematically (see the cyan arrow in Fig.~\ref{fig:compare}).
 % improve the accuracy of the probability density.
@@
 ask that the hybrid radial distribution function (RDF) should be the
-same as that of the reference system (see the green arrow in Fig.~\ref{fig:compare}):
+same as that of the reference system:
 \begin{align}\label{eqn:necessary-2nd}
@@
 It is fully justified to systematically raise the necessary conditions
-upto $m$-th multibody probability density, for example the third necessary condition would be
+up to $m$-th multibody probability density, for example the third necessary condition would be
 \begin{align}
@@
 system, it has been shown in Ref.~\cite{wang2013grand} that when the
-thermodynamic force is applied, the AdResS atomistic region reporduces (with satisfory accuracy)
-mulit-body configurational probability densities of the reference system
-upto three-body correlation.
+thermodynamic force is applied, the AdResS atomistic region reproduces (with satisfactory accuracy)
+multi-body configurational probability densities of the reference system
+up to the three-body correlation.
 % In principle, higher order of mulit-body correlation can be investigated in
@@
 $\{\vect r \,:\, \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$ that is interacting with
-the atomistic region. While the third necessary condition is not satisfied because deviation
-in the three-body correlation presents in the buffer bybrid region.
+the atomistic region. The third necessary condition is not satisfied because deviation
+in the three-body correlation presents in the buffer hybrid region.
 It should be noted that there is no theoretical background why the second necessary
@@
 necessary condition is automatically satisfied~\cite{wang2013grand}. Again, there is no
-theoretical prove behind this phenomenum, and one cannot expect the same
+theoretical prove behind this phenomenon, and one cannot expect the same
 benefit for other systems.
@@
 
-The second order accuracy is achieved if the isothermo-compressibilty of the atomistic and coarse-grained resolutions match:
+The second order accuracy is achieved if the isothermo-compressibility of the atomistic and coarse-grained resolutions match:
 \begin{align}
@@
 
-\subsection{The WCA potential as a generic energy and particle reservior}
-
-From the analysis on statistical mechanics one surprising fact is that if the
+\subsection{The WCA potential as a generic energy and particle reservoir}
+
+From the analysis on statistical mechanics, one surprising fact is that if the
 requirement for the accuracy is not very high (only applying the
@@
 a coarse-grained model.  The computational difficulty lies in the
-sudden switching on of the atomistic interactions when a coarse-grained
-molecule enters the hybrid region. If two molecules enters at
+sudden switching-on of the atomistic interactions when a coarse-grained
+molecule enters the hybrid region. If two molecules enter at
 the same time and the same location, then the atomistic contribution
@@
 interaction.  For an SPC/E water system, the cut-off radius of WCA potential
-can be 2.4 time smaller than the cut-off used in the atomistic
+can be 2.4 time smaller than the cut-off radius used in the atomistic
 region. Since the computational cost of cut-off scheme is of order $\mo(r_c^3)$,
@@
 WCA model computes only one. Therefore the WCA model in total costs only $1/190$ 
-on force computation than atomistic model.
+on force computation than the SPC/E atomistic model.
 The WCA approach has been successfully used in calculating the
@@
 In AdResS system, the global uniform
-temperture distrubution in equilibrium is equilibriated by the Langevin
-thermostat.  However, extra term appear in the pressure or chemical
+temperature distribution in equilibrium is equilibriated by the Langevin
+thermostat.  However, extra terms appear in the pressure or chemical
 potential relations when the momentum or energy conservation is absent
@@
 when the uniform density distribution is guaranteed, the chemical potential
-difference between the resolutions is compensited by $\omega_0$, which
+difference between the resolutions is compensated by $\omega_0$, which
 is the work per molecule from the filter when a molecule leaves the
@@
 where $ \omega^{\thf,V}$ denotes the work of the thermodynamic force
-of potential interpolation.
+of the potential interpolation.
 This work is path independent if the thermodynamic force is defined as a function of the distance to the atomistic region, and applies along the gradient of the weighting function.
@@
 For the force interpolation, 
-we denote the extra contribution due to the absence of the enregy conservation
+we denote the extra contribution due to the absence of the energy conservation
 by $\omega^\exc$, then
@@
 \end{align}
-where $\omega^{\thf}$ is the work of the thermodynamic force of force interpolation.
+where $\omega^{\thf}$ is the work of the thermodynamic force of the force interpolation.
 The magnitude of the extra term $\omega^\exc$ is unclear up to now.
@@
 role.  For the potential interpolation, the pressure relation can be
-investigated by an imaginary infiniesimal volume increment of the atomistic
+investigated by an imaginary infinitesimal volume increment of the atomistic
 region, and the same amount of volume decrement of the coarse-grained
@@
 \end{align}
-where $\omega^\rep$ is the work done by the average force of change representation:
+where $\omega^\rep$ is the work done by the average force of changing representation:
 \begin{align}\label{eqn:work-rep}
@@
 where ``$\circ$'' means that the integral should be understood as along the path.
-Since the force of changing representation acts always along the gradient of the weighting
-function, therefore, if the system is homogeneous in the hybrid region, then the integral~\eqref{eqn:work-rep}
+The force of changing representation acts always along the gradient of the weighting
+function, and the weighting function is a function of the distance to the atomistic region,
+therefore, if the system is homogeneous in the hybrid region, then the integral~\eqref{eqn:work-rep}
 is path independent. The ensemble average  can be estimated by sampling.
-The force of changing representation merges from the last term of potential
+The force of changing representation stems from the last term of potential
 interpolation~\eqref{eqn:f-v-interpol}, and contributes to the
-pressure relation~\eqref{eqn:p-eq-v} because it does not satisfies the Newton's third
-law.
+pressure relation~\eqref{eqn:p-eq-v} because it does not satisfies the Newton's action-reaction
+law~\cite{agarwal2014chemical}.
 
@@
 % interpolation.
-It should be noted that the ensemble averge in the work
+It should be noted that the ensemble average in the work
 of changing representation~\eqref{eqn:work-rep} is defined for the
@@
 density. In Ref.~\cite{wang2013grand} an even stronger conclusion is shown numerically in the SPC/E water system: The
-averge force of changing representation estimated from potential
+average force of changing representation estimated from potential
 interpolation is pointwisly identical to that estimated from the force
-interpolation. The thermodynamic relation discoved in
+interpolation. The thermodynamic relations discovered in
 force and potential interpolation AdResS schemes are summarized
@@
   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}lll}\hline\hline
-    &         Force interp. AdResS     &       Potential interp. AdResS \\
+    &         Force interpol. AdResS     &       Potential interpol. AdResS \\
     Temperature    &   {$T_\AT = T_\CG$}                                                & {$T_\AT = T_\CG$}                                        \\
@@
 can be written down in terms of equilibrium ensemble averages should
-be computed with high accuracy accuracy when using an AdResS simulation that approximately samples the grand-canonial ensemble.
+be computed with high accuracy accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
 However, under this framework one has little knowledge regarding the quantities
@@
 In principle, the Hamiltonian dynamics should be used to compute the dynamical properties,
-however, due to the trunction error in computer simulations, it
+however, due to the truncation error in computer simulations, it
 is technically difficult to conserve the energy in very long MD simulations.
@@
 state.
-It worth noting that the thermostats are designed to bring the system to equilibrium distributions, and 
+It worth noting that the thermostats are designed to sample equilibrium distributions, and 
 disturb the Hamiltonian dynamics in an artificial way.
@@
 in computing the dynamical properties, the potential artifacts
-should be check carefully.
+should be checked carefully.
 In the context of AdResS, we propose an alternative way of thermostating
 the system, the local thermostat method~\cite{wang2014exploring},
-which is proved to be free of the artifacts in computing the dynamical properties in the following sections.
+which is proved to be free of the artifacts in computing the dynamical properties in the following section.
 
@@
     present the potential and force interpolation AdResS with local
-    thermostat, respectively.  The time-scales of the global- and local- Langevin
+    thermostat, respectively.  The time-scales of the global and local Langevin
   thermostat are both $\tau_T = 0.1$~ps.}
@@
 $\langle \vect v(0)\cdot \vect v(t)\rangle$ computes the correlation
-between the velocity at time $0$ and $t$. 
+between the velocity at time $0$ and $t$, which depends on the dynamics of the system. 
 An illustrative example of the thermostating artifact is 
@@
 The standard AdResS simulations, since the Langevin thermostat
-is globally coupled to the system,  is not suitable to reproduce the dynamical
+is globally coupled to the system,  is not suitable for reproducing the dynamical
 properties of the system.
 
-The solution is to adopt the local-thermostat method that was initially
+The solution is to adopt the local thermostat method that was initially
 developed for non-equilibrium MD simulations~\cite{wang2014exploring}.
-This method divide the system in to two regions.
-The dynamical region of out of which the dynamical properties are calculated is not coupled
+This method divide the system into two regions.
+The dynamical region, out of which the dynamical properties are calculated, is not coupled
 to any thermostat, so the dynamics there is preserved as Hamiltonian dynamics.
-The thermostated region is coupled to Langevin thermostat in order to keep the system
+The thermostated region is coupled to the Langevin thermostat in order to keep the system
 at the desired thermodynamic state.
@@
 and
-the hybrid and coarse-grained regions, which serve as particle and energy reservior, coupled to thermostat.
+the hybrid and coarse-grained regions, which serve as particle and energy reservoir, coupled to the thermostat.
 % The idea is to leave the atomistic region uncoupled to any thermostat, so the dynamics 
@@
 simulation region is $14.7\times3.2\times3.2~\textrm{nm}^3$,
-in which the resolution changes only on $x$-direction.
+in which the resolution changes only in $x$-direction.
 The atomistic region is of size $1.5\times3.2\times3.2~\textrm{nm}^3$, and the width of the hybrid region is $d_{\HY} = 2.85$~nm.
@@
 The thermodynamic forces of force and potential interpolations are iteratively computed by
-Eq.~\eqref{eqn:thf-f} and \eqref{eqn:thf-p}, respectively.
-The electrocstatic interaction is treated by the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized},
+Eq.~\eqref{eqn:tfi}.
+The electrostatic interaction is treated by the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized},
 with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$, which conserves the energy, and
-is proved to be a special case of the more
-accurate Zero-multiple method~\cite{fukuda2011molecular,fukuda2013zero}.
+is proved to be a special case of the  Zero-multiple method~\cite{fukuda2011molecular,fukuda2013zero}.
 The cut-off radius is 1.2~nm, and the van der Waals interaction is smoothed by the ``\texttt{switch}'' method provided by
@@
 functions computed by fully equilibriated MD trajectories of length 1~ns, with the
-velocities recored every 0.04~ps.  Here full equilibriation means
+velocities recorded every 0.04~ps.  Here full equilibriation means
 uniform temperature and density distributions in the system.
-In the Figure, both the force and potential interpolations are presented along with the
-NVE atomistic simulation, and show almost perfect consistency.
+In the Figure, both the force and potential interpolations are
+in almost perfect agreement with the  atomistic simulation under Hamiltonian dynamics.
+% presented along with the
+% NVE atomistic simulation, and show almost perfect consistency.
 This indicates that the AdResS with the local thermostat
@@
 biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
-We investiage a system composed of
+We investigate a system composed of
 7235 TIP3P water molecules, and
@@
 a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
-The rest of the system is treated coarse-grainly by the WCA interpolation.
+The rest of the system is treated coarse-grainly by the WCA interaction.
 The dynamical region  is
@@
 when using force interpolation, the extra energy production might not be effectively equilibriated.
-To this end, we only investiage the potential interpolation. The corresponding
+To this end, we only investigate the potential interpolation. The corresponding
 thermodynamic force is iteratively computed by
-Eq.~\eqref{eqn:thf-p}.
-The electrocstatic interaction is computed by the Reaction-Field with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
-Both the electrocstatic and the van der Waals intercations (smoothed by ``\texttt{switch}'' method in Gromacs)
+Eq.~\eqref{eqn:tfi}.
+The electrostatic interaction is computed by the Reaction-Field method with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
+Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
 are cut-offed at 1.0~nm.
 
-The system presents a very clear timescale seperation: There are fast
+The system presents a very clear time-scale separation: There are fast
 motions like bond and angle vibrations that happen in tens of femtoseconds, while
-there are slow conformational transformations that happen in hundreds of picoseconds.
+there are slow conformational transitions that happen in hundreds of picoseconds.
 The dihedral angles $\phi$ and $\psi$ (see
@@
 
-The free energy defined as the logrithm of the projected equilibrium probability density on the
+The free energy is defined as the logarithm of the projected equilibrium probability density on the
 $\phi$--$\psi$ space:
@@
 The free energy of the full atomistic reference system is showed in
-Fig.~\ref{fig:ala}~(b), which clearly presents the metastablity in the
+Fig.~\ref{fig:ala}~(b), which clearly presents the metastability in the
 system: several highly populated regions that correspond to metastable
-conformations are seperated by lowly populated regions that are
+conformations are separated by lowly populated regions that are
 identified as transition regions.
@@
 
-In pratice, not only the equilibrium properties like the free energy are of interest,
-but also the dynamical properties like the conformational transitions and the corresponding relaxation timescales
+In practice, not only the equilibrium properties like the free energy are of interest,
+but also the dynamical properties like the conformational transitions and the corresponding relaxation time-scales
 are of highly biological importance.
@@
 % Or equivalently
-% at which timescale the slow dynamics  happens and from which conformation to which it corresponds to.
-When the system presents metastablity,
+% at which time-scale the slow dynamics  happens and from which conformation to which it corresponds to.
+When the system presents metastability,
 one powerful tool for this purpose
 is the Markov state model (MSM)~\cite{prinz2011probing,prinz2011markov,schuette2011markov}, which
-approximate the original high-dimensional dynamics by a finite-state reduced
+approximates the original high-dimensional dynamics by a finite-state reduced
 Markov process.
 The accuracy analysis regarding  this approximation is well-established~\cite{sarich2010approximation,djurdjevac2012estimating}.
-The MSM has found successfully applications in various fileds, for example studying complex protein systems
+The MSM has found successfully applications in various fields, for example studying complex protein systems
 (two of the hundreds examples are Ref.~\cite{noe2009constructing,kohlhoff2014cloud}).
 
-In a standard MSM approach, the full phase space is firstly deomposed into a non-overlapping union of finite number of states
+In a standard MSM approach, the full phase space is firstly decomposed into a non-overlapping union of finite number of states
 (not necessarily identical to the metastable conformations),
@@
 The reduced
-dynamics is assumed to be Markovian,
-although uaually it is not (or not perfectly Markovian),  and in practice it becomes one of the main sources of the error.
-We will not discuss the accuracy issue of the MSM in this paper,
-because it is not very relavant to the performance of the AdResS method.
-% It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
-% Due to the Markovianity of the reduced dynamics, the
+dynamics is assumed to be Markovian.
+% although uaually it is not (or not perfectly Markovian),  and in practice it becomes one of the main sources of the error.
+% We will not discuss the accuracy issue of the MSM in this paper,
+% because it is not very relavant to the performance of the AdResS method.
+% % It would be lengthy to discuss the topic here, and the interested readers are refereed to Ref.~\cite{}.
+% % Due to the Markovianity of the reduced dynamics, the
 Under the assumption of Markovianity, the original continuous dynamics is approximated by the Markov processes governed by
@@
 \end{align}
-where $\vect T(\tau)$ is the transition maxtix that
+where $\vect T(\tau)$ is the transition matrix that
 associates to the reduced dynamics of $\vect p^\top_{k\tau}$. The matrix element, for example $T_{ij}$
@@
 If the transition matrix is irreducible and aperiodic, then according to Perron-Frobenius theorem, the maximum
-eigenvalue is reached and single. Due to the stochaticity of the matrix, this eigenvalue is equal to 1.
+eigenvalue is reached and single. Due to the stochasticity of the matrix, this eigenvalue is equal to 1.
 If the dynamics
@@
 The first $m$ largest eigenvalues are denoted by $1 = \lambda_1 > \lambda_2 \geq \lambda_3 \geq \cdots \geq \lambda_m$, and
-the corresponding left eigenvetors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$.
+the corresponding left eigenvectors are denoted by $\Phi_1, \Phi_2, \cdots, \Phi_m$.
 The leading eigenvector is non-negative, and satisfies $\Phi^\top_1 = \Phi^\top_1\cdot\vect T(\tau)$.
-With proper normalization (integrate to 1) the leanding eigenvector is identical to the 
+With proper normalization (integrate to 1) the leading eigenvector is identical to the 
 equilibrium probability density.
-At inifinitely long time, the probability density $\vect p_{k\tau}$ converges to the equilibrium probability.
-The speed of the convergence is characterized by the leading relaxation timescales that are
+At infinitely long time, the probability density $\vect p_{k\tau}$ converges to the equilibrium probability.
+The speed of the convergence is characterized by the leading relaxation time-scales that are
 determined by the leading eigenvalues:  $t_i  = -{\tau}/{\log\lambda_i}, \ i=2, \cdots, m$.
-Since the eigenvectors are orthorgonal and the first eigenvector is non-negative, the reset
+Since the eigenvectors are orthogonal and the first eigenvector is non-negative, the reset
 of the eigenvectors have a vanished sum over all elements: Their
@@
 The different signs in the eigenvectors denote the conformational transition corresponding to the
-timescale $t_i$.
+time-scale $t_i$.
 
@@
 % \end{align}
-% where $t_i$ is the timescale that corresponds to the $i$th eigenvalue:
-% \begin{align}\label{eqn:timescale}
+% where $t_i$ is the time-scale that corresponds to the $i$th eigenvalue:
+% \begin{align}\label{eqn:time-scale}
 %   t_i  = -\frac{\tau}{\log\lambda_i}, \quad i=2, \cdots, m,
@@
 % time-dependent probability  converges to the equilibrium probability as time goes to infinity.
-% The timescale of the slow part of the relaxation is govenerned by the leanding eigenvalues through Eq.~\eqref{eqn:timescale},
-% while the conformational change corresponds to each timescale is indicated by the eigenvector.
+% The time-scale of the slow part of the relaxation is govenerned by the leanding eigenvalues through Eq.~\eqref{eqn:time-scale},
+% while the conformational change corresponds to each time-scale is indicated by the eigenvector.
 % We assume a gap in the spectrum between $\lambda_m$ and the rest of the spectrum $\lambda_{m+1}, \cdots$,
@@
 % The spectral anaysis of the MSM will reveal the
-% implied timescales, and corresponding conformational changes.
+% implied time-scales, and corresponding conformational changes.
 % It has
@@
   \includegraphics[width=0.5\textwidth]{figs/system.alanine/fig-eig-val.png}
-  \caption{The non-trivial leading timescale calculated from the
+  \caption{The non-trivial leading time-scale calculated from the
     Markov state modeling for the system of alanine dipeptide
@@
     correspond to the first, second and third non-trivial leading
-    timescale, respectively. The horizontal axis $\tau$ is the
+    time-scale, respectively. The horizontal axis $\tau$ is the
     lag-time used to build the Markov state model. For a sufficient
-    large $\tau$ the values of the timescales should be independent on
+    large $\tau$ the values of the time-scales should be independent on
     the lag-time. The shadowing regions around the lines indicate the
@@
   \includegraphics[width=0.3\textwidth]{figs/system.alanine/fig-eig-vec-adress-4.eps}\\
-  \caption{The eigenvectors corresponding to the first three leading timescales computed using lag-time $20$~ps.
+  \caption{The eigenvectors corresponding to the first three leading time-scales computed using lag-time $20$~ps.
     The first row presents the eigenvectors of the full atomistic reference, while the second
     row presents those of the AdResS. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
-    timescales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
+    time-scales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
     denoted by the color. 
@@
 
-In the example of alanine dipeptide dissoved in water, the states in the MSM
+In the example of alanine dipeptide dissolved in water, the states in the MSM
 is defined by uniformly dividing the $\phi$-$\psi$ space in to $20\times 20$ bins.
@@
 uncertainty.
-From Fig.~\ref{fig:ala-msm-v}, the conformational transitions corrspond
+From Fig.~\ref{fig:ala-msm-v}, the conformational transitions correspond
 to $t_2$, $t_3$ and $t_4$ are $\{\confa \} \leftrightarrow \{\confc,\confd\}$,
@@
 those of the full atomistic reference. Although calculated from the
-equilibrium MD simulations, it sould be noted that the leading timescales and the
+equilibrium MD simulations, it should be noted that the leading time-scales and the
 corresponding eigenvectors are not the equilibrium properties, because
@@
 In this paper, we investigated both the potential and force
-interpolation under a uniform theoretical framework of GC-AdResS. The
+interpolations under a uniform theoretical framework of GC-AdResS. The
 necessary conditions for the grand-canonical like equilibrium
-simulation are provided. However, it sould be noticed that these
-conditions are not sufficient, and the very-high accuracy in the  numerical simulations indicate
+simulation are provided. However, it should be noticed that these
+conditions are not sufficient, and the high accuracy in the  numerical simulations indicates
 that these conditions tend to be too ``strong''.  Take the AdResS
@@
 investigation, so it was not studied.}, and the second necessary condition (RDF consistency)
-is automatically fulfilled.  If the necessary conditions were not
-sufficient, it might also be possible that the errors in the numercial simulations are too
+is automatically fulfilled.
+% If the necessary conditions were not
+% sufficient,
+It might also be possible that the errors in the numerical simulations are too
 small to be observed.  In this context, it would be helpful
@@
 averages would be automatically answered. However, the dynamical properties, which are
-not equilibrium ensemble averages, are out of the scope of the current
-theoretical framework. In order to numerically check the accuracy of AdResS
+not equilibrium ensemble averages, are out of the scope of the 
+GC-AdResS framework. In order to numerically check the accuracy of AdResS
 in computing the dynamical properties, we investigated the velocity auto-correlation
 function of pure water and the leading relaxation time-scales of alanine dipeptide
-dissoved in water.
-The vanishing time-scale of the time-correlations ranges from 1~ps in the case of velocity auto-correlation
+dissolved in water.
+The significant time-scale of the time-correlations ranges from 1~ps in the case of velocity auto-correlation
 to almost 600~ps in the case of conformational relaxation of alanine dipeptide.
@@
 Although these positive numerically evidences cannot answer the open questions
-on the reason behind the high accuracy or the error estimates of the dynamical properties,
+on the reason behind the high accuracy, nor the error estimates of the dynamical properties,
 they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
@@
 Currently the AdResS method has only been applied to model systems and small scale
-applications. The advantage in the efficiency is not very obvious.
+applications. The advantage in the efficiency is not very obvious in these studies.
 One important reason that prevents the AdResS method from
 large scale applications is the software implementation~\cite{agarwal2014chemical}.
-The software we used in the simulations is Gromacs\footnote{Verions higher than 4.6 support
-AdResS}.
+The software we used in the simulations is Gromacs\footnote{Versions higher than 4.6 support
+AdResS.}.
 Currently the force computation kernel for the hybrid region is written in C language~\cite{kernighan1988c}.
@@
 }.
-Since in the coarse-grained region the force computation is very cheap, majority
+Since in the coarse-grained region the force computation is very cheap, the majority
 of the computational cost is actually spent on keeping and integrating the atomistic DOFs.
-On straightforward solution is the remove the atomistic DOFs in the coarse-grained
+On straightforward solution is to remove the atomistic DOFs in the coarse-grained
 region, which was actually proposed by the very original paper of AdResS~\cite{praprotnik2005adaptive}.
 Owing to the fact that the coarse-grained interactions are usually ``softer''
-than the atomistic interactions, one way of futher boost the performance is
+than the atomistic interactions, one way of further boost the performance is
 to integrate the coarse-grained molecules with larger time-steps.
@@
 error estimates should be developed along the application this adaptive time-step idea.
-All these technical difficulties would hopfully be solved in the near futher.
+All these technical difficulties would hopefully be solved in the near future.
 

### 2014-11-23 writeDown/pub.epj/paper.tex
animesh's revise

@@
 simulated with lower resolution models for the purpose of saving computational cost.
-The AdResS is, therefore, suitable for the systems that different physical
-phenomena happen concurrently at different time and length scales. For example,
+AdResS is, therefore, suitable for the systems where different physical
+phenomena is happening concurrently at different time and length scales. For example,
 the structure of a protein and its solvation shell
 should be resolved at the atomistic level, while far away form the protein,
-the only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
+only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
 accuracy with very coarse-grained or even continuum
@@
 Similar  
-techniques sharing the concurrent idea of multiscale simulation can be found in, for example, Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.
+techniques sharing the concurrent idea of multiscale simulation can be found, for example in Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.
 
@@
 In this context,
-it worth noting that the energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
+it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
 although out of the energy conservation
@@
 
-The GC-AdResS framework answers of how to accurately compute the  equilibrium properties.
+The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
 However, although the system is in equilibrium,
@@
 The paper is closed by a concluding section
-that mainly discusses the opening problems in AdResS from both theoretical
+that mainly discusses the open problems in AdResS from both theoretical
 and practical perspectives.
@@
 In AdResS scheme, the simulation region $\Omega$ is 
-is decomposed without overlapping into three regions:
+decomposed without overlapping into three regions:
 the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
@@
 The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
-however, the extra cost of is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
+however, the extra cost is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
 which is treated in atomistic resolution. This cost is relatively small for systems with a large atomistic region.
@@
 A well-known conclusion of the standard statistical mechanics is that
-when the reference system approximate the thermodynamic limit, the subsystem is
+when the reference system approximates the thermodynamic limit, the subsystem is
 subject to the grand-canonical ensemble. Therefore, it is natural to investigate
@@
   \includegraphics[width=0.8\textwidth]{figs/system.water/compare.eps}
-  \caption{A schematic plot of the comparison between the AdResS system (left) and the full atomistic reference system (right).}
+  \caption{A schematic plot of the comparison between an AdResS system (left) and the full atomistic reference system (right).}
   \label{fig:compare}
@@
 $\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
-All DOFs of the system is denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
+All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
 generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
@@
 and the coarse-grained regions are infinitely large, and at the same
-time, the atomistic region is much larger than the coarse-grained
+time, the atomistic region is much smaller than the coarse-grained
 region. The hybrid region is much smaller than both the atomistic and
@@
 region can be treated as an infinitely large particle and energy
-reservoir of the atomistic region, and the hybrid region is an
+reservoir for the atomistic region, and the hybrid region is an
 infinitely thin filter that changes molecular resolution when a
@@
 considering the full atomistic reference system), it is obvious that
-the subregion corresponds to the atomistic region samples the
+the subregion corresponding to the atomistic region samples the
 grand-canonical ensemble.  The question regarding the accuracy of
 AdResS can be asked by: How accurately the atomistic region samples
-the grand-canonical ensemble in the thermodynamic limit. Being more
+the grand-canonical ensemble in the thermodynamic limit? More
 specifically, we want to prove the probability density of the atomistic region satisfies
@@
 
-In stead of directly proving Eq.~\eqref{eqn:dist-0}, Ref.~\cite{wang2013grand}
+Instead of directly proving Eq.~\eqref{eqn:dist-0}, Ref.~\cite{wang2013grand}
 suggest investigating the following equivalent equations:
@@
 \end{align}
-where $k$ denotes the step of iteration. $\kappa$ is the
-isothermo-compressibility. In equilibrium the density profile $\rho(\vect r)$ in the
+where $k$ denotes the step of iteration and $\kappa$ is the
+isothermal-compressibility. In equilibrium the density profile $\rho(\vect r)$ in the
 atomistic and coarse-grained regions are constants, so the thermodynamic force
@@
 $\{\vect r \,:\, \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$ that is interacting with
-the atomistic region. The third necessary condition is not satisfied because deviation
-in the three-body correlation presents in the buffer hybrid region.
+the atomistic region. The third necessary condition is not satisfied because there is deviation
+in the three-body correlation in the buffer hybrid region.
 It should be noted that there is no theoretical background why the second necessary
@@
 and coarse-grained densities match. The conclusion is derived under
-the assumption of thermodynamic limit and the decorrlation between the
+the assumption of thermodynamic limit and the decorrelation between the
 atomistic and coarse-grained regions.
 
-The second order accuracy is achieved if the isothermo-compressibility of the atomistic and coarse-grained resolutions match:
+The second order accuracy is achieved if the isothermal-compressibility of the atomistic and coarse-grained resolutions match:
 \begin{align}
@@
 In AdResS system, the global uniform
-temperature distribution in equilibrium is equilibriated by the Langevin
+temperature distribution in equilibrium is equilibrated by the Langevin
 thermostat.  However, extra terms appear in the pressure or chemical
@@
 interpolation~\eqref{eqn:f-v-interpol}, and contributes to the
-pressure relation~\eqref{eqn:p-eq-v} because it does not satisfies the Newton's action-reaction
+pressure relation~\eqref{eqn:p-eq-v} because it does not satisfy the Newton's action-reaction
 law~\cite{agarwal2014chemical}.
@@
 can be written down in terms of equilibrium ensemble averages should
-be computed with high accuracy accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
+be computed with high accuracy when using an AdResS simulation that approximately samples the grand-canonical ensemble.
 However, under this framework one has little knowledge regarding the quantities
@@
 is technically difficult to conserve the energy in very long MD simulations.
-To this end thermostats are sometime coupled to keep the system at desired thermodynamic
+To this end thermostats are sometimes coupled to keep the system at desired thermodynamic
 state.
-It worth noting that the thermostats are designed to sample equilibrium distributions, and 
+It is worth noting that the thermostats are designed to sample equilibrium distributions, and 
 disturb the Hamiltonian dynamics in an artificial way.
@@
 the system, the local thermostat method~\cite{wang2014exploring},
-which is proved to be free of the artifacts in computing the dynamical properties in the following section.
+which is proved to be free of the artifacts in computing the dynamical properties, in the following section.
 
@@
     The square and cross points
-    present the potential and force interpolation AdResS with local
+    represent the potential and force interpolation AdResS with local
     thermostat, respectively.  The time-scales of the global and local Langevin
@@
 developed for non-equilibrium MD simulations~\cite{wang2014exploring}.
-This method divide the system into two regions.
+This method divides the system into two regions.
 The dynamical region, out of which the dynamical properties are calculated, is not coupled
@@
 The Fig.~\ref{fig:vac} presents the velocity auto-correlation
-functions computed by fully equilibriated MD trajectories of length 1~ns, with the
-velocities recorded every 0.04~ps.  Here full equilibriation means
+functions computed by fully equilibrated MD trajectories of length 1~ns, with the
+velocities recorded every 0.04~ps.  Here full equilibration means
 uniform temperature and density distributions in the system.
@@
 % NVE atomistic simulation, and show almost perfect consistency.
-This indicates that the AdResS with the local thermostat
+This indicates that AdResS with local thermostat
 is a promising method to investigate the dynamical properties
@@
 The MSM has found successfully applications in various fields, for example studying complex protein systems
-(two of the hundreds examples are Ref.~\cite{noe2009constructing,kohlhoff2014cloud}).
+(two of the hundreds of examples are Ref.~\cite{noe2009constructing,kohlhoff2014cloud}).
 
@@
   \caption{The eigenvectors corresponding to the first three leading time-scales computed using lag-time $20$~ps.
-    The first row presents the eigenvectors of the full atomistic reference, while the second
-    row presents those of the AdResS. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
+    The first row represents the eigenvectors of the full atomistic reference, while the second
+    row represents those of the AdResS. From left to right $\Phi_2$, $\Phi_3$ and $\Phi_4$ that correspond to
     time-scales $t_2$, $t_3$ and $t_4$ are given (see also Fig.~\ref{fig:ala-msm-t}). The magnitude of the eigenvectors are
@@
 Fig.~\ref{fig:ala-msm-t} and \ref{fig:ala-msm-v}. The
-eigenvalues should be $\tau$ independent for sufficiently large $\tau$ if the MSM is of good
+eigenvalues should be independent for sufficiently large $\tau$ if the MSM is of good
 accuracy, and from Fig.~\ref{fig:ala-msm-t} they are so for $\tau \geq 20$~ps.
@@
 necessary conditions for the grand-canonical like equilibrium
-simulation are provided. However, it should be noticed that these
+simulations are provided. However, it should be noticed that these
 conditions are not sufficient, and the high accuracy in the  numerical simulations indicates
@@
 they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
-and suggests a direction of theoretical investigations.
+and suggests a direction for theoretical investigations.
 
@@
 consistency and the corresponding
-error estimates should be developed along the application this adaptive time-step idea.
+error estimates should be developed along the application of this adaptive time-step idea.
 All these technical difficulties would hopefully be solved in the near future.

### 2015-02-21 writeDown/pub.epj/paper.tex
change email
revise the paper according to the referees

@@
 \title{Adaptive Resolution Simulation in Equilibrium and Beyond}
-\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{han.wang@fu-berlin.de}}, Animesh Agarwal\inst{3}}
+\author{Han Wang\inst{1,2}\fnmsep\thanks{\email{wang\_han@iapcm.ac.cn}}, Animesh Agarwal\inst{3}}
 %
@@
 rather than directly on the mechanical conservation laws.
+\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
+very high accuray in equilibrium properties such as the radial distribution function, three-body correlation and chemical potential~\cite{wang2013grand}.}
 In this context,
@@
 However, although the system is in equilibrium,
-some properties, which are called dynamical properties, cannot be simply computed from the equilibrium ensemble averages.
+some properties, which are called dynamical properties,
+\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
+% cannot be simply computed from the equilibrium ensemble averages.
 % These properties are called dynamical properties.
-A typical example is the velocity auto-correlation.
+A typical example is the velocity auto-correlation\footnote{
+  \recheck{
+  The velocity auto-correlation
+  % is the ensemble average
+  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
+  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
+  It should be noted that
+  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
+  therefore, it is a dynamical property. }}.
 % that describs the infiniesimal response of the system
@@
 of bio-macromolecules (e.g.~protein and DNA)
-are, again, not equilibrium averages.
+are, again, dynamical properties.
 The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
@@
 all interactions\footnote{The long-range electrostatic interactions
-  are also treated by the cut-off method, e.g.~the Reaction-Field method.
+  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method
+  to calculate the electrostatic interactions.}
 } being treated
-by the cut-off method, and the thickness of
+by the cut-off method\footnote{\recheck{The general cut-off method is used
+    in AdResS MD simulations.  The details of the cut-off method can be find in, e.g., Ref.~\cite{frenkel2001understanding}}}, and the thickness of
 the hybrid region being at least one cut-off radius (denoted by $r_c$).
@@
 The potential interpolation approach defines the hybrid energy by
+\footnote{
+\recheck{
+  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
+  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
 \begin{align}\label{eqn:v-v-interpol}
@@
 A well-known conclusion of the standard statistical mechanics is that
-when the reference system approximates the thermodynamic limit, the subsystem is
-subject to the grand-canonical ensemble. Therefore, it is natural to investigate
-if the atomistic region of AdResS is also subject to the grand-canonical ensemble
+when the reference system approximates the thermodynamic limit, the subsystem
+\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
+if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
 in the same thermodynamic limit. The theoretical framework presented in this section works for
@@
 the desired equilibrium, $\mathcal Z$ is the partition function
-normalizing the probability density, and $\mh^\AT$ is the \emph{atomistic}
-Hamiltonian.
+normalizing the probability density, $\mh^\AT$ is the \emph{atomistic}
+Hamiltonian, \recheck{and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
 % defined in the the subregion of the reference system that
@@
 It can be shown that if
-(1) All interactions in the system are cut-offed;
+(1) All interactions in the system are cut-off;
 (2) The atomistic region interacts with the hybrid region only in an atomistic way;
@@
 However, under this framework one has little knowledge regarding the quantities
-that are not ensemble averages.
+that are \recheck{beyond} ensemble averages.
 For example, the non-equilibrium response of the system
@@
 Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
-are cut-offed at 1.0~nm.
+are cut-off at 1.0~nm.
 
@@
 The eigenvectors and the indicated conformational transitions of the AdResS are also consistent with
-those of the full atomistic reference. Although calculated from the
+those of the full atomistic reference.
+\recheck{
+  The statistical uncertainty of estimating the longest non-trivial time-scale $t_2$ is higher than
+  the shorter time-scales. One possible reason is that
+  the transitions $\{\confa \} \leftrightarrow \{\confc,\confd\}$ are less frequently sampled in
+  a MD simulation than other transition events, owing to the longer implied time-scale. Moreover, the
+  states $\confc$ and $\confd$ are less frequently visited, so the estimate of the  equilibrium probabilities of these
+  states are of lower accuracy, which also introduces larger statistical uncertainty
+  in estimating the implied time-scales of the transitions related to these states.
+  The accuracy may be improved by the enhanced sampling techniques~\cite{rosta2014free}, however, this
+  issue is out of the scope of the current paper.}
+Although calculated from the
 equilibrium MD simulations, it should be noted that the leading time-scales and the
@@
 the transition probabilities (elements of the transition matrix) are actually
-auto-correlation functions of the characteristic functions that are not equilibrium ensemble averages.
+auto-correlation functions of the characteristic functions that are not \recheck{purely} equilibrium ensemble averages.
 
@@
 
+\section*{Acknowledgments}
+The computation of this work was performed at the North-German Supercomputing Alliance (HLRN) under project bec00100. The authors are grateful for this support.
+HW would like to acknowledge the finial support from National High Technology Research and Development Program of China under Grant No.~2015AA011201.
+
 \bibliography{ref}{}

### 2015-02-25 writeDown/pub.epj/paper.tex
revised paper

@@
 
-Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
+Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular systems.
 The terminology ``concurrent multiscale simulation'' means that
@@
 the structure of a protein and its solvation shell
-should be resolved at the atomistic level, while far away form the protein,
+should be resolved at the atomistic level, while far away from the protein,
 only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
@@
 
-The time evolution of a classical molecular systems
+The time evolution of a classical molecular system
 is modeled with Newtonian dynamics, and fundamental conservation laws
@@
 due to the spacial change of molecular resolution,
-the two conservation laws cannot be satisfied in the same system~\cite{praprotnik2011comment,dellesite2007some}.
+the two conservation laws cannot be satisfied at the same time~\cite{praprotnik2011comment,dellesite2007some}.
 Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
-that preserves the momentum conservation while breaks the energy
+that preserves the momentum conservation while breaking the energy
 conservation.
@@
 alternative approaches based on \emph{potential interpolation},
-which preserve energy conservation while break the momentum conservation,
+which preserve energy conservation while breaking the momentum conservation,
 were designed~\cite{wang2013grand,potestio2013hamiltonian}.
@@
 \recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
-very high accuray in equilibrium properties such as the radial distribution function, three-body correlation and chemical potential~\cite{wang2013grand}.}
+very high accuracy in equilibrium properties, such as the radial distribution function, the three-body correlation and the chemical potential~\cite{wang2013grand}.}
 In this context,
@@
 are, again, dynamical properties.
-The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
-and to the best of our knowledge, there is no theoretical answers on how accurately  AdResS reproduces the 
+The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework and,
+to the best of our knowledge, there is no theoretical answer on how accurately  AdResS reproduces the 
 dynamical properties of a system.
@@
 \vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
-region. We always assume the thickness of the hybrid region is
+region. We always assume the thickness of the hybrid region to be
 uniform, which indicates that the weighting function smoothly vanishes
@@
 all interactions\footnote{The long-range electrostatic interactions
-  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method
+  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
   to calculate the electrostatic interactions.}
 } being treated
-by the cut-off method\footnote{\recheck{The general cut-off method is used
-    in AdResS MD simulations.  The details of the cut-off method can be find in, e.g., Ref.~\cite{frenkel2001understanding}}}, and the thickness of
+by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
 the hybrid region being at least one cut-off radius (denoted by $r_c$).
@@
 by the potential interpolation.
-By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
+By  definition~\eqref{eqn:f-v-interpol}, the force of the potential interpolation is conservative. 
 The difference between the force and potential
@@
 does not conserve the momentum.
-We define the accumulative effect of this term by the \emph{force of changing representation}:
+We define the cumulative effect of this term by the \emph{force of changing representation}:
 \begin{align}
@@
 the momentum and energy are conserved, neither of the AdResS systems conserves
-both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
+both laws. The breaking of these mechanics conservations has substantial influence on the thermodynamic
 properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
@@
 \end{align}
-The force on the atomistic degrees of freedom (DOFs) of a hybrid molecules is distributed 
+The force on the atomistic degrees of freedom (DOFs) of a hybrid molecule is distributed 
 by, 
@@
 \end{align}
-where  $\atomidxone$ is the indexes of atoms in molecule $\moleidxone$.
-$m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.
+where  $\atomidxone$ is the index of an atom in molecule $\moleidxone$.
+$m_\atomidxone$ is the mass of atom $\alpha$, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.
 
@@
 choice of the weighting function should be added. 
-In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function with
+In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighting function with
 a buffer region so that the atomistic region
@@
 The minimum thickness of the hybrid region is therefore $2r_c$.
-It worth noting that the coarse-grained region does not require a buffer in the hybrid region, because
+It is worth noting that the coarse-grained region does not require a buffer in the hybrid region, because
 by definition the coarse-grained region interacts with the hybrid region only via the coarse-grained intermolecular interaction.
@@
 
-In order to consider the accuracy of the AdResS from statistical perspective, we always compare it with a full
+In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
 atomistic reference system, which is of the same size as the AdResS system,
@@
 If the configuration of the atomistic region in the AdResS 
-is same as the corresponding subregion in the atomistic reference, then
+is the same as that of the corresponding subregion in the atomistic reference, then
 the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
@@
 $\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
-All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
+All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without loss of
 generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
@@
 Instead of directly proving Eq.~\eqref{eqn:dist-0}, Ref.~\cite{wang2013grand}
-suggest investigating the following equivalent equations:
+suggests investigating the following equivalent equations:
 \begin{align}\label{eqn:dist-1-0}
@@
 The probability density and local Hamiltonian
-can be written down for the coarse-grained region analogically.
+can be written down for the coarse-grained region analogously.
 
@@
 density in the hybrid region is the same as the full atomistic
-reference, In homogeneous and isotropic system, it is equivalent to
+reference. In homogeneous and isotropic system, it is equivalent to
 ask that the hybrid radial distribution function (RDF) should be the
@@
 only the thermodynamic force is applied, the second order necessary condition~\eqref{eqn:necessary-2nd}
-is automatically fulfilled, because the RDF is identical to the reference system in the buffer hybrid region
+is automatically fulfilled, because the RDF is identical to that of the reference system in the buffer hybrid region
 $\{\vect r \,:\, \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$ that is interacting with
@@
 condition is satisfied by only using the thermodynamic force,
-so one cannot expect the same benefit in other systems.
+so one cannot expect the same benefit in other systems than SPC/E water.
 
@@
 thermodynamic force~\eqref{eqn:tfi} coupled with the iterative Boltzmann inversion~\eqref{eqn:ibi}
-is effective in correcting the density profile $g_\HY(\vect r)$ and
+is effective in correcting the density profile $\rho_\HY(\vect r)$ and
 RDF $g_\HY(r)$ simultaneously~\cite{wang2012adaptive}.
@@
 theoretical prove behind this phenomenon, and one cannot expect the same
-benefit for other systems.
+benefit for other systems than SPC/E water.
 
@@
 molecule that leaves the coarse-grained region and  enters the atomistic region. An important conclusion
-form Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
+from Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
 holds automatically when the thermodynamic force is applied so that the atomistic
@@
 However, under this framework one has little knowledge regarding the quantities
-that are \recheck{beyond} ensemble averages.
+that are \recheck{beyond equilibrium} ensemble averages.
 For example, the non-equilibrium response of the system
@@
 \end{align}
-The free energy of the full atomistic reference system is showed in
+The free energy of the full atomistic reference system is shown in
 Fig.~\ref{fig:ala}~(b), which clearly presents the metastability in the
@@
 then
-the original time-dependent probability density define on the phase
+the original time-dependent probability density defined on the phase
 space ($p_t(\vect x)$) is approximated by a temporal discrete probability $\vect p_{k\tau}$ defined on the finite-state space.
@@
   The statistical uncertainty of estimating the longest non-trivial time-scale $t_2$ is higher than
-  the shorter time-scales. One possible reason is that
-  the transitions $\{\confa \} \leftrightarrow \{\confc,\confd\}$ are less frequently sampled in
-  a MD simulation than other transition events, owing to the longer implied time-scale. Moreover, the
-  states $\confc$ and $\confd$ are less frequently visited, so the estimate of the  equilibrium probabilities of these
-  states are of lower accuracy, which also introduces larger statistical uncertainty
-  in estimating the implied time-scales of the transitions related to these states.
-  The accuracy may be improved by the enhanced sampling techniques~\cite{rosta2014free}, however, this
-  issue is out of the scope of the current paper.}
+  those of the shorter time-scales, because
+  the transition $\{\confa \} \leftrightarrow \{\confc,\confd\}$ is less frequently sampled in
+  an MD simulation than other transition events corresponding to shorter time-scales.
+  Moreover, the fact that the equilibrium probability of being in states $\confc$ and $\confd$ is
+  much less than that of being in state $\{\confa \}$ also leads to low frequency of the transition.
+  % (This can be easily seen by, e.g., considering a simplified 2-state reversible Markov model).
+  % Moreover, the
+  % states $\confc$ and $\confd$ are less frequently visited, so the estimate of the  equilibrium probabilities of these
+  % states are of lower accuracy, which also introduces larger statistical uncertainty
+  % in estimating the implied time-scales of the transitions related to these states.
+  The accuracy of estimating the 
+  non-trivial time-scales may be improved by longer MD simulations, 
+  or by deliberately choosing the initial states for MD runs~\cite{kohlhoff2014cloud}.}
 Although calculated from the
 equilibrium MD simulations, it should be noted that the leading time-scales and the
-corresponding eigenvectors are not the equilibrium properties, because
+corresponding eigenvectors are not equilibrium properties, because
 the transition probabilities (elements of the transition matrix) are actually

### 2015-02-25 writeDown/pub.epj/reply/reply.tex
add reply

\documentclass{article}

\addtolength{\textwidth}{2.5cm}
\addtolength{\hoffset}{-.4in}

\usepackage{graphicx}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage{lipsum}

\renewcommand{\baselinestretch}{1.0}
% \setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
% \sloppy

\renewcommand{\arraystretch}{1.2}

\newcommand{\confa}[0]{{\alpha_{\footnotesize\textrm{R}}}}
\newcommand{\confb}[0]{{\textrm{C}7_{\textrm{eq}}}}
\newcommand{\confc}[0]{{\alpha_{\footnotesize\textrm{L}}}}
\newcommand{\confd}[0]{{\textrm{C}7_{\textrm{ax}}}}

\begin{document}

\hfill\begin{tabular}{@{}p{.4\linewidth}@{}}
\multicolumn{1}{@{}c@{}}{} \\
        Han Wang\\
        CAEP Software Center for \\
        High Performance Numerical\\
        Simulation\\
        Huayuan Road 6\\
        Beijing 100088, China\\
        \\
        \today
\end{tabular}
\vskip .1cm
\noindent
\begin{tabular}{@{}p{.45\linewidth}@{}}
\multicolumn{1}{@{}c@{}}{} \\
PD Dr. Luigi Delle Site \\
\\
Freie Universit\"at Berlin \\
Institute for Mathematics\\
Arnimallee 6 \\
14195, Berlin \\
  Germany\\  
\end{tabular}\hfill

\vskip 1cm

\noindent
\textbf{\large Resubmission for manuscript}

\vskip .5cm
\noindent
Dear PD Dr. Luigi Delle Site,\\

On behalf of the co-author, I would like to resubmit our article:
\textit{``Adaptive Resolution Simulation in Equilibrium and Beyond''}
by H.~Wang and A.~Agarwal to the
\textit{European Physical Journal Special Topics}.
We gratefully acknowledge the reviewers for the positive reports, and for
their insight and suggestions, which helped us improving the quality
of the manuscript.  In response to their comments, the major questions raised by the referees are
reported below in detail.

We revised the manuscript respectively and reworked the English.
To help the referees spot the major changes in
the manuscript, we have highlighted them in red.

We hope that the revised manuscript is fit for publication now.

\vskip 1cm

\noindent Best regards,\\
Han Wang

\vskip 1cm
\newpage
\section*{Reply to Referee 1}

\noindent
\textit{For the sake of being a self-contained text, I would like some
elaboration of the claim "energy conservation is not a must for
theoretical analyses on the equilibrium statistical properties". A
statement discussed in properly quoted references, but some words may be
helpful here as well.}\\

\noindent
Following this suggestion, We have added a short comment on page 2, pointing out the result that
the force interpolation AdResS (without energy conservation) achieves very high accuracy in
equilibrium properties, such as the radial distribution function, the three-body correlation
and the chemical potential.\\

\noindent
\textit{"... although the system is in equilibrium, some properties, which are
called dynamical properties, cannot be simply computed from the
equilibrium ensemble averages". This is actually not true; in fact,
within the linear response theory, transport (dynamical) properties are
sampled via equilibrium averages of spontaneous fluctuations, as, by the
way, the authors discuss later.
The sentence should be made more accurate.
}\\

\noindent
The referee is correct, and we have changed the sentence to
``... some properties, which are called dynamical properties,
depend not only on the equilibrium ensemble, but also on the dynamics of the system.''\\

\noindent
Further, a footnote has been added to page 2 to help the readers
understand how the dynamics of system plays a role in the definition
of velocity auto-correlation, which was used as a typical example of the  dynamical properties.
\\

\noindent
\textit{In Eq. 3, the authors describe a potential interpolation scheme which
is different from the one presented in e.g., Ref 21 in this very
manuscript. There is no contradiction in the way the potential
interpolation scheme is presented in the present manuscript, but the
reader may find helpful to learn that there are different
potential-based adaptive resolution schemes. For the sake of brevity,
this discussion could/should be limited to few sentences.}
\\

\noindent
A footnote has been added to page 4, discussing the difference between the potential interpolation
used in this manuscript and that of Ref.21.\\

\noindent
\textit{At the beginning of paragraph 3, the authors write two times that the
"the subsystem/atomistic region is subject to the grand-canonical
ensemble". I think "subject" is not the right word. A (sub)system may
sample the ensemble, not being subject to.
}\\

\noindent
Corrected. We have changed ``subject'' to ``sample''.\\

\noindent
\textit{$\beta$ ( = 1/kT) should be defined E(E.g, after Eq. 9). It is standard
to use the letter $\beta$, but it is customary to define it.}\\

\noindent
The definition has been added under Eq.9.\\

\noindent
\textit{IMPORTANT: In Fig. 5 the discrepancy between all-atomistic and AdResS
schemes increases the longer the time-scale related to an eigenvalue of
the MSM transition matrix is. It is true the agreement between the two
schemes is satisfactory within the error bars, but is this increased
difference for increasing time scale a systematic behaviour or is it
limited to the particular system studied? In either case, why this
happens? Is there a strategy to improve the accuracy of such longer
time-scales in case they are important to be known with high accuracy?
Even though the answers to all these questions are not all known, some
discussion along these lines may be helpful to the reader.}\\

\noindent
The leading time-scale is usually estimated with higher statistical
uncertainty, because the corresponding transition is less frequently
sampled in an MD simulation than other transition events, owing to its longer implied time-scale.
Moreover, the fact that the probability of being in states $\{\confc,\confd\}$ is
much less that that of being in state $\{\confa \}$ also leads to rare transition.
This can be seen by,
e.g., considering a simplified 2-state (saying $A$ and $B$) reversible Markov model:
if $p(A) \gg p(B)$, by $ p(B\vert A) p(A) = p(A\vert B) p(B) $, we have $p(B\vert A) \ll p(B\vert A) \leq 1$, which indicates that the 
transition from $A$ to $B$ is rare.\\

\noindent
Longer MD simulations will improve the accuracy.  Deliberately choosing
initial states for MD runs also helped in recovering leading
time-scales that are even longer than one single MD simulation, see,
e.g., Kohlhoff et. al. Nat. Chem. 1, 15--21, 2014.  Discussion along
these lines have been added to page 16.

\section*{Reply to Referee 2}

\noindent
\textit{In the beginning of the paper (page 3) the paper reads ``AdResS
requires all interactions being treated by the cutoff method''
find the statement a bit vague. It is not clear if this is a specific
cut-off method that is used in AdResS, and in that case should be
defined or a reference should be added, or is just applying a general
cutoff, and in that case the sentence should be slightly modified to
something along the lines of ``a cut-off has to be applied''.}\\

\noindent
The cut-off method is the same as the general cut-off method  used in normal MD simulations.
The electrostatic interactions are treated by the Reaction-Field method, so they are also cut-off.
The footnote 2 on page 3 has been revised, and a new footnote has been added on page 3.

\end{document}

### 2015-02-25 writeDown/pub.epj/paper.tex
merge with Animeshs revise.

@@
   \caption{A schematic plot of an AdResS simulation.
-In side the red circle is the atomistic region.
+Inside the red circle is the atomistic region.
 Between the red and blue circles is the hybrid region.
@@
 A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
-The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
+AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
 to denote the resolution of the molecule at position $\vect r$.
@@
 well defined in the atomistic and coarse-grained regions by the corresponding models.
-To setup an AdResS simulation, one only needs to define the
+To set up an AdResS simulation, one only needs to define the
 interactions in the hybrid region. There are in general two
@@
 the momentum and energy are conserved, neither of the AdResS systems conserves
-both laws. The breaking of these mechanics conservations has substantial influence on the thermodynamic
+both laws. The violation of these mechanical conservation laws has substantial influence on the thermodynamic
 properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
@@
 Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
-force exerts on one molecule is the sum of all pairwise forces:
+force exerted on one molecule is the sum of all pairwise forces:
 \begin{align}
@@
 and contains the same number of molecules.
-If the configuration of the atomistic region in the AdResS 
-is the same as that of the corresponding subregion in the atomistic reference, then
-the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
+If the configuration of the atomistic region in AdResS 
+is same as that of the corresponding subregion in the atomistic reference, then
+AdResS is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
 A well-known conclusion of the standard statistical mechanics is that
@@
 for example, those of the atomistic region are 
-$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
+$N_\AT$, $V_\AT$ and $T_\AT$ and those of the hybrid and coarse-grained regions
 are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
@@
 \end{align}
-where the thermodynamic forces is a one-body force defined over space,
+where the thermodynamic force is a one-body force defined over space,
 i.e.~$\vect F^\thf_i = \vect F^\thf(\vect r_\moleidxone)$ and $\vect F^{\thf, V}_\moleidxone = \vect F^{\thf,V}(\vect r_\moleidxone)$,
@@
 atomistic and coarse-grained regions are constants, so the thermodynamic force
-is updated only in the hybrid region. When the hybrid density is flat, the thermodynamic
+is updated only in the hybrid region. When the density in hybrid region is flat, the thermodynamic
 force converges. An important consequence is that
@@
 interaction~\cite{heyes2010thermodynamic}.
-In Ref.~\cite{wang2013grand}, the authors instead tested with
+In Ref.~\cite{wang2013grand}, the authors instead tested 
 Weeks-Chandler-Andersen (WCA) potential~\cite{weeks1971role} as the
-coarse-grained model, which is a short-ranged and pure repulsive
+coarse-grained potential, which is a short-ranged and pure repulsive
 interaction.  For an SPC/E water system, the cut-off radius of WCA potential
-can be 2.4 time smaller than the cut-off radius used in the atomistic
+can be 2.4 times smaller than the cut-off radius used in the atomistic
 region. Since the computational cost of cut-off scheme is of order $\mo(r_c^3)$,
@@
 a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
-The rest of the system is treated coarse-grainly by the WCA interaction.
+The rest of the system is coarse-grained by the WCA interaction.
 The dynamical region  is
 also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
-It has been proved that the conformational dynamics of alanine dipeptide is not sensitive to the size of
+It has been proven that the conformational dynamics of alanine dipeptide is not sensitive to the size of
 the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
@@
 Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
-are cut-off at 1.0~nm.
+are treated using cut-off scheme. The cut-off used in both the cases is 1.0~nm.
 
@@
 with a satisfactory agreement.
-Although these positive numerically evidences cannot answer the open questions
+Although these positive numerical evidences can neither answer the open questions
 on the reason behind the high accuracy, nor the error estimates of the dynamical properties,
 they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
-and suggests a direction for theoretical investigations.
+and suggest a direction for theoretical investigations.
 
@@
 Owing to the fact that the coarse-grained interactions are usually ``softer''
-than the atomistic interactions, one way of further boost the performance is
+than the atomistic interactions, one way to further boost the performance is
 to integrate the coarse-grained molecules with larger time-steps.

### 2015-04-23 writeDown/pub.epj/paper.tex
rm color text

@@
 rather than directly on the mechanical conservation laws.
-\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
+{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
 very high accuracy in equilibrium properties, such as the radial distribution function, the three-body correlation and the chemical potential~\cite{wang2013grand}.}
@@
 some properties, which are called dynamical properties,
-\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
+{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
 % cannot be simply computed from the equilibrium ensemble averages.
@@
 A typical example is the velocity auto-correlation\footnote{
-  \recheck{
+  {
   The velocity auto-correlation
@@
 all interactions\footnote{The long-range electrostatic interactions
-  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
+  are also treated by the cut-off method. {It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
   to calculate the electrostatic interactions.}
 } being treated
-by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
+by the cut-off method\footnote{{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
 the hybrid region being at least one cut-off radius (denoted by $r_c$).
@@
 \footnote{
-\recheck{
+{
   It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
@@
 
-% \recheck{Remark, add the remark of inversed weighting function}
+% {Remark, add the remark of inversed weighting function}
 % \vskip .2cm
@@
 when the reference system approximates the thermodynamic limit, the subsystem
-\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
-if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
+{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
+if the atomistic region of AdResS also {samples} the grand-canonical ensemble
 in the same thermodynamic limit. The theoretical framework presented in this section works for
@@
 % Here the corresponding atomistic region in the reference sys
-% \recheck{comments on the ``atomistic region'' of the reference system}
+% {comments on the ``atomistic region'' of the reference system}
 \begin{figure}
@@
 normalizing the probability density, $\mh^\AT$ is the \emph{atomistic}
-Hamiltonian, \recheck{and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
+Hamiltonian, {and $\beta$ denotes the inverse temperature $1/(k_BT)$.}
 % defined in the the subregion of the reference system that
@@
 However, under this framework one has little knowledge regarding the quantities
-that are \recheck{beyond equilibrium} ensemble averages.
+that are {beyond equilibrium} ensemble averages.
 For example, the non-equilibrium response of the system
@@
 
-% \recheck{the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
+% {the difficulty of Langevin thermostat: destroy dynamics. Test local thermostating~\cite{wang2014exploring}
 % }
@@
 those of the full atomistic reference.
-\recheck{
+{
   The statistical uncertainty of estimating the longest non-trivial time-scale $t_2$ is higher than
@@
 the transition probabilities (elements of the transition matrix) are actually
-auto-correlation functions of the characteristic functions that are not \recheck{purely} equilibrium ensemble averages.
+auto-correlation functions of the characteristic functions that are not {purely} equilibrium ensemble averages.
 

### 2015-06-15 writeDown/pub.epj/comment.klein.reply/main.tex
add reply to Klein

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for The European Physical Journal Special Topics
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[epjST]{svjour}
%
\usepackage{graphics}
\usepackage{color, colortbl}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{tabularx}

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mh}[0]{\mathcal {H}}
\newcommand{\dist}[0]{\textrm {dist}}
\newcommand{\AT}[0]{\textrm{AT}}
\newcommand{\HY}[0]{\textrm{HY}}
\newcommand{\CG}[0]{\textrm{CG}}
\newcommand{\EX}[0]{\textrm{EX}}
\newcommand{\moleidxone}[0]{i}
\newcommand{\moleidxtwo}[0]{j}
\newcommand{\atomidxone}[0]{\alpha}
\newcommand{\atomidxtwo}[0]{\beta}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\rep}{{\textrm{rep}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\exc}{{\textrm{extra}}}
\newcommand{\equi}{{\textrm{eq}}}

\newcommand{\confa}[0]{{\alpha_{\textrm{R}}}}
\newcommand{\confb}[0]{{\textrm{C}7_{\textrm{eq}}}}
\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}
\newcommand{\confd}[0]{{\textrm{C}7_{\textrm{ax}}}}

% \usepackage{amsfonts}
% \newcommand{\tickYes}{\checkmark}
% \usepackage{pifont}
% \newcommand{\tickNo}{\hspace{1pt}\ding{55}}
% \definecolor{MyGray}{gray}{0.85}

%
\begin{document}
%
\title{Reply to comment by R.~Klein on ``Adaptive Resolution Simulation in Equilibrium and Beyond''}
\author{Han Wang\inst{1}\fnmsep\thanks{\email{wang\_han@iapcm.ac.cn}}, Animesh Agarwal\inst{2}}
%
\institute{CAEP Software Center for High Performance Numerical Simulation, Beijing, China
  \and Institut f\"ur Mathematik, Freie Universit\"at Berlin, Berlin, Germany}
%
% \abstract{
%   We reply comments~\cite{klein2015comment}
%   on our recent paper~\cite{wang2015adaptive}.
% } %end of abstract
%
\maketitle
%

We would like to thank R.~Klein who provided valuable comments~\cite{klein2015comment}
on our recent paper~\cite{wang2015adaptive}.
The questions raised therein will be replied in the following.

\paragraph{Particles in the hybrid region}
In the AdResS Scheme, the minimum thickness of the hybrid region
should be $r_c$ (cut-off radius) if the traditional weighting function
(i.e.~Eq.1 in \cite{wang2015adaptive}) is used, while it should be at least
$2r_c$ if a buffer region  is added to the hybrid
region (i.e.~Eq.8 in the same reference).
The average molecular spacing of liquid water under ambient
condition is about 0.3~nm. Therefore, if one take 1.2~nm as the cut-off
radius, the thickness is 4 and 8 times the
the average molecular spacing for traditional and buffered hybrid region, respectively.

We assume the interactions between particles are pairwise, and denote
the energy contribution of one particle pair by $u(r)$, with $r$ being the distance
between the paticles. Cutting-off this interaction means that it is assumed to vanish
if the distance between the paticles is larger than the cut-off radius $r_c$.
``The correlation between the atomistic and the coarse-grained
regions is negligible'' means that the
degrees of freedomes (positions and velocities) of two paticles
in the atomistic and the coarse-grained regions, respectively, are almost un-correlated.

It is true that by intrducing the adaptive resolution, the system is not homogeneous
and isotropic anymore. Therefore, strictly speaking the definition
of RDF and 3-body correlation is problematic. However, if the configuration
of the coarse-grained and the
hybrid regions are designed with high accuracy, one can approximately
treat the system as homogeneous and isotropic, and the RDF and 3-body correlation
are well-defined for (at least) the center-of-mass configuration of water system.
On the other hand, if the coarse-grained or hybrid
configuration deviates from the full-atomistic reference,
one can anyway computes the RDF,
which is the averged structure around a particle, and contains information on
the difference to the
full-atomistic reference (probably with positive-negative cancellation).
In practice,
the deviating RDFs is to improve the accuracy of AdResS, and a
satisfactory accuracy of RDF and 3-body correlation is achieved by
using a fully converged RDF correction force in
AdResS~\cite{wang2012adaptive,wang2013grand}.

\paragraph{The thermodynamic force}
The thermodynamic force in the atomistic and the coarse-grained
regions are force to vanish, that means if a zero thermodynamic force
is used initially, only the value in the hybrid region is updated
iterativly. In order to calculate the density,
take the pure TIP3P water system in Ref~\cite{wang2015adaptive}
for example, we did the following:
\begin{enumerate}
\item The hybrid region was divided into bins of width 0.01~nm in the
  direction of resolution changing.
\item The number of molecules (center-of-mass position) falling in
  each bin was counted and averged to calculate a density. Each density data point
  has a statistical uncertainty of roughly 8\%.
  The productive trajectory for the computation was 200~ps long
  and the molecular positions were saved every 0.2~ps.
\item The resulting density profile was still oscillatory,
  so we smooth it by fitting the density
  to a  spline with a grid spacing of 0.4~nm.
  The spline was calculated by software VOTCA~\cite{ruehle2009versatile}.
\item This smoothed density was used
  by the iterative algorithm (Eq.~21 in Ref.~\cite{wang2015adaptive}),
  % that computes the
  and the thermodynamic force converges in 10 iterations.
\end{enumerate}

\paragraph{Particular properties of the SPC/E water system}
Actually we used the AdResS simulation to compute the chemical
potential for various liquids and mixtures in
Ref.~\cite{agarwal2014chemical}.  In the simulations, only the
thermodynamic force was calculated and applied to correct the density
in the hybrid region.  The chemical potential were computed with
satisfactory accuracy.  Moreover, although no RDF correction was used
and the system was simulated under extreme technical conditions (very
small atomistic and coarse-grained regions and a relatively large
hybrid region), the RDFs were be reproduced with satisfactory
agreement to full-atomistic reference (see e.g.~Fig.3 of Ref.~\cite{agarwal2014chemical}).

\paragraph{Structure of the hybrid zone}
The major difference between a phase coexisting system and an AdResS
system is that the former satisfies both the momentum and energy
conservations, while the later can satisfy only one of the two.
It would be very intersting to establish the analogue between
the phase coexisting and the AdResS system, however one must pay attention
to this difference that may play a significant role in the final conclusions.

\bibliography{ref}{}
\bibliographystyle{unsrt}

% \begin{thebibliography}{}
% % and use \bibitem to create references.
% \bibitem{RefJ}
% % Format for Journal Reference
% Author, Journal \textbf{Volume}, (year) page numbers
% % Format for books
% \bibitem{RefB}
% Author, \textit{Book title} (Publisher, place year) page numbers
% % etc
% \end{thebibliography}

\end{document}

% end of file template.tex

### 2015-06-15 writeDown/pub.epj/comment.klein.reply/main.tex
add Animesh's revise

@@
 
-We would like to thank R.~Klein who provided valuable comments~\cite{klein2015comment}
+We would like to thank R.~Klein for providing valuable comments~\cite{klein2015comment}
 on our recent paper~\cite{wang2015adaptive}. 
@@
 The average molecular spacing of liquid water under ambient
-condition is about 0.3~nm. Therefore, if one take 1.2~nm as the cut-off
+condition is about 0.3~nm. Therefore, if one takes 1.2~nm as the cut-off
 radius, the thickness is 4 and 8 times the
@@
 
-We assume the interactions between particles are pairwise, and denote
+We assume that the interactions between particles are pairwise, and denote
 the energy contribution of one particle pair by $u(r)$, with $r$ being the distance
-between the paticles. Cutting-off this interaction means that it is assumed to vanish
-if the distance between the paticles is larger than the cut-off radius $r_c$.
+between the particles. Cuting-off this interaction means that it is assumed to vanish
+if the distance between the particles is larger than the cut-off radius $r_c$.
 ``The correlation between the atomistic and the coarse-grained
 regions is negligible'' means that the
-degrees of freedomes (positions and velocities) of two paticles
+degrees of freedom (positions and velocities) of two particles
 in the atomistic and the coarse-grained regions, respectively, are almost un-correlated.
 
-It is true that by intrducing the adaptive resolution, the system is not homogeneous
-and isotropic anymore. Therefore, strictly speaking the definition
-of RDF and 3-body correlation is problematic. However, if the configuration
+It is true that by introducing the adaptive resolution, the system is not homogeneous
+and isotropic anymore. Therefore, strictly speaking the standard definition
+of RDF's and 3-body correlation functions is problematic. However, if the configuration
 of the coarse-grained and the
@@
 configuration deviates from the full-atomistic reference,
-one can anyway computes the RDF,
-which is the averged structure around a particle, and contains information on
+one can anyway compute the RDF,
+which is the averaged structure around a particle, and contains information on
 the difference to the
 full-atomistic reference (probably with positive-negative cancellation).
-In practice,
-the deviating RDFs is to improve the accuracy of AdResS, and a
+\redc{In practice,
+the deviating RDFs is to improve the accuracy of AdResS,} and a
 satisfactory accuracy of RDF and 3-body correlation is achieved by
@@
 The thermodynamic force in the atomistic and the coarse-grained
-regions are force to vanish, that means if a zero thermodynamic force
-is used initially, only the value in the hybrid region is updated
-iterativly. In order to calculate the density,
+regions are forced to vanish, that means if a zero thermodynamic force
+is used initially, then only the value in the hybrid region is updated
+iteratively. In order to calculate the density,
 take the pure TIP3P water system in Ref~\cite{wang2015adaptive}
@@
 \item The hybrid region was divided into bins of width 0.01~nm in the
-  direction of resolution changing.
-\item The number of molecules (center-of-mass position) falling in
-  each bin was counted and averged to calculate a density. Each density data point
+  direction of changing resolution.
+\item The number of molecules (center-of-mass position) in
+  each bin was counted and averaged to calculate a density. Each density data point
   has a statistical uncertainty of roughly 8\%.
@@
   to a  spline with a grid spacing of 0.4~nm.
-  The spline was calculated by software VOTCA~\cite{ruehle2009versatile}.
+  The spline was calculated by VOTCA~\cite{ruehle2009versatile} software.
 \item This smoothed density was used
@@
   % that computes the
-  and the thermodynamic force converges in 10 iterations.
+  and the thermodynamic force converged within 10 iterations.
 \end{enumerate}
@@
 \paragraph{Particular properties of the SPC/E water system}
-Actually we used the AdResS simulation to compute the chemical
+Actually we used AdResS to compute the chemical
 potential for various liquids and mixtures in
-Ref.~\cite{agarwal2014chemical}.  In the simulations, only the
+Ref.~\cite{agarwal2014chemical}. In the simulations, only 
 thermodynamic force was calculated and applied to correct the density
-in the hybrid region.  The chemical potential were computed with
+in the hybrid region. The chemical potential was computed with
 satisfactory accuracy.  Moreover, although no RDF correction was used
@@
 small atomistic and coarse-grained regions and a relatively large
-hybrid region), the RDFs were be reproduced with satisfactory
+hybrid region), the RDFs were reproduced with satisfactory
 agreement to full-atomistic reference (see e.g.~Fig.3 of Ref.~\cite{agarwal2014chemical}).
@@
 conservations, while the later can satisfy only one of the two.
-It would be very intersting to establish the analogue between
-the phase coexisting and the AdResS system, however one must pay attention
+It would be very interesting to establish an analogue between
+both the systems, however one must pay attention
 to this difference that may play a significant role in the final conclusions.

### 2015-06-15 writeDown/pub.epj/comment.klein.reply/main.tex
revise

@@
 the energy contribution of one particle pair by $u(r)$, with $r$ being the distance
-between the particles. Cuting-off this interaction means that it is assumed to vanish
+between the particles. Cutting-off this interaction means that it is assumed to vanish
 if the distance between the particles is larger than the cut-off radius $r_c$.
@@
 It is true that by introducing the adaptive resolution, the system is not homogeneous
-and isotropic anymore. Therefore, strictly speaking the standard definition
+and isotropic anymore. Therefore, strictly speaking, the standard definition
 of RDF's and 3-body correlation functions is problematic. However, if the configuration
@@
 are well-defined for (at least) the center-of-mass configuration of water system.
-On the other hand, if the coarse-grained or hybrid
+On the other hand, if the hybrid
 configuration deviates from the full-atomistic reference,
 one can anyway compute the RDF,
-which is the averaged structure around a particle, and contains information on
+which is the averaged anisotropic structure around a particle, and contains information on
 the difference to the
 full-atomistic reference (probably with positive-negative cancellation).
-\redc{In practice,
-the deviating RDFs is to improve the accuracy of AdResS,} and a
-satisfactory accuracy of RDF and 3-body correlation is achieved by
-using a fully converged RDF correction force in
-AdResS~\cite{wang2012adaptive,wang2013grand}.
+In practice,
+it has been shown that this information is sufficient for computing
+a RDF correlation that drives the system
+to the correct RDF in the hybrid region~\cite{wang2012adaptive,wang2013grand}.
+
+% it has been shown that  
+% the RDF correlation can be effectively computed by using
+% this averaged RDF.
 
@@
 \paragraph{Structure of the hybrid zone}
-The major difference between a phase coexisting system and an AdResS
-system is that the former satisfies both the momentum and energy
-conservations, while the later can satisfy only one of the two.
 It would be very interesting to establish an analogue between
-both the systems, however one must pay attention
-to this difference that may play a significant role in the final conclusions.
+a phase coexisting system
+and an AdResS system.
+We would like to note that the major difference between them
+is that the former satisfies both the momentum and energy
+conservations, while the latter can satisfy only one of the two.
+This difference may play a significant role in deriving the final conclusions.
 
